### 2022-05-18 Manuscript/inter_spike_manuscript.tex
added manuscript

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}    % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Nonlinear Dynamics}
%
\begin{document}

\title{Recurrence spike spectra}

\titlerunning{Recurrence spike spectra}        % if too long for running head

\author{K. Hauke Kraemer \and
		Frank Hellmann \and
        J\"urgen Kurths \and 
        Norbert Marwan
}

\institute{K. Hauke Kraemer \and J\"urgen Kurths \and Norbert Marwan \and Frank Hellmann \at Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, 
Germany \email{hkraemer@pik-potsdam.de}\and
           K. Hauke Kraemer \and J\"urgen Kurths \at Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany \and
		   Norbert Marwan \at Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany \and
		   J\"urgen Kurths \at Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms spike-train-like signals into their frequency domain. This method 
clearly shows the apparent cycles in the data and overcomes the problems when using the obvious idea of Fourier-transforming it. We invent this instructive approach with the 
idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is simple to compute, robust to noise and is able to detect bifurcations 
inducing regular-regular, regular-chaos as well as chaos-chaos transitions.

\keywords{Bifurcations \and Recurrence Analysis \and Decomposition \and Frequency Analysis}
\PACS{05.45.Tp, 05.90.+m, 89.90.+n, 02.70.Uu, 05.10.Ln, 05.45.-a, 05.45.Ac}
\end{abstract}

\section{Introduction}\label{sec_tau_rr_intro}

Recurrence Plots (RPs) provide a vivid representation of complex dynamics stemming from potentially high dimensional systems, Eq.~\eqref{eq_rp_definition}. 
\begin{equation}\label{eq_rp_definition}
R_{i,j}(\varepsilon) = \Theta\left(\varepsilon - D_{i,j}\right) 
= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N].
\end{equation}
The simple idea to 
track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, but also for its 
quantification, using certain structures in the RP, such as diagonal or vertical lines \cite{marwan2007}.

Some of these recurrence quantification measures, the entropy of diagonal lines and the entropy of 
recurrence times, can be related to the Kolmogorov-Sinai entropy \cite{march2005,baptista2010}. However, these quantifiers have a free parameter, the minimal considered line length, and 
are usually biased, due to the finite size of the RP and thickened diagonal lines, which needs to be corrected \cite{Kraemer2019}. Moreover, the mentioned statistics cannot account for 
changing regular (non-chaotic) dynamics, such as period-doubling bifurcations.
A rather simple idea is to look at the $\tau$-recurrence rate of the RP ($\tau$-RR, Eq.~\ref{eq_tau_rr}) \cite{marwan2002pla,Zbilut2008}.
This is the density of recurrence points along the diagonals of the recurrence matrix, as a function of the distance $\tau$ (sampling units) to the main diagonal:
\begin{equation}\label{eq_tau_rr}
\tau\text{-RR}(\varepsilon) = RR(\tau, \varepsilon) = \frac{1}{N-\tau} \sum_{i=1}^{N-\tau	} R_{i,i+\tau}.
\end{equation}
$\tau$-RR serves as an estimator for the probability that the system recurs after time $\tau \Delta t$, with $\Delta t$ being the sampling time of the trajectory 
$\vec{x}_i = \vec{x}(\Delta t \cdot i),\, i=1,\ldots,N$. 
\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
``generalized'' powerspectrum can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 
\begin{equation}
\overline{D}(\tau) = \frac{1}{N-\tau}\sum_{i=1}^{N-\tau} D_{i, i+\tau}
\end{equation}
can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived 
powerspectrum, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D), instead 
of $C(\tau)$ (Fig.~\ref{fig_tau_rr_spectrum_example}C): There are no assumptions for stationarity or sampling, when constructing a RP.
Furthermore, the correlation structures of higher dimensional spaces can be resolved in the recurrence-derived Fourier-spectrum.\\

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_spectrum_example}
 \caption{Schematic illustration of a $\tau$-recurrence rate based spectrum. \textbf{A} $x$-component time series of the Lorenz63-System (Eq.~\eqref{eq_model_Lorenz63}) and 
 \textbf{B} its corresponding Fourier power spectrum. 
 \textbf{C} Reconstructed state space portrait from the time series shown in \textbf{A} using PECUZAL time-delay embedding \cite{Kraemer2021}. 
 \textbf{D} Subset of the recurrence plot and the corresponding $\tau$-recurrence rate obtained from the state space trajectory in \textbf{C}. The shaded interval in the time series in \textbf{A} corresponds to the shown subset. 
 \textbf{E} Fourier Power spectrum obtained from the $\tau$-recurrence (subset shown in panel \textbf{D}) \cite{Zbilut2008}.
 }\label{fig_tau_rr_spectrum_example}
\end{figure}

However, there is a drawback to this approach. Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for 
map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g. \cite{Schild1982,Cordoba1989}, see 
Fig.~\ref{fig_tau_rr_spectrum_example}D). Thus, it is not intuitive how to extract meaningful information about dominant frequencies of the systems' state space trajectory.

For clarification, consider the signal we would like to analyze 
(e.g. the $\tau$-RR of a system) to be a Dirac comb (DC) with inter-spike period $T_\text{is}$: 
\begin{equation}
\text{DC}_{\text{is}}(t) = \sum_{k=-\infty}^{\infty} \delta(t-kT_\text{is}),
\label{eq_dirac_comb}
\end{equation}
i.e., a series of Dirac delta functions for a period $T_\text{is}$. There is only one single period -- $T_\text{is}$ -- in this signal (Fig.~\ref{fig_tau_rr_dirac_comb}A, D), so 
in principle we would strive for a single peak in the frequency domain of this signal at a frequency $f=1/T_\text{is}$. Surprisingly the Fourier spectrum does not meet this expectation 
and instead of a single frequency, there are exceptionally many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is, because the Fourier components add constructively 
for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.

\begin{figure}[h]
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_dirac_comb}
 \caption{The transformation of a Dirac comb (series of Dirac delta functions) with a single inter-spike period $T_{\text{is}}=100$ ($\widehat{=}f=0.01$) 
 into the frequency domain. 
 \textbf{A} Dirac Comb (DC) with equal amplitudes and
 \textbf{B} its FFT-based powerspectrum.
 \textbf{C} Proposed inter spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
 \textbf{D} DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in \textbf{A}, and
 \textbf{E} its FFT-based powerspectrum. 
 \textbf{F} Proposed inter spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$).  
}
\label{fig_tau_rr_dirac_comb}
\end{figure}

In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter spike spectrum} does not show resonance 
behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
FT. In Section \ref{sec_tau_rr_application} we exemplify its use when transforming the $\tau$-RR of a system under study. In this case, the inter spike spectrum can unravel 
characteristic time scales of high dimensional systems, which is not possible when using a FT.

\section{Method}\label{sec_tau_rr_method}

The idea is as simple as it is obvious. The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal -- 
is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform with length $N$ and 
$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional vector $\bf{s}$. 
First, $N$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,N]$. Second, in order to account for possible phase shifts of 
these basis functions occurring 
in $\bf{s}$, each of these $N$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of $M = \sum_{i=1}^{N}i$ 
basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure)
\begin{align}
\bfX_{i,j} &= \sum_{k=0}^N\delta\left(j-1-kT(i)-i+T(i) \right),\\
T(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
\label{eq_basis_matrix}
\end{align}
Due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, 
$\bfX$ is not linear independent anymore. Thus, an under-determined linear system
\begin{equation}
\bf{X}^T\bf{\beta}=\bf{s}
\label{eq_linear_system}
\end{equation}  
has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms, which can solve this problem, we are 
particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). Therefore, we here choose the \textit{least absolute shrinkage and selection operator} 
(LASSO regression) \cite{Tibshirani1996}. Finally, we group loadings which correspond to basis functions having the same period $T_\text{is}$ into $\bf{\beta}_f$ and obtain the 
\textit{inter spike spectrum} by simply plotting $\bf{\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$ (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).

\begin{figure}
  \begin{minipage}[b]{0.3\textwidth}
    \vspace{0pt}
    \includegraphics[width=0.95\textwidth]{./figures/fig_tau_rr_basis_functions}
  \end{minipage}\hfill
  \begin{minipage}[b]{0.7\textwidth}
    \vspace{0pt}
    \caption{Example for a set of basis functions for an input signal of length $N=5$, aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
  \end{minipage}
\end{figure}

\section{Application}\label{sec_tau_rr_application}

We exemplify the use of the inter spike spectrum in combination with the $\tau$-RR as outlined in 
Section \ref{sec_tau_rr_intro} on several interesting research questions. The procedure is the following:
\begin{itemize}[noitemsep]
\item[(1)] Compute a RP of the trajectory of the system, Eq.~\eqref{eq_rp_definition}. 
\item[(2)] Compute the $\tau$-RR of that RP, Eq.~\eqref{eq_tau_rr}.
\item[(3)] Transform the $\tau$-RR into the proposed inter spike spectrum, see Section \ref{sec_tau_rr_method}.
\end{itemize}

\subsection{Period estimation for different dynamics in the R\"ossler system}
First, we consider the R\"ossler system (Eq.~\eqref{eq_model_roessler} in Appendix \ref{sec_models_roessler}) 
in three different dynamical setups. We use the proposed inter spike spectrum to
identify the type of dynamics.
We set the parameters $b=2$, $c=4$ and analyze period-2 limit cycle dynamics ($a=0.36$, Fig.~\ref{fig_tau_rr_example_roessler}A, D, G, J), 
period-3 limit cycle dynamics ($a=0.41$, Fig.~\ref{fig_tau_rr_example_roessler}B, E, H, K) and chaotic dynamics ($a=0.428$, Fig.~\ref{fig_tau_rr_example_roessler}C, F, I, L).

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler}
 \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
 Trajectory of the system in a \textbf{A} period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
 \textbf{C} in a chaotic regime (parameter $a=0.428$). 
 \textbf{D, E, F} The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for D \& E and 5\% for F. 
  \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a regularization threshold corresponding to 
  $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
 }
\label{fig_tau_rr_example_roessler}
\end{figure}

The inter spike spectra unravel the specific dynamics, which are also apparent in the state space portraits (Fig.~\ref{fig_tau_rr_example_roessler}A, B, C) and in the 
$\tau$-RRs (Fig.~\ref{fig_tau_rr_example_roessler}G, H, I). The proposed idea is also 
robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. While the peak shape does 
change in the presence of noise, its position does not, and this is what the inter spike spectrum encrypts after all.

\subsection{Bifurcations in the Logistic map}

We consider the Logistic map $x_{n+1}=r\cdot x_n \left( 1-x_n \right)$ for changing control parameter $r$. We vary $r$ from $r=3.4$ to $r=4$ in steps of $0.001$. For 
each setting of $r$ 
\begin{itemize}[noitemsep]
\item[(1)] a time series of length $N=201$ is computed with a random initial condition $u_0 \in [0,\ 1]$, neglecting the first $1,000$ samples as transients,
\item[(2)] $100$ iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000} are computed,
\item[(3)] the time series and its iAAFT surrogates are embedded in a 2-dimensional state space using a time delay of unity,
\item[(4)] from the 2-dimensional trajectories RPs, Eq.~\eqref{eq_rp_definition}, are computed under a threshold $\varepsilon=0.05$,
\item[(5)] $\tau$-RR, Eq.~\eqref{eq_tau_rr}, is computed from the RP of the signal and from the RPs of the surrogates,
\item[(6)] inter spike spectra are obtained from $\tau$-RR of the signal and from the $\tau$-RRs of the surrogates, see Section \ref{sec_tau_rr_method}, and finally,
\item[(7)] from the distribution of the surrogate inter spike spectra the $95^\text{th}$ percentile is computed. The peaks of the inter spike spectrum of the signal which exceed 
this percentile are counted. 
\end{itemize}
In this example, the according null hypothesis is that the data stems from a process which yields the same auto-correlation, hence the same Fourier powerspectrum, and the same 
amplitude distribution. We consider the number of significant peaks in the inter spike spectrum with
respect to the control parameter in order to distinguish the corresponding dynamics (Fig.~\ref{fig_tau_rr_logistic}C).
A correlation with the positive Lyapunov exponent (Fig.~\ref{fig_tau_rr_logistic}A) is discernible 
($\rho_{\text{Pearson}}=0.88$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum.

A less computationally intensive approach is to compute surrogates for the $\tau$-RR analytically, rather than computing a RP and its $\tau$-RR for each iAAFT surrogate of the 
time series. This translates into a null hypothesis 
that the $\tau$-RR and its corresponding inter spike spectrum stems from a RP of a random signal. In this case the probability of finding a black point in the RP can be obtained 
from a binomial distribution with probability parameter $p$ set to the recurrence rate of the RP of the signal. This way $100$ surrogate $\tau$-RRs are computed in step (5). 
The results are similar to the ones obtained from the iAAFT surrogates and nearly as good (Fig.~\ref{fig_tau_rr_logistic}B). The first period doubling at 
$r \approx 3.458$ cannot be detected, while the correlation to the positive Lyapunov exponent is only slightly worse ($\rho_{\text{Pearson}}=0.84$).

The described procedure does work well for map data, because most often the $\tau$-RR for those kind of data reveals a ``spiky enough'' nature. 
On the contrary, highly sampled (flow-) data often yield not as 
spiky $\tau$-RR's and, thus, the number of significant peaks in the inter spike spectrum may not be sensitive enough to detect period-doubling bifurcations. Nevertheless the 
according inter spike spectra is still revealing important information (Fig.~\ref{fig_tau_rr_example_roessler}) and practitioners can design appropriate quantifying statistics based 
on these spectra, which suit the 
research task.

\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_tau_rr_logistic}
 \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. 
 \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR, random surrogates. 
 \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}.
}
\label{fig_tau_rr_logistic}
\end{figure}

\subsection{Evolutionary spike spectrogram of CENOGRID isotope time series}

%To demonstrate XXXXXX we applied it to the recently published CENOzoic Global Reference
%benthic foraminifer carbon and oxygen Isotope Dataset (CENOGRID) \cite{Westerhold2020}. 
%The temperature-dependent fractionation of carbon and oxygen isotopes in benthic foraminifera
%is an important means to reconstruct past global temperatures and environmental conditions.
%Moreover, the Cenozoic is interesting, because it provides an analogue of future greenhouse 
%climate and how and which regime shifts in large-scale atmospheric and ocean circulation 
%can be expected in the future warming climate. The dataset consists of a detrended $\delta^{18}$O and a detrended $\delta^{13}$C isotope record with a total length
%of $N=13,421$ samples and a sampling period of $\Delta t= 5,000 \text{yrs}$ (Figure \ref{fig_time_series_cenogrid} in Appendix \ref{sec_appendix_cenogrid}). Here we made predictions 
%on the $\delta^{13}$C isotope record.
%
%We again utilize the Cenozoic Global Reference benthic foraminifer carbon and oxygen Isotope Dataset (CENOGRID) \cite{Westerhold2020}. The time series 
%have a total length of $N=13,421$ samples and a sampling period of 
%$\Delta t= 5,000 \text{yrs}$. The records and their corresponding RPs are shown in 
%Figure~\ref{fig_tauRR_cenogrid_RPs} together with remarkable climate transitions in the Cenozoic (detrended time series in Fig.~\ref{fig_time_series_cenogrid} in 
%Appendix~\ref{sec_appendix_cenogrid}). Among other things, the large-scale patterns in the RPs shown were used by \textcite{Westerhold2020} to classify major climate 
%states: Hothouse, Warmhouse, Coldhouse and Icehouse. 
%
%\begin{figure}[h!]
% \centering
% \includegraphics[width=\textwidth]{./figures/chapter06_tauRR/fig_tauRR_cenogrid_RPs}
% \caption{\textbf{A} $\delta^{13}$C and \textbf{B} $\delta^{18}$O isotope records and their corresponding RPs (\textbf{C+D}), obtained from the non-embedded time 
% series under a fixed recurrence threshold corresponding to 8\% global RR. These plots were used by \textcite{Westerhold2020} to classify the major climate states 
% Hothouse, Warmhouse, Cold- and Icehouse.
% }
%\label{fig_tauRR_cenogrid_RPs}
%\end{figure}
%
%
%While in Chapter \ref{chapter:MCDTS}, 
%Section \ref{sec_mcdts_cenogrid_prediction} predictions were made for the detrended $\delta^{13}$C record, here the focus is on the analysis of the characteristic time scales 
%in both, the detrended $\delta^{18}$O and the detrended $\delta^{13}$C isotope records. Specifically, we have computed spike powerspectra of the $\tau$-RR windowed over each record. 
%Figures~\ref{fig_tauRR_O18_pecuzal},~\ref{fig_tauRR_C13_pecuzal} show that major features of their linear counterparts, namely ordinary FFT spectrograms (A panels), are also present in 
%these spectrograms. But there is additional information in the spike spectrograms (B panels). Firstly, overall there seem to be less frequencies excited than in the FFT spectrograms, but these 
%excited frequencies are therefore more pronounced. This is especially apparent in the oxygen isotope record spectrogram (Fig.~\ref{fig_tauRR_O18_pecuzal}), in which the obliquity-related time 
%scale (\mytilde 41 kyrs) is very prominent from 17-0 Mio yrs BP in the spike spectrogram (panel B). Our spike spectrograms also support the general conlusion given by \textcite{Westerhold2020} 
%that ``in the Hothouse and Warmhouse climate states, as well as the first Coolhouse phase, eccentricity-related cycles (\mytilde 100 \& \mytilde 405 kyrs) dominate the CENOGRID records, while 
%after the increasing influence of highlatitude cooling and ice growth during the second Coolhouse phase, the obliquity-band response steadily increases after 13.9 Mio yrs BP (middle Miocene 
%climate transition) before dominating climate dynamics by \mytilde 5 Mio yrs BP (late Miocene–early Pliocene)''. The spike spectrograms indicate a strong obliquity influence already from 17 
%Mio yrs BP (the onset of the Miocene Climate optimum). Moreover, in the carbon isotope record based spike spectrogram (Fig.~\ref{fig_tauRR_C13_pecuzal}B) there is a strong influence of the 
%100-kyr-eccentricity cycle in the first Warmhouse phase from \mytilde 61-56 Mio yrs BP, which is not represented in the FFT-based spectrogram (panel A). 
%
%
%\begin{figure}
% \centering
% \includegraphics[width=\textwidth]{./figures/fig_tauRR_O18_pecuzal}
% \caption{Evolutionary spectrograms based on \textbf{A} FFT powerspectra of the detrended $\delta^{18}$O time series and \textbf{B} 
% on the spike powerspectra of the 
% $\tau$-RR of the PECUZAL embedded $\delta^{18}$O record. The spectrograms were computed with a $w = 1,000 (\hat{=}~\text{5-Myr})$ window 
% and a step $ws=1$. We used the 
% embedding computed in Chapter~\ref{chapter:MCDTS} (Section~\ref{sec_mcdts_cenogrid_prediction}, see Table~\ref{tab:cenogrid_embedding}) 
% and a recurrence threshold fixed to 
% 5\% global RR, in order to ensure comparability within the different windows \cite{kraemer2018} (Chapter~\ref{chapter:threshold}). 
% Dashed red horizontal lines indicate major climate transitions according to \textcite{Westerhold2020}.
% }
%\label{fig_tauRR_O18_pecuzal}
%\end{figure}
%
%\begin{figure}
% \centering
% \includegraphics[width=\textwidth]{./figures/fig_tauRR_C13_pecuzal}
% \caption{Same as in Figure \ref{fig_tauRR_O18_pecuzal}, but for the detrended $\delta^{13}$C isotope record.
% }
%\label{fig_tauRR_C13_pecuzal}
%\end{figure}
%
%The shown spike spectrograms in Figs.~\ref{fig_tauRR_O18_pecuzal},~\ref{fig_tauRR_C13_pecuzal} are based on the $\tau$-RR of the respective records, which have been time delay embedded by using 
%the PECUZAL algorithm \cite{Kraemer2021} (Chapter \ref{chapter:unified}). By construction, we would expect different spike spectrograms, when different embeddings are used. This is indeed the case 
%as shown in Figures~\ref{fig_tauRR_O18_mcdts},~\ref{fig_tauRR_C13_mcdts},~\ref{fig_tauRR_O18_ne},~\ref{fig_tauRR_C13_ne} (Appendix \ref{appendix_tauRR_spectrograms}), which also show spike 
%spectrograms, but for an embedding using MCDTS-R-MSE (Chapter~\ref{chapter:MCDTS}, see Table~\ref{tab:cenogrid_embedding}) and for the non-embedded time series. Even though differences are 
%discernible, the mentioned overall conclusion given by \textcite{Westerhold2020} also holds for these cases.

\section{Conclusion}\label{sec_tau_rr_conclusion}

A novel type of powerspectrum, the \textit{inter spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution (we chose LASSO). Since there are 
$M = \sum_{i=1}^{N}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
of the frequency (or period) the inter spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
appearance. The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RR's) into their frequency domain. 
This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, and the inter spike spectrum can reliably reveal the system's dominant frequencies, 
which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
in the $\tau$-RR are not sensitive to noise, the corresponding inter spike spectrum also yields robust results in the presence of noise. We have successfully used the idea 
of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter spike spectra, and thus a null model, 
the number of significant peaks in the inter spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve period-doubling bifurcations.

We could think of a broad range of applications of the proposed idea. The inter spike spectrum itself can serve as a valuable tool for the analysis of any sort of 
spike-train-like data. On the other hand, the inter spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021} show that 
this reconstruction process can be reliably automated and applied to multivariate data as well. This would allow for a ``running window'' approach, in order to detect transitions. 
Due to the mentioned computational constraints of our proposed method, a window size $w\leq 1,000$ would possibly suffice for most data, especially when it is map-like, i.e., not 
highly sampled.

\begin{acknowledgements}
This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9). All computations have been carried out in the Julia language 
and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
 \section*{Conflict of interest}

 The authors declare that they have no conflict of interest.

\clearpage
\appendix
\section{Inter spike spectra for noisy R\"ossler system}

\begin{figure}[h!]
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
 \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise. The appearance of the inter spike spectra 
 in \textbf{J, K, L} and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise noise.
 }
\label{fig_tau_rr_example_roessler_noise}
\end{figure}

\section{Exemplary models}

\subsection{Lorenz system}\label{sec_models_lorenz63}

The classical Lorenz-63 system \cite{lorenz1963} is defined as

\begin{equation}
\begin{array}{rcl}
\dot{x}&=&\sigma(y-x) \\
\dot{y}&=&x(r-z)-y \\
\dot{z}&=&xy - \beta z.
\end{array}
\label{eq_model_Lorenz63}
\end{equation}

\noindent For producing Fig.~\ref{fig_tau_rr_spectrum_example} we set the initial condition to $u_0=[0.0, 10.0, 0.0]$, used a sampling time of $\Delta t=0.01$ and discarded the first 
2,000 points of the integration as transients. The parameters have been set to 
$\sigma=10, \beta=8/3, \rho=28$ and we used a time series consisting of 6,000 samples.

\subsection{R\"ossler system}\label{sec_models_roessler}

The R\"ossler system \cite{roessler1976} is defined as
\begin{align}
\begin{array}{rcl}
\dot{x}&=&-y-z \\
\dot{y}&=&x+ay \\
\dot{z}&=&b+ z(x-c) .
\end{array}
\label{eq_model_roessler}
\end{align}
For producing Figs.~\ref{fig_tau_rr_example_roessler_noise},~\ref{fig_tau_rr_example_roessler} the initial condition for producing panels \textbf{A} \& \textbf{B} was set to $u_0=[.7, -1, 0.4]$ with a sampling time 
of $dt=0.05$ and in case of panel \textbf{C} $u_0=[-0.1242, -2.5415, 0.2772]$ with a sampling time of $dt=0.1$. The first $5,000$ samples were discarded as transients and trajectories of length $N=5,000$ were 
obtained from which we computed the RPs and the corresponding $\tau$-RR's. For the inter spike spectra only the first $1,000$ values of the $\tau$-RR's were considered.

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base

% Non-BibTeX users please use
\bibliographystyle{spbasic} 
\bibliography{inter_spike_bib}

\end{document}
% end of file

### 2022-05-18 Applications/Lorenz Example/comm_Lorenz_example.jl
Lorenz example added

@@ -1,0 +1,43 @@
+using tau_recurrence
+using DelimitedFiles
+using DynamicalSystemsBase
+using DelayEmbeddings
+using RecurrenceAnalysis
+using PyPlot
+using Statistics
+using DSP
+pygui(true)
+
+dt = 0.01
+N = 6000
+transients = 2000
+lo = Systems.lorenz()
+data = trajectory(lo, dt*N; dt = dt, Ttr = transients*dt)
+data = regularize(data)
+
+# compute RP and τ_rr
+ε = 0.08
+
+Y, tau_pec, _, _, _ = pecuzal_embedding(data[:,1]; τs = 0:50, w = estimate_delay(data[:,1], "mi_min"))
+
+RP = RecurrenceAnalysis.RecurrenceMatrix(Y[1:1000,:], ε; fixedrate = true)
+τ_rr = RecurrenceAnalysis.tau_recurrence(RP)
+τ_rr /= maximum(τ_rr)
+
+Rg = grayscale(RP)
+
+# FT of x and of Y
+perio = DSP.Periodograms.periodogram(data[:,1]; fs = 1/dt)
+perio2 = DSP.Periodograms.periodogram(τ_rr; fs = 1/dt)
+
+
+# save variables and plot everything in Matlab
+writedlm("./application/simple example/tau_rr.csv", τ_rr)
+writedlm("./application/simple example/data.csv", data)
+writedlm("./application/simple example/Y.csv", Y)
+writedlm("./application/simple example/tau_pec.csv", tau_pec)
+writedlm("./application/simple example/RP.csv", Rg)
+writedlm("./application/simple example/perio_freq.csv", perio.freq)
+writedlm("./application/simple example/perio_power.csv", perio.power)
+writedlm("./application/simple example/perio_freq2.csv", perio2.freq)
+writedlm("./application/simple example/perio_power2.csv", perio2.power)

### 2022-05-18 Applications/Lorenz Example/plots.m

@@ -1,0 +1,231 @@
+clear, clc
+
+Y = load("Y.csv");
+tau_rr = load("tau_rr.csv");
+tau_pec = load("tau_pec.csv");
+RP = load("RP.csv");
+perio_power = load("perio_power.csv");
+perio_freq = load("perio_freq.csv");
+perio_power2 = load("perio_power2.csv");
+perio_freq2 = load("perio_freq2.csv");
+data = load("data.csv");
+
+%% Plot periodogram of x-component
+
+periodogram(data(:,1))
+
+%% Plot periodogram of tau-RR
+
+periodogram(tau_rr)
+
+%%
+subset = 1:length(tau_rr);
+
+t = 1:length(tau_rr(subset));
+
+lw = 3;
+fs = 20;
+
+figure('Units','normalized','Position',[.1 .1 .7 .8])
+subplot(3,3,[1,4])
+plot(tau_rr(subset),t, 'LineWidth', lw)
+set(gca,'XDir','reverse');
+set(gca,'LineWidth',2)
+set(gca,'FontSize',fs)
+xlabel("\tau-RR")
+ylabel("time [\Deltat]")
+xlim([0 1])
+yticklabels([])
+grid on
+
+subplot(3,3,[2,3,5,6])
+imagesc(t,t,RP), colormap([0 0 0; 1 1 1])
+title("Recurrence Plot (8% rec.-rate)")
+xticklabels([])
+yticklabels([])
+set(gca,'LineWidth',2)
+set(gca,'FontSize',fs)
+grid on
+
+subplot(3,3,[8,9])
+plot(t,tau_rr(subset), 'LineWidth', lw)
+set(gca,'YDir','reverse');
+set(gca,'LineWidth',2)
+set(gca,'FontSize',fs)
+ylabel("\tau-RR")
+ylim([0 1])
+xlabel("time [\Deltat]")
+xticklabels([])
+grid on
+
+
+figure
+subplot(211)
+plot(perio_freq, perio_power.^2, 'LineWidth', lw)
+xlabel("frequency [1/\Deltat]")
+ylabel("Power")
+title("Periodogram of x-component")
+set(gca,'LineWidth',2)
+set(gca,'FontSize',fs)
+%set(gca, 'YScale', 'log')
+xlim([0 4])
+grid on
+subplot(212)
+plot(perio_freq2, perio_power2.^2, 'LineWidth', lw)
+xlabel("frequency [1/\Deltat]")
[…]

### 2022-05-18 Manuscript/inter_spike_manuscript.tex
Dircac Comb example added

@@
 \begin{abstract}
-A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms spike-train-like signals into their frequency domain. This method 
-clearly shows the apparent cycles in the data and overcomes the problems when using the obvious idea of Fourier-transforming it. We invent this instructive approach with the 
+A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
+clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
+We invent this instructive approach with the 
 idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
 along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
-spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is simple to compute, robust to noise and is able to detect bifurcations 
-inducing regular-regular, regular-chaos as well as chaos-chaos transitions.
+spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.
 
@@
  \textbf{F} Proposed inter spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
+ Inter spike spectra were obtained with a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and its re-composed signals. 
 }

### 2022-05-18 Applications/Dircac Comb Example/transform_dirac_combs.m

@@ -1,0 +1,91 @@
+%% Consider a Dirac-Comb and its FFT
+
+clear, clc
+
+rng(2)
+N = 1000; % length of dirac comb
+T = 100; % inter-spike period
+
+dirac1 = zeros(1,N);
+dirac2 = zeros(1,N);
+
+dirac1(1:T:end) = 1;
+dirac2(1:T:end) = rand(1,length(1:T:length(dirac2)));
+
+% compute new spectra (0.9 rho-threshold, LASSO)
+spectrum1 = inter_spike_spectrum(dirac1,'threshold',0.9);
+spectrum2 = inter_spike_spectrum(dirac2,'threshold',0.9);
+% compute periodograms
+[p1,w1] = periodogram(dirac1,[],length(dirac1));
+[p2,w2] = periodogram(dirac2,[],length(dirac1));
+
+%% Plot DCs, Periodograms & Inter Spike Spectra
+
+fs = 18;
+lw2 = 2;
+
+figure('Units','normalized','Position',[.01 .01 .99 .99]) 
+subplot(2,3,1)
+plot(1:N,dirac1,'LineWidth',3)
+set(gca,'LineWidth',lw2)
+set(gca,'FontSize',fs)
+xlabel('time t [a.u.]')
+ylabel('[a.u.]')
+title('Perfect Dirac comb (DC)')
+ylim([0 1])
+grid on
+
+subplot(2,3,4)
+plot(1:N,dirac2,'LineWidth',3)
+set(gca,'LineWidth',lw2)
+set(gca,'FontSize',fs)
+xlabel('time t [a.u.]')
+ylabel('[a.u.]')
+title('DC with random amplitudes')
+ylim([0 1])
+grid on
+
+subplot(2,3,2)
+plot((w1./(2*pi)),p1,'LineWidth',3)
+set(gca,'LineWidth',lw2)
+set(gca,'FontSize',fs)
+xlabel('frequency [1/t]')
+ylabel('Power/frequency')
+xlim([0 0.2])
+ylim([0 0.035])
+title('Periodogram of perfect DC')
+grid on
+
+subplot(2,3,5)
+plot((w2./(2*pi)),p2,'LineWidth',3)
+set(gca,'LineWidth',lw2)
+set(gca,'FontSize',fs)
+xlabel('frequency [1/t]')
+ylabel('Power/frequency')
+xlim([0 0.2])
+ylim([0 0.035])
[…]

### 2022-05-18 Manuscript/inter_spike_manuscript.tex
Logistic example updated

@@
 A correlation with the positive Lyapunov exponent (Fig.~\ref{fig_tau_rr_logistic}A) is discernible 
-($\rho_{\text{Pearson}}=0.88$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum.
+($\rho_{\text{Pearson}}=0.72$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum.
 
@@
 from a binomial distribution with probability parameter $p$ set to the recurrence rate of the RP of the signal. This way $100$ surrogate $\tau$-RRs are computed in step (5). 
-The results are similar to the ones obtained from the iAAFT surrogates and nearly as good (Fig.~\ref{fig_tau_rr_logistic}B). The first period doubling at 
-$r \approx 3.458$ cannot be detected, while the correlation to the positive Lyapunov exponent is only slightly worse ($\rho_{\text{Pearson}}=0.84$).
+The results are even slightly better compared to the ones obtained from the iAAFT surrogates (Fig.~\ref{fig_tau_rr_logistic}B, $\rho_{\text{Pearson}}=0.81$). The first period doubling at 
+$r \approx 3.458$ cannot be detected by any of the surrogates.
 
@@
 On the contrary, highly sampled (flow-) data often yield not as 
-spiky $\tau$-RR's and, thus, the number of significant peaks in the inter spike spectrum may not be sensitive enough to detect period-doubling bifurcations. Nevertheless the 
+spiky $\tau$-RR's and, thus, the number of significant peaks in the inter spike spectrum may not be sensitive enough to detect period-doubling bifurcations. Moreover the sensitivity of the 
+inter spike spectrum to detect the regime shifts also depends on the critical regularization threshold. Nevertheless the 
 according inter spike spectra is still revealing important information (Fig.~\ref{fig_tau_rr_example_roessler}) and practitioners can design appropriate quantifying statistics based 
@@
  \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. 
- \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR, random surrogates. 
- \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}.
+ \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 
+ (white noise surrogates). 
+ \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}. For obtaining the inter spike spectra we used 
+ a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals.  
 }

### 2022-05-18 Manuscript/inter_spike_manuscript.tex
New figure for schema for basis functions

@@
 \usepackage{enumitem}
+\usepackage{mathtools}
+\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
 %
@@
     \vspace{0pt}
-    \caption{Example for a set of basis functions for an input signal of length $N=5$, aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
+    \caption{Example for a set of basis functions for an input signal of length $N=4$, aligned in the matrix $\bfX$. Inter spike periods $T_{\text{is}}$ larger 
+    than $\ceil*{N/2}$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which can not be uniquely assigned to a certain inter spike period 
+    (blue sheared).} \label{fig_tau_rr_basis_functions}
   \end{minipage}

### 2022-06-09 Manuscript/inter_spike_manuscript.tex
Upper bound for T_is, rendered corresponding figure and method section; astronomical data for playing around

--- 2022-05-18 Manuscript/inter_spike_manuscript.tex
@@
 
-The idea is as simple as it is obvious. The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal -- 
+The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal -- 
 is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
 different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform with length $N$ and 
-$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$.
-In the following we label this time series as a $(1\times N)$-dimensional vector $\bf{s}$.
-First, $N$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,N]$. Second, in order to account for possible phase shifts of 
-these basis functions occurring 
-in $\bf{s}$, each of these $N$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of $M = \sum_{i=1}^{N}i$ 
+$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
+vector $\bf{s}$. 
+First, $\tilde{N}$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
+for possible phase shifts of 
+these basis functions occurring in $\bf{s}$, each of these $\tilde{N}$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
+$M = \sum_{i=1}^{\tilde{N}}i$ 
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure)
+(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure)
 \begin{align}
-\bfX_{i,j} &= \sum_{k=0}^N\delta\left(j-1-kT(i)-i+T(i) \right),\\
+\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT(i)-i+T(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
 T(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
@@
 \end{align}
-Due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, 
-$\bfX$ is not linear independent anymore. Thus, an under-determined linear system
+Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
+Furthermore, there will be identical basis functions and also basis functions, which do not allow for a unambiguous inter spike period, 
+if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
+The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, here 
+the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
+Fig.~\ref{fig_tau_rr_basis_functions}B).\\
+
+\noindent Eventually, an under-determined linear system
 \begin{equation}
@@
 \end{equation}  
-has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms, which can solve this problem, we are 
+has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
 particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
 functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). Therefore, we here choose the \textit{least absolute shrinkage and selection operator} 
-(LASSO regression) \cite{Tibshirani1996}. Finally, we group loadings which correspond to basis functions having the same period $T_\text{is}$ into $\bf{\beta}_f$ and obtain the 
-\textit{inter spike spectrum} by simply plotting $\bf{\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$ (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+(LASSO regression) \cite{Tibshirani1996} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings which correspond to basis functions having the same period 
+$T_\text{is}$ into $\hat{\bf{\beta}}_f$ and obtain the 
+\textit{inter spike spectrum} by simply plotting $\hat{\bf{\beta}}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
+(Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
 
 \begin{figure}
-  \begin{minipage}[b]{0.3\textwidth}
-    \vspace{0pt}
-    \includegraphics[width=0.95\textwidth]{./figures/fig_tau_rr_basis_functions}
-  \end{minipage}\hfill
-  \begin{minipage}[b]{0.7\textwidth}
-    \vspace{0pt}
-    \caption{Example for a set of basis functions for an input signal of length $N=5$, aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
-  \end{minipage}
+\centering
+\includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_basis_functions}
+\caption{\textbf{A} Example for a full set of basis functions for an input signal of length $N=4$, aligned in the matrix $\bfX'$. Inter spike periods $T_{\text{is}}$ larger 
+than $\ceil*{N/2}+1$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which can not be uniquely assigned to a certain inter spike period 
+(blue sheared). \textbf{B} The final set of unambiguous, but still linearly dependent, basis functions aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
 \end{figure}
+
+In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the proposed method must also deal with the free choice of the regression regularization parameter $\alpha$, 
+which determines the sparsity of the regression coefficient vector $\hat{\bf{\beta}}$. Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small, 
+since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\bf{\beta}}$ is an exact solution of Eq.~\ref{eq_linear_system} and not sparse.
+On the other hand, only a sparse number
+of non-zero loadings in $\hat{\bf{\beta}}$ -- \textit{aka} peaks in the inter spike spectrum -- are obtained when $\alpha$ is sufficiently large. In this paper we select $\alpha$ such that the 
+re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\bf{\beta}}$ matches a given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.
 

### 2022-06-09 Applications/Astronomical data/play_around.m

@@ -1,0 +1,41 @@
+clear, clc
+
+%% Load the data
+
+data1 = load("./data/0791780601_imaging_S001");
+data2 = load("./data/0670920501_timing_S003"); % this here takes ages for the spike spectrum and also yields rand deficient warnings
+
+% data1 = load("./data/0411083201_image_S600.txt");
+% data2 = load("./data/0502030101_timing_S003.txt");
+
+% data1 = load("./data/0153950701_imaging_S005.txt");
+% data2 = load("./data/0153951201_timing_S005.txt");
+
+subplot(211)
+plot(data1(:,1),data1(:,2))
+grid on
+subplot(212)
+plot(data2(:,1),data2(:,2))
+grid on
+
+%% Construct RP
+
+threshold = 0.10;
+
+RP = rp(data2(:,2),threshold,'var');
+tauRR = tau_recurrence_rate(RP);
+spectrum = inter_spike_spectrum(tauRR, 'method', "STLS");
+
+figure
+subplot(4,1,[1,2])
+imagesc(RP), colormap([1 1 1; 0 0 0]), axis xy square
+subplot(4,1,3)
+plot(tauRR)
+grid on
+subplot(4,1,4)
+plot(spectrum)
+grid on
+
+%%
+
+save("test_tauRR.csv", "tauRR", "-ascii")

### 2022-06-09 Applications/CENOGRID/data/Laskar/select_laskar_data.m
CENOGRID embedding params

@@ -1,0 +1,8 @@
+clear, clc
+
+ecc = load("La2010d_ecc3.dat");
+
+eccentricity = ecc(1:13421,2);
+
+save("ecc_Laskar.txt", "eccentricity", "-ascii")
+

### 2022-06-09 Applications/CENOGRID/data/gaussian_filter_time_series.m

@@ -1,0 +1,25 @@
+% apply a Gaussian filter to the detrended time series.
+
+clear, clc
+
+data = load("../data/detrended.txt");
+
+t = data(:,1);
+O18 = data(:,2);
+C13 = data(:,3);
+
+t = flipud(t);
+O18 = flipud(O18);
+C13 = flipud(C13);
+
+Filterlength = 10;
+
+w = gausswin(Filterlength);
+w = w/sum(w);
+
+O18_filtered_time_reverse = filter(w,1,O18);
+C13_filtered_time_reverse = filter(w,1,C13);
+
+%% 
+save("O18_filtered_time_reverse.txt", "O18_filtered_time_reverse","-ascii")
+save("C13_filtered_time_reverse.txt", "C13_filtered_time_reverse","-ascii")

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/compute_embedding_parameters.jl

@@ -1,0 +1,32 @@
+# we compute the optimal embedding parameters for the Laskar eccentricity data and for the 
+# CENOGRID data in order to compute RPs, τ-RRs and the according inter spike spectra
+
+using DelayEmbeddings
+using TreeEmbedding  # this will be merged into DelayEmbeddings soon
+using DelimitedFiles
+
+## Eccentricity
+ecc = vec(readdlm("./Applications/CENOGRID/data/Laskar/ecc_Laskar.txt"))
+
+# PECUZAL
+w = estimate_delay(ecc, "mi_min", 0:200)
+L_threshold = 0.005
+KNN = 5
+τs = 0:150
+Y, τ_pec, _, Ls , _ = pecuzal_embedding(ecc; w, L_threshold, KNN, τs, econ=true)
+
+# MCDTS
+runs = 50
+tws = 2:2:τs[end]
+pecuzal = TreeEmbedding.MCDTSOptimGoal(TreeEmbedding.L_statistic(-L_threshold,KNN,tws), TreeEmbedding.Continuity_function())
+tree = mcdts_embedding(ecc, pecuzal, w, τs, runs; verbose=true)
+best_node = TreeEmbedding.best_embedding(tree)
+τ_mcdts = best_node.τs
+
+#out
+# τ_pec = [0, 8, 4, 21, 15, 33, 27, 128, 74, 135, 64]
+# τ_mcdts = []
+
+## O18
+
+data_O18 = 

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/compute_windowed_fft_periodograms.m

@@ -1,0 +1,49 @@
+% FFT - ANALYSIS
+%
+% For the CENOGRID dataset we perform a windowed FFT analysis (short time 
+% Fourier Transform with a Hamming window), in order to obtain a wavelet-like 
+% spectrum.
+
+clear, clc
+
+data = load("../data/detrended.txt");
+
+t = data(:,1);
+O18_raw = flipud(data(:,2));
+C13_raw = flipud(data(:,3));
+t = flipud(t);
+t = t.*1000000;
+
+O18 = load("../data/O18_filtered_time_reverse.txt");
+C13 = load("../data/C13_filtered_time_reverse.txt");
+
+ecc = load("../data/Laskar/ecc_Laskar.txt");
+
+
+%% Compute windowed periodogramm
+
+dt = abs(mean(diff(t))); % Sampling period
+Fs = 1/dt; % Sampling frequency
+
+%%
+windowsize2 = 1000; % windowsize for trajectory
+windowsize1 = 100; % windowsize for the spectrum
+ws = 1; % windowstep
+
+
+[s, f, ~] = spectrogram(O18_raw,windowsize2,windowsize2-ws,[],1);
+pxx_raw = abs(s).^2;
+[s, ~, ~] = spectrogram(O18,windowsize2,windowsize2-ws,[],1);
+pxx_filtered = abs(s).^2;
+[s, ~, ~] = spectrogram(C13_raw,windowsize2,windowsize2-ws,[],1);
+pxy_raw = abs(s).^2;
+[s, ~, ~] = spectrogram(C13,windowsize2,windowsize2-ws,[],1);
+pxy_filtered = abs(s).^2;
+[s, ~, ~] = spectrogram(ecc,windowsize2,windowsize2-ws,[],1);
+p_ecc = abs(s).^2;
+
+f = f .* Fs;
+
+
+save("periodograms_raw.mat",'f','pxx_raw','pxy_raw','p_ecc')
+save("periodograms_filtered.mat",'f','pxx_filtered','pxy_filtered','p_ecc')

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms.m

@@ -1,0 +1,517 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum.
+
+
+% Here: TRAJECTORY BASED ON PECUZAL, MCDTS & NO EMBEDDING (RAW TIME SERIES)
+
+
+clear, clc
+
+data = load("../data/detrended.txt");
+
+t = data(:,1);
+O18 = data(:,2);
+C13 = data(:,3);
+
+t = flipud(t);
+O18 = flipud(O18);
+C13 = flipud(C13);
+
+%%%%%%%%% CAUTION %%%%%%%%%%%%% O18 and C13 are swapped!!!!! 
+%% ---> actually O18 is C13 in this case and vice versa %%%%%%%%%%%%%%
+
+%% Set parameters
+
+epsilon = 0.05; % recurrence threshold
+windowsize2 = 1000; % windowsize for trajectory
+windowsize1 = 100; % windowsize for the spectrum
+ws = 1; % windowstep
+N = length(t); % length of the time series
+taus = 0:100; % delay range passed to PECUZAL
+lambda = 0.003;
+
+M = length(1:ws:N-windowsize2);
+
+spectrum_O18_pec = zeros(windowsize1,M); 
+spectrum_C13_pec = zeros(windowsize1,M);
+spectrum_O18_mcdts = zeros(windowsize1,M); 
+spectrum_C13_mcdts = zeros(windowsize1,M);
+spectrum_O18_ne = zeros(windowsize1,M); 
+spectrum_C13_ne = zeros(windowsize1,M);
+
+%% Compute spike powerspectra in windowed analysis
+
+cnt = 1;
+tic
+for i = 1:ws:M
+    display(i)
+    % extract time series
+    x = O18(i:i+windowsize2);
+    y = C13(i:i+windowsize2);
+    % 1) Pecuzal embedding gained from whole dataset analysis
+    Yx = genembed(x,[0,13,7,10,56,27,3,5,77,42,20,17,15], ones(1,13));
+    Yy = genembed(y,[0,13,7,10,56,27,3,5,77,42,20,17,15], ones(1,13));
+    % compute RP and tau-rr
+    RPx = rp(Yx,epsilon,'var');
[…]

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms2.m

@@ -1,0 +1,758 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum.
+
+
+% Here: TRAJECTORY BASED ON KENNEL, MCDTS & NO EMBEDDING (FILTERED TIME SERIES)
+
+clear, clc
+
+data = load("../data/detrended.txt");
+
+t = data(:,1);
+t = flipud(t);
+
+O18 = load("../data/O18_filtered_time_reverse.txt");
+C13 =load("../data/C13_filtered_time_reverse.txt");
+
+
+%% Set parameters
+
+epsilon = 0.05; % recurrence threshold
+windowsize2 = 1000; % windowsize for trajectory
+windowsize1 = 100; % windowsize for the spectrum
+ws = 1; % windowstep
+N = length(t); % length of the time series
+taus = 0:100; % delay range passed to PECUZAL
+lambda = 0.003;
+
+M = length(1:ws:N-windowsize2);
+
+spectrum_O18_ken = zeros(windowsize1,M); 
+spectrum_C13_ken = zeros(windowsize1,M);
+spectrum_O18_mcdts_mse = zeros(windowsize1,M); 
+spectrum_C13_mcdts_mse = zeros(windowsize1,M);
+spectrum_O18_mcdts_mse_KL = zeros(windowsize1,M); 
+spectrum_C13_mcdts_mse_KL = zeros(windowsize1,M);
+spectrum_O18_ne = zeros(windowsize1,M); 
+spectrum_C13_ne = zeros(windowsize1,M);
+
+%% Compute spike powerspectra in windowed analysis
+
+cnt = 1;
+tic
+for i = 1:ws:M
+    display(i)
+    % extract time series
+    x = O18(i:i+windowsize2);
+    y = C13(i:i+windowsize2);
+    X = horzcat(x,y);
+    % 1) Kennel embedding gained from whole dataset analysis
+    Yx = genembed(x,[0,51,102,153,204,255],[1,1,1,1,1,1]);
+    Yy = genembed(y,[0,51,102,153,204,255],[1,1,1,1,1,1]);
+    % compute RP and tau-rr
+    RPx = rp(Yx,epsilon,'var');
[…]

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms3.m

@@ -1,0 +1,118 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum.
+
+% Here: TRAJECTORY BASED ON CONCATENATION OF O18 AND C13 (FILTERED TIME SERIES)
+
+
+clear, clc
+
+data = load("../data/detrended.txt");
+
+t = data(:,1);
+O18_raw = flipud(data(:,2));
+C13_raw = flipud(data(:,3));
+t = flipud(t);
+
+O18 = load("../data/O18_filtered_time_reverse.txt");
+C13 =load("../data/C13_filtered_time_reverse.txt");
+
+
+%% Set parameters
+
+epsilon = 0.05; % recurrence threshold
+windowsize2 = 1000; % windowsize for trajectory
+windowsize1 = 100; % windowsize for the spectrum
+ws = 1; % windowstep
+N = length(t); % length of the time series
+taus = 0:100; % delay range passed to PECUZAL
+lambda = 0.003;
+
+M = length(1:ws:N-windowsize2);
+
+spectrum_raw = zeros(windowsize1,M); 
+spectrum_filtered = zeros(windowsize1,M); 
+
+%% Compute spike powerspectra in windowed analysis
+
+cnt = 1;
+tic
+for i = 1:ws:M
+    display(i)
+    % extract time series
+    x = O18_raw(i:i+windowsize2);
+    y = C13_raw(i:i+windowsize2);
+    Yx = horzcat(x,y);
+    x = O18(i:i+windowsize2);
+    y = C13(i:i+windowsize2);
+    Yy = horzcat(x,y);
+    
+    % compute RP and tau-rr
+    RPx = rp(Yx,epsilon,'var');
+    RPy = rp(Yy,epsilon,'var');
+    tauRRx = tau_recurrence_rate(RPx);
+    tauRRy = tau_recurrence_rate(RPy);
+    % compute spike powerspectra
+    spectrum_raw(:,cnt) = get_spike_spectrum(tauRRx(1:windowsize1), lambda);
+    spectrum_filtered(:,cnt) = get_spike_spectrum(tauRRy(1:windowsize1), lambda);
+    
+    cnt = cnt + 1;
+    
+end
+toc
+    
+save("mixed_spectrum_raw.mat", "spectrum_raw")
[…]

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms_eccentricity.m

@@ -1,0 +1,81 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum. Here we
+% analyze the eccentricity time series from Laskar 2011.
+ 
+% Here: TRAJECTORY BASED ON PECUZAL embedding (script 
+% `compute_embedding_parameters.jl` in this folder)
+
+clear, clc
+
+data = load("../data/Laskar/ecc_Laskar.txt");
+
+
+%% Set parameters
+
+epsilon = 0.05; % recurrence threshold
+windowsize2 = 1000; % windowsize for trajectory
+windowsize1 = 100; % windowsize for the spectrum
+ws = 1; % windowstep
+N = length(data); % length of the time series
+taus = 0:150; % delay range passed to PECUZAL
+rho_thres = 0.95; % threshold for inter spike spectrum
+
+M = length(1:ws:N-windowsize2);
+
+%% Compute inter spike spectrogram in windowed analysis
+
+spectrum_ecc_pec = zeros(windowsize1,M); 
+spectrum_ecc_ne = zeros(windowsize1,M); 
+
+cnt = 1;
+tic
+for i = 1:ws:M
+    display(i)
+    % extract time series
+    x = data(i:i+windowsize2);
+    % 1) Pecuzal embedding gained from whole dataset analysis
+    Yx = genembed(x,[0, 8, 4, 21, 15, 33, 27, 128, 74, 135, 64], ones(1,10));
+
+    % compute RP and tau-rr
+    RPx = rp(Yx,epsilon,'var');
+    tauRRx = tau_recurrence_rate(RPx);
+    % compute spike powerspectra
+    spectrum_ecc_pec(:,cnt) = get_spike_spectrum(tauRRx(1:windowsize1), lambda);
+
+   
+    cnt = cnt + 1;
+    
+end
+toc
+
+
+save("spectrum_ecc_pec.mat", "spectrum_ecc_pec")
+
+
+%% Compute spike powerspectra in windowed analysis
+
+spectrum_ecc_pec2 = zeros(windowsize1,M); 
+
+cnt = 1;
+tic
+for i = 1:ws:M
+    display(i)
+    % extract time series
+    x = data(i:i+windowsize2);
+    % 1) Pecuzal embedding gained from whole dataset analysis
[…]

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/embed.m

@@ -1,0 +1,59 @@
+function y = embed(varargin)
+%
+%   version 1.0
+%
+%
+%     Create embedding vector using time delay embedding
+%     Y=EMBED(X,M,T) create the embedding vector Y from the time
+%     series X using a time delay embedding with dimension M and
+%     delay T. The resulting embedding vector has length N-T*(M-1),
+%     where N is the length of the original time series.
+%
+%     Example:
+%         N = 300; % length of time series
+%         x = .9*sin((1:N)*2*pi/70); % exemplary time series
+%         y = embed(x,2,17);
+%         plot(y(:,1),y(:,2))
+%
+% Copyright (c) 2012
+% Norbert Marwan, Potsdam Institute for Climate Impact Research, Germany
+% http://www.pik-potsdam.de
+%
+% This program is free software; you can redistribute it and/or
+% modify it under the terms of the GNU General Public License
+% as published by the Free Software Foundation; either version 2
+% of the License, or any later version.
+
+narginchk(1,3)
+nargoutchk(0,1)
+
+try
+    t = varargin{3};
+catch
+        t = 1;
+end
+        
+try
+    m = varargin{2};
+catch
+        m = 1;
+end    
+
+x = varargin{1}(:);
+
+% length of time series
+Nx = length(x);
+NX = Nx-t*(m-1);
+if t*(m-1) > Nx
+   warning('embedding timespan exceeding length of time series')
+end
+
+%% create embeeding vector using Matlab's vectorization
+% index series considering the time delay and dimension
+for mi = 1:m
+    jx(1+NX*(mi-1):NX+NX*(mi-1)) = 1+t*(mi-1):NX+t*(mi-1);
+end
+
+% the final embedding vector
+y = reshape(x(jx),NX,m);
+end

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/mutualinformation.m

@@ -1,0 +1,81 @@
+function Z = mutualinformation(varargin)
+% MUTUALINFORMATION computes the automutualinformation values of timeseries.
+%    I = MUTUALINFORMATION(X) returns the auto mutual information I of X,
+%    where X can be a multi-column vector.
+%
+%    I = MUTUALINFORMATION(X, MAXTAU) returns the auto mutual information for
+%    the lags in the range [0 MAXTAU] (default 50).
+%
+%    I = MUTUALINFORMATION(X, MAXTAU, FLAG) plots auto mutual information 
+%    when FLAG is set to 1 (default 0).
+%
+%    I = MUTUALINFORMATION(X, MAXTAU, FLAG, BINS) uses the number BINS for
+%    the estimation of the marginal probabilities. If not specified, the 
+%    number of bins is computed using Freedman-Diaconis' rule.
+
+% Copyright (c) 2020
+% K. Hauke Kraemer, N. Marwan
+% Potsdam Institute for Climate Impact Research, Germany
+% http://www.pik-potsdam.de
+%
+% This program is free software and runs under MIT licence.
+
+%% Assign input
+
+y = varargin{1};
+assert(isvector(y))
+
+y = (y-mean(y)) ./ std(y);
+
+try
+    tau_max = varargin{2};
+    assert(isscalar(tau_max), 'tau-values must be positive integers.')
+    assert(tau_max > 0, 'tau-values must be positive integers.')
+catch
+    tau_max = 100;
+end
+
+try
+    show = varargin{3};
+    if ~(show==0 || show == 1)
+        warning('input show needs to be 1 (display figure) or 0 (no figure displayed). Now set to 0.')
+        show = 0;
+    end
+catch 
+    show = 0;
+end
+
+try
+    bins = varargin{4};
+catch x 
+    [~,edges] = histcounts(y);
+    bins = length(edges)-1;
+end
+
+%% Check input
+narginchk(1,4)
+nargoutchk(0,1)
+
+tau_min = 0;
+Z(:,1)=tau_min:tau_max;
+
+%% Compute mutual information
+try
+    I = mi(y, bins, tau_max,'nogui');
+    Z(:,2) = zeros(1,size(I,3));
+    Z(:,2) = I(1,1,:);
+catch
+    disp('no')
+    Z(:,2) = NaN;
+end
+
+%% Plotting Automutualinformation against lag tau
+if show
+    figure
[…]

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/plot_CENOGRID_RPs.m

@@ -1,0 +1,105 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum.
+
+
+% Here: Plot RPs (RAW TIME SERIES)
+
+
+clear, clc
+
+data = load("../data/Loess20.txt");
+
+t = data(:,1);
+O18 = data(:,2);
+C13 = data(:,3);
+
+%% first interpolate the data
+% t2 = 0:0.005:67.1;
+% data_interp1 = interp1(t, O18, t2, 'spline');
+% data_interp2 = interp1(t, C13, t2, 'spline');
+% 
+% clear data
+% data(:,1) = t2;
+% data(:,2) = data_interp1;
+% data(:,3) = data_interp2;
+% 
+% save("../data/Loess_20_int.txt","data","-ascii")
+
+%%
+clear, clc
+
+data = load("../data/Loess_20_int.txt");
+
+t = data(:,1);
+C13 = data(:,2);
+O18 = data(:,3);
+
+t = flipud(t);
+O18 = flipud(O18);
+C13 = flipud(C13);
+
+%%
+
+[RP1, D1] = rp(C13,0.08,'fan');
+[RP2, D2] = rp(O18,0.08,'fan');
+
+%%
+RP1 = D1<0.08;
+RP2 = D2<0.08;
+
+fs = 22; % fontsize
+
+figure('Units','normalized','Position',[.01 .01 .99 .99])
+
+subplot(121)
+imagesc(t,t,RP1), colormap([1 1 1;0 0 0]), axis xy square
+set(gca,'YDir','reverse')
+set(gca,'XDir','reverse')
+set(gca,'LineWidth',2)
+set(gca,'FontSize',fs)
+xlabel("time [Mio yrs BP]")
+xticks(0:5:65)
+yticks(0:5:65)
+grid on
+
+subplot(122)
+imagesc(t,t,RP2), colormap([1 1 1;0 0 0]), axis xy square
+set(gca,'YDir','reverse')
+set(gca,'XDir','reverse')
+set(gca,'YAxisLocation','right')
+set(gca,'LineWidth',2)
+set(gca,'FontSize',fs)
+xlabel("time [Mio yrs BP]")
+xticks(0:5:65)
+yticks(0:5:65)
+grid on
+
+%%
+
+figure('Units','normalized','Position',[.01 .01 .99 .3])
+
+subplot(121)
[…]

### 2022-06-09 Applications/CENOGRID/windowed spectrograms/plot_evolutionary_spectrograms.m

@@ -1,0 +1,425 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum.
+
+
+% Here: TRAJECTORY BASED ON PECUZAL, MCDTS & NO EMBEDDING (RAW TIME SERIES)
+
+
+clear, clc
+
+data = load("../data/detrended.txt");
+ecc = load("../data/Laskar/ecc_Laskar.txt");
+
+t = data(:,1);
+C13 = data(:,2);
+O18 = data(:,3);
+
+t = flipud(t);
+O18 = flipud(O18);
+C13 = flipud(C13);
+
+%% Set parameters
+% 
+% epsilon = 0.05; % recurrence threshold
+% windowsize2 = 1000; % windowsize for trajectory
+% windowsize1 = 100; % windowsize for the spectrum
+% ws = 1; % windowstep
+% N = length(t); % length of the time series
+% taus = 0:100; % delay range passed to PECUZAL
+% lambda = 0.003;
+% 
+% M = length(1:ws:N-windowsize2);
+% 
+% spectrum_O18_pec = zeros(windowsize1,M); 
+% spectrum_C13_pec = zeros(windowsize1,M);
+% spectrum_O18_mcdts = zeros(windowsize1,M); 
+% spectrum_C13_mcdts = zeros(windowsize1,M);
+% spectrum_O18_ne = zeros(windowsize1,M); 
+% spectrum_C13_ne = zeros(windowsize1,M);
+% 
+% %% Compute spike powerspectra in windowed analysis
+% 
+% cnt = 1;
+% tic
+% for i = 1:ws:M
+%     display(i)
+%     % extract time series
+%     x = O18(i:i+windowsize2);
+%     y = C13(i:i+windowsize2);
+%     % 1) Pecuzal embedding gained from whole dataset analysis
+%     Yx = genembed(x,[0,13,7,10,56,27,3,5,77,42,20,17,15], ones(1,13));
+%     Yy = genembed(y,[0,13,7,10,56,27,3,5,77,42,20,17,15], ones(1,13));
+%     % compute RP and tau-rr
+%     RPx = rp(Yx,epsilon,'var');
+%     RPy = rp(Yy,epsilon,'var');
[…]

### 2022-06-10 Manuscript/inter_spike_manuscript.tex
CENOGRID computed spectrograms and ISS spectrogram (.mat)-files ignored

@@
  \textbf{F} Proposed inter spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
- Inter spike spectra were obtained with a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and its re-composed signals. 
+ Inter spike spectra were obtained with a LASSO regression and a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and 
+ its re-composed signals (c.f. Section~\ref{sec_tau_rr_method}). 
 }
@@
 particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
-functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). Therefore, we here choose the \textit{least absolute shrinkage and selection operator} 
-(LASSO regression) \cite{Tibshirani1996} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings which correspond to basis functions having the same period 
+functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
+(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings 
+which correspond to basis functions having the same period 
 $T_\text{is}$ into $\hat{\bf{\beta}}_f$ and obtain the 
@@
   \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
-  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a regularization threshold corresponding to 
-  $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
+  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a LASSO regression and a regularization threshold 
+  corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
   \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
@@
  \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}. For obtaining the inter spike spectra we used 
- a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals.  
+ a LASSO regression and a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals.  
 }

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_embedding_parameters.jl

@@ -1,9 +1,11 @@
-# we compute the optimal embedding parameters for the Laskar eccentricity data and for the 
-# CENOGRID data in order to compute RPs, τ-RRs and the according inter spike spectra
+# Here we compute the optimal embedding parameters for the Laskar eccentricity data and for the 
+# CENOGRID data in order to compute RPs, τ-RRs and the according inter spike spectra. We use 
+# PECUZAL algorithm and the corresponding MCDTS-routine.
 
 using DelayEmbeddings
 using TreeEmbedding  # this will be merged into DelayEmbeddings soon
 using DelimitedFiles
+using Random
 
 ## Eccentricity
 ecc = vec(readdlm("./Applications/CENOGRID/data/Laskar/ecc_Laskar.txt"))
@@ -12,21 +14,52 @@ ecc = vec(readdlm("./Applications/CENOGRID/data/Laskar/ecc_Laskar.txt"))
 w = estimate_delay(ecc, "mi_min", 0:200)
 L_threshold = 0.005
 KNN = 5
-τs = 0:150
-Y, τ_pec, _, Ls , _ = pecuzal_embedding(ecc; w, L_threshold, KNN, τs, econ=true)
+τs = 0:150 # sampling time is 5 kyrs, so this covers 750 kyrs
+Y, τ_pec_ecc, _, Ls , _ = pecuzal_embedding(ecc; w, L_threshold, KNN, τs, econ=true)
 
-# MCDTS
+# MCDTS -> PECUZAL
 runs = 50
 tws = 2:2:τs[end]
 pecuzal = TreeEmbedding.MCDTSOptimGoal(TreeEmbedding.L_statistic(-L_threshold,KNN,tws), TreeEmbedding.Continuity_function())
+Random.seed!(1)
 tree = mcdts_embedding(ecc, pecuzal, w, τs, runs; verbose=true)
 best_node = TreeEmbedding.best_embedding(tree)
-τ_mcdts = best_node.τs
+τ_mcdts_ecc_pec = best_node.τs
+# MCDTS -> FNN + Continuity_function
+optimgoal = TreeEmbedding.MCDTSOptimGoal(TreeEmbedding.FNN_statistic(), TreeEmbedding.Continuity_function())
+Random.seed!(1)
[…]

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_windowed_fft_periodograms.m

@@ -27,16 +27,14 @@ Fs = 1/dt; % Sampling frequency
 
 %%
 windowsize2 = 1000; % windowsize for trajectory
-windowsize1 = 100; % windowsize for the spectrum
 ws = 1; % windowstep
 
-
-[s, f, ~] = spectrogram(O18_raw,windowsize2,windowsize2-ws,[],1);
-pxx_raw = abs(s).^2;
-[s, ~, ~] = spectrogram(O18,windowsize2,windowsize2-ws,[],1);
+% [s, f, ~] = spectrogram(O18_raw,windowsize2,windowsize2-ws,[],1);
+% pxx_raw = abs(s).^2;
+[s, f, ~] = spectrogram(O18,windowsize2,windowsize2-ws,[],1);
 pxx_filtered = abs(s).^2;
-[s, ~, ~] = spectrogram(C13_raw,windowsize2,windowsize2-ws,[],1);
-pxy_raw = abs(s).^2;
+% [s, ~, ~] = spectrogram(C13_raw,windowsize2,windowsize2-ws,[],1);
+% pxy_raw = abs(s).^2;
 [s, ~, ~] = spectrogram(C13,windowsize2,windowsize2-ws,[],1);
 pxy_filtered = abs(s).^2;
 [s, ~, ~] = spectrogram(ecc,windowsize2,windowsize2-ws,[],1);
@@ -44,6 +42,4 @@ p_ecc = abs(s).^2;
 
 f = f .* Fs;
 
-
-save("periodograms_raw.mat",'f','pxx_raw','pxy_raw','p_ecc')
-save("periodograms_filtered.mat",'f','pxx_filtered','pxy_filtered','p_ecc')
+save("./computed spectra/periodograms_short_time_fourier.mat",'f','pxx_filtered','pxy_filtered','p_ecc')

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms.m

@@ -1,517 +1,0 @@
-% For the CENOGRID dataset we perform a windowed analysis with the spike 
-% powerspectrum, in order to obtain a wavelet-like spectrum.
-
-
-% Here: TRAJECTORY BASED ON PECUZAL, MCDTS & NO EMBEDDING (RAW TIME SERIES)
-
-
-clear, clc
-
-data = load("../data/detrended.txt");
-
-t = data(:,1);
-O18 = data(:,2);
-C13 = data(:,3);
-
-t = flipud(t);
-O18 = flipud(O18);
-C13 = flipud(C13);
-
-%%%%%%%%% CAUTION %%%%%%%%%%%%% O18 and C13 are swapped!!!!! 
-%% ---> actually O18 is C13 in this case and vice versa %%%%%%%%%%%%%%
-
-%% Set parameters
-
-epsilon = 0.05; % recurrence threshold
-windowsize2 = 1000; % windowsize for trajectory
-windowsize1 = 100; % windowsize for the spectrum
-ws = 1; % windowstep
-N = length(t); % length of the time series
-taus = 0:100; % delay range passed to PECUZAL
-lambda = 0.003;
-
-M = length(1:ws:N-windowsize2);
-
-spectrum_O18_pec = zeros(windowsize1,M); 
-spectrum_C13_pec = zeros(windowsize1,M);
-spectrum_O18_mcdts = zeros(windowsize1,M); 
-spectrum_C13_mcdts = zeros(windowsize1,M);
-spectrum_O18_ne = zeros(windowsize1,M); 
-spectrum_C13_ne = zeros(windowsize1,M);
-
-%% Compute spike powerspectra in windowed analysis
-
-cnt = 1;
-tic
-for i = 1:ws:M
-    display(i)
-    % extract time series
-    x = O18(i:i+windowsize2);
-    y = C13(i:i+windowsize2);
-    % 1) Pecuzal embedding gained from whole dataset analysis
-    Yx = genembed(x,[0,13,7,10,56,27,3,5,77,42,20,17,15], ones(1,13));
-    Yy = genembed(y,[0,13,7,10,56,27,3,5,77,42,20,17,15], ones(1,13));
-    % compute RP and tau-rr
-    RPx = rp(Yx,epsilon,'var');
[…]

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms2.m

@@ -1,758 +1,0 @@
-% For the CENOGRID dataset we perform a windowed analysis with the spike 
-% powerspectrum, in order to obtain a wavelet-like spectrum.
-
-
-% Here: TRAJECTORY BASED ON KENNEL, MCDTS & NO EMBEDDING (FILTERED TIME SERIES)
-
-clear, clc
-
-data = load("../data/detrended.txt");
-
-t = data(:,1);
-t = flipud(t);
-
-O18 = load("../data/O18_filtered_time_reverse.txt");
-C13 =load("../data/C13_filtered_time_reverse.txt");
-
-
-%% Set parameters
-
-epsilon = 0.05; % recurrence threshold
-windowsize2 = 1000; % windowsize for trajectory
-windowsize1 = 100; % windowsize for the spectrum
-ws = 1; % windowstep
-N = length(t); % length of the time series
-taus = 0:100; % delay range passed to PECUZAL
-lambda = 0.003;
-
-M = length(1:ws:N-windowsize2);
-
-spectrum_O18_ken = zeros(windowsize1,M); 
-spectrum_C13_ken = zeros(windowsize1,M);
-spectrum_O18_mcdts_mse = zeros(windowsize1,M); 
-spectrum_C13_mcdts_mse = zeros(windowsize1,M);
-spectrum_O18_mcdts_mse_KL = zeros(windowsize1,M); 
-spectrum_C13_mcdts_mse_KL = zeros(windowsize1,M);
-spectrum_O18_ne = zeros(windowsize1,M); 
-spectrum_C13_ne = zeros(windowsize1,M);
-
-%% Compute spike powerspectra in windowed analysis
-
-cnt = 1;
-tic
-for i = 1:ws:M
-    display(i)
-    % extract time series
-    x = O18(i:i+windowsize2);
-    y = C13(i:i+windowsize2);
-    X = horzcat(x,y);
-    % 1) Kennel embedding gained from whole dataset analysis
-    Yx = genembed(x,[0,51,102,153,204,255],[1,1,1,1,1,1]);
-    Yy = genembed(y,[0,51,102,153,204,255],[1,1,1,1,1,1]);
-    % compute RP and tau-rr
-    RPx = rp(Yx,epsilon,'var');
[…]

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms3.m

@@ -1,118 +1,0 @@
-% For the CENOGRID dataset we perform a windowed analysis with the spike 
-% powerspectrum, in order to obtain a wavelet-like spectrum.
-
-% Here: TRAJECTORY BASED ON CONCATENATION OF O18 AND C13 (FILTERED TIME SERIES)
-
-
-clear, clc
-
-data = load("../data/detrended.txt");
-
-t = data(:,1);
-O18_raw = flipud(data(:,2));
-C13_raw = flipud(data(:,3));
-t = flipud(t);
-
-O18 = load("../data/O18_filtered_time_reverse.txt");
-C13 =load("../data/C13_filtered_time_reverse.txt");
-
-
-%% Set parameters
-
-epsilon = 0.05; % recurrence threshold
-windowsize2 = 1000; % windowsize for trajectory
-windowsize1 = 100; % windowsize for the spectrum
-ws = 1; % windowstep
-N = length(t); % length of the time series
-taus = 0:100; % delay range passed to PECUZAL
-lambda = 0.003;
-
-M = length(1:ws:N-windowsize2);
-
-spectrum_raw = zeros(windowsize1,M); 
-spectrum_filtered = zeros(windowsize1,M); 
-
-%% Compute spike powerspectra in windowed analysis
-
-cnt = 1;
-tic
-for i = 1:ws:M
-    display(i)
-    % extract time series
-    x = O18_raw(i:i+windowsize2);
-    y = C13_raw(i:i+windowsize2);
-    Yx = horzcat(x,y);
-    x = O18(i:i+windowsize2);
-    y = C13(i:i+windowsize2);
-    Yy = horzcat(x,y);
-    
-    % compute RP and tau-rr
-    RPx = rp(Yx,epsilon,'var');
-    RPy = rp(Yy,epsilon,'var');
-    tauRRx = tau_recurrence_rate(RPx);
-    tauRRy = tau_recurrence_rate(RPy);
-    % compute spike powerspectra
-    spectrum_raw(:,cnt) = get_spike_spectrum(tauRRx(1:windowsize1), lambda);
-    spectrum_filtered(:,cnt) = get_spike_spectrum(tauRRy(1:windowsize1), lambda);
-    
-    cnt = cnt + 1;
-    
-end
-toc
-    
-save("mixed_spectrum_raw.mat", "spectrum_raw")
[…]

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms_cenogrid.m

@@ -1,0 +1,78 @@
+% For the CENOGRID dataset we perform a windowed analysis with the spike 
+% powerspectrum, in order to obtain a wavelet-like spectrum. Here we
+% analyze the CENOGRID time series.
+ 
+% Here: TRAJECTORY BASED ON MCDTS embedding, FNN + continuity statistic (script 
+% `compute_embedding_parameters.jl` in this folder)
+
+clear, clc
+
+data = load("../data/detrended.txt");
+
+t = data(:,1);
+t = flipud(t);
+t = t.*1000000;
+
+O18 = load("../data/O18_filtered_time_reverse.txt");
+C13 = load("../data/C13_filtered_time_reverse.txt");
+
+% sampling time is dt = 5,000 yrs
+
+%% Set parameters
+
+epsilon = 0.1; % recurrence threshold
+windowsize = 1200; % windowsize for trajectory
+ws = 1; % windowstep
+N = length(data); % length of the time series
+rho_thres = 0.9; % thresholds for inter spike spectrum
+M = length(1:ws:N-windowsize); % number of computed spectra
+
+%% Compute inter spike spectrogram in windowed analysis
+
+window_tau = 200; % sampling time is 5.000 yrs so this corresponds to 1 Mio yrs
+length_of_spectra = ceil(window_tau/2);
+
+spectrum_O18_mcdts = zeros(length_of_spectra,M); 
+spectrum_O18_ne = zeros(length_of_spectra,M);
+spectrum_C13_mcdts = zeros(length_of_spectra,M); 
+spectrum_C13_ne = zeros(length_of_spectra,M);
+
+taus_O18_mcdts = [0  50  104  35  43  149  39  47  45]; % from script `compute_embedding_parameters.jl`
+taus_C13_mcdts = [0  136  32  123  130  126  133  128]; % from script `compute_embedding_parameters.jl`
+
+%%
+cnt = 1;
+tic
+for i = 1:ws:M
+    display(i)
+    % extract time series
+    x = O18(i:i+windowsize);
+    y = C13(i:i+windowsize);
+    % 1) MCDTS embedding gained from whole dataset analysis
+    Yx = genembed(x,taus_O18_mcdts, ones(1,length(taus_O18_mcdts)));
[…]

### 2022-06-10 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms_eccentricity.m

@@ -2,80 +2,57 @@
 % powerspectrum, in order to obtain a wavelet-like spectrum. Here we
 % analyze the eccentricity time series from Laskar 2011.
  
-% Here: TRAJECTORY BASED ON PECUZAL embedding (script 
+% Here: TRAJECTORY BASED ON MCDTS embedding, FNN + continuity statistic (script 
 % `compute_embedding_parameters.jl` in this folder)
 
 clear, clc
 
 data = load("../data/Laskar/ecc_Laskar.txt");
 
+% sampling time is dt = 5,000 yrs
 
 %% Set parameters
 
-epsilon = 0.05; % recurrence threshold
-windowsize2 = 1000; % windowsize for trajectory
-windowsize1 = 100; % windowsize for the spectrum
+epsilon = 0.1; % recurrence threshold
+windowsize = 1200; % windowsize for trajectory
 ws = 1; % windowstep
 N = length(data); % length of the time series
-taus = 0:150; % delay range passed to PECUZAL
-rho_thres = 0.95; % threshold for inter spike spectrum
-
-M = length(1:ws:N-windowsize2);
+rho_thres = 0.9; % thresholds for inter spike spectrum
+M = length(1:ws:N-windowsize); % number of computed spectra
 
 %% Compute inter spike spectrogram in windowed analysis
 
-spectrum_ecc_pec = zeros(windowsize1,M); 
-spectrum_ecc_ne = zeros(windowsize1,M); 
+window_tau = 200; % sampling time is 5.000 yrs so this corresponds to 1 Mio yrs
+length_of_spectra = ceil(window_tau/2);
 
+spectrum_ecc_mcdts = zeros(length_of_spectra,M); 
+spectrum_ecc_ne = zeros(length_of_spectra,M);
+
+taus_mcdts = [0 8 62 115 4 3]; % from script `compute_embedding_parameters.jl`
+
+%%
 cnt = 1;
 tic
 for i = 1:ws:M
     display(i)
     % extract time series
-    x = data(i:i+windowsize2);
-    % 1) Pecuzal embedding gained from whole dataset analysis
-    Yx = genembed(x,[0, 8, 4, 21, 15, 33, 27, 128, 74, 135, 64], ones(1,10));
+    x = data(i:i+windowsize);
[…]

### 2022-06-27 Applications/Kuramoto model/CE and GB frequencies/compute_fft_spectrogram.m
Kuramoto 50-dim: results for transformed phases; Added Vostok data

@@ -1,0 +1,58 @@
+% FFT of the frequency-data
+
+clear, clc
+
+f_ce = load("./data/frequencies_ce.mat").frequencies_ce;
+f_gb = load("./data/frequencies_gb.mat").frequencies_gb;
+
+%%
+
+L_ce = length(f_ce); % length of the signal
+L_gb = length(f_gb);
+T_ce = 0.2; % sampling time in secs
+T_gb = 1;
+Fs_ce = 1/T_ce; % sampling frequency
+Fs_gb = 1/T_gb;
+
+t_ce = (0:L_ce-1)*T_ce; % time vector
+t_gb = (0:L_gb-1)*T_gb;
+
+% FFT
+Y_ce = fft(f_ce(1:L_ce));
+Y_gb = fft(f_gb(1:L_gb));
+
+P2_ce = abs(Y_ce/L_ce);
+P1_ce = P2_ce(1:L_ce/2+1);
+P1_ce(2:end-1) = 2*P1_ce(2:end-1);
+fs_ce= Fs_ce*(0:(L_ce/2))/L_ce;
+
+P2_gb = abs(Y_gb/L_gb);
+P1_gb = P2_gb(1:L_gb/2+1);
+P1_gb(2:end-1) = 2*P1_gb(2:end-1);
+fs_gb= Fs_gb*(0:(L_gb/2))/L_gb;
+
+%%
+
+fs_ce= (1/(0.2/60))*(0:(L_ce/2))/L_ce;
+fs_gb= (1/(1/60))*(0:(L_gb/2))/L_gb;
+
+
+figure
+subplot(211)
+semilogx(fs_ce,P1_ce)
+title('Single-Sided Amplitude Spectrum of F_{CE}')
+xlabel('f (Hz)')
+ylabel('|P1(f)|')
+xlim([10e-5 1])
+grid on
+
+subplot(212)
+semilogx(fs_gb,P1_gb)
+title('Single-Sided Amplitude Spectrum of F_{GB}')
+xlabel('f (Hz)')
+ylabel('|P1(f)|')
+xlim([10e-5 1])
+grid on
+
+
+

### 2022-06-27 Applications/Kuramoto model/system with switch/Cluster scripts/analyze_system_with_transition_cl_distributed_2.jl

@@ -96,7 +96,7 @@ end
 varnames = ["spectrum_0_8", "spectrum_0_85", "spectrum_0_9", "spectrum_0_95", "spectrum_0_8_t", "spectrum_0_85_t", "spectrum_0_9_t", "spectrum_0_95_t", "fft_spectrum", "fft_spectrum_t", "rhos1", "rhos2", "rhos3", "rhos4", "rhos1t", "rhos2t", "rhos3t", "rhos4t"]
 
 for i = 1:length(varnames)
-    writestr = "results_kuramoto_switch_"*varnames[i]*".csv"
+    writestr = "results_kuramoto_switch_"*varnames[i]*"_no_noise.csv"
     data = []
     for j = 1:length(results)
         push!(data,results[j][i])

### 2022-06-27 Applications/Kuramoto model/system with switch/Cluster scripts/slurm_kuramoto_3.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+#SBATCH --qos=priority
+#SBATCH --partition=priority
+#SBATCH --job-name=Kuramoto
+#SBATCH --account=synet
+#SBATCH --output=name-%j.out
+#SBATCH --error=name-%j.err
+#SBATCH --nodes=2
+#SBATCH --ntasks-per-node=8
+
+
+echo "------------------------------------------------------------"
+echo "SLURM JOB ID: $SLURM_JOBID"
+echo "$SLURM_NTASKS tasks"
+echo "------------------------------------------------------------"
+
+module load julia/1.7.0
+julia analyze_system_with_transition_cl_distributed_2.jl $SLURM_NTASKS

### 2022-06-27 Applications/Kuramoto model/system with switch/analyze_system_with_transition_transformed.m

@@ -6,36 +6,48 @@
 clear, clc
 % load the results for the different rho-thresholds:
 
-spectrum1 = load("./results/results_kuramoto_switchspectrum_0_8.csv");
-spectrum2 = load("./results/results_kuramoto_switchspectrum_0_85.csv");
-spectrum3 = load("./results/results_kuramoto_switchspectrum_0_9.csv");
-spectrum4 = load("./results/results_kuramoto_switchspectrum_0_95.csv");
+spectrum1 = load("./results/results_kuramoto_switch_spectrum_0_8.csv");
+spectrum2 = load("./results/results_kuramoto_switch_spectrum_0_85.csv");
+spectrum3 = load("./results/results_kuramoto_switch_spectrum_0_9.csv");
+spectrum4 = load("./results/results_kuramoto_switch_spectrum_0_95.csv");
 
-spectrum1t = load("./results/results_kuramoto_switchspectrum_0_8_t.csv");
-spectrum2t = load("./results/results_kuramoto_switchspectrum_0_85_t.csv");
-spectrum3t = load("./results/results_kuramoto_switchspectrum_0_9_t.csv");
-spectrum4t = load("./results/results_kuramoto_switchspectrum_0_95_t.csv");
+% spectrum1t = load("./results/results_kuramoto_switch_spectrum_0_8_t.csv");
+% spectrum2t = load("./results/results_kuramoto_switch_spectrum_0_85_t.csv");
+% spectrum3t = load("./results/results_kuramoto_switch_spectrum_0_9_t.csv");
+% spectrum4t = load("./results/results_kuramoto_switch_spectrum_0_95_t.csv");
 
-rhos1 = load("./results/results_kuramoto_switchrhos1.csv");
-rhos2 = load("./results/results_kuramoto_switchrhos2.csv");
-rhos3 = load("./results/results_kuramoto_switchrhos3.csv");
-rhos4 = load("./results/results_kuramoto_switchrhos4.csv");
+spectrum1t = load("./results/results_kuramoto_switch_spectrum_0_8_t_no_noise.csv");
+spectrum2t = load("./results/results_kuramoto_switch_spectrum_0_85_t_no_noise.csv");
+spectrum3t = load("./results/results_kuramoto_switch_spectrum_0_9_t_no_noise.csv");
[…]

### 2022-06-27 Applications/Kuramoto model/system with switch/compute_emd_system_with_transition.jl

@@ -9,18 +9,34 @@ using Distributions
 
 # load the results:
 
-spectrum1 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_8.csv")
-spectrum2 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_85.csv")
-spectrum3 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_9.csv")
-spectrum4 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_95.csv")
+spectrum1 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_8.csv")
+spectrum2 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_85.csv")
+spectrum3 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_9.csv")
+spectrum4 = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_95.csv")
 
-spectrum1t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_8_t.csv")
-spectrum2t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_85_t.csv")
-spectrum3t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_9_t.csv")
-spectrum4t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switchspectrum_0_95_t.csv")
+spectrum1t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_8_t.csv")
+spectrum2t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_85_t.csv")
+spectrum3t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_spectrum_0_9_t.csv")
[…]

### 2022-06-27 Applications/Roessler Transition/plot_roessler_emds.m

@@ -74,32 +74,32 @@ lw1 = 0.5;
 figure('Units','normalized','Position',[.01 .01 .99 .99])
 subplot(3,4,[1,2,5,6])
 imagesc(as,as,RP_emd1), colormap([1 1 1; 0 0 0]), axis xy square
-for j = 1:length(transitions)
-    xline(transitions(j),'r--','linewidth',lw1)
-end
+% for j = 1:length(transitions)
+%     xline(transitions(j),'r--','linewidth',lw1)
+% end
 title("EMD 1")
 grid on
 
 subplot(3,4,[3,4,7,8])
 imagesc(as,as,RP_emd2), colormap([1 1 1; 0 0 0]), axis xy square
-for j = 1:length(transitions)
-    xline(transitions(j),'r--','linewidth',lw1)
-end
+% for j = 1:length(transitions)
+%     xline(transitions(j),'r--','linewidth',lw1)
+% end
 title("EMD 2")
 grid on
 
 subplot(3,4,[9,10])
 plot(as,RR_emd1), hold on
-for j = 1:length(transitions)
-    xline(transitions(j),'r--','linewidth',lw1)
-end
+% for j = 1:length(transitions)
+%     xline(transitions(j),'r--','linewidth',lw1)
+% end
 xlim([as(1) as(end)])
 grid on
 subplot(3,4,[11,12])
 plot(as,RR_emd2), hold on
-for j = 1:length(transitions)
-    xline(transitions(j),'r--','linewidth',lw1)
-end
+% for j = 1:length(transitions)
+%     xline(transitions(j),'r--','linewidth',lw1)
+% end
 xlim([as(1) as(end)])
 grid on
 
@@ -107,64 +107,64 @@ grid on
 figure('Units','normalized','Position',[.01 .01 .99 .99])
 subplot(3,4,[1,2,5,6])
 imagesc(as,as,RP_emd3), colormap([1 1 1; 0 0 0]), axis xy square
-for j = 1:length(transitions)
-    xline(transitions(j),'r--','linewidth',lw1)
-end
+% for j = 1:length(transitions)
+%     xline(transitions(j),'r--','linewidth',lw1)
+% end
 title("EMD 3")
 grid on
 
 subplot(3,4,[3,4,7,8])
 imagesc(as,as,RP_emd4), colormap([1 1 1; 0 0 0]), axis xy square
-for j = 1:length(transitions)
-    xline(transitions(j),'r--','linewidth',lw1)
-end
[…]

### 2022-06-27 Applications/Roessler Transition/plot_roessler_spectrograms.m

@@ -28,7 +28,7 @@ w2 = tau_window/2;
 tt = 0:dt:(tau_window-1)*dt;
 
 % plotting params
-% cax_max = 0.013;
+cax_max = 0.013;
 Fs = 22;
 lw2 = 1;
 
@@ -45,7 +45,7 @@ shading flat
 % xline(61,'r--','LineWidth',lw2)
 colormap(parula)
 % caxis([0 cax_max])
-title('ISS1')
+title('FFT')
 ylabel('Period [\Delta t]')
 ylim([tt(1) tt(w2)])
 xlim([as(1) as(end)])
@@ -59,7 +59,7 @@ view(2)
 shading flat
 colormap(parula)
 % caxis([0 cax_max])
-title('ISS1 true')
+title('FFT true')
 ylabel('Period [\Delta t]')
 ylim([tt(1) tt(w2)])
 xlim([as(1) as(end)])
@@ -81,7 +81,7 @@ shading flat
 % xline(61,'r--','LineWidth',lw2)
 colormap(parula)
 caxis([0 cax_max])
-title('ISS1')
+title('ISS')
 ylabel('Period [\Delta t]')
 ylim([tt(1) tt(w2)])
 xlim([as(1) as(end)])
@@ -95,7 +95,7 @@ view(2)
 shading flat
 colormap(parula)
 caxis([0 cax_max])
-title('ISS1 true')
+title('ISS true')
 ylabel('Period [\Delta t]')
 ylim([tt(1) tt(w2)])
 xlim([as(1) as(end)])

### 2022-06-27 Applications/Laskar/windowed spectrograms/compute_embedding_parameters.jl
Laskar example initialized

@@ -1,0 +1,31 @@
+# Here we compute the optimal embedding parameters for the Laskar eccentricity data and for the 
+# CENOGRID data in order to compute RPs, τ-RRs and the according inter spike spectra. We use 
+# PECUZAL algorithm and the corresponding MCDTS-routine.
+
+using DelayEmbeddings
+using TreeEmbedding  # this will be merged into DelayEmbeddings soon
+using DelimitedFiles
+using Random
+
+## Eccentricity
+ecc = vec(readdlm("./Applications/Laskar/data/Laskar/ecc_Laskar.txt"))
+
+# PECUZAL
+w = estimate_delay(ecc, "mi_min", 0:200)
+L_threshold = 0.005
+KNN = 5
+τs = 0:150 # sampling time is 5 kyrs, so this covers 750 kyrs
+Y, τ_pec_ecc, _, Ls , _ = pecuzal_embedding(ecc; w, L_threshold, KNN, τs, econ=true)
+
+# MCDTS -> FNN + Continuity_function
+runs = 50
+fnn_threshold = 0.01 # 1% false neighbors
+optimgoal = TreeEmbedding.MCDTSOptimGoal(TreeEmbedding.FNN_statistic(fnn_threshold), TreeEmbedding.Continuity_function())
+Random.seed!(2)
+tree = mcdts_embedding(ecc, optimgoal, w, τs, runs; verbose=true)
+best_node = TreeEmbedding.best_embedding(tree)
+τ_mcdts_ecc_fnn = best_node.τs
+
+#out
+# τ_pec_ecc = [0, 8, 4, 21, 15, 33, 27, 128, 74, 135, 64]
+# τ_mcdts_ecc_fnn = [0  8  101  62  114  36  18  4]

### 2022-06-27 Applications/Laskar/windowed spectrograms/compute_windowed_fft_periodograms.m

@@ -1,0 +1,27 @@
+% FFT - ANALYSIS
+%
+% For the LASKAR dataset we perform a windowed FFT analysis (short time 
+% Fourier Transform with a Hamming window), in order to obtain a wavelet-like 
+% spectrum of the eccentricity time series.
+
+clear, clc
+
+ecc = load("../data/Laskar/ecc_Laskar.txt");
+
+dt = 5000; % Sampling period
+Fs = 1/dt; % Sampling frequency
+
+t = linspace(0,6.7100e+07,length(ecc)); % time vector
+
+
+%% Compute windowed periodogramm
+
+windowsize2 = 1000; % windowsize for trajectory
+ws = 1; % windowstep
+
+[s, f, ~] = spectrogram(ecc,windowsize2,windowsize2-ws,[],1);
+p_ecc = abs(s).^2;
+
+f = f .* Fs;
+
+save("./computed spectra/periodograms_short_time_fourier.mat", 'f', 'p_ecc')

### 2022-06-27 Applications/Laskar/windowed spectrograms/genembed.m

@@ -1,0 +1,21 @@
+function YY = genembed(Y, taus, ts)
+    assert(taus(1) == 0, "provide a delay-vector, which has a 0 in its first entry.")
+    assert(length(taus)==length(ts), "provide delay- and ts-index vectors, which have the same length.")
+    if size(Y,2)>size(Y,1)
+        Y = Y';
+    end
+    assert(max(ts) <= size(Y,2), "The maximum ts-index must be smaller or equal to the number of provided time series.")
+    
+    YY = Y(:,ts(1));
+    for i = 2:length(taus)
+        YY = embed_for_prediction(YY, Y(:,ts(i)), taus(i));
+    end
+end
+
+function Y2 = embed_for_prediction(Y, x, tau)
+    N = length(Y);
+    MM = length(x);
+    MMM = MM - tau;
+    M = min([N, MMM]);
+    Y2 = horzcat(Y(end-M+1:end,:), x(end-M-tau+1:end-tau));
+end

### 2022-06-28 Manuscript/inter_spike_manuscript.tex
Laskar results: no success... :/

@@
 % please place your own definitions here and don't use \def but
-% \newcommand{}{}
+\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
 %
@@
 
-\subsection{Evolutionary spike spectrogram of CENOGRID isotope time series}
+\subsection{Evolutionary spike spectrogram of Earth's orbit time series}
 
-%To demonstrate XXXXXX we applied it to the recently published CENOzoic Global Reference
-%benthic foraminifer carbon and oxygen Isotope Dataset (CENOGRID) \cite{Westerhold2020}. 
-%The temperature-dependent fractionation of carbon and oxygen isotopes in benthic foraminifera
-%is an important means to reconstruct past global temperatures and environmental conditions.
-%Moreover, the Cenozoic is interesting, because it provides an analogue of future greenhouse 
-%climate and how and which regime shifts in large-scale atmospheric and ocean circulation 
-%can be expected in the future warming climate. The dataset consists of a detrended $\delta^{18}$O and a detrended $\delta^{13}$C isotope record with a total length
-%of $N=13,421$ samples and a sampling period of $\Delta t= 5,000 \text{yrs}$ (Figure \ref{fig_time_series_cenogrid} in Appendix \ref{sec_appendix_cenogrid}). Here we made predictions 
-%on the $\delta^{13}$C isotope record.
-%
-%We again utilize the Cenozoic Global Reference benthic foraminifer carbon and oxygen Isotope Dataset (CENOGRID) \cite{Westerhold2020}. The time series 
-%have a total length of $N=13,421$ samples and a sampling period of 
-%$\Delta t= 5,000 \text{yrs}$. The records and their corresponding RPs are shown in 
-%Figure~\ref{fig_tauRR_cenogrid_RPs} together with remarkable climate transitions in the Cenozoic (detrended time series in Fig.~\ref{fig_time_series_cenogrid} in 
-%Appendix~\ref{sec_appendix_cenogrid}). Among other things, the large-scale patterns in the RPs shown were used by \textcite{Westerhold2020} to classify major climate 
-%states: Hothouse, Warmhouse, Coldhouse and Icehouse. 
-%
-%\begin{figure}[h!]
-% \centering
-% \includegraphics[width=\textwidth]{./figures/chapter06_tauRR/fig_tauRR_cenogrid_RPs}
-% \caption{\textbf{A} $\delta^{13}$C and \textbf{B} $\delta^{18}$O isotope records and their corresponding RPs (\textbf{C+D}), obtained from the non-embedded time 
-% series under a fixed recurrence threshold corresponding to 8\% global RR. These plots were used by \textcite{Westerhold2020} to classify the major climate states 
-% Hothouse, Warmhouse, Cold- and Icehouse.
-% }
-%\label{fig_tauRR_cenogrid_RPs}
-%\end{figure}
-%
-%
+To demonstrate the usefulness of the proposed inter spike spectrum, we apply it to the freely available eccentricity time series of 
+\citet{Laskar2011}. \todo[inline]{blabla what is this used for usually? etc.} We use a time series which covers the past \mytilde $67$ Mio. years, which a total length
+of $N=13,421$ samples and a sampling period of $\Delta t= 5,000$.
+
 %While in Chapter \ref{chapter:MCDTS}, 
@@
 A novel type of powerspectrum, the \textit{inter spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
-combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution (we chose LASSO). Since there are 
-$M = \sum_{i=1}^{N}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the frequency (or period) the inter spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
-appearance. The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RR's) into their frequency domain. 
+combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution (we chose LASSO or a sequentially 
+thresholded least squares regression STLS). Since there are 
+$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
+of the period (or frequency) the inter spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
+appearance. Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
+appearance of the obtained inter spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
+the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
+
+The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RR's) into their frequency domain. 
 This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
@@
 the number of significant peaks in the inter spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve period-doubling bifurcations. 
+\todo[inline]{Here a quick summary of the other applications.}
 
@@
 spike-train-like data. On the other hand, the inter spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
-When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021} show that 
+When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021,Kraemer2022} show that 
 this reconstruction process can be reliably automated and applied to multivariate data as well. This would allow for a ``running window'' approach, in order to detect transitions. 
@@
 \begin{acknowledgements}
-This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9). All computations have been carried out in the Julia language 
-and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
+This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9). All computations have been carried out in MATLAB\textsuperscript{\textregistered} 
+and the Julia language and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
 \end{acknowledgements}
@@
 The authors declare that they have no conflict of interest.
+
+\section*{Code availability}
+
+The study that we present here is available as a fully reproducible code base
+**Repository will be published and cited here, when accepted** and the method
+will be available in the Julia language **Package will be published and cited here, 
+when accepted** and as a MATLAB\textsuperscript{\textregistered} toolbox 
+**Toolbox will be published and cited here, when accepted**.
 

### 2022-07-12 Manuscript/inter_spike_manuscript.tex
Power Grid application prepared

@@
 
-\subsection{Evolutionary spike spectrogram of Earth's orbit time series}
+\subsection{Inter spike spectra of power grid frequency data}
 
-To demonstrate the usefulness of the proposed inter spike spectrum, we apply it to the freely available eccentricity time series of 
-\citet{Laskar2011}. \todo[inline]{blabla what is this used for usually? etc.} We use a time series which covers the past \mytilde $67$ Mio. years, which a total length
-of $N=13,421$ samples and a sampling period of $\Delta t= 5,000$.
+lalalalalala
+lalalal \\
 
-%While in Chapter \ref{chapter:MCDTS}, 
-%Section \ref{sec_mcdts_cenogrid_prediction} predictions were made for the detrended $\delta^{13}$C record, here the focus is on the analysis of the characteristic time scales 
-%in both, the detrended $\delta^{18}$O and the detrended $\delta^{13}$C isotope records. Specifically, we have computed spike powerspectra of the $\tau$-RR windowed over each record. 
-%Figures~\ref{fig_tauRR_O18_pecuzal},~\ref{fig_tauRR_C13_pecuzal} show that major features of their linear counterparts, namely ordinary FFT spectrograms (A panels), are also present in 
-%these spectrograms. But there is additional information in the spike spectrograms (B panels). Firstly, overall there seem to be less frequencies excited than in the FFT spectrograms, but these 
-%excited frequencies are therefore more pronounced. This is especially apparent in the oxygen isotope record spectrogram (Fig.~\ref{fig_tauRR_O18_pecuzal}), in which the obliquity-related time 
-%scale (\mytilde 41 kyrs) is very prominent from 17-0 Mio yrs BP in the spike spectrogram (panel B). Our spike spectrograms also support the general conlusion given by \textcite{Westerhold2020} 
-%that ``in the Hothouse and Warmhouse climate states, as well as the first Coolhouse phase, eccentricity-related cycles (\mytilde 100 \& \mytilde 405 kyrs) dominate the CENOGRID records, while 
-%after the increasing influence of highlatitude cooling and ice growth during the second Coolhouse phase, the obliquity-band response steadily increases after 13.9 Mio yrs BP (middle Miocene 
-%climate transition) before dominating climate dynamics by \mytilde 5 Mio yrs BP (late Miocene–early Pliocene)''. The spike spectrograms indicate a strong obliquity influence already from 17 
-%Mio yrs BP (the onset of the Miocene Climate optimum). Moreover, in the carbon isotope record based spike spectrogram (Fig.~\ref{fig_tauRR_C13_pecuzal}B) there is a strong influence of the 
-%100-kyr-eccentricity cycle in the first Warmhouse phase from \mytilde 61-56 Mio yrs BP, which is not represented in the FFT-based spectrogram (panel A). 
-%
-%
-%\begin{figure}
-% \centering
-% \includegraphics[width=\textwidth]{./figures/fig_tauRR_O18_pecuzal}
-% \caption{Evolutionary spectrograms based on \textbf{A} FFT powerspectra of the detrended $\delta^{18}$O time series and \textbf{B} 
-% on the spike powerspectra of the 
-% $\tau$-RR of the PECUZAL embedded $\delta^{18}$O record. The spectrograms were computed with a $w = 1,000 (\hat{=}~\text{5-Myr})$ window 
-% and a step $ws=1$. We used the 
-% embedding computed in Chapter~\ref{chapter:MCDTS} (Section~\ref{sec_mcdts_cenogrid_prediction}, see Table~\ref{tab:cenogrid_embedding}) 
-% and a recurrence threshold fixed to 
-% 5\% global RR, in order to ensure comparability within the different windows \cite{kraemer2018} (Chapter~\ref{chapter:threshold}). 
-% Dashed red horizontal lines indicate major climate transitions according to \textcite{Westerhold2020}.
-% }
-%\label{fig_tauRR_O18_pecuzal}
-%\end{figure}
-%
-%\begin{figure}
-% \centering
-% \includegraphics[width=\textwidth]{./figures/fig_tauRR_C13_pecuzal}
-% \caption{Same as in Figure \ref{fig_tauRR_O18_pecuzal}, but for the detrended $\delta^{13}$C isotope record.
-% }
-%\label{fig_tauRR_C13_pecuzal}
-%\end{figure}
-%
-%The shown spike spectrograms in Figs.~\ref{fig_tauRR_O18_pecuzal},~\ref{fig_tauRR_C13_pecuzal} are based on the $\tau$-RR of the respective records, which have been time delay embedded by using 
-%the PECUZAL algorithm \cite{Kraemer2021} (Chapter \ref{chapter:unified}). By construction, we would expect different spike spectrograms, when different embeddings are used. This is indeed the case 
-%as shown in Figures~\ref{fig_tauRR_O18_mcdts},~\ref{fig_tauRR_C13_mcdts},~\ref{fig_tauRR_O18_ne},~\ref{fig_tauRR_C13_ne} (Appendix \ref{appendix_tauRR_spectrograms}), which also show spike 
-%spectrograms, but for an embedding using MCDTS-R-MSE (Chapter~\ref{chapter:MCDTS}, see Table~\ref{tab:cenogrid_embedding}) and for the non-embedded time series. Even though differences are 
-%discernible, the mentioned overall conclusion given by \textcite{Westerhold2020} also holds for these cases.
+lalala\\
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra_lasso_standard_20s}
+ \caption{THIS WILL BE A HIGH-RES FIGURE SOON AND A CAPTION WILL BE ADDED  
+}
+\label{fig_power_spectra_frequency}
+\end{figure}
 

### 2022-07-12 Applications/Kuramoto model/system with switch/compute_emd_system_with_transition.jl

@@ -36,7 +36,7 @@ spectrum_fft = readdlm("./Applications/Kuramoto model/system with switch/results
 spectrum_fft_t = readdlm("./Applications/Kuramoto model/system with switch/results/results_kuramoto_switch_fft_spectrum_t_no_noise.csv")
 
 
-N, M = size(spectrum1)
+N, M = size(spectrum1t)
 
 # standardize FFT-spectra to probabilities
 for j = 1:N

### 2022-07-12 Applications/Power Grid/CE and GB frequencies/compute_embedding_parameters.jl

@@ -1,0 +1,21 @@
+# Here we compute the optimal embedding parameters for the Vostok data
+
+using DelayEmbeddings
+using TreeEmbedding  # this will be merged into DelayEmbeddings soon
+using DelimitedFiles
+using Random
+
+## Downsampled frequency data
+f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled.csv"))
+f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled.csv"))
+
+# Cao Embedding
+w = estimate_delay(f_ce[1:14400], "mi_min", 0:150)
+D_ce, τ_ce, E_ce = optimal_traditional_de(f_ce[1:14400], "ifnn", "mi_min"; τs, w)
+
+w = estimate_delay(f_gb[1:14400], "mi_min", 0:150)
+D_gb, τ_gb, E_gb = optimal_traditional_de(f_gb[1:14400], "ifnn", "mi_min"; τs, w)
+
+# out Cao
+# D_ce = 7, τ_ce = 19 
+# D_gb = 7, τ_gb = 17

### 2022-07-12 Applications/Power Grid/CE and GB frequencies/compute_fft_spectrogram_downsampled.m

@@ -8,8 +8,8 @@ f_gb = load("./data/frequencies_gb.mat").frequencies_gb;
 T_ce = 0.2; % sampling time in secs
 T_gb = 1;
 
-T_ce_ds = 60; % new sampling time
-T_gb_ds = 60;
+T_ce_ds = 20; % new sampling time
+T_gb_ds = 20;
 
 factor_ce = 1/T_ce * T_ce_ds;
 factor_gb = 1/T_gb * T_gb_ds;
@@ -44,7 +44,7 @@ L_gb = length(f_gb);
 L_block_ce = 1440; % block length covering one full day (24 hours)
 L_block_gb = 1440;
 
-t_ce = (0:L_block_ce-1)*T_ce; % time vector
+t_ce = (0:L_block_ce-1)*T_ce; % time vector for block
 t_gb = (0:L_block_gb-1)*T_gb;
 
 fs_ce= Fs_ce*(0:(L_block_ce/2))*60/L_block_ce; % frequency vector
@@ -64,22 +64,96 @@ spec_gb = mean(spectrum_gb,2);
 
 %% Plotting
 
+% iss_spec_ce = load("./data/iss_spec_ce_cao_0_8_0_5.csv");
+% iss_spec_gb = load("./data/iss_spec_gb_cao_0_8_0_5.csv");
+% iss_spec_ce = load("./data/iss_spec_ce_hegger_0_8_0_5.csv");
+% iss_spec_gb = load("./data/iss_spec_gb_hegger_0_8_0_5.csv");
+% iss_spec_ce = load("./data/iss_spec_ce_hegger_0_9_0_5.csv");
+% iss_spec_gb = load("./data/iss_spec_gb_hegger_0_9_0_5.csv");
+% iss_spec_ce = load("./data/iss_spec_ce_standard_60_0_9_0_5.csv");
+% iss_spec_gb = load("./data/iss_spec_gb_standard_60_0_9_0_5.csv");
+% iss_spec_ce = load("./data/iss_spec_ce_cao_60_0_95_0_8.csv");
+% iss_spec_gb = load("./data/iss_spec_gb_cao_60_0_95_0_8.csv");
+% iss_spec_ce = load("./data/iss_spec_ce_cao_60_0_99_0_8.csv");
+% iss_spec_gb = load("./data/iss_spec_gb_cao_60_0_99_0_8.csv");
+% iss_spec_ce = load("./data/iss_spec_ce_cao_STLS_60_0_95_0_8.csv");
[…]

### 2022-07-12 Applications/Power Grid/CE and GB frequencies/compute_iss_spectrogram_downsampled.jl

@@ -1,0 +1,118 @@
+using DelayEmbeddings
+using TreeEmbedding  # this will be merged into DelayEmbeddings soon
+using DelimitedFiles
+using Random
+using InterSpikeSpectra
+using RecurrenceAnalysis
+using Statistics
+
+## Downsampled frequency data
+f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled.csv"))
+f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled.csv"))
+
+# f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled_30s.csv"))
+# f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled_30s.csv"))
+
+T_ce = 60 # sampling time in secs
+T_gb = 60
+
+# T_ce = 30 # sampling time in secs
+# T_gb = 30
+
+L_block_ce = 1440 # block length covering one full day (24 hours)
+L_block_gb = 1440
+
+# L_block_ce = 2880 # block length covering one full day (24 hours)
+# L_block_gb = 2880
+
+rho = 0.95
+epsilon = 0.08
+τs = 0:150
+tau_window = 200
+
+spec_ce, d_ce, taus_ce = iss_spec(f_ce, L_block_ce, τs, epsilon, tau_window, rho; embed_method="afnn")
+avrg_spec_ce = [mean(spec_ce[i,:]) for i = 1:size(spec_ce,1)]
+
+spec_gb, d_gb, taus_gb = iss_spec(f_gb, L_block_gb, τs, epsilon, tau_window, rho; embed_method="afnn")
+avrg_spec_gb = [mean(spec_gb[i,:]) for i = 1:size(spec_gb,1)]
+
+writedlm("./Applications/Power Grid/CE and GB frequencies/data/iss_spec_ce_cao_STLS_60_0_95_0_8.csv", avrg_spec_ce)
+writedlm("./Applications/Power Grid/CE and GB frequencies/data/iss_spec_gb_cao_STLS_60_0_95_0_8.csv", avrg_spec_gb)
+
+using PyPlot
+pygui(true)
+
+figure()
+subplot(211)
+plot(1:100, avrg_spec_ce[1:100])
+grid()
+subplot(212)
[…]

### 2022-07-14 Manuscript/inter_spike_manuscript.tex
add frequency part

@@
 \usepackage{mathtools}
+\usepackage{siunitx}
 \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
@@
 		Frank Hellmann \and
+		Mehrnaz Anvari \and
         J\"urgen Kurths \and 
@@
 
-lalalalalala
-lalalal \\
+Power grids are a large synchronized complex network that modern societies are depend on the stable functionality of them.
+To maintain the stability of a power grid, the balance between the energy consumption and energy production should be provided.
+In an AC-power grid, the grid frequency is an observable variable that reflects how well this balance is satisfied.
+Thereby, the grid frequency and, indeed its variations over the nominal frequency (which is $50$ \si{Hz} in Europe and many parts of the world, or $60$ \si{Hz} in the Americas, Southern Japan and some other
+regions) is continuously recorded and monitored by grid operators.
+For instance, in the case that there is more (less) demand than supply, the grid frequency decreases (increases) form nominal frequency \cite{}.
+\\
 
-lalala\\
+The frequency variations can include other information, such as the functionality of control systems \cite{}, the effect of fluctuations in
+renewable energies (REs) and demands on the grid \cite{} and, moreover, the effect of regular dispatches due to the trading market \cite{}.
+The latter induce periodic frequency jumps.
+The frequency trajectory for the Great Britain (GB) grid Continental Europe (CE) grid shown in Fig.~\ref{} demonstrates clear jumps every hour {\color{red} (maybe we should add this figure and one from auto-correlation or $\tau$-RP)}.
+Moreover, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{}).
+These peaks are caused by a mismatch of power
+supply and demand \cite{} during dispatches. In most electricity grids the
+operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
+might exist. Hence\\
+
 \begin{figure}
@@
 \bibliographystyle{spbasic} 
-\bibliography{inter_spike_bib}
+\bibliography{in\\
+	pike_bib}
 

### 2022-07-14 Manuscript/inter_spike_manuscript.tex
correction to frequency part
add references

@@
 regions) is continuously recorded and monitored by grid operators.
-For instance, in the case that there is more (less) demand than supply, the grid frequency decreases (increases) form nominal frequency \cite{}.
+For instance, in the case that there is more (less) demand than supply, the grid frequency decreases (increases) form nominal frequency \cite{kundur1994power}.
 \\
 
-The frequency variations can include other information, such as the functionality of control systems \cite{}, the effect of fluctuations in
-renewable energies (REs) and demands on the grid \cite{} and, moreover, the effect of regular dispatches due to the trading market \cite{}.
+The frequency variations can include other information, such as the functionality of control systems \cite{gorjao2020data}, the effect of fluctuations in
+renewable energies (REs) and demands on the grid \cite{anvari2020stochastic} and, moreover, the effect of regular dispatches due to the trading market \cite{meyer2020identifying}.
 The latter induce periodic frequency jumps.
@@
 These peaks are caused by a mismatch of power
-supply and demand \cite{} during dispatches. In most electricity grids the
+supply and demand \cite{weissbach2009high} during dispatches. In most electricity grids the
 operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
-might exist. Hence\\
+might exist. Looking at the frequency spectrum in Fig.~\ref{}, however does not display sharp peaks exactly at $30$ and $60$ \si{min}. \\
+
+{\color{red} Now we should start the story of Inter-spike-spectrum}.
 

### 2022-07-15 Manuscript/inter_spike_manuscript.tex
Power Grid: spelling

--- 2022-07-12 Manuscript/inter_spike_manuscript.tex
@@
 
-lalalalalala
-lalalal \\
+Power grids are large, synchronized, complex networks whose stable functioning is indispensable for modern societies.
+To maintain the stability of a power grid, the balance between energy consumption and energy generation must be ensured. 
+In an AC-power grid, the grid frequency is an observable variable that reflects how well this balance is satisfied. 
+In this process, the grid frequency and its deviations from the nominal frequency are continuously recorded and monitored by 
+the grid operators (in Europe and many parts of the world this is $50$ \si{Hz} or $60$ \si{Hz} in America and, for example, southern Japan).
+For example, if there is more (less) demand than supply supply, the network frequency decreases (increases) compared to the nominal frequency \cite{kundur1994power}.
+\\
+The frequency variations can include other information, such as the functionality of control systems \cite{gorjao2020data}, the effect of fluctuations in
+renewable energies (REs), demands on the grid \cite{anvari2020stochastic} and, moreover, the effect of regular dispatches due to the trading market 
+\cite{meyer2020identifying}. The latter induce periodic frequency jumps. The frequency trajectory for the Great Britain (GB) and Continental Europe (CE) 
+grid shown in Fig.~\ref{} demonstrates clear jumps every hour \todo[inline]{(maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. 
+Furthermore, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{}). These peaks are caused by a mismatch of power 
+supply and demand \cite{weissbach2009high} during dispatches. In most electricity grids the
+operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
+might exist. Looking at the frequency spectrum in Fig.~\ref{}, however, does not display sharp peaks exactly at $30$ and $60$ \si{min}. \\
 
-lalala\\
+\todo[inline]{Now we should start the story of Inter-spike-spectrum}.
+
 \begin{figure}

### 2022-07-15 Manuscript/inter_spike_manuscript.tex
Power grid: proper Figures added

@@
 \cite{meyer2020identifying}. The latter induce periodic frequency jumps. The frequency trajectory for the Great Britain (GB) and Continental Europe (CE) 
-grid shown in Fig.~\ref{} demonstrates clear jumps every hour \todo[inline]{(maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. 
-Furthermore, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{}). These peaks are caused by a mismatch of power 
+grid shown in Fig.~\ref{fig_power_grid_time_series} demonstrates clear jumps every hour \todo[inline]{(maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. 
+Furthermore, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{fig_power_grid_spectra}). These peaks are caused by a mismatch of power 
 supply and demand \cite{weissbach2009high} during dispatches. In most electricity grids the
 operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
-might exist. Looking at the frequency spectrum in Fig.~\ref{}, however, does not display sharp peaks exactly at $30$ and $60$ \si{min}. \\
+might exist. Looking at the frequency spectrum in Fig.~\ref{fig_power_grid_spectra}, however, does not display sharp peaks exactly at $30$ and $60$ \si{min}. \\
 
@@
  \centering
- \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra_lasso_standard_20s}
- \caption{THIS WILL BE A HIGH-RES FIGURE SOON AND A CAPTION WILL BE ADDED  
-}
-\label{fig_power_spectra_frequency}
+ \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra}
+ \caption{CAPTION WILL BE ADDED}
+\label{fig_power_grid_spectra}
 \end{figure}
@@
 
+\subsection{Power grid frequency time series}\label{sec_power_grid_appendix}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
+ \caption{CAPTION WILL BE ADDED}
+\label{fig_power_grid_time_series}
+\end{figure}
+
 % BibTeX users please use one of

### 2022-07-15 Applications/Power Grid/CE and GB frequencies/compute_fft_spectrogram_downsampled.m

@@ -1,14 +1,17 @@
+% In this script we 1) downsample the original data and 2) compute
+% FFT-spectrograms on these downsampled time series.
+
 clear, clc
 
 f_ce = load("./data/frequencies_ce.mat").frequencies_ce;
 f_gb = load("./data/frequencies_gb.mat").frequencies_gb;
 
-%% Downsample to a sampling time of one minute
+%% Downsample to a sampling time of one minute/ 20 sec / 30 sec
 
-T_ce = 0.2; % sampling time in secs
+T_ce = 0.2; % original sampling time in secs
 T_gb = 1;
 
-T_ce_ds = 20; % new sampling time
+T_ce_ds = 20; % new sampling time 20 s
 T_gb_ds = 20;
 
 factor_ce = 1/T_ce * T_ce_ds;
@@ -23,13 +26,6 @@ L_gb_ds = length(f_gb_ds);
 t_ce = (0:L_ce_ds-1)*T_ce_ds; % time vector
 t_gb = (0:L_gb_ds-1)*T_gb_ds;
 
-% % checking
-% subplot(211)
-% plot(t_ce(1:21000), f_ce(1:21000), '.-')
-% grid on
-% subplot(212)
-% plot(t_ce_ds(1:21000/factor_ce), f_ce_ds(1:21000/factor_ce), '.-')
-% grid on
 
 %% Short time FFT
 
@@ -41,8 +37,8 @@ Fs_gb = 1/T_gb;
 L_ce = length(f_ce); % length of signal
 L_gb = length(f_gb);
 
-L_block_ce = 1440; % block length covering one full day (24 hours)
-L_block_gb = 1440;
+L_block_ce = 4320; % block length covering one full day (24 hours)
+L_block_gb = 4320;
 
 t_ce = (0:L_block_ce-1)*T_ce; % time vector for block
 t_gb = (0:L_block_gb-1)*T_gb;
@@ -62,98 +58,14 @@ toc
 spec_ce = mean(spectrum_ce,2);
 spec_gb = mean(spectrum_gb,2);
 
-%% Plotting
+%% Save results 
 
-% iss_spec_ce = load("./data/iss_spec_ce_cao_0_8_0_5.csv");
-% iss_spec_gb = load("./data/iss_spec_gb_cao_0_8_0_5.csv");
[…]

### 2022-07-15 Applications/Power Grid/CE and GB frequencies/plot_frequency_results.m

@@ -1,0 +1,128 @@
+% We plot the downsampled time series 
+% (computed in `compute_fft_spectrogram_downsampled`), the FFT-spectrograms 
+% (computed in `compute_fft_spectrogram_downsampled`) and the according ISS 
+% (computed in `compute_iss_spectrogram_downsampled.jl`).
+
+clear, clc
+
+%% Load the computed data
+
+% (downsampled) time series (computed in `compute_fft_spectrogram_downsampled`)
+f_ce = load("./data/frequencies_ce_downsampled_20s.csv");
+f_gb = load("./data/frequencies_gb_downsampled_20s.csv");
+
+% FFT spec (computed in `compute_fft_spectrogram_downsampled`)
+spec_ce = load("./data/fft_spec_ce.csv");
+spec_gb = load("./data/fft_spec_gb.csv");
+
+% ISS spec (computed in `compute_iss_spectrogram_downsampled.jl`)
+iss_spec_ce = load("./data/iss_spec_ce_standard_20_0_95_0_8.csv");
+iss_spec_gb = load("./data/iss_spec_gb_standard_20_0_95_0_8.csv");
+
+%% Set time and frequency vectors
+
+dt_s = 20; % sampling time is sec
+dt_m = 1/ (60/dt_s);
+
+% time/period vector for ISS 
+N = length(iss_spec_ce);
+t = (1:N)*dt_m;
+
+% time/period/frequency vector for FFT spectrogram
+Fs_ce = 60/dt_s; % sampling frequency min^-1
+Fs_gb = 60/dt_s;
+
+L_block_ce = 4320; % block length covering one full day (24 hours, 60/dt_s * 60 * 24))
+L_block_gb = 4320;
+
+t_ce = (0:L_block_ce-1)*dt_m; % time vector for block in min
+t_gb = (0:L_block_gb-1)*dt_m;
+
+fs_ce= Fs_ce*(0:(L_block_ce/2))/L_block_ce; % frequency vector in min^1
+fs_gb= Fs_gb*(0:(L_block_gb/2))/L_block_gb;
+
+%% Plotting
+
+font = 22; % fontsize
+lw1 = 2.5;
+lw2 = 2;
+
+
+figure('Units','normalized','Position',[.001 .001 .999 .999])
+subplot(221)
[…]

### 2022-07-15 Manuscript/inter_spike_manuscript.tex
Changes in manuscript: Comments version 1

@@
 
-\institute{K. Hauke Kraemer \and J\"urgen Kurths \and Norbert Marwan \and Frank Hellmann \at Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, 
+\institute{K.
+Hauke Kraemer \and J\"urgen Kurths \and Norbert Marwan \and Frank Hellmann \and Mehrnaz Anvari \at Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam,
 Germany \email{hkraemer@pik-potsdam.de}\and
@@
 $\vec{x}_i = \vec{x}(\Delta t \cdot i),\, i=1,\ldots,N$. 
-\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
+\cite{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
 ``generalized'' powerspectrum can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 
@@
  \textbf{D} Subset of the recurrence plot and the corresponding $\tau$-recurrence rate obtained from the state space trajectory in \textbf{C}.
-The shaded interval in the time series in \textbf{A} corresponds to the shown subset.
+\sout{The shaded interval in the time series in \textbf{A} corresponds to the shown subset.}
  \textbf{E} Fourier Power spectrum obtained from the $\tau$-recurrence (subset shown in panel \textbf{D}) \cite{Zbilut2008}.
+\todo[inline]{\textbf{D} and \textbf{E} show the results of a part of the time series in \textbf{A} which is highlighted in pink.
+}\todo[inline]{I think Fig.~\ref{fig_tau_rr_spectrum_example} should be restructured.
+We could talk about it.}
  }\label{fig_tau_rr_spectrum_example}
@@
 any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
-FT. In Section \ref{sec_tau_rr_application} we exemplify its use when transforming the $\tau$-RR of a system under study. In this case, the inter spike spectrum can unravel 
-characteristic time scales of high dimensional systems, which is not possible when using a FT.
+FT.
+In Section \ref{sec_tau_rr_application} we exemplify \sout{its use} \todo{the usage of inter spike spectrum} when transforming the $\tau$-RR of a system under study.
+In this case, the inter spike spectrum can unravel
+characteristic time scales of high dimensional systems, which is not possible when using a FT. \todo{Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized}
 
@@
 
-The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal -- 
+The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal \todo{what do you mean with any signal?
+do you mean to look at data set instead of $\tau$-RP or RP?}--
 is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
-different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform with length $N$ and 
+different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal \todo{which} we want to transform. \sout{with}\todo{The signal has} length $N$ and 
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
@@
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure)
+(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure) \todo{$T$ in the following eqs.
+should not be $T_{is}$ to be consistent with the text?}\todo{$n$ in eq.6 is not clear for me}
 \begin{align}
@@
 Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
-Furthermore, there will be identical basis functions and also basis functions, which do not allow for a unambiguous inter spike period, 
+Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter spike period, 
 if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
@@
 
-In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the proposed method must also deal with the free choice of the regression regularization parameter $\alpha$, 
+In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the proposed method \todo{which method?
+STLS?}must also deal with the free choice of the regression regularization parameter $\alpha$,
 which determines the sparsity of the regression coefficient vector $\hat{\bf{\beta}}$. Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small, 
@@
 On the other hand, only a sparse number
-of non-zero loadings in $\hat{\bf{\beta}}$ -- \textit{aka} peaks in the inter spike spectrum -- are obtained when $\alpha$ is sufficiently large. In this paper we select $\alpha$ such that the 
+of non-zero loadings in $\hat{\bf{\beta}}$ -- \textit{aka} \todo{what is aka?}peaks in the inter spike spectrum -- are obtained when $\alpha$ is sufficiently large.
+In this paper we select $\alpha$ such that the
 re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\bf{\beta}}$ matches a given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.
@@
 identify the type of dynamics.
-We set the parameters $b=2$, $c=4$ and analyze period-2 limit cycle dynamics ($a=0.36$, Fig.~\ref{fig_tau_rr_example_roessler}A, D, G, J), 
-period-3 limit cycle dynamics ($a=0.41$, Fig.~\ref{fig_tau_rr_example_roessler}B, E, H, K) and chaotic dynamics ($a=0.428$, Fig.~\ref{fig_tau_rr_example_roessler}C, F, I, L).
+We set the parameters $b=2$, $c=4$ and analyze period-2 limit cycle dynamics ($a=0.36$ in Fig.~\ref{fig_tau_rr_example_roessler}A, D, G, J), 
+period-3 limit cycle dynamics ($a=0.41$ in Fig.~\ref{fig_tau_rr_example_roessler}B, E, H, K) and chaotic dynamics ($a=0.428$ in Fig.~\ref{fig_tau_rr_example_roessler}C, F, I, L).
 
@@
  \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
- Trajectory of the system in a \textbf{A} period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
+ \textbf{A} Trajectory of the system in a period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
  \textbf{C} in a chaotic regime (parameter $a=0.428$). 
@@
   \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
- }
+\todo[inline]{why you have not used STLS method here?} }
 \label{fig_tau_rr_example_roessler}
@@
  \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise. The appearance of the inter spike spectra 
- in \textbf{J, K, L} and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise noise.
- }
+ in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.
+\todo[inline]{Where do you add the additive noise?
+for all components, i.e.
+x, y and z?
+What is the take home message of this figure?
+In your abstract you mention that " The proposed measure is robust to noise and is able to detect and analyze bifurcations." but then here there is also no noise effect on FFT.
+So please make clear the main message of this figure.
+ }}
 \label{fig_tau_rr_example_roessler_noise}
@@
 \end{align}
-For producing Figs.~\ref{fig_tau_rr_example_roessler_noise},~\ref{fig_tau_rr_example_roessler} the initial condition for producing panels \textbf{A} \& \textbf{B} was set to $u_0=[.7, -1, 0.4]$ with a sampling time
-of $dt=0.05$ and in case of panel \textbf{C} $u_0=[-0.1242, -2.5415, 0.2772]$ with a sampling time of $dt=0.1$.
+For producing Figs.~\ref{fig_tau_rr_example_roessler_noise} and ~\ref{fig_tau_rr_example_roessler}, the initial condition for producing panels \textbf{A} \& \textbf{B} was set to $u_0=[.7, -1, 0.4]$ with a sampling time
+of $dt=0.05$ and in case of panel \textbf{C}, $u_0=[-0.1242, -2.5415, 0.2772]$ with a sampling time of $dt=0.1$.
 The first $5,000$ samples were discarded as transients and trajectories of length $N=5,000$ were

### 2022-07-19 Manuscript/MDPI_template/template.tex
Prepare for entropy journal

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[entropy,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{mathptmx}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{siunitx}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Spike spectra for recurrences}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Spike spectra for recurrences}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-9943-5391} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1,4}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{K. Hauke Kraemer, Frank Hellmann, Mehrnaz Anvari, J\"urgen Kurths and Norbert Marwan}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Kraemer, K.H..; Hellmann, F.; Anvari M.; Kurths, J.; Marwan, N.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
$^{3}$ \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany\\
$^{4}$ \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany}

% Contact information of the corresponding author
\corres{Correspondence: hkraemer@pik-potsdam.de; marwan@pik-potsdam.de}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
We invent this instructive approach with the 
idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}

% Keywords
\keyword{Decomposition; Frequency Analysis; Recurrence Analysis; Bifurcations}
\PACS{05.45.Tp, 05.90.+m, 89.90.+n, 02.70.Uu, 05.10.Ln, 05.45.-a, 05.45.Ac}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.

% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}
\unskip

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
			Entry 1		& Data			& Data			& Data\\
			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. If the study did not report any data, you might add ``Not applicable'' here.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the~results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-07-19 Manuscript/inter_spike_manuscript.tex
Prepare for entropy journal

@@
 $\vec{x}_i = \vec{x}(\Delta t \cdot i),\, i=1,\ldots,N$. 
-\cite{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
+\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
 ``generalized'' powerspectrum can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 

### 2022-07-20 Manuscript/Definitions/journalnames.tex
Switched format for entropy journal (MDPI)

%%Updated on 29 June 2022
%,% Website Name,%,%,% Website Name,%%,% Full Name,%%,% Short Name,%%,% DOI abbr,%%,% ISSN,% \continuouspages
%\DeclareOption{}{\gdef\@journal{}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{acoustics}{\gdef\@journal{acoustics}\gdef\@journalfull{Acoustics}\gdef\@journalshort{Acoustics}\gdef\@doiabbr{acoustics}\gdef\@ISSN{2624-599X}\gdef\@continuouspages{yes}}
\DeclareOption{actuators}{\gdef\@journal{actuators}\gdef\@journalfull{Actuators}\gdef\@journalshort{Actuators}\gdef\@doiabbr{act}\gdef\@ISSN{2076-0825}}
\DeclareOption{addictions}{\gdef\@journal{addictions}\gdef\@journalfull{Addictions}\gdef\@journalshort{Addictions}\gdef\@doiabbr{}\gdef\@ISSN{0006-0006}}
\DeclareOption{admsci}{\gdef\@journal{admsci}\gdef\@journalfull{Administrative Sciences}\gdef\@journalshort{Adm. Sci.}\gdef\@doiabbr{admsci}\gdef\@ISSN{2076-3387}}
\DeclareOption{adolescents}{\gdef\@journal{adolescents}\gdef\@journalfull{Adolescents}\gdef\@journalshort{Adolescents}\gdef\@doiabbr{adolescents}\gdef\@ISSN{2673-7051}\gdef\@continuouspages{yes}}
\DeclareOption{aerospace}{\gdef\@journal{aerospace}\gdef\@journalfull{Aerospace}\gdef\@journalshort{Aerospace}\gdef\@doiabbr{aerospace}\gdef\@ISSN{2226-4310}}
\DeclareOption{agriculture}{\gdef\@journal{agriculture}\gdef\@journalfull{Agriculture}\gdef\@journalshort{Agriculture}\gdef\@doiabbr{agriculture}\gdef\@ISSN{2077-0472}}
\DeclareOption{agriengineering}{\gdef\@journal{agriengineering}\gdef\@journalfull{AgriEngineering}\gdef\@journalshort{AgriEngineering}\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}\gdef\@continuouspages{yes}}
\DeclareOption{agrochemicals}{\gdef\@journal{agrochemicals}\gdef\@journalfull{Agrochemicals}\gdef\@journalshort{Agrochemicals}\gdef\@doiabbr{agrochemicals}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{agronomy}{\gdef\@journal{agronomy}\gdef\@journalfull{Agronomy}\gdef\@journalshort{Agronomy}\gdef\@doiabbr{agronomy}\gdef\@ISSN{2073-4395}}
\DeclareOption{ai}{\gdef\@journal{ai}\gdef\@journalfull{AI}\gdef\@journalshort{AI}\gdef\@doiabbr{ai}\gdef\@ISSN{2673-2688}\gdef\@continuouspages{yes}}
\DeclareOption{air}{\gdef\@journal{air}\gdef\@journalfull{Air}\gdef\@journalshort{Air}\gdef\@doiabbr{air}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{algorithms}{\gdef\@journal{algorithms}\gdef\@journalfull{Algorithms}\gdef\@journalshort{Algorithms}\gdef\@doiabbr{a}\gdef\@ISSN{1999-4893}}
\DeclareOption{allergies}{\gdef\@journal{allergies}\gdef\@journalfull{Allergies}\gdef\@journalshort{Allergies}\gdef\@doiabbr{allergies}\gdef\@ISSN{2313-5786}}
\DeclareOption{alloys}{\gdef\@journal{alloys}\gdef\@journalfull{Alloys}\gdef\@journalshort{Alloys}\gdef\@doiabbr{alloys}\gdef\@ISSN{2674-063X}\gdef\@continuouspages{yes}}
\DeclareOption{analytica}{\gdef\@journal{analytica}\gdef\@journalfull{Analytica}\gdef\@journalshort{Analytica}\gdef\@doiabbr{analytica}\gdef\@ISSN{2673-4532}\gdef\@continuouspages{yes}}
\DeclareOption{analytics}{\gdef\@journal{analytics}\gdef\@journalfull{Analytics}\gdef\@journalshort{Analytics}\gdef\@doiabbr{analytics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{anatomia}{\gdef\@journal{anatomia}\gdef\@journalfull{Anatomia}\gdef\@journalshort{Anatomia}\gdef\@doiabbr{anatomia}\gdef\@ISSN{2813-0545}\gdef\@continuouspages{yes}}
\DeclareOption{animals}{\gdef\@journal{animals}\gdef\@journalfull{Animals}\gdef\@journalshort{Animals}\gdef\@doiabbr{ani}\gdef\@ISSN{2076-2615}}
\DeclareOption{antibiotics}{\gdef\@journal{antibiotics}\gdef\@journalfull{Antibiotics}\gdef\@journalshort{Antibiotics}\gdef\@doiabbr{antibiotics}\gdef\@ISSN{2079-6382}}
\DeclareOption{antibodies}{\gdef\@journal{antibodies}\gdef\@journalfull{Antibodies}\gdef\@journalshort{Antibodies}\gdef\@doiabbr{antib}\gdef\@ISSN{2073-4468}}
\DeclareOption{antioxidants}{\gdef\@journal{antioxidants}\gdef\@journalfull{Antioxidants}\gdef\@journalshort{Antioxidants}\gdef\@doiabbr{antiox}\gdef\@ISSN{2076-3921}}
\DeclareOption{applbiosci}{\gdef\@journal{applbiosci}\gdef\@journalfull{Applied Biosciences}\gdef\@journalshort{Appl. Biosci.}\gdef\@doiabbr{applbiosci}\gdef\@ISSN{2813-0464}\gdef\@continuouspages{yes}}
\DeclareOption{appliedchem}{\gdef\@journal{appliedchem}\gdef\@journalfull{AppliedChem}\gdef\@journalshort{AppliedChem}\gdef\@doiabbr{appliedchem}\gdef\@ISSN{2673-9623}\gdef\@continuouspages{yes}}
\DeclareOption{appliedmath}{\gdef\@journal{appliedmath}\gdef\@journalfull{AppliedMath}\gdef\@journalshort{AppliedMath}\gdef\@doiabbr{appliedmath}\gdef\@ISSN{2673-9909}\gdef\@continuouspages{yes}}
\DeclareOption{applmech}{\gdef\@journal{applmech}\gdef\@journalfull{Applied Mechanics}\gdef\@journalshort{Appl. Mech.}\gdef\@doiabbr{applmech}\gdef\@ISSN{2673-3161}\gdef\@continuouspages{yes}}
\DeclareOption{applmicrobiol}{\gdef\@journal{applmicrobiol}\gdef\@journalfull{Applied Microbiology}\gdef\@journalshort{Appl. Microbiol.}\gdef\@doiabbr{applmicrobiol}\gdef\@ISSN{2673-8007}\gdef\@continuouspages{yes}}
\DeclareOption{applnano}{\gdef\@journal{applnano}\gdef\@journalfull{Applied Nano}\gdef\@journalshort{Appl. Nano}\gdef\@doiabbr{applnano}\gdef\@ISSN{2673-3501}\gdef\@continuouspages{yes}}
\DeclareOption{applsci}{\gdef\@journal{applsci}\gdef\@journalfull{Applied Sciences}\gdef\@journalshort{Appl. Sci.}\gdef\@doiabbr{app}\gdef\@ISSN{2076-3417}}
\DeclareOption{aquacj}{\gdef\@journal{aquacj}\gdef\@journalfull{Aquaculture Journal}\gdef\@journalshort{Aquac. J.}\gdef\@doiabbr{aj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{architecture}{\gdef\@journal{architecture}\gdef\@journalfull{Architecture}\gdef\@journalshort{Architecture}\gdef\@doiabbr{architecture}\gdef\@ISSN{2673-8945}\gdef\@continuouspages{yes}}
\DeclareOption{arm}{\gdef\@journal{arm}\gdef\@journalfull{Advances in Respiratory Medicine}\gdef\@journalshort{Adv. Respir. Med.}\gdef\@doiabbr{arm}\gdef\@ISSN{2543-6031}\gdef\@continuouspages{yes}}
\DeclareOption{arts}{\gdef\@journal{arts}\gdef\@journalfull{Arts}\gdef\@journalshort{Arts}\gdef\@doiabbr{arts}\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{\gdef\@journal{asc}\gdef\@journalfull{Automatic Systems and Control}\gdef\@journalshort{Autom. Syst. Control}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{asi}{\gdef\@journal{asi}\gdef\@journalfull{Applied System Innovation}\gdef\@journalshort{Appl. Syst. Innov.}\gdef\@doiabbr{asi}\gdef\@ISSN{2571-5577}}
\DeclareOption{astronomy}{\gdef\@journal{astronomy}\gdef\@journalfull{Astronomy}\gdef\@journalshort{Astronomy}\gdef\@doiabbr{astronomy}\gdef\@ISSN{2674-0346}\gdef\@continuouspages{yes}}
\DeclareOption{atmosphere}{\gdef\@journal{atmosphere}\gdef\@journalfull{Atmosphere}\gdef\@journalshort{Atmosphere}\gdef\@doiabbr{atmos}\gdef\@ISSN{2073-4433}}
\DeclareOption{atoms}{\gdef\@journal{atoms}\gdef\@journalfull{Atoms}\gdef\@journalshort{Atoms}\gdef\@doiabbr{atoms}\gdef\@ISSN{2218-2004}}
\DeclareOption{audiolres}{\gdef\@journal{audiolres}\gdef\@journalfull{Audiology Research}\gdef\@journalshort{Audiol. Res.}\gdef\@doiabbr{audiolres}\gdef\@ISSN{2039-4349}\gdef\@continuouspages{yes}}
\DeclareOption{automation}{\gdef\@journal{automation}\gdef\@journalfull{Automation}\gdef\@journalshort{Automation}\gdef\@doiabbr{automation}\gdef\@ISSN{2673-4052}\gdef\@continuouspages{yes}}
\DeclareOption{axioms}{\gdef\@journal{axioms}\gdef\@journalfull{Axioms}\gdef\@journalshort{Axioms}\gdef\@doiabbr{axioms}\gdef\@ISSN{2075-1680}}
\DeclareOption{bacteria}{\gdef\@journal{bacteria}\gdef\@journalfull{Bacteria}\gdef\@journalshort{Bacteria}\gdef\@doiabbr{bacteria}\gdef\@ISSN{2674-1334}\gdef\@continuouspages{yes}}
\DeclareOption{batteries}{\gdef\@journal{batteries}\gdef\@journalfull{Batteries}\gdef\@journalshort{Batteries}\gdef\@doiabbr{batteries}\gdef\@ISSN{2313-0105}}
\DeclareOption{bdcc}{\gdef\@journal{bdcc}\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@journalshort{Big Data Cogn. Comput.}\gdef\@doiabbr{bdcc}\gdef\@ISSN{2504-2289}}
\DeclareOption{behavsci}{\gdef\@journal{behavsci}\gdef\@journalfull{Behavioral Sciences}\gdef\@journalshort{Behav. Sci.}\gdef\@doiabbr{bs}\gdef\@ISSN{2076-328X}}
\DeclareOption{beverages}{\gdef\@journal{beverages}\gdef\@journalfull{Beverages}\gdef\@journalshort{Beverages}\gdef\@doiabbr{beverages}\gdef\@ISSN{2306-5710}}
\DeclareOption{biochem}{\gdef\@journal{biochem}\gdef\@journalfull{BioChem}\gdef\@journalshort{BioChem}\gdef\@doiabbr{biochem}\gdef\@ISSN{2673-6411}\gdef\@continuouspages{yes}}
\DeclareOption{bioengineering}{\gdef\@journal{bioengineering}\gdef\@journalfull{Bioengineering}\gdef\@journalshort{Bioengineering}\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}}
\DeclareOption{biologics}{\gdef\@journal{biologics}\gdef\@journalfull{Biologics}\gdef\@journalshort{Biologics}\gdef\@doiabbr{biologics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biology}{\gdef\@journal{biology}\gdef\@journalfull{Biology}\gdef\@journalshort{Biology}\gdef\@doiabbr{biology}\gdef\@ISSN{2079-7737}}
\DeclareOption{biomass}{\gdef\@journal{biomass}\gdef\@journalfull{Biomass}\gdef\@journalshort{Biomass}\gdef\@doiabbr{biomass}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomechanics}{\gdef\@journal{biomechanics}\gdef\@journalfull{Biomechanics}\gdef\@journalshort{Biomechanics}\gdef\@doiabbr{biomechanics}\gdef\@ISSN{2673-7078}\gdef\@continuouspages{yes}}
\DeclareOption{biomed}{\gdef\@journal{biomed}\gdef\@journalfull{BioMed}\gdef\@journalshort{BioMed}\gdef\@doiabbr{biomed}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomedicines}{\gdef\@journal{biomedicines}\gdef\@journalfull{Biomedicines}\gdef\@journalshort{Biomedicines}\gdef\@doiabbr{biomedicines}\gdef\@ISSN{2227-9059}}
\DeclareOption{biomedinformatics}{\gdef\@journal{biomedinformatics}\gdef\@journalfull{Biomedinformatics}\gdef\@journalshort{Biomedinformatics}\gdef\@doiabbr{biomedinformatics}\gdef\@ISSN{2673-7426}\gdef\@continuouspages{yes}}
\DeclareOption{biomimetics}{\gdef\@journal{biomimetics}\gdef\@journalfull{Biomimetics}\gdef\@journalshort{Biomimetics}\gdef\@doiabbr{biomimetics}\gdef\@ISSN{2313-7673}}
\DeclareOption{biomolecules}{\gdef\@journal{biomolecules}\gdef\@journalfull{Biomolecules}\gdef\@journalshort{Biomolecules}\gdef\@doiabbr{biom}\gdef\@ISSN{2218-273X}}
\DeclareOption{biophysica}{\gdef\@journal{biophysica}\gdef\@journalfull{Biophysica}\gdef\@journalshort{Biophysica}\gdef\@doiabbr{biophysica}\gdef\@ISSN{2673-4125}\gdef\@continuouspages{yes}}
\DeclareOption{biosensors}{\gdef\@journal{biosensors}\gdef\@journalfull{Biosensors}\gdef\@journalshort{Biosensors}\gdef\@doiabbr{bios}\gdef\@ISSN{2079-6374}}
\DeclareOption{biotech}{\gdef\@journal{biotech}\gdef\@journalfull{BioTech}\gdef\@journalshort{BioTech}\gdef\@doiabbr{biotech}\gdef\@ISSN{2673-6284}}
\DeclareOption{birds}{\gdef\@journal{birds}\gdef\@journalfull{Birds}\gdef\@journalshort{Birds}\gdef\@doiabbr{birds}\gdef\@ISSN{2673-6004}\gdef\@continuouspages{yes}}
\DeclareOption{bloods}{\gdef\@journal{bloods}\gdef\@journalfull{Bloods}\gdef\@journalshort{Bloods}\gdef\@doiabbr{bloods}\gdef\@ISSN{2673-415X}}
\DeclareOption{blsf}{\gdef\@journal{blsf}\gdef\@journalfull{Biology and Life Sciences Forum}\gdef\@journalshort{Biol. Life Sci. Forum}\gdef\@doiabbr{blsf	}\gdef\@ISSN{2673-9976}}
\DeclareOption{brainsci}{\gdef\@journal{brainsci}\gdef\@journalfull{Brain Sciences}\gdef\@journalshort{Brain Sci.}\gdef\@doiabbr{brainsci}\gdef\@ISSN{2076-3425}}
\DeclareOption{breath}{\gdef\@journal{breath}\gdef\@journalfull{Breath}\gdef\@journalshort{Breath}\gdef\@doiabbr{breath}\gdef\@ISSN{}}
\DeclareOption{buildings}{\gdef\@journal{buildings}\gdef\@journalfull{Buildings}\gdef\@journalshort{Buildings}\gdef\@doiabbr{buildings}\gdef\@ISSN{2075-5309}}
\DeclareOption{businesses}{\gdef\@journal{businesses}\gdef\@journalfull{Businesses}\gdef\@journalshort{Businesses}\gdef\@doiabbr{businesses}\gdef\@ISSN{2673-7116}\gdef\@continuouspages{yes}}
\DeclareOption{cancers}{\gdef\@journal{cancers}\gdef\@journalfull{Cancers}\gdef\@journalshort{Cancers}\gdef\@doiabbr{cancers}\gdef\@ISSN{2072-6694}}
\DeclareOption{carbon}{\gdef\@journal{carbon}\gdef\@journalfull{C}\gdef\@journalshort{C}\gdef\@doiabbr{c}\gdef\@ISSN{2311-5629}}
\DeclareOption{cardiogenetics}{\gdef\@journal{cardiogenetics}\gdef\@journalfull{Cardiogenetics}\gdef\@journalshort{Cardiogenetics}\gdef\@doiabbr{cardiogenetics}\gdef\@ISSN{2035-8148}\gdef\@continuouspages{yes}}
\DeclareOption{catalysts}{\gdef\@journal{catalysts}\gdef\@journalfull{Catalysts}\gdef\@journalshort{Catalysts}\gdef\@doiabbr{catal}\gdef\@ISSN{2073-4344}}
\DeclareOption{cells}{\gdef\@journal{cells}\gdef\@journalfull{Cells}\gdef\@journalshort{Cells}\gdef\@doiabbr{cells}\gdef\@ISSN{2073-4409}}
\DeclareOption{ceramics}{\gdef\@journal{ceramics}\gdef\@journalfull{Ceramics}\gdef\@journalshort{Ceramics}\gdef\@doiabbr{ceramics}\gdef\@ISSN{2571-6131}\gdef\@continuouspages{yes}}
\DeclareOption{challenges}{\gdef\@journal{challenges}\gdef\@journalfull{Challenges}\gdef\@journalshort{Challenges}\gdef\@doiabbr{challe}\gdef\@ISSN{2078-1547}}
\DeclareOption{chemengineering}{\gdef\@journal{chemengineering}\gdef\@journalfull{ChemEngineering}\gdef\@journalshort{ChemEngineering}\gdef\@doiabbr{chemengineering}\gdef\@ISSN{2305-7084}}
\DeclareOption{chemistry}{\gdef\@journal{chemistry}\gdef\@journalfull{Chemistry}\gdef\@journalshort{Chemistry}\gdef\@doiabbr{chemistry}\gdef\@ISSN{2624-8549}\gdef\@continuouspages{yes}}
\DeclareOption{chemosensors}{\gdef\@journal{chemosensors}\gdef\@journalfull{Chemosensors}\gdef\@journalshort{Chemosensors}\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}}
\DeclareOption{chemproc}{\gdef\@journal{chemproc}\gdef\@journalfull{Chemistry Proceedings}\gdef\@journalshort{Chem. Proc.}\gdef\@doiabbr{chemproc}\gdef\@ISSN{2673-4583}}
\DeclareOption{children}{\gdef\@journal{children}\gdef\@journalfull{Children}\gdef\@journalshort{Children}\gdef\@doiabbr{children}\gdef\@ISSN{2227-9067}}
\DeclareOption{chips}{\gdef\@journal{chips}\gdef\@journalfull{Chips}\gdef\@journalshort{Chips}\gdef\@doiabbr{chips}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{cimb}{\gdef\@journal{cimb}\gdef\@journalfull{Current Issues in Molecular Biology}\gdef\@journalshort{Curr. Issues Mol. Biol.}\gdef\@doiabbr{cimb}\gdef\@ISSN{1467-3045}\gdef\@continuouspages{yes}}
\DeclareOption{civileng}{\gdef\@journal{civileng}\gdef\@journalfull{CivilEng}\gdef\@journalshort{CivilEng}\gdef\@doiabbr{civileng}\gdef\@ISSN{2673-4109}\gdef\@continuouspages{yes}}
\DeclareOption{cleantechnol}{\gdef\@journal{cleantechnol}\gdef\@journalfull{Clean Technologies}\gdef\@journalshort{Clean Technol.}\gdef\@doiabbr{cleantechnol}\gdef\@ISSN{2571-8797}\gdef\@continuouspages{yes}}
\DeclareOption{climate}{\gdef\@journal{climate}\gdef\@journalfull{Climate}\gdef\@journalshort{Climate}\gdef\@doiabbr{cli}\gdef\@ISSN{2225-1154}}
\DeclareOption{clinpract}{\gdef\@journal{clinpract}\gdef\@journalfull{Clinics and Practice}\gdef\@journalshort{Clin. Pract.}\gdef\@doiabbr{clinpract}\gdef\@ISSN{2039-7283}\gdef\@continuouspages{yes}}
\DeclareOption{clockssleep}{\gdef\@journal{clockssleep}\gdef\@journalfull{Clocks \& Sleep}\gdef\@journalshort{Clocks\&Sleep}\gdef\@doiabbr{clockssleep}\gdef\@ISSN{2624-5175}\gdef\@continuouspages{yes}}
\DeclareOption{cmd}{\gdef\@journal{cmd}\gdef\@journalfull{Corrosion and Materials Degradation}\gdef\@journalshort{Corros. Mater. Degrad.}\gdef\@doiabbr{cmd}\gdef\@ISSN{2624-5558}\gdef\@continuouspages{yes}}
\DeclareOption{coasts}{\gdef\@journal{coasts}\gdef\@journalfull{Coasts}\gdef\@journalshort{Coasts}\gdef\@doiabbr{coasts}\gdef\@ISSN{2673-964X}\gdef\@continuouspages{yes}}
\DeclareOption{coatings}{\gdef\@journal{coatings}\gdef\@journalfull{Coatings}\gdef\@journalshort{Coatings}\gdef\@doiabbr{coatings}\gdef\@ISSN{2079-6412}}
\DeclareOption{colloids}{\gdef\@journal{colloids}\gdef\@journalfull{Colloids Interfaces}\gdef\@journalshort{Colloids Interfaces}\gdef\@doiabbr{colloids}\gdef\@ISSN{2504-5377}}
\DeclareOption{colorants}{\gdef\@journal{colorants}\gdef\@journalfull{Colorants}\gdef\@journalshort{Colorants}\gdef\@doiabbr{colorants}\gdef\@ISSN{2079-6447}\gdef\@continuouspages{yes}}
\DeclareOption{commodities}{\gdef\@journal{commodities}\gdef\@journalfull{Commodities}\gdef\@journalshort{Commodities}\gdef\@doiabbr{commodities}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{compounds}{\gdef\@journal{compounds}\gdef\@journalfull{Compounds}\gdef\@journalshort{Compounds}\gdef\@doiabbr{compounds}\gdef\@ISSN{2673-6918}\gdef\@continuouspages{yes}}
\DeclareOption{computation}{\gdef\@journal{computation}\gdef\@journalfull{Computation}\gdef\@journalshort{Computation}\gdef\@doiabbr{computation}\gdef\@ISSN{2079-3197}}
\DeclareOption{computers}{\gdef\@journal{computers}\gdef\@journalfull{Computers}\gdef\@journalshort{Computers}\gdef\@doiabbr{computers}\gdef\@ISSN{2073-431X}}
\DeclareOption{condensedmatter}{\gdef\@journal{condensedmatter}\gdef\@journalfull{Condensed Matter}\gdef\@journalshort{Condens. Matter}\gdef\@doiabbr{condmat}\gdef\@ISSN{2410-3896}}
\DeclareOption{conservation}{\gdef\@journal{conservation}\gdef\@journalfull{Conservation}\gdef\@journalshort{Conservation}\gdef\@doiabbr{conservation}\gdef\@ISSN{2673-7159}\gdef\@continuouspages{yes}}
\DeclareOption{constrmater}{\gdef\@journal{constrmater}\gdef\@journalfull{Construction Materials}\gdef\@journalshort{Constr. Mater.}\gdef\@doiabbr{constrmater}\gdef\@ISSN{2673-7108}\gdef\@continuouspages{yes}}
\DeclareOption{cosmetics}{\gdef\@journal{cosmetics}\gdef\@journalfull{Cosmetics}\gdef\@journalshort{Cosmetics}\gdef\@doiabbr{cosmetics}\gdef\@ISSN{2079-9284}}
\DeclareOption{covid}{\gdef\@journal{covid}\gdef\@journalfull{COVID}\gdef\@journalshort{COVID}\gdef\@doiabbr{covid}\gdef\@ISSN{2673-8112}\gdef\@continuouspages{yes}}
\DeclareOption{crops}{\gdef\@journal{crops}\gdef\@journalfull{Crops}\gdef\@journalshort{Crops}\gdef\@doiabbr{crops}\gdef\@ISSN{2673-7655}\gdef\@continuouspages{yes}}
\DeclareOption{cryptography}{\gdef\@journal{cryptography}\gdef\@journalfull{Cryptography}\gdef\@journalshort{Cryptography}\gdef\@doiabbr{cryptography}\gdef\@ISSN{2410-387X}}
\DeclareOption{crystals}{\gdef\@journal{crystals}\gdef\@journalfull{Crystals}\gdef\@journalshort{Crystals}\gdef\@doiabbr{cryst}\gdef\@ISSN{2073-4352}}
\DeclareOption{csmf}{\gdef\@journal{csmf}\gdef\@journalfull{Computer Sciences \& Mathematics Forum}\gdef\@journalshort{Comput. Sci. Math. Forum}\gdef\@doiabbr{csmf}\gdef\@ISSN{2813-0324}}
\DeclareOption{ctn}{\gdef\@journal{ctn}\gdef\@journalfull{Clinical and Translational Neuroscience}\gdef\@journalshort{CTN}\gdef\@doiabbr{Clin. Transl. Neurosci.}\gdef\@ISSN{2514-183X}}
\DeclareOption{curroncol}{\gdef\@journal{curroncol}\gdef\@journalfull{Current Oncology}\gdef\@journalshort{Curr. Oncol.}\gdef\@doiabbr{curroncol}\gdef\@ISSN{1718-7729}\gdef\@continuouspages{yes}}
\DeclareOption{cyber}{\gdef\@journal{cyber}\gdef\@journalfull{Cyber}\gdef\@journalshort{Cyber}\gdef\@doiabbr{cyber}\gdef\@ISSN{2624-800X}}
\DeclareOption{dairy}{\gdef\@journal{dairy}\gdef\@journalfull{Dairy}\gdef\@journalshort{Dairy}\gdef\@doiabbr{dairy}\gdef\@ISSN{2624-862X}\gdef\@continuouspages{yes}}
\DeclareOption{data}{\gdef\@journal{data}\gdef\@journalfull{Data}\gdef\@journalshort{Data}\gdef\@doiabbr{data}\gdef\@ISSN{2306-5729}}
\DeclareOption{dentistry}{\gdef\@journal{dentistry}\gdef\@journalfull{Dentistry Journal}\gdef\@journalshort{Dent. J.}\gdef\@doiabbr{dj}\gdef\@ISSN{2304-6767}}
\DeclareOption{dermato}{\gdef\@journal{dermato}\gdef\@journalfull{Dermato}\gdef\@journalshort{Dermato}\gdef\@doiabbr{dermato}\gdef\@ISSN{2673-6179}\gdef\@continuouspages{yes}}
\DeclareOption{dermatopathology}{\gdef\@journal{dermatopathology}\gdef\@journalfull{Dermatopathology}\gdef\@journalshort{Dermatopathology}\gdef\@doiabbr{dermatopathology}\gdef\@ISSN{2296-3529}\gdef\@continuouspages{yes}}
\DeclareOption{designs}{\gdef\@journal{designs}\gdef\@journalfull{Designs}\gdef\@journalshort{Designs}\gdef\@doiabbr{designs}\gdef\@ISSN{2411-9660}}
\DeclareOption{devices}{\gdef\@journal{devices}\gdef\@journalfull{Devices}\gdef\@journalshort{Devices}\gdef\@doiabbr{devices}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{diabetology}{\gdef\@journal{diabetology}\gdef\@journalfull{Diabetology}\gdef\@journalshort{Diabetology}\gdef\@doiabbr{diabetology}\gdef\@ISSN{2673-4540}\gdef\@continuouspages{yes}}
\DeclareOption{diagnostics}{\gdef\@journal{diagnostics}\gdef\@journalfull{Diagnostics}\gdef\@journalshort{Diagnostics}\gdef\@doiabbr{diagnostics}\gdef\@ISSN{2075-4418}}
\DeclareOption{dietetics}{\gdef\@journal{dietetics}\gdef\@journalfull{Dietetics}\gdef\@journalshort{Dietetics}\gdef\@doiabbr{dietetics}\gdef\@ISSN{2674-0311}\gdef\@continuouspages{yes}}
\DeclareOption{digital}{\gdef\@journal{digital}\gdef\@journalfull{Digital}\gdef\@journalshort{Digital}\gdef\@doiabbr{digital}\gdef\@ISSN{2673-6470}\gdef\@continuouspages{yes}}
\DeclareOption{disabilities}{\gdef\@journal{disabilities}\gdef\@journalfull{Disabilities}\gdef\@journalshort{Disabilities}\gdef\@doiabbr{disabilities}\gdef\@ISSN{2673-7272}\gdef\@continuouspages{yes}}
\DeclareOption{diseases}{\gdef\@journal{diseases}\gdef\@journalfull{Diseases}\gdef\@journalshort{Diseases}\gdef\@doiabbr{diseases}\gdef\@ISSN{2079-9721}}
\DeclareOption{diversity}{\gdef\@journal{diversity}\gdef\@journalfull{Diversity}\gdef\@journalshort{Diversity}\gdef\@doiabbr{d}\gdef\@ISSN{1424-2818}}
\DeclareOption{dna}{\gdef\@journal{dna}\gdef\@journalfull{DNA}\gdef\@journalshort{DNA}\gdef\@doiabbr{dna}\gdef\@ISSN{2673-8856}\gdef\@continuouspages{yes}}
\DeclareOption{drones}{\gdef\@journal{drones}\gdef\@journalfull{Drones}\gdef\@journalshort{Drones}\gdef\@doiabbr{drones}\gdef\@ISSN{2504-446X}}
\DeclareOption{dynamics}{\gdef\@journal{dynamics}\gdef\@journalfull{Dynamics}\gdef\@journalshort{Dynamics}\gdef\@doiabbr{dynamics}\gdef\@ISSN{2673-8716}\gdef\@continuouspages{yes}}
\DeclareOption{earth}{\gdef\@journal{earth}\gdef\@journalfull{Earth}\gdef\@journalshort{Earth}\gdef\@doiabbr{earth}\gdef\@ISSN{2673-4834}\gdef\@continuouspages{yes}}
\DeclareOption{ebj}{\gdef\@journal{ebj}\gdef\@journalfull{European Burn Journal}\gdef\@journalshort{Eur. Burn J.}\gdef\@doiabbr{ebj}\gdef\@ISSN{2673-1991}\gdef\@continuouspages{yes}}
\DeclareOption{ecologies}{\gdef\@journal{ecologies}\gdef\@journalfull{Ecologies}\gdef\@journalshort{Ecologies}\gdef\@doiabbr{ecologies}\gdef\@ISSN{2673-4133}\gdef\@continuouspages{yes}}
\DeclareOption{econometrics}{\gdef\@journal{econometrics}\gdef\@journalfull{Econometrics}\gdef\@journalshort{Econometrics}\gdef\@doiabbr{econometrics}\gdef\@ISSN{2225-1146}}
\DeclareOption{economies}{\gdef\@journal{economies}\gdef\@journalfull{Economies}\gdef\@journalshort{Economies}\gdef\@doiabbr{economies}\gdef\@ISSN{2227-7099}}
\DeclareOption{education}{\gdef\@journal{education}\gdef\@journalfull{Education Sciences}\gdef\@journalshort{Educ. Sci.}\gdef\@doiabbr{educsci}\gdef\@ISSN{2227-7102}}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalfull{European Journal of Investigation in Health Psychology and Education}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}\gdef\@continuouspages{yes}}
\DeclareOption{electricity}{\gdef\@journal{electricity}\gdef\@journalfull{Electricity}\gdef\@journalshort{Electricity}\gdef\@doiabbr{electricity}\gdef\@ISSN{2673-4826}\gdef\@continuouspages{yes}}
\DeclareOption{electrochem}{\gdef\@journal{electrochem}\gdef\@journalfull{Electrochem}\gdef\@journalshort{Electrochem}\gdef\@doiabbr{electrochem}\gdef\@ISSN{2673-3293}\gdef\@continuouspages{yes}}
\DeclareOption{electronicmat}{\gdef\@journal{electronicmat}\gdef\@journalfull{Electronic Materials}\gdef\@journalshort{Electron. Mater.}\gdef\@doiabbr{electronicmat}\gdef\@ISSN{2673-3978}\gdef\@continuouspages{yes}}
\DeclareOption{electronics}{\gdef\@journal{electronics}\gdef\@journalfull{Electronics}\gdef\@journalshort{Electronics}\gdef\@doiabbr{electronics}\gdef\@ISSN{2079-9292}}
\DeclareOption{encyclopedia}{\gdef\@journal{encyclopedia}\gdef\@journalfull{Encyclopedia}\gdef\@journalshort{Encyclopedia}\gdef\@doiabbr{encyclopedia}\gdef\@ISSN{2673-8392}\gdef\@continuouspages{yes}}
\DeclareOption{endocrines}{\gdef\@journal{endocrines}\gdef\@journalfull{Endocrines}\gdef\@journalshort{Endocrines}\gdef\@doiabbr{endocrines}\gdef\@ISSN{2673-396X}\gdef\@continuouspages{yes}}
\DeclareOption{energies}{\gdef\@journal{energies}\gdef\@journalfull{Energies}\gdef\@journalshort{Energies}\gdef\@doiabbr{en}\gdef\@ISSN{1996-1073}}
\DeclareOption{eng}{\gdef\@journal{eng}\gdef\@journalfull{Eng-Advances in Engineering}\gdef\@journalshort{Eng}\gdef\@doiabbr{eng}\gdef\@ISSN{2673-4117}\gdef\@continuouspages{yes}}
\DeclareOption{engproc}{\gdef\@journal{engproc}\gdef\@journalfull{Engineering Proceedings}\gdef\@journalshort{Eng. Proc.}\gdef\@doiabbr{engproc}\gdef\@ISSN{2673-4591}}
%\DeclareOption{ent}{\gdef\@journal{ent}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{entomology}{\gdef\@journal{entomology}\gdef\@journalfull{Entomology}\gdef\@journalshort{Entomology}\gdef\@doiabbr{entomology}\gdef\@ISSN{2813-0502}\gdef\@continuouspages{yes}}	
\DeclareOption{entropy}{\gdef\@journal{entropy}\gdef\@journalfull{Entropy}\gdef\@journalshort{Entropy}\gdef\@doiabbr{e}\gdef\@ISSN{1099-4300}}
\DeclareOption{environments}{\gdef\@journal{environments}\gdef\@journalfull{Environments}\gdef\@journalshort{Environments}\gdef\@doiabbr{environments}\gdef\@ISSN{2076-3298}}
\DeclareOption{environsciproc}{\gdef\@journal{environsciproc}\gdef\@journalfull{Environmental Sciences Proceedings}\gdef\@journalshort{Environ. Sci. Proc.}\gdef\@doiabbr{environsciproc}\gdef\@ISSN{2673-4931}}
\DeclareOption{epidemiologia}{\gdef\@journal{epidemiologia}\gdef\@journalfull{Epidemiologia}\gdef\@journalshort{Epidemiologia}\gdef\@doiabbr{epidemiologia}\gdef\@ISSN{2673-3986}\gdef\@continuouspages{yes}}
\DeclareOption{epigenomes}{\gdef\@journal{epigenomes}\gdef\@journalfull{Epigenomes}\gdef\@journalshort{Epigenomes}\gdef\@doiabbr{epigenomes}\gdef\@ISSN{2075-4655}}
\DeclareOption{est}{\gdef\@journal{est}\gdef\@journalfull{Electrochemical Science and Technology}\gdef\@journalshort{Electrochem. Sci. Technol.}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{fermentation}{\gdef\@journal{fermentation}\gdef\@journalfull{Fermentation}\gdef\@journalshort{Fermentation}\gdef\@doiabbr{fermentation}\gdef\@ISSN{2311-5637}}
\DeclareOption{fibers}{\gdef\@journal{fibers}\gdef\@journalfull{Fibers}\gdef\@journalshort{Fibers}\gdef\@doiabbr{fib}\gdef\@ISSN{2079-6439}}
\DeclareOption{fintech}{\gdef\@journal{fintech}\gdef\@journalfull{FinTech}\gdef\@journalshort{FinTech}\gdef\@doiabbr{fintech}\gdef\@ISSN{2674-1032}\gdef\@continuouspages{yes}}
\DeclareOption{fire}{\gdef\@journal{fire}\gdef\@journalfull{Fire}\gdef\@journalshort{Fire}\gdef\@doiabbr{fire}\gdef\@ISSN{2571-6255}}
\DeclareOption{fishes}{\gdef\@journal{fishes}\gdef\@journalfull{Fishes}\gdef\@journalshort{Fishes}\gdef\@doiabbr{fishes}\gdef\@ISSN{2410-3888}}
\DeclareOption{fluids}{\gdef\@journal{fluids}\gdef\@journalfull{Fluids}\gdef\@journalshort{Fluids}\gdef\@doiabbr{fluids}\gdef\@ISSN{2311-5521}}
\DeclareOption{foods}{\gdef\@journal{foods}\gdef\@journalfull{Foods}\gdef\@journalshort{Foods}\gdef\@doiabbr{foods}\gdef\@ISSN{2304-8158}}
\DeclareOption{forecasting}{\gdef\@journal{forecasting}\gdef\@journalfull{Forecasting}\gdef\@journalshort{Forecasting}\gdef\@doiabbr{forecast}\gdef\@ISSN{2571-9394}\gdef\@continuouspages{yes}}
\DeclareOption{forensicsci}{\gdef\@journal{forensicsci}\gdef\@journalfull{Forensic Sciences}\gdef\@journalshort{Forensic Sci.}\gdef\@doiabbr{forensicsci}\gdef\@ISSN{2673-6756}\gdef\@continuouspages{yes}}
\DeclareOption{forests}{\gdef\@journal{forests}\gdef\@journalfull{Forests}\gdef\@journalshort{Forests}\gdef\@doiabbr{f}\gdef\@ISSN{1999-4907}}
\DeclareOption{foundations}{\gdef\@journal{foundations}\gdef\@journalfull{Foundations}\gdef\@journalshort{Foundations}\gdef\@doiabbr{foundations}\gdef\@ISSN{2673-9321}\gdef\@continuouspages{yes}}
\DeclareOption{fractalfract}{\gdef\@journal{fractalfract}\gdef\@journalfull{Fractal and Fractional}\gdef\@journalshort{Fractal Fract.}\gdef\@doiabbr{fractalfract}\gdef\@ISSN{2504-3110}}
\DeclareOption{fuels}{\gdef\@journal{fuels}\gdef\@journalfull{Fuels}\gdef\@journalshort{Fuels}\gdef\@doiabbr{fuels}\gdef\@ISSN{2673-3994}\gdef\@continuouspages{yes}}
\DeclareOption{future}{\gdef\@journal{future}\gdef\@journalfull{Future}\gdef\@journalshort{Future}\gdef\@doiabbr{future}\gdef\@ISSN{2813-2882}\gdef\@continuouspages{yes}}
\DeclareOption{futureinternet}{\gdef\@journal{futureinternet}\gdef\@journalfull{Future Internet}\gdef\@journalshort{Future Internet}\gdef\@doiabbr{fi}\gdef\@ISSN{1999-5903}}
%\DeclareOption{futureparasites}{\gdef\@journal{futureparasites}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{futurepharmacol}{\gdef\@journal{futurepharmacol}\gdef\@journalfull{Future Pharmacology}\gdef\@journalshort{Future Pharm.}\gdef\@doiabbr{futurepharmacol}\gdef\@ISSN{2673-9879}\gdef\@continuouspages{yes}}
\DeclareOption{futurephys}{\gdef\@journal{futurephys}\gdef\@journalfull{Future Physics}\gdef\@journalshort{Future Phys.}\gdef\@doiabbr{futurephys}\gdef\@ISSN{2624-6503}}
\DeclareOption{futuretransp}{\gdef\@journal{futuretransp}\gdef\@journalfull{Future Transportation}\gdef\@journalshort{Future Transp.}\gdef\@doiabbr{futuretransp}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{galaxies}{\gdef\@journal{galaxies}\gdef\@journalfull{Galaxies}\gdef\@journalshort{Galaxies}\gdef\@doiabbr{galaxies}\gdef\@ISSN{2075-4434}}
\DeclareOption{games}{\gdef\@journal{games}\gdef\@journalfull{Games}\gdef\@journalshort{Games}\gdef\@doiabbr{g}\gdef\@ISSN{2073-4336}}
\DeclareOption{gases}{\gdef\@journal{gases}\gdef\@journalfull{Gases}\gdef\@journalshort{Gases}\gdef\@doiabbr{gases}\gdef\@ISSN{2673-5628}\gdef\@continuouspages{yes}}
\DeclareOption{gastroent}{\gdef\@journal{gastroent}\gdef\@journalfull{Gastroenterology Insights}\gdef\@journalshort{Gastroenterol. Insights}\gdef\@doiabbr{gastroent}\gdef\@ISSN{2036-7422}\gdef\@continuouspages{yes}}
\DeclareOption{gastrointestdisord}{\gdef\@journal{gastrointestdisord}\gdef\@journalfull{Gastrointestinal Disorders}\gdef\@journalshort{Gastrointest. Disord.}\gdef\@doiabbr{gidisord}\gdef\@ISSN{2624-5647}\gdef\@continuouspages{yes}}
\DeclareOption{gels}{\gdef\@journal{gels}\gdef\@journalfull{Gels}\gdef\@journalshort{Gels}\gdef\@doiabbr{gels}\gdef\@ISSN{2310-2861}}
\DeclareOption{genealogy}{\gdef\@journal{genealogy}\gdef\@journalfull{Genealogy}\gdef\@journalshort{Genealogy}\gdef\@doiabbr{genealogy}\gdef\@ISSN{2313-5778}}
\DeclareOption{genes}{\gdef\@journal{genes}\gdef\@journalfull{Genes}\gdef\@journalshort{Genes}\gdef\@doiabbr{genes}\gdef\@ISSN{2073-4425}}
\DeclareOption{geographies}{\gdef\@journal{geographies}\gdef\@journalfull{Geographies}\gdef\@journalshort{Geographies}\gdef\@doiabbr{geographies}\gdef\@ISSN{2673-7086}\gdef\@continuouspages{yes}}
\DeclareOption{geohazards}{\gdef\@journal{geohazards}\gdef\@journalfull{GeoHazards}\gdef\@journalshort{GeoHazards}\gdef\@doiabbr{geohazards}\gdef\@ISSN{2624-795X}\gdef\@continuouspages{yes}}
\DeclareOption{geomatics}{\gdef\@journal{geomatics}\gdef\@journalfull{Geomatics}\gdef\@journalshort{Geomatics}\gdef\@doiabbr{geomatics}\gdef\@ISSN{2673-7418}\gdef\@continuouspages{yes}}
\DeclareOption{geosciences}{\gdef\@journal{geosciences}\gdef\@journalfull{Geosciences}\gdef\@journalshort{Geosciences}\gdef\@doiabbr{geosciences}\gdef\@ISSN{2076-3263}}
\DeclareOption{geotechnics}{\gdef\@journal{geotechnics}\gdef\@journalfull{Geotechnics}\gdef\@journalshort{Geotechnics}\gdef\@doiabbr{geotechnics}\gdef\@ISSN{2673-7094}\gdef\@continuouspages{yes}}
\DeclareOption{geriatrics}{\gdef\@journal{geriatrics}\gdef\@journalfull{Geriatrics}\gdef\@journalshort{Geriatrics}\gdef\@doiabbr{geriatrics}\gdef\@ISSN{2308-3417}}
\DeclareOption{grasses}{\gdef\@journal{grasses}\gdef\@journalfull{Grasses}\gdef\@journalshort{Grasses}\gdef\@doiabbr{grasses}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hazardousmatters}{\gdef\@journal{hazardousmatters}\gdef\@journalfull{Hazardous Matters}\gdef\@journalshort{Hazard. Matters}\gdef\@doiabbr{}\gdef\@ISSN{0014-0014}}
\DeclareOption{healthcare}{\gdef\@journal{healthcare}\gdef\@journalfull{Healthcare}\gdef\@journalshort{Healthcare}\gdef\@doiabbr{healthcare}\gdef\@ISSN{2227-9032}}
\DeclareOption{hearts}{\gdef\@journal{hearts}\gdef\@journalfull{Hearts}\gdef\@journalshort{Hearts}\gdef\@doiabbr{hearts}\gdef\@ISSN{2673-3846}\gdef\@continuouspages{yes}}
\DeclareOption{hemato}{\gdef\@journal{hemato}\gdef\@journalfull{Hemato}\gdef\@journalshort{Hemato}\gdef\@doiabbr{hemato}\gdef\@ISSN{2673-6357}\gdef\@continuouspages{yes}}
\DeclareOption{hematolrep}{\gdef\@journal{hematolrep}\gdef\@journalfull{Hematology Reports}\gdef\@journalshort{Hematol. Rep.}\gdef\@doiabbr{hematolrep}\gdef\@ISSN{2038-8330}\gdef\@continuouspages{yes}}
\DeclareOption{heritage}{\gdef\@journal{heritage}\gdef\@journalfull{Heritage}\gdef\@journalshort{Heritage}\gdef\@doiabbr{heritage}\gdef\@ISSN{2571-9408}\gdef\@continuouspages{yes}}
\DeclareOption{higheredu}{\gdef\@journal{higheredu}\gdef\@journalfull{Trends in Higher Education}\gdef\@journalshort{Trends High. Educ.}\gdef\@doiabbr{higheredu}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{highthroughput}{\gdef\@journal{highthroughput}\gdef\@journalfull{High-Throughput}\gdef\@journalshort{High-Throughput}\gdef\@doiabbr{ht}\gdef\@ISSN{2571-5135}}
\DeclareOption{histories}{\gdef\@journal{histories}\gdef\@journalfull{Histories}\gdef\@journalshort{Histories}\gdef\@doiabbr{histories}\gdef\@ISSN{2409-9252}\gdef\@continuouspages{yes}}
\DeclareOption{horticulturae}{\gdef\@journal{horticulturae}\gdef\@journalfull{Horticulturae}\gdef\@journalshort{Horticulturae}\gdef\@doiabbr{horticulturae}\gdef\@ISSN{2311-7524}}
\DeclareOption{humanities}{\gdef\@journal{humanities}\gdef\@journalfull{Humanities}\gdef\@journalshort{Humanities}\gdef\@doiabbr{h}\gdef\@ISSN{2076-0787}}
\DeclareOption{humans}{\gdef\@journal{humans}\gdef\@journalfull{Humans}\gdef\@journalshort{Humans}\gdef\@doiabbr{humans}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hydrobiology}{\gdef\@journal{hydrobiology}\gdef\@journalfull{Hydrobiology}\gdef\@journalshort{Hydrobiology	}\gdef\@doiabbr{hydrobiology}\gdef\@ISSN{2673-9917}\gdef\@continuouspages{yes}}
\DeclareOption{hydrogen}{\gdef\@journal{hydrogen}\gdef\@journalfull{Hydrogen}\gdef\@journalshort{Hydrogen}\gdef\@doiabbr{hydrogen}\gdef\@ISSN{2673-4141}\gdef\@continuouspages{yes}}
\DeclareOption{hydrology}{\gdef\@journal{hydrology}\gdef\@journalfull{Hydrology}\gdef\@journalshort{Hydrology}\gdef\@doiabbr{hydrology}\gdef\@ISSN{2306-5338}}
\DeclareOption{hygiene}{\gdef\@journal{hygiene}\gdef\@journalfull{Hygiene}\gdef\@journalshort{Hygiene}\gdef\@doiabbr{hygiene}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{idr}{\gdef\@journal{idr}\gdef\@journalfull{Infectious Disease Reports}\gdef\@journalshort{Infect. Dis. Rep.}\gdef\@doiabbr{idr}\gdef\@ISSN{2036-7449}\gdef\@continuouspages{yes}}
\DeclareOption{ijerph}{\gdef\@journal{ijerph}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}}
\DeclareOption{ijfs}{\gdef\@journal{ijfs}\gdef\@journalfull{International Journal of Financial Studies}\gdef\@journalshort{Int. J. Financial Stud.}\gdef\@doiabbr{ijfs}\gdef\@ISSN{2227-7072}}
\DeclareOption{ijgi}{\gdef\@journal{ijgi}\gdef\@journalfull{ISPRS International Journal of Geo-Information}\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}\gdef\@doiabbr{ijgi}\gdef\@ISSN{2220-9964}}
\DeclareOption{ijms}{\gdef\@journal{ijms}\gdef\@journalfull{International Journal of Molecular Sciences}\gdef\@journalshort{Int. J. Mol. Sci.}\gdef\@doiabbr{ijms}\gdef\@ISSN{1422-0067}}
\DeclareOption{ijns}{\gdef\@journal{ijns}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@doiabbr{ijns}\gdef\@ISSN{2409-515X}}
\DeclareOption{ijpb}{\gdef\@journal{ijpb}\gdef\@journalfull{International Journal of Plant Biology}\gdef\@journalshort{Int. J. Plant Biol.}\gdef\@doiabbr{ijpb}\gdef\@ISSN{2037-0164}\gdef\@continuouspages{yes}}
\DeclareOption{ijtm}{\gdef\@journal{ijtm}\gdef\@journalfull{International Journal of Translational Medicine}\gdef\@journalshort{Int. J. Transl. Med.}\gdef\@doiabbr{ijtm}\gdef\@ISSN{2673-8937}\gdef\@continuouspages{yes}}
\DeclareOption{ijtpp}{\gdef\@journal{ijtpp}\gdef\@journalfull{International Journal of Turbomachinery Propulsion and Power}\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}}
\DeclareOption{ime}{\gdef\@journal{ime}\gdef\@journalfull{International Medical Education}\gdef\@journalshort{Int. Med. Educ.}\gdef\@doiabbr{ime}\gdef\@ISSN{2813-141X}\gdef\@continuouspages{yes}}
\DeclareOption{immuno}{\gdef\@journal{immuno}\gdef\@journalfull{Immuno}\gdef\@journalshort{Immuno}\gdef\@doiabbr{immuno}\gdef\@ISSN{2673-5601}\gdef\@continuouspages{yes}}
\DeclareOption{informatics}{\gdef\@journal{informatics}\gdef\@journalfull{Informatics}\gdef\@journalshort{Informatics}\gdef\@doiabbr{informatics}\gdef\@ISSN{2227-9709}}
\DeclareOption{information}{\gdef\@journal{information}\gdef\@journalfull{Information}\gdef\@journalshort{Information}\gdef\@doiabbr{info}\gdef\@ISSN{2078-2489}}
\DeclareOption{infrastructures}{\gdef\@journal{infrastructures}\gdef\@journalfull{Infrastructures}\gdef\@journalshort{Infrastructures}\gdef\@doiabbr{infrastructures}\gdef\@ISSN{2412-3811}}
\DeclareOption{inorganics}{\gdef\@journal{inorganics}\gdef\@journalfull{Inorganics}\gdef\@journalshort{Inorganics}\gdef\@doiabbr{inorganics}\gdef\@ISSN{2304-6740}}
\DeclareOption{insects}{\gdef\@journal{insects}\gdef\@journalfull{Insects}\gdef\@journalshort{Insects}\gdef\@doiabbr{insects}\gdef\@ISSN{2075-4450}}
\DeclareOption{instruments}{\gdef\@journal{instruments}\gdef\@journalfull{Instruments}\gdef\@journalshort{Instruments}\gdef\@doiabbr{instruments}\gdef\@ISSN{2410-390X}}
\DeclareOption{inventions}{\gdef\@journal{inventions}\gdef\@journalfull{Inventions}\gdef\@journalshort{Inventions}\gdef\@doiabbr{inventions}\gdef\@ISSN{2411-5134}}
\DeclareOption{iot}{\gdef\@journal{iot}\gdef\@journalfull{IoT}\gdef\@journalshort{IoT}\gdef\@doiabbr{iot}\gdef\@ISSN{2624-831X}\gdef\@continuouspages{yes}}
\DeclareOption{j}{\gdef\@journal{j}\gdef\@journalfull{J}\gdef\@journalshort{J}\gdef\@doiabbr{j}\gdef\@ISSN{2571-8800}\gdef\@continuouspages{yes}}
\DeclareOption{jal}{\gdef\@journal{jal}\gdef\@journalfull{Journal of Ageing and Longevity}\gdef\@journalshort{J. Ageing Longev.}\gdef\@doiabbr{jal}\gdef\@ISSN{2673-9259}\gdef\@continuouspages{yes}}
\DeclareOption{jcdd}{\gdef\@journal{jcdd}\gdef\@journalfull{Journal of Cardiovascular Development and Disease}\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}\gdef\@doiabbr{jcdd}\gdef\@ISSN{2308-3425}}
\DeclareOption{jcm}{\gdef\@journal{jcm}\gdef\@journalfull{Journal of Clinical Medicine}\gdef\@journalshort{J. Clin. Med.}\gdef\@doiabbr{jcm}\gdef\@ISSN{2077-0383}}
\DeclareOption{jcp}{\gdef\@journal{jcp}\gdef\@journalfull{Journal of Cybersecurity and Privacy}\gdef\@journalshort{J. Cybersecur. Priv.}\gdef\@doiabbr{jcp}\gdef\@ISSN{2624-800X}\gdef\@continuouspages{yes}}
\DeclareOption{jcs}{\gdef\@journal{jcs}\gdef\@journalfull{Journal of Composites Science}\gdef\@journalshort{J. Compos. Sci.}\gdef\@doiabbr{jcs}\gdef\@ISSN{2504-477X}}
\DeclareOption{jcto}{\gdef\@journal{jcto}\gdef\@journalfull{Journal of Clinical \& Translational Ophthalmology}\gdef\@journalshort{J. Clin. Transl. Ophthalmol.}\gdef\@doiabbr{jcto}\gdef\@ISSN{2813-1053}\gdef\@continuouspages{yes}}
\DeclareOption{jdb}{\gdef\@journal{jdb}\gdef\@journalfull{Journal of Developmental Biology}\gdef\@journalshort{J. Dev. Biol.}\gdef\@doiabbr{jdb}\gdef\@ISSN{2221-3759}}
\DeclareOption{jeta}{\gdef\@journal{jeta}\gdef\@journalfull{Journal of Experimental and Theoretical Analyses}\gdef\@journalshort{J. Exp. Theor. Anal.}\gdef\@doiabbr{jeta}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jfb}{\gdef\@journal{jfb}\gdef\@journalfull{Journal of Functional Biomaterials}\gdef\@journalshort{J. Funct. Biomater.}\gdef\@doiabbr{jfb}\gdef\@ISSN{2079-4983}}
\DeclareOption{jfmk}{\gdef\@journal{jfmk}\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}\gdef\@doiabbr{jfmk}\gdef\@ISSN{2411-5142}}
\DeclareOption{jimaging}{\gdef\@journal{jimaging}\gdef\@journalfull{Journal of Imaging}\gdef\@journalshort{J. Imaging}\gdef\@doiabbr{jimaging}\gdef\@ISSN{2313-433X}}
\DeclareOption{jintelligence}{\gdef\@journal{jintelligence}\gdef\@journalfull{Journal of Intelligence}\gdef\@journalshort{J. Intell.}\gdef\@doiabbr{jintelligence}\gdef\@ISSN{2079-3200}}
\DeclareOption{jlpea}{\gdef\@journal{jlpea}\gdef\@journalfull{Journal of Low Power Electronics and Applications}\gdef\@journalshort{J. Low Power Electron. Appl.}\gdef\@doiabbr{jlpea}\gdef\@ISSN{2079-9268}}
\DeclareOption{jmmp}{\gdef\@journal{jmmp}\gdef\@journalfull{Journal of Manufacturing and Materials Processing}\gdef\@journalshort{J. Manuf. Mater. Process.}\gdef\@doiabbr{jmmp}\gdef\@ISSN{2504-4494}}
\DeclareOption{jmp}{\gdef\@journal{jmp}\gdef\@journalfull{Journal of Molecular Pathology}\gdef\@journalshort{J. Mol. Pathol.}\gdef\@doiabbr{jmp}\gdef\@ISSN{2673-5261}\gdef\@continuouspages{yes}}
\DeclareOption{jmse}{\gdef\@journal{jmse}\gdef\@journalfull{Journal of Marine Science and Engineering}\gdef\@journalshort{J. Mar. Sci. Eng.}\gdef\@doiabbr{jmse}\gdef\@ISSN{2077-1312}}
\DeclareOption{jne}{\gdef\@journal{jne}\gdef\@journalfull{Journal of Nuclear Engineering}\gdef\@journalshort{J. Nucl. Eng.}\gdef\@doiabbr{jne}\gdef\@ISSN{2673-4362}\gdef\@continuouspages{yes}}
\DeclareOption{jnt}{\gdef\@journal{jnt}\gdef\@journalfull{Journal of Nanotheranostics}\gdef\@journalshort{J. Nanotheranostics}\gdef\@doiabbr{jnt}\gdef\@ISSN{2624-845X}\gdef\@continuouspages{yes}}
\DeclareOption{jof}{\gdef\@journal{jof}\gdef\@journalfull{Journal of Fungi}\gdef\@journalshort{J. Fungi}\gdef\@doiabbr{jof}\gdef\@ISSN{2309-608X}}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalfull{Journal of Open Innovation: Technology Market and Complexity}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{jor}{\gdef\@journal{jor}\gdef\@journalfull{Journal of Respiration}\gdef\@journalshort{J. Respir.}\gdef\@doiabbr{jor}\gdef\@ISSN{2673-527X}\gdef\@continuouspages{yes}}
\DeclareOption{journalmedia}{\gdef\@journal{journalmedia}\gdef\@journalfull{Journalism and Media}\gdef\@journalshort{Journal. Media}\gdef\@doiabbr{journalmedia}\gdef\@ISSN{2673-5172}\gdef\@continuouspages{yes}}
\DeclareOption{jox}{\gdef\@journal{jox}\gdef\@journalfull{Journal of Xenobiotics}\gdef\@journalshort{J. Xenobiot.}\gdef\@doiabbr{jox}\gdef\@ISSN{2039-4713}\gdef\@continuouspages{yes}}
\DeclareOption{jpm}{\gdef\@journal{jpm}\gdef\@journalfull{Journal of Personalized Medicine}\gdef\@journalshort{J. Pers. Med.}\gdef\@doiabbr{jpm}\gdef\@ISSN{2075-4426}}
\DeclareOption{jrfm}{\gdef\@journal{jrfm}\gdef\@journalfull{Journal of Risk and Financial Management}\gdef\@journalshort{J. Risk Financial Manag.}\gdef\@doiabbr{jrfm}\gdef\@ISSN{1911-8074}}
\DeclareOption{jsan}{\gdef\@journal{jsan}\gdef\@journalfull{Journal of Sensor and Actuator Networks}\gdef\@journalshort{J. Sens. Actuator Netw.}\gdef\@doiabbr{jsan}\gdef\@ISSN{2224-2708}}
\DeclareOption{jtaer}{\gdef\@journal{jtaer}\gdef\@journalfull{Journal of Theoretical and Applied Electronic Commerce Research}\gdef\@journalshort{J. Theor. Appl. Electron. Commer. Res.}\gdef\@doiabbr{jtaer}\gdef\@ISSN{0718-1876}\gdef\@continuouspages{yes}}
\DeclareOption{jvd}{\gdef\@journal{jvd}\gdef\@journalfull{Journal of Vascular Diseases}\gdef\@journalshort{JVD}\gdef\@doiabbr{jvd}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jzbg}{\gdef\@journal{jzbg}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@doiabbr{jzbg}\gdef\@ISSN{2673-5636}\gdef\@continuouspages{yes}}
%\DeclareOption{kidney}{\gdef\@journal{kidney}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kidneydial}{\gdef\@journal{kidneydial}\gdef\@journalfull{Kidney and Dialysis}\gdef\@journalshort{Kidney Dial.}\gdef\@doiabbr{kinasesphosphatases}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kinasesphosphatases}{\gdef\@journal{kinasesphosphatases}\gdef\@journalfull{Kinases and Phosphatases}\gdef\@journalshort{Kinases Phosphatases}\gdef\@doiabbr{kinasesphosphatases}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{knowledge}{\gdef\@journal{knowledge}\gdef\@journalfull{Knowledge}\gdef\@journalshort{Knowledge}\gdef\@doiabbr{knowledge}\gdef\@ISSN{2673-9585}\gdef\@continuouspages{yes}}
\DeclareOption{land}{\gdef\@journal{land}\gdef\@journalfull{Land}\gdef\@journalshort{Land}\gdef\@doiabbr{land}\gdef\@ISSN{2073-445X}}
\DeclareOption{languages}{\gdef\@journal{languages}\gdef\@journalfull{Languages}\gdef\@journalshort{Languages}\gdef\@doiabbr{languages}\gdef\@ISSN{2226-471X}}
\DeclareOption{laws}{\gdef\@journal{laws}\gdef\@journalfull{Laws}\gdef\@journalshort{Laws}\gdef\@doiabbr{laws}\gdef\@ISSN{2075-471X}}
\DeclareOption{life}{\gdef\@journal{life}\gdef\@journalfull{Life}\gdef\@journalshort{Life}\gdef\@doiabbr{life}\gdef\@ISSN{2075-1729}}
\DeclareOption{liquids}{\gdef\@journal{liquids}\gdef\@journalfull{Liquids}\gdef\@journalshort{Liquids}\gdef\@doiabbr{liquids}\gdef\@ISSN{2673-8015}\gdef\@continuouspages{yes}}
\DeclareOption{literature}{\gdef\@journal{literature}\gdef\@journalfull{Literature}\gdef\@journalshort{Literature}\gdef\@doiabbr{literature}\gdef\@ISSN{2410-9789}\gdef\@continuouspages{yes}}
\DeclareOption{livers}{\gdef\@journal{livers}\gdef\@journalfull{Livers}\gdef\@journalshort{Livers}\gdef\@doiabbr{livers}\gdef\@ISSN{2673-4389}\gdef\@continuouspages{yes}}
\DeclareOption{logics}{\gdef\@journal{logics}\gdef\@journalfull{Logics}\gdef\@journalshort{Logics}\gdef\@doiabbr{logics}\gdef\@ISSN{2813-0405}\gdef\@continuouspages{yes}}
\DeclareOption{logistics}{\gdef\@journal{logistics}\gdef\@journalfull{Logistics}\gdef\@journalshort{Logistics}\gdef\@doiabbr{logistics}\gdef\@ISSN{2305-6290}}
\DeclareOption{lubricants}{\gdef\@journal{lubricants}\gdef\@journalfull{Lubricants}\gdef\@journalshort{Lubricants}\gdef\@doiabbr{lubricants}\gdef\@ISSN{2075-4442}}
\DeclareOption{lymphatics}{\gdef\@journal{lymphatics}\gdef\@journalfull{Lymphatics}\gdef\@journalshort{Lymphatics}\gdef\@doiabbr{lymphatics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}	
\DeclareOption{machines}{\gdef\@journal{machines}\gdef\@journalfull{Machines}\gdef\@journalshort{Machines}\gdef\@doiabbr{machines}\gdef\@ISSN{2075-1702}}
\DeclareOption{macromol}{\gdef\@journal{macromol}\gdef\@journalfull{Macromol}\gdef\@journalshort{Macromol}\gdef\@doiabbr{macromol}\gdef\@ISSN{2673-6209}\gdef\@continuouspages{yes}}
\DeclareOption{magnetism}{\gdef\@journal{magnetism}\gdef\@journalfull{Magnetism}\gdef\@journalshort{Magnetism}\gdef\@doiabbr{magnetism}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{magnetochemistry}{\gdef\@journal{magnetochemistry}\gdef\@journalfull{Magnetochemistry}\gdef\@journalshort{Magnetochemistry}\gdef\@doiabbr{magnetochemistry}\gdef\@ISSN{2312-7481}}
\DeclareOption{make}{\gdef\@journal{make}\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@journalshort{Mach. Learn. Knowl. Extr.}\gdef\@doiabbr{make}\gdef\@ISSN{2504-4990}\gdef\@continuouspages{yes}}
\DeclareOption{marinedrugs}{\gdef\@journal{marinedrugs}\gdef\@journalfull{Marine Drugs}\gdef\@journalshort{Mar. Drugs}\gdef\@doiabbr{md}\gdef\@ISSN{1660-3397}}
\DeclareOption{materials}{\gdef\@journal{materials}\gdef\@journalfull{Materials}\gdef\@journalshort{Materials}\gdef\@doiabbr{ma}\gdef\@ISSN{1996-1944}}
\DeclareOption{materproc}{\gdef\@journal{materproc}\gdef\@journalfull{Materials Proceedings}\gdef\@journalshort{Mater. Proc.}\gdef\@doiabbr{materproc}\gdef\@ISSN{2673-4605}}
\DeclareOption{mathematics}{\gdef\@journal{mathematics}\gdef\@journalfull{Mathematics}\gdef\@journalshort{Mathematics}\gdef\@doiabbr{math}\gdef\@ISSN{2227-7390}}
\DeclareOption{mca}{\gdef\@journal{mca}\gdef\@journalfull{Mathematical and Computational Applications}\gdef\@journalshort{Math. Comput. Appl.}\gdef\@doiabbr{mca}\gdef\@ISSN{2297-8747}}
\DeclareOption{measurements}{\gdef\@journal{measurements}\gdef\@journalfull{Measurements}\gdef\@journalshort{Measurements}\gdef\@doiabbr{measurements}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{medicina}{\gdef\@journal{medicina}\gdef\@journalfull{Medicina}\gdef\@journalshort{Medicina}\gdef\@doiabbr{medicina}\gdef\@ISSN{1648-9144}}
\DeclareOption{medicines}{\gdef\@journal{medicines}\gdef\@journalfull{Medicines}\gdef\@journalshort{Medicines}\gdef\@doiabbr{medicines}\gdef\@ISSN{2305-6320}}
\DeclareOption{medsci}{\gdef\@journal{medsci}\gdef\@journalfull{Medical Sciences}\gdef\@journalshort{Med. Sci.}\gdef\@doiabbr{medsci}\gdef\@ISSN{2076-3271}}
\DeclareOption{membranes}{\gdef\@journal{membranes}\gdef\@journalfull{Membranes}\gdef\@journalshort{Membranes}\gdef\@doiabbr{membranes}\gdef\@ISSN{2077-0375}}
\DeclareOption{merits}{\gdef\@journal{merits}\gdef\@journalfull{Merits}\gdef\@journalshort{Merits}\gdef\@doiabbr{merits}\gdef\@ISSN{2673-8104}\gdef\@continuouspages{yes}}
\DeclareOption{metabolites}{\gdef\@journal{metabolites}\gdef\@journalfull{Metabolites}\gdef\@journalshort{Metabolites}\gdef\@doiabbr{metabo}\gdef\@ISSN{2218-1989}}
\DeclareOption{metals}{\gdef\@journal{metals}\gdef\@journalfull{Metals}\gdef\@journalshort{Metals}\gdef\@doiabbr{met}\gdef\@ISSN{2075-4701}}
\DeclareOption{meteorology}{\gdef\@journal{meteorology}\gdef\@journalfull{Meteorology}\gdef\@journalshort{Meteorology}\gdef\@doiabbr{meteorology}\gdef\@ISSN{2674-0494}\gdef\@continuouspages{yes}}
\DeclareOption{methane}{\gdef\@journal{methane}\gdef\@journalfull{Methane}\gdef\@journalshort{Methane}\gdef\@doiabbr{methane}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{metrology}{\gdef\@journal{metrology}\gdef\@journalfull{Metrology}\gdef\@journalshort{Metrology}\gdef\@doiabbr{metrology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{micro}{\gdef\@journal{micro}\gdef\@journalfull{Micro}\gdef\@journalshort{Micro}\gdef\@doiabbr{micro}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{microarrays}{\gdef\@journal{microarrays}\gdef\@journalfull{Microarrays}\gdef\@journalshort{Microarrays}\gdef\@doiabbr{microarrays}\gdef\@ISSN{2076-3905}}
\DeclareOption{microbiolres}{\gdef\@journal{microbiolres}\gdef\@journalfull{Microbiology Research}\gdef\@journalshort{Microbiol. Res.}\gdef\@doiabbr{microbiolres}\gdef\@ISSN{2036-7481}\gdef\@continuouspages{yes}}
\DeclareOption{micromachines}{\gdef\@journal{micromachines}\gdef\@journalfull{Micromachines}\gdef\@journalshort{Micromachines}\gdef\@doiabbr{mi}\gdef\@ISSN{2072-666X}}
\DeclareOption{microorganisms}{\gdef\@journal{microorganisms}\gdef\@journalfull{Microorganisms}\gdef\@journalshort{Microorganisms}\gdef\@doiabbr{microorganisms}\gdef\@ISSN{2076-2607}}
\DeclareOption{microplastics}{\gdef\@journal{microplastics}\gdef\@journalfull{Microplastics}\gdef\@journalshort{Microplastics}\gdef\@doiabbr{microplastics}\gdef\@ISSN{2673-8929}\gdef\@continuouspages{yes}}
\DeclareOption{minerals}{\gdef\@journal{minerals}\gdef\@journalfull{Minerals}\gdef\@journalshort{Minerals}\gdef\@doiabbr{min}\gdef\@ISSN{2075-163X}}
\DeclareOption{mining}{\gdef\@journal{mining}\gdef\@journalfull{Mining}\gdef\@journalshort{Mining}\gdef\@doiabbr{mining}\gdef\@ISSN{2673-6489}\gdef\@continuouspages{yes}}
\DeclareOption{modelling}{\gdef\@journal{modelling}\gdef\@journalfull{Modelling}\gdef\@journalshort{Modelling}\gdef\@doiabbr{modelling}\gdef\@ISSN{2673-3951}\gdef\@continuouspages{yes}}
\DeclareOption{molbank}{\gdef\@journal{molbank}\gdef\@journalfull{Molbank}\gdef\@journalshort{Molbank}\gdef\@doiabbr{M}\gdef\@ISSN{1422-8599}}
\DeclareOption{molecules}{\gdef\@journal{molecules}\gdef\@journalfull{Molecules}\gdef\@journalshort{Molecules}\gdef\@doiabbr{molecules}\gdef\@ISSN{1420-3049}}
\DeclareOption{mps}{\gdef\@journal{mps}\gdef\@journalfull{Methods and Protocols}\gdef\@journalshort{Methods Protoc.}\gdef\@doiabbr{mps}\gdef\@ISSN{2409-9279}}
\DeclareOption{msf}{\gdef\@journal{msf}\gdef\@journalfull{Medical Sciences Forum}\gdef\@journalshort{Med. Sci. Forum}\gdef\@doiabbr{msf}\gdef\@ISSN{2673-9992}}
\DeclareOption{mti}{\gdef\@journal{mti}\gdef\@journalfull{Multimodal Technologies and Interaction}\gdef\@journalshort{Multimodal Technol. Interact.}\gdef\@doiabbr{mti}\gdef\@ISSN{2414-4088}}
\DeclareOption{muscles}{\gdef\@journal{muscles}\gdef\@journalfull{Muscles}\gdef\@journalshort{Muscles}\gdef\@doiabbr{muscles}\gdef\@ISSN{2813-0413}\gdef\@continuouspages{yes}}
\DeclareOption{nanoenergyadv}{\gdef\@journal{nanoenergyadv}\gdef\@journalfull{Nanoenergy Advances}\gdef\@journalshort{Nanoenergy Adv.}\gdef\@doiabbr{nanoenergyadv}\gdef\@ISSN{2673-706X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomanufacturing}{\gdef\@journal{nanomanufacturing}\gdef\@journalfull{Nanomanufacturing}\gdef\@journalshort{Nanomanufacturing}\gdef\@doiabbr{nanomanufacturing}\gdef\@ISSN{2673-687X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomaterials}{\gdef\@journal{nanomaterials}\gdef\@journalfull{Nanomaterials}\gdef\@journalshort{Nanomaterials}\gdef\@doiabbr{nano}\gdef\@ISSN{2079-4991}}
\DeclareOption{ncrna}{\gdef\@journal{ncrna}\gdef\@journalfull{Non-Coding RNA}\gdef\@journalshort{Non-Coding RNA}\gdef\@doiabbr{ncrna}\gdef\@ISSN{2311-553X}}
\DeclareOption{network}{\gdef\@journal{network}\gdef\@journalfull{Network}\gdef\@journalshort{Network}\gdef\@doiabbr{network}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{neuroglia}{\gdef\@journal{neuroglia}\gdef\@journalfull{Neuroglia}\gdef\@journalshort{Neuroglia}\gdef\@doiabbr{neuroglia}\gdef\@ISSN{2571-6980}\gdef\@continuouspages{yes}}
\DeclareOption{neurolint}{\gdef\@journal{neurolint}\gdef\@journalfull{Neurology International}\gdef\@journalshort{Neurol. Int.}\gdef\@doiabbr{neurolint}\gdef\@ISSN{2035-8377}\gdef\@continuouspages{yes}}
\DeclareOption{neurosci}{\gdef\@journal{neurosci}\gdef\@journalfull{NeuroSci}\gdef\@journalshort{NeuroSci}\gdef\@doiabbr{neurosci}\gdef\@ISSN{2673-4087}\gdef\@continuouspages{yes}}
\DeclareOption{nitrogen}{\gdef\@journal{nitrogen}\gdef\@journalfull{Nitrogen}\gdef\@journalshort{Nitrogen}\gdef\@doiabbr{nitrogen}\gdef\@ISSN{2504-3129}\gdef\@continuouspages{yes}}
\DeclareOption{notspecified}{\gdef\@journal{notspecified}\gdef\@journalfull{Journal Not Specified}\gdef\@journalshort{Journal Not Specified}\gdef\@doiabbr{}\gdef\@ISSN{}}
%%\DeclareOption{nri}{\gdef\@journal{nri}\gdef\@journalfull{Natural Resources Informatics}\gdef\@journalshort{Nat. Resour. Inform.}\gdef\@doiabbr{nri}\gdef\@ISSN{2673-981X}\gdef\@continuouspages{yes}}
\DeclareOption{nursrep}{\gdef\@journal{nursrep}\gdef\@journalfull{Nursing Reports}\gdef\@journalshort{Nurs. Rep.}\gdef\@doiabbr{nursrep}\gdef\@ISSN{2039-4403}\gdef\@continuouspages{yes}}
\DeclareOption{nutraceuticals}{\gdef\@journal{nutraceuticals}\gdef\@journalfull{Nutraceuticals}\gdef\@journalshort{Nutraceuticals}\gdef\@doiabbr{nutraceuticals}\gdef\@ISSN{1661-3821}\gdef\@continuouspages{yes}}
\DeclareOption{nutrients}{\gdef\@journal{nutrients}\gdef\@journalfull{Nutrients}\gdef\@journalshort{Nutrients}\gdef\@doiabbr{nu}\gdef\@ISSN{2072-6643}}
\DeclareOption{obesities}{\gdef\@journal{obesities}\gdef\@journalfull{Obesities}\gdef\@journalshort{Obesities}\gdef\@doiabbr{obesities}\gdef\@ISSN{2673-4168}\gdef\@continuouspages{yes}}
\DeclareOption{oceans}{\gdef\@journal{oceans}\gdef\@journalfull{Oceans}\gdef\@journalshort{Oceans}\gdef\@doiabbr{oceans}\gdef\@ISSN{2673-1924}\gdef\@continuouspages{yes}}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalfull{Journal of Otorhinolaryngology Hearing and Balance Medicine}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@doiabbr{ohbm}\gdef\@ISSN{2504-463X}}
\DeclareOption{onco}{\gdef\@journal{onco}\gdef\@journalfull{Onco}\gdef\@journalshort{Onco}\gdef\@doiabbr{onco}\gdef\@ISSN{2673-7523}\gdef\@continuouspages{yes}}
%\DeclareOption{oncopathology}{\gdef\@journal{oncopathology}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{optics}{\gdef\@journal{optics}\gdef\@journalfull{Optics}\gdef\@journalshort{Optics}\gdef\@doiabbr{opt}\gdef\@ISSN{2673-3269}\gdef\@continuouspages{yes}}
\DeclareOption{oral}{\gdef\@journal{oral}\gdef\@journalfull{Oral}\gdef\@journalshort{Oral}\gdef\@doiabbr{oral}\gdef\@ISSN{2673-6373}\gdef\@continuouspages{yes}}
\DeclareOption{organics}{\gdef\@journal{organics}\gdef\@journalfull{Organics}\gdef\@journalshort{Organics}\gdef\@doiabbr{org}\gdef\@ISSN{2673-401X}\gdef\@continuouspages{yes}}
\DeclareOption{organoids}{\gdef\@journal{organoids}\gdef\@journalfull{Organoids}\gdef\@journalshort{Organoids}\gdef\@doiabbr{organoids}\gdef\@ISSN{2674-1172}\gdef\@continuouspages{yes}}
\DeclareOption{osteology}{\gdef\@journal{osteology}\gdef\@journalfull{Osteology}\gdef\@journalshort{Osteology}\gdef\@doiabbr{osteology}\gdef\@ISSN{2673-4036}\gdef\@continuouspages{yes}}
\DeclareOption{oxygen}{\gdef\@journal{oxygen}\gdef\@journalfull{Oxygen}\gdef\@journalshort{Oxygen}\gdef\@doiabbr{oxygen}\gdef\@ISSN{2673-9801}\gdef\@continuouspages{yes}}
\DeclareOption{parasites}{\gdef\@journal{parasites}\gdef\@journalfull{Parasites}\gdef\@journalshort{Parasites}\gdef\@doiabbr{parasites}\gdef\@ISSN{2673-5946}}
\DeclareOption{parasitologia}{\gdef\@journal{parasitologia}\gdef\@journalfull{Parasitologia}\gdef\@journalshort{Parasitologia}\gdef\@doiabbr{parasitologia}\gdef\@ISSN{2673-6772}\gdef\@continuouspages{yes}}
\DeclareOption{particles}{\gdef\@journal{particles}\gdef\@journalfull{Particles}\gdef\@journalshort{Particles}\gdef\@doiabbr{particles}\gdef\@ISSN{2571-712X}\gdef\@continuouspages{yes}}
\DeclareOption{pathogens}{\gdef\@journal{pathogens}\gdef\@journalfull{Pathogens}\gdef\@journalshort{Pathogens}\gdef\@doiabbr{pathogens}\gdef\@ISSN{2076-0817}}
\DeclareOption{pathophysiology}{\gdef\@journal{pathophysiology}\gdef\@journalfull{Pathophysiology}\gdef\@journalshort{Pathophysiology}\gdef\@doiabbr{pathophysiology}\gdef\@ISSN{0928-4680}\gdef\@continuouspages{yes}}
\DeclareOption{pediatrrep}{\gdef\@journal{pediatrrep}\gdef\@journalfull{Pediatric Reports}\gdef\@journalshort{Pediatr. Rep.}\gdef\@doiabbr{pediatric}\gdef\@ISSN{2036-7503}\gdef\@continuouspages{yes}}
\DeclareOption{pharmaceuticals}{\gdef\@journal{pharmaceuticals}\gdef\@journalfull{Pharmaceuticals}\gdef\@journalshort{Pharmaceuticals}\gdef\@doiabbr{ph}\gdef\@ISSN{1424-8247}}
\DeclareOption{pharmaceutics}{\gdef\@journal{pharmaceutics}\gdef\@journalfull{Pharmaceutics}\gdef\@journalshort{Pharmaceutics}\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}}
\DeclareOption{pharmacoepidemiology}{\gdef\@journal{pharmacoepidemiology}\gdef\@journalfull{Pharmacoepidemiology}\gdef\@journalshort{Pharmacoepidemiology}\gdef\@doiabbr{pharma}\gdef\@ISSN{2813-0618}\gdef\@continuouspages{yes}}
\DeclareOption{pharmacy}{\gdef\@journal{pharmacy}\gdef\@journalfull{Pharmacy}\gdef\@journalshort{Pharmacy}\gdef\@doiabbr{pharmacy}\gdef\@ISSN{2226-4787}}
\DeclareOption{philosophies}{\gdef\@journal{philosophies}\gdef\@journalfull{Philosophies}\gdef\@journalshort{Philosophies}\gdef\@doiabbr{philosophies}\gdef\@ISSN{2409-9287}}
\DeclareOption{photochem}{\gdef\@journal{photochem}\gdef\@journalfull{Photochem}\gdef\@journalshort{Photochem}\gdef\@doiabbr{photochem}\gdef\@ISSN{2673-7256}\gdef\@continuouspages{yes}}
\DeclareOption{photonics}{\gdef\@journal{photonics}\gdef\@journalfull{Photonics}\gdef\@journalshort{Photonics}\gdef\@doiabbr{photonics}\gdef\@ISSN{2304-6732}}
\DeclareOption{phycology}{\gdef\@journal{phycology}\gdef\@journalfull{Phycology}\gdef\@journalshort{Phycology}\gdef\@doiabbr{phycology}\gdef\@ISSN{2673-9410}\gdef\@continuouspages{yes}}
\DeclareOption{physchem}{\gdef\@journal{physchem}\gdef\@journalfull{Physchem}\gdef\@journalshort{Physchem}\gdef\@doiabbr{physchem}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{physics}{\gdef\@journal{physics}\gdef\@journalfull{Physics}\gdef\@journalshort{Physics}\gdef\@doiabbr{physics}\gdef\@ISSN{2624-8174}\gdef\@continuouspages{yes}}
\DeclareOption{physiologia}{\gdef\@journal{physiologia}\gdef\@journalfull{Physiologia}\gdef\@journalshort{Physiologia}\gdef\@doiabbr{physiologia}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{plants}{\gdef\@journal{plants}\gdef\@journalfull{Plants}\gdef\@journalshort{Plants}\gdef\@doiabbr{plants}\gdef\@ISSN{2223-7747}}
\DeclareOption{plasma}{\gdef\@journal{plasma}\gdef\@journalfull{Plasma}\gdef\@journalshort{Plasma}\gdef\@doiabbr{plasma}\gdef\@ISSN{2571-6182}\gdef\@continuouspages{yes}}
\DeclareOption{pollutants}{\gdef\@journal{pollutants}\gdef\@journalfull{Pollutants}\gdef\@journalshort{Pollutants}\gdef\@doiabbr{pollutants}\gdef\@ISSN{2673-4672}\gdef\@continuouspages{yes}}
\DeclareOption{polymers}{\gdef\@journal{polymers}\gdef\@journalfull{Polymers}\gdef\@journalshort{Polymers}\gdef\@doiabbr{polym}\gdef\@ISSN{2073-4360}}
\DeclareOption{polysaccharides}{\gdef\@journal{polysaccharides}\gdef\@journalfull{Polysaccharides}\gdef\@journalshort{Polysaccharides}\gdef\@doiabbr{polysaccharides}\gdef\@ISSN{2673-4176}\gdef\@continuouspages{yes}}
\DeclareOption{poultry}{\gdef\@journal{poultry}\gdef\@journalfull{Poultry}\gdef\@journalshort{Poultry}\gdef\@doiabbr{poultry}\gdef\@ISSN{2674-1164}\gdef\@continuouspages{yes}}
\DeclareOption{powders}{\gdef\@journal{powders}\gdef\@journalfull{Powders}\gdef\@journalshort{Powders}\gdef\@doiabbr{powders}\gdef\@ISSN{2674-0516}\gdef\@continuouspages{yes}}
\DeclareOption{preprints}{\gdef\@journal{preprints}\gdef\@journalfull{Preprints}\gdef\@journalshort{Preprints}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{proceedings}{\gdef\@journal{proceedings}\gdef\@journalfull{Proceedings}\gdef\@journalshort{Proceedings}\gdef\@doiabbr{proceedings}\gdef\@ISSN{2504-3900}}
\DeclareOption{processes}{\gdef\@journal{processes}\gdef\@journalfull{Processes}\gdef\@journalshort{Processes}\gdef\@doiabbr{pr}\gdef\@ISSN{2227-9717}}
\DeclareOption{prosthesis}{\gdef\@journal{prosthesis}\gdef\@journalfull{Prosthesis}\gdef\@journalshort{Prosthesis}\gdef\@doiabbr{prosthesis}\gdef\@ISSN{2673-1592}\gdef\@continuouspages{yes}}
\DeclareOption{proteomes}{\gdef\@journal{proteomes}\gdef\@journalfull{Proteomes}\gdef\@journalshort{Proteomes}\gdef\@doiabbr{proteomes}\gdef\@ISSN{2227-7382}}
\DeclareOption{psf}{\gdef\@journal{psf}\gdef\@journalfull{Physical Sciences Forum}\gdef\@journalshort{Phys. Sci. Forum}\gdef\@doiabbr{psf}\gdef\@ISSN{2673-9984}}
\DeclareOption{psych}{\gdef\@journal{psych}\gdef\@journalfull{Psych}\gdef\@journalshort{Psych}\gdef\@doiabbr{psych}\gdef\@ISSN{2624-8611}\gdef\@continuouspages{yes}}
\DeclareOption{psychiatryint}{\gdef\@journal{psychiatryint}\gdef\@journalfull{Psychiatry International}\gdef\@journalshort{Psychiatry Int.}\gdef\@doiabbr{psychiatryint}\gdef\@ISSN{2673-5318}\gdef\@continuouspages{yes}}
\DeclareOption{psychoactives}{\gdef\@journal{psychoactives}\gdef\@journalfull{Psychoactives}\gdef\@journalshort{Psychoactives}\gdef\@doiabbr{psychoactives}\gdef\@ISSN{2813-1851}\gdef\@continuouspages{yes}}
\DeclareOption{publications}{\gdef\@journal{publications}\gdef\@journalfull{Publications}\gdef\@journalshort{Publications}\gdef\@doiabbr{publications}\gdef\@ISSN{2304-6775}}
\DeclareOption{quantumrep}{\gdef\@journal{quantumrep}\gdef\@journalfull{Quantum Reports}\gdef\@journalshort{Quantum Rep.}\gdef\@doiabbr{quantum}\gdef\@ISSN{2624-960X}\gdef\@continuouspages{yes}}
\DeclareOption{quaternary}{\gdef\@journal{quaternary}\gdef\@journalfull{Quaternary}\gdef\@journalshort{Quaternary}\gdef\@doiabbr{quat}\gdef\@ISSN{2571-550X}}
\DeclareOption{qubs}{\gdef\@journal{qubs}\gdef\@journalfull{Quantum Beam Science}\gdef\@journalshort{Quantum Beam Sci.}\gdef\@doiabbr{qubs}\gdef\@ISSN{2412-382X}}
\DeclareOption{radiation}{\gdef\@journal{radiation}\gdef\@journalfull{Radiation}\gdef\@journalshort{Radiation}\gdef\@doiabbr{radiation}\gdef\@ISSN{2673-592X}\gdef\@continuouspages{yes}}
\DeclareOption{reactions}{\gdef\@journal{reactions}\gdef\@journalfull{Reactions}\gdef\@journalshort{Reactions}\gdef\@doiabbr{reactions}\gdef\@ISSN{2624-781X}\gdef\@continuouspages{yes}}
\DeclareOption{receptors}{\gdef\@journal{receptors}\gdef\@journalfull{Receptors}\gdef\@journalshort{Receptors}\gdef\@doiabbr{receptors}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{recycling}{\gdef\@journal{recycling}\gdef\@journalfull{Recycling}\gdef\@journalshort{Recycling}\gdef\@doiabbr{recycling}\gdef\@ISSN{2313-4321}}
\DeclareOption{regeneration}{\gdef\@journal{regeneration}\gdef\@journalfull{Regeneration}\gdef\@journalshort{Regeneration}\gdef\@doiabbr{regeneration}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{religions}{\gdef\@journal{religions}\gdef\@journalfull{Religions}\gdef\@journalshort{Religions}\gdef\@doiabbr{rel}\gdef\@ISSN{2077-1444}}
\DeclareOption{remotesensing}{\gdef\@journal{remotesensing}\gdef\@journalfull{Remote Sensing}\gdef\@journalshort{Remote Sens.}\gdef\@doiabbr{rs}\gdef\@ISSN{2072-4292}}
\DeclareOption{reports}{\gdef\@journal{reports}\gdef\@journalfull{Reports}\gdef\@journalshort{Reports}\gdef\@doiabbr{reports}\gdef\@ISSN{2571-841X}}
\DeclareOption{reprodmed}{\gdef\@journal{reprodmed}\gdef\@journalfull{Reproductive Medicine}\gdef\@journalshort{Reprod. Med.}\gdef\@doiabbr{reprodmed}\gdef\@ISSN{2673-3897}\gdef\@continuouspages{yes}}
\DeclareOption{resources}{\gdef\@journal{resources}\gdef\@journalfull{Resources}\gdef\@journalshort{Resources}\gdef\@doiabbr{resources}\gdef\@ISSN{2079-9276}}
\DeclareOption{rheumato}{\gdef\@journal{rheumato}\gdef\@journalfull{Rheumato}\gdef\@journalshort{Rheumato}\gdef\@doiabbr{rheumato}\gdef\@ISSN{2674-0621}\gdef\@continuouspages{yes}}
\DeclareOption{risks}{\gdef\@journal{risks}\gdef\@journalfull{Risks}\gdef\@journalshort{Risks}\gdef\@doiabbr{risks}\gdef\@ISSN{2227-9091}}
\DeclareOption{robotics}{\gdef\@journal{robotics}\gdef\@journalfull{Robotics}\gdef\@journalshort{Robotics}\gdef\@doiabbr{robotics}\gdef\@ISSN{2218-6581}}
\DeclareOption{ruminants}{\gdef\@journal{ruminants}\gdef\@journalfull{Ruminants}\gdef\@journalshort{Ruminants}\gdef\@doiabbr{ruminants}\gdef\@ISSN{2673-933X}\gdef\@continuouspages{yes}}
\DeclareOption{safety}{\gdef\@journal{safety}\gdef\@journalfull{Safety}\gdef\@journalshort{Safety}\gdef\@doiabbr{safety}\gdef\@ISSN{2313-576X}}
\DeclareOption{sci}{\gdef\@journal{sci}\gdef\@journalfull{Sci}\gdef\@journalshort{Sci}\gdef\@doiabbr{sci}\gdef\@ISSN{2413-4155}}
\DeclareOption{scipharm}{\gdef\@journal{scipharm}\gdef\@journalfull{Scientia Pharmaceutica}\gdef\@journalshort{Sci. Pharm.}\gdef\@doiabbr{scipharm}\gdef\@ISSN{2218-0532}}
\DeclareOption{seeds}{\gdef\@journal{seeds}\gdef\@journalfull{Seeds}\gdef\@journalshort{Seeds}\gdef\@doiabbr{seeds}\gdef\@ISSN{2674-1024}\gdef\@continuouspages{yes}}
\DeclareOption{sensors}{\gdef\@journal{sensors}\gdef\@journalfull{Sensors}\gdef\@journalshort{Sensors}\gdef\@doiabbr{s}\gdef\@ISSN{1424-8220}}
\DeclareOption{separations}{\gdef\@journal{separations}\gdef\@journalfull{Separations}\gdef\@journalshort{Separations}\gdef\@doiabbr{separations}\gdef\@ISSN{2297-8739}}
\DeclareOption{sexes}{\gdef\@journal{sexes}\gdef\@journalfull{Sexes}\gdef\@journalshort{Sexes}\gdef\@doiabbr{sexes}\gdef\@ISSN{2411-5118}\gdef\@continuouspages{yes}}
\DeclareOption{signals}{\gdef\@journal{signals}\gdef\@journalfull{Signals}\gdef\@journalshort{Signals}\gdef\@doiabbr{signals}\gdef\@ISSN{2624-6120}\gdef\@continuouspages{yes}}
\DeclareOption{sinusitis}{\gdef\@journal{sinusitis}\gdef\@journalfull{Sinusitis}\gdef\@journalshort{Sinusitis}\gdef\@doiabbr{sinusitis}\gdef\@ISSN{2309-107X}\gdef\@continuouspages{yes}}
\DeclareOption{skins}{\gdef\@journal{skins}\gdef\@journalfull{Skins}\gdef\@journalshort{Skins}\gdef\@doiabbr{skins}\gdef\@ISSN{}}
\DeclareOption{smartcities}{\gdef\@journal{smartcities}\gdef\@journalfull{Smart Cities}\gdef\@journalshort{Smart Cities}\gdef\@doiabbr{smartcities}\gdef\@ISSN{2624-6511}\gdef\@continuouspages{yes}}
\DeclareOption{sna}{\gdef\@journal{sna}\gdef\@journalfull{Sinusitis and Asthma}\gdef\@journalshort{Sinusitis Asthma}\gdef\@doiabbr{sna}\gdef\@ISSN{2624-7003}}
\DeclareOption{societies}{\gdef\@journal{societies}\gdef\@journalfull{Societies}\gdef\@journalshort{Societies}\gdef\@doiabbr{soc}\gdef\@ISSN{2075-4698}}
\DeclareOption{socsci}{\gdef\@journal{socsci}\gdef\@journalfull{Social Sciences}\gdef\@journalshort{Soc. Sci.}\gdef\@doiabbr{socsci}\gdef\@ISSN{2076-0760}}
\DeclareOption{software}{\gdef\@journal{software}\gdef\@journalfull{Software}\gdef\@journalshort{Software}\gdef\@doiabbr{software}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{soilsystems}{\gdef\@journal{soilsystems}\gdef\@journalfull{Soil Systems}\gdef\@journalshort{Soil Syst.}\gdef\@doiabbr{soilsystems}\gdef\@ISSN{2571-8789}}
\DeclareOption{solar}{\gdef\@journal{solar}\gdef\@journalfull{Solar}\gdef\@journalshort{Solar}\gdef\@doiabbr{solar}\gdef\@ISSN{2673-9941}\gdef\@continuouspages{yes}}
\DeclareOption{solids}{\gdef\@journal{solids}\gdef\@journalfull{Solids}\gdef\@journalshort{Solids}\gdef\@doiabbr{solids}\gdef\@ISSN{2673-6497}\gdef\@continuouspages{yes}}
\DeclareOption{spectroscj}{\gdef\@journal{spectroscj}\gdef\@journalfull{Spectroscopy Journal}\gdef\@journalshort{Spectrosc. J.}\gdef\@doiabbr{spectroscj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{sports}{\gdef\@journal{sports}\gdef\@journalfull{Sports}\gdef\@journalshort{Sports}\gdef\@doiabbr{sports}\gdef\@ISSN{2075-4663}}
\DeclareOption{standards}{\gdef\@journal{standards}\gdef\@journalfull{Standards}\gdef\@journalshort{Standards}\gdef\@doiabbr{standards}\gdef\@ISSN{2305-6703}\gdef\@continuouspages{yes}}
\DeclareOption{stats}{\gdef\@journal{stats}\gdef\@journalfull{Stats}\gdef\@journalshort{Stats}\gdef\@doiabbr{stats}\gdef\@ISSN{2571-905X}\gdef\@continuouspages{yes}}
\DeclareOption{std}{\gdef\@journal{std}\gdef\@journalfull{Surgical Techniques Development}\gdef\@journalshort{Surg. Tech. Dev.}\gdef\@doiabbr{std}\gdef\@ISSN{2038-9582}\gdef\@continuouspages{yes}}
\DeclareOption{stresses}{\gdef\@journal{stresses}\gdef\@journalfull{Stresses}\gdef\@journalshort{Stresses}\gdef\@doiabbr{stresses}\gdef\@ISSN{2673-7140}\gdef\@continuouspages{yes}}
\DeclareOption{surfaces}{\gdef\@journal{surfaces}\gdef\@journalfull{Surfaces}\gdef\@journalshort{Surfaces}\gdef\@doiabbr{surfaces}\gdef\@ISSN{2571-9637}\gdef\@continuouspages{yes}}
\DeclareOption{surgeries}{\gdef\@journal{surgeries}\gdef\@journalfull{Surgeries}\gdef\@journalshort{Surgeries}\gdef\@doiabbr{surgeries}\gdef\@ISSN{2017-2017}\gdef\@continuouspages{yes}}
\DeclareOption{suschem}{\gdef\@journal{suschem}\gdef\@journalfull{Sustainable Chemistry}\gdef\@journalshort{Sustain. Chem.}\gdef\@doiabbr{suschem}\gdef\@ISSN{2673-4079}\gdef\@continuouspages{yes}}
\DeclareOption{sustainability}{\gdef\@journal{sustainability}\gdef\@journalfull{Sustainability}\gdef\@journalshort{Sustainability}\gdef\@doiabbr{su}\gdef\@ISSN{2071-1050}}
\DeclareOption{symmetry}{\gdef\@journal{symmetry}\gdef\@journalfull{Symmetry}\gdef\@journalshort{Symmetry}\gdef\@doiabbr{sym}\gdef\@ISSN{2073-8994}}
\DeclareOption{synbio}{\gdef\@journal{synbio}\gdef\@journalfull{Synbio}\gdef\@journalshort{Synbio}\gdef\@doiabbr{synbio}\gdef\@ISSN{2674-0583}\gdef\@continuouspages{yes}}
\DeclareOption{systems}{\gdef\@journal{systems}\gdef\@journalfull{Systems}\gdef\@journalshort{Systems}\gdef\@doiabbr{systems}\gdef\@ISSN{2079-8954}}
\DeclareOption{targets}{\gdef\@journal{targets}\gdef\@journalfull{Targets}\gdef\@journalshort{Targets}\gdef\@doiabbr{targets}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{taxonomy}{\gdef\@journal{taxonomy}\gdef\@journalfull{Taxonomy}\gdef\@journalshort{Taxonomy}\gdef\@doiabbr{taxonomy}\gdef\@ISSN{2673-6500}\gdef\@continuouspages{yes}}
\DeclareOption{technologies}{\gdef\@journal{technologies}\gdef\@journalfull{Technologies}\gdef\@journalshort{Technologies}\gdef\@doiabbr{technologies}\gdef\@ISSN{2227-7080}}
\DeclareOption{telecom}{\gdef\@journal{telecom}\gdef\@journalfull{Telecom}\gdef\@journalshort{Telecom}\gdef\@doiabbr{telecom}\gdef\@ISSN{2673-4001}\gdef\@continuouspages{yes}}
\DeclareOption{test}{\gdef\@journal{test}\gdef\@journalfull{Test}\gdef\@journalshort{Test}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{textiles}{\gdef\@journal{textiles}\gdef\@journalfull{Textiles}\gdef\@journalshort{Textiles}\gdef\@doiabbr{textiles}\gdef\@ISSN{2673-7248}\gdef\@continuouspages{yes}}
\DeclareOption{thalassrep}{\gdef\@journal{thalassrep}\gdef\@journalfull{Thalassemia Reports}\gdef\@journalshort{Thalass. Rep.}\gdef\@doiabbr{thalassrep}\gdef\@ISSN{2039-4365}\gdef\@continuouspages{yes}}
\DeclareOption{thermo}{\gdef\@journal{thermo}\gdef\@journalfull{Thermo}\gdef\@journalshort{Thermo}\gdef\@doiabbr{thermo}\gdef\@ISSN{2673-7264}\gdef\@continuouspages{yes}}
\DeclareOption{tomography}{\gdef\@journal{tomography}\gdef\@journalfull{Tomography}\gdef\@journalshort{Tomography}\gdef\@doiabbr{tomography}\gdef\@ISSN{2379-139X}\gdef\@continuouspages{yes}}
\DeclareOption{tourismhosp}{\gdef\@journal{tourismhosp}\gdef\@journalfull{Tourism and Hospitality}\gdef\@journalshort{Tour. Hosp.}\gdef\@doiabbr{tourhosp}\gdef\@ISSN{2673-5768}\gdef\@continuouspages{yes}}
\DeclareOption{toxics}{\gdef\@journal{toxics}\gdef\@journalfull{Toxics}\gdef\@journalshort{Toxics}\gdef\@doiabbr{toxics}\gdef\@ISSN{2305-6304}}
\DeclareOption{toxins}{\gdef\@journal{toxins}\gdef\@journalfull{Toxins}\gdef\@journalshort{Toxins}\gdef\@doiabbr{toxins}\gdef\@ISSN{2072-6651}}
\DeclareOption{transplantology}{\gdef\@journal{transplantology}\gdef\@journalfull{Transplantology}\gdef\@journalshort{Transplantology}\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}\gdef\@continuouspages{yes}}
\DeclareOption{transportation}{\gdef\@journal{transportation}\gdef\@journalfull{Transportation}\gdef\@journalshort{Transportation}\gdef\@doiabbr{transportation}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{traumacare}{\gdef\@journal{traumacare}\gdef\@journalfull{Trauma Care}\gdef\@journalshort{Trauma Care}\gdef\@doiabbr{traumacare}\gdef\@ISSN{2673-866X}\gdef\@continuouspages{yes}}
\DeclareOption{traumas}{\gdef\@journal{traumas}\gdef\@journalfull{Traumas}\gdef\@journalshort{Traumas}\gdef\@doiabbr{traumas}\gdef\@ISSN{2673-7477}\gdef\@continuouspages{yes}}
\DeclareOption{tropicalmed}{\gdef\@journal{tropicalmed}\gdef\@journalfull{Tropical Medicine and Infectious Disease}\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@doiabbr{tropicalmed}\gdef\@ISSN{2414-6366}}
\DeclareOption{universe}{\gdef\@journal{universe}\gdef\@journalfull{Universe}\gdef\@journalshort{Universe}\gdef\@doiabbr{universe}\gdef\@ISSN{2218-1997}}
\DeclareOption{urbansci}{\gdef\@journal{urbansci}\gdef\@journalfull{Urban Science}\gdef\@journalshort{Urban Sci.}\gdef\@doiabbr{urbansci}\gdef\@ISSN{2413-8851}}
\DeclareOption{uro}{\gdef\@journal{uro}\gdef\@journalfull{Uro}\gdef\@journalshort{Uro}\gdef\@doiabbr{uro}\gdef\@ISSN{2673-4397}\gdef\@continuouspages{yes}}
\DeclareOption{vaccines}{\gdef\@journal{vaccines}\gdef\@journalfull{Vaccines}\gdef\@journalshort{Vaccines}\gdef\@doiabbr{vaccines}\gdef\@ISSN{2076-393X}}
\DeclareOption{vehicles}{\gdef\@journal{vehicles}\gdef\@journalfull{Vehicles}\gdef\@journalshort{Vehicles}\gdef\@doiabbr{vehicles}\gdef\@ISSN{2624-8921}\gdef\@continuouspages{yes}}
\DeclareOption{venereology}{\gdef\@journal{venereology}\gdef\@journalfull{Venereology}\gdef\@journalshort{Venereology}\gdef\@doiabbr{venereology}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{vetsci}{\gdef\@journal{vetsci}\gdef\@journalfull{Veterinary Sciences}\gdef\@journalshort{Vet. Sci.}\gdef\@doiabbr{vetsci}\gdef\@ISSN{2306-7381}}
\DeclareOption{vibration}{\gdef\@journal{vibration}\gdef\@journalfull{Vibration}\gdef\@journalshort{Vibration}\gdef\@doiabbr{vibration}\gdef\@ISSN{2571-631X}\gdef\@continuouspages{yes}}
\DeclareOption{virtualworlds}{\gdef\@journal{virtualworlds}\gdef\@journalfull{Virtual Worlds}\gdef\@journalshort{Virtual Worlds}\gdef\@doiabbr{virtualworlds}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{viruses}{\gdef\@journal{viruses}\gdef\@journalfull{Viruses}\gdef\@journalshort{Viruses}\gdef\@doiabbr{v}\gdef\@ISSN{1999-4915}}
\DeclareOption{vision}{\gdef\@journal{vision}\gdef\@journalfull{Vision}\gdef\@journalshort{Vision}\gdef\@doiabbr{vision}\gdef\@ISSN{2411-5150}}
\DeclareOption{waste}{\gdef\@journal{waste}\gdef\@journalfull{Waste}\gdef\@journalshort{Waste}\gdef\@doiabbr{waste}\gdef\@ISSN{2813-0391}\gdef\@continuouspages{yes}}
\DeclareOption{water}{\gdef\@journal{water}\gdef\@journalfull{Water}\gdef\@journalshort{Water}\gdef\@doiabbr{w}\gdef\@ISSN{2073-4441}}
\DeclareOption{wem}{\gdef\@journal{wem}\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@journalshort{Wildl. Ecol. Manag.}\gdef\@doiabbr{}\gdef\@ISSN{1234-4321}}
\DeclareOption{wevj}{\gdef\@journal{wevj}\gdef\@journalfull{World Electric Vehicle Journal}\gdef\@journalshort{World Electr. Veh. J.}\gdef\@doiabbr{wevj}\gdef\@ISSN{2032-6653}}
\DeclareOption{wind}{\gdef\@journal{wind}\gdef\@journalfull{Wind}\gdef\@journalshort{Wind}\gdef\@doiabbr{wind}\gdef\@ISSN{2674-032X}\gdef\@continuouspages{yes}}
\DeclareOption{women}{\gdef\@journal{women}\gdef\@journalfull{Women}\gdef\@journalshort{Women}\gdef\@doiabbr{women}\gdef\@ISSN{2673-4184}\gdef\@continuouspages{yes}}
\DeclareOption{world}{\gdef\@journal{world}\gdef\@journalfull{World}\gdef\@journalshort{World}\gdef\@doiabbr{world}\gdef\@ISSN{2673-4060}\gdef\@continuouspages{yes}}
\DeclareOption{youth}{\gdef\@journal{youth}\gdef\@journalfull{Youth}\gdef\@journalshort{Youth}\gdef\@doiabbr{youth}\gdef\@ISSN{2673-995X}\gdef\@continuouspages{yes}}
\DeclareOption{zoonoticdis}{\gdef\@journal{zoonoticdis}\gdef\@journalfull{Zoonotic Diseases}\gdef\@journalshort{Zoonotic Dis.}\gdef\@doiabbr{zoonoticdis}\gdef\@ISSN{2813-0227}\gdef\@continuouspages{yes}}

### 2022-07-20 Manuscript/inter_spike_manuscript_mdpi.tex
Switched format for entropy journal (MDPI)

--- 2022-07-19 Manuscript/inter_spike_manuscript.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
-\begin{filecontents*}{example.eps}
-%!PS-Adobe-3.0 EPSF-3.0
-%%BoundingBox: 19 19 221 221
-%%CreationDate: Mon Sep 29 1997
-%%Creator: programmed by hand (JK)
-%%EndComments
-gsave
-newpath
-  20 20 moveto
-  20 220 lineto
-  220 220 lineto
-  220 20 lineto
-closepath
-2 setlinewidth
-gsave
-  .4 setgray fill
-grestore
-stroke
-grestore
-\end{filecontents*}
-%
-\RequirePackage{fix-cm}
-%
-%\documentclass{svjour3}                     % onecolumn (standard format)
-\documentclass[smallcondensed]{svjour3}    % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
+%  LaTeX support: latex@mdpi.com 
+%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
 
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-\usepackage{graphicx}
-%
+%=================================================================
+\documentclass[entropy,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
+The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
+This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
+For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+
+%=================================================================
+% MDPI internal commands
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother
+\pubvolume{1}
+\issuenum{1}
+\articlenumber{0}
+\pubyear{2022}
+\copyrightyear{2022}
+%\externaleditor{Academic Editor: Firstname Lastname}
+\datereceived{} 
+%\daterevised{} % Only for the journal Acoustics
+\dateaccepted{} 
+\datepublished{} 
+%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
+%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
+\hreflink{https://doi.org/} % If needed use \linebreak
+%\doinum{}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
+
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+
 % \usepackage{mathptmx}      % use Times fonts if available on your TeX system
@@
 %\usepackage{latexsym}
+\newcommand\hmmax{0}
+\newcommand\bmmax{0}
+
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 %\linenumbers\relax % Commence numbering lines
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
 \usepackage{mathptmx}
-\usepackage{amsmath}
 \usepackage{amssymb}
 \usepackage{statmath}
-\usepackage[numbers]{natbib}
-\usepackage{hyperref}
 \usepackage{enumitem}
@@
 \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
-%
-% Insert the name of "your journal" with
-\journalname{Nonlinear Dynamics}
-%
-\begin{document}
 
-\title{Recurrence spike spectra}
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
 
-\titlerunning{Recurrence spike spectra}        % if too long for running head
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{Spike spectra for recurrences}
 
-\author{K. Hauke Kraemer \and
-		Frank Hellmann \and
-		Mehrnaz Anvari \and
-        J\"urgen Kurths \and 
-        Norbert Marwan
-}
+% MDPI internal command: Title for citation in the left column
+\TitleCitation{Spike spectra for recurrences}
 
-\institute{K.
-Hauke Kraemer \and J\"urgen Kurths \and Norbert Marwan \and Frank Hellmann \and Mehrnaz Anvari \at Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam,
-Germany \email{hkraemer@pik-potsdam.de}\and
-           K. Hauke Kraemer \and J\"urgen Kurths \at Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany \and
-		   Norbert Marwan \at Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany \and
-		   J\"urgen Kurths \at Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany
-}
+% Author Orchid ID: enter ID or remove command
+\newcommand{\orcidauthorA}{0000-0002-9943-5391} % Add \orcidA{} behind the author's name
+%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
 
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
+% Authors, for the paper (add full first names)
+\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1,4}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}
 
-\maketitle
+%\longauthorlist{yes}
 
-\begin{abstract}
-A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
+% MDPI internal command: Authors, for metadata in PDF
+\AuthorNames{K. Hauke Kraemer, Frank Hellmann, Mehrnaz Anvari, J\"urgen Kurths and Norbert Marwan}
+
+% MDPI internal command: Authors, for citation in the left column
+\AuthorCitation{Kraemer, K.H..; Hellmann, F.; Anvari M.; Kurths, J.; Marwan, N.}
+% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany\\
+$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
+$^{3}$ \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany\\
+$^{4}$ \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany}
+
+% Contact information of the corresponding author
+\corres{Correspondence: hkraemer@pik-potsdam.de; marwan@pik-potsdam.de}
+
+% Current address and/or shared authorship
+%\firstnote{Current address: Affiliation 3.} 
+%\secondnote{These authors contributed equally to this work.}
+% The commands \thirdnote{} till \eighthnote{} are available for further notes
+
+%\simplesumm{} % Simple summary
+
+% Abstract (Do not insert blank lines, i.e. \\) 
+\abstract{A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
 clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
@@
 along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
-spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.
+spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
 
-\keywords{Bifurcations \and Recurrence Analysis \and Decomposition \and Frequency Analysis}
+% Keywords
+\keyword{Decomposition; Frequency Analysis; Recurrence Analysis; Bifurcations}
 \PACS{05.45.Tp, 05.90.+m, 89.90.+n, 02.70.Uu, 05.10.Ln, 05.45.-a, 05.45.Ac}
-\end{abstract}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
 
@@
 any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
-FT.
-In Section \ref{sec_tau_rr_application} we exemplify \sout{its use} \todo{the usage of inter spike spectrum} when transforming the $\tau$-RR of a system under study.
-In this case, the inter spike spectrum can unravel
-characteristic time scales of high dimensional systems, which is not possible when using a FT. \todo{Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized}
+FT. In Section \ref{sec_tau_rr_application} we exemplify the usage of inter spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter spike spectrum 
+can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Method}\label{sec_tau_rr_method}
 
-The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal \todo{what do you mean with any signal?
+The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal \todo{MA: what do you mean with any signal?
 do you mean to look at data set instead of $\tau$-RP or RP?}--
 is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
-different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal \todo{which} we want to transform. \sout{with}\todo{The signal has} length $N$ and 
+different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
@@
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure) \todo{$T$ in the following eqs.
-should not be $T_{is}$ to be consistent with the text?}\todo{$n$ in eq.6 is not clear for me}
+(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure) \todo{MA: $n$ in eq.6 is not clear for me}
 \begin{align}
-\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT(i)-i+T(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-T(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
+T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \label{eq_basis_matrix}
@@
 \begin{equation}
-\bf{X}^T\bf{\beta}=\bf{s}
+\bf{X}^T \boldsymbol\beta=\bf{s}
 \label{eq_linear_system}
 \end{equation}  
-has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
-particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
+has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
+particularly interested in those solutions, which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
 functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
-(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings 
+(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$.
+Finally, we group loadings
 which correspond to basis functions having the same period 
-$T_\text{is}$ into $\hat{\bf{\beta}}_f$ and obtain the 
-\textit{inter spike spectrum} by simply plotting $\hat{\bf{\beta}}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
+$T_\text{is}$ into $\hat{\boldsymbol\beta}_f$ and obtain the 
+\textit{inter spike spectrum} by simply plotting $\hat{\boldsymbol\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$
 (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
@@
 
-In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the proposed method \todo{which method?
-STLS?}must also deal with the free choice of the regression regularization parameter $\alpha$,
-which determines the sparsity of the regression coefficient vector $\hat{\bf{\beta}}$. Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small, 
-since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\bf{\beta}}$ is an exact solution of Eq.~\ref{eq_linear_system} and not sparse.
-On the other hand, only a sparse number
-of non-zero loadings in $\hat{\bf{\beta}}$ -- \textit{aka} \todo{what is aka?}peaks in the inter spike spectrum -- are obtained when $\alpha$ is sufficiently large.
-In this paper we select $\alpha$ such that the
-re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\bf{\beta}}$ matches a given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.
+In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
+which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$.
+Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small,
+since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~\ref{eq_linear_system} and not sparse. On the other hand, 
+only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter spike spectrum, are obtained when $\alpha$ is sufficiently large. 
+The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
+different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ matches a 
+given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.
 
-\section{Application}\label{sec_tau_rr_application}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{sec_tau_rr_application}
 
@@
   \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
-\todo[inline]{why you have not used STLS method here?} }
+\todo[inline]{MA: why you have not used STLS method here?} }
 \label{fig_tau_rr_example_roessler}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+
+Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
+The findings and their implications should be discussed in the broadest context possible.
+Future research directions may also be highlighted.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}\label{sec_tau_rr_conclusion}
@@
 
-\begin{acknowledgements}
-This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9). All computations have been carried out in MATLAB\textsuperscript{\textregistered} 
-and the Julia language and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
-\end{acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{6pt}
 
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
-\section*{Conflict of interest}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorcontributions{Conceptualization, KHK and FH; methodology, KHK, FH and NM; software, KHK and FH; validation, KHK, FH, MA and NM.; formal analysis, KHK; data curation, KHK and MA; writing---original draft preparation, KHK; writing---review and editing, KHK, FH, MA and NM; visualization, KHK; supervision, NM; project administration, JK; All authors have read and agreed to the published version of the manuscript.}
 
-The authors declare that they have no conflict of interest.
+\funding{This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9).}
 
-\section*{Code availability}
-
-The study that we present here is available as a fully reproducible code base
+\dataavailability{The study that we present here is available as a fully reproducible code base
 **Repository will be published and cited here, when accepted** and the method
@@
 when accepted** and as a MATLAB\textsuperscript{\textregistered} toolbox 
-**Toolbox will be published and cited here, when accepted**.
+**Toolbox will be published and cited here, when accepted**.}
 
-\clearpage
+\acknowledgments{
+All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
+and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
+}
+
+\conflictsofinterest{The authors declare that they have no conflict of interest.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Optional
+\appendixtitles{yes} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
+If the appendix sections contain a heading then change the argument to "yes".
+\appendixstart
 \appendix
+
 \section{Inter spike spectra for noisy R\"ossler system}
@@
  \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
- \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise. The appearance of the inter spike spectra 
+ \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
  in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.
-\todo[inline]{Where do you add the additive noise?
+\todo[inline]{MA: Where do you add the additive noise?
 for all components, i.e.
@@
 
+\section{Power grid frequency time series}\label{sec_power_grid_appendix}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
+ \caption{CAPTION WILL BE ADDED}
+\label{fig_power_grid_time_series}
+\end{figure}
+
 \section{Exemplary models}
@@
 
-The classical Lorenz-63 system \cite{lorenz1963} is defined as
+\noindent The classical Lorenz-63 system \cite{lorenz1963} is defined as
 
@@
 
-The R\"ossler system \cite{roessler1976} is defined as
+\noindent The R\"ossler system \cite{roessler1976} is defined as
 \begin{align}
@@
 
-\subsection{Power grid frequency time series}\label{sec_power_grid_appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{adjustwidth}{-\extralength}{0cm}
+%\printendnotes[custom] % Un-comment to print a list of endnotes
 
-\begin{figure}
- \centering
- \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
- \caption{CAPTION WILL BE ADDED}
-\label{fig_power_grid_time_series}
-\end{figure}
+\reftitle{References}
 
+% References, variant A: external bibliography
+
+%\bibliography{your_external_BibTeX_file}
 % BibTeX users please use one of
@@
 
-% Non-BibTeX users please use
-\bibliographystyle{spbasic} 
+%\bibliographystyle{spbasic} 
 \bibliography{inter_spike_bib}
 
+% If authors have biography, please use the format below
+%\section*{Short Biography of Authors}
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
+%{\textbf{Firstname Lastname} Biography of first author}
+%
+%\bio
+%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
+%{\textbf{Firstname Lastname} Biography of second author}
+
+% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
+% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
+% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
+328; \citeyear{ref-journal-3b}, p.475).
+This produces: Wong (1999, p.
+328; 2000, p.
+475)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% for journal Sci
+%\reviewreports{\\
+%Reviewer 1 comments and authors’ response\\
+%Reviewer 2 comments and authors’ response\\
+%Reviewer 3 comments and authors’ response
+%}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{adjustwidth}
 \end{document}
-% end of file

### 2022-07-21 Manuscript/inter_spike_manuscript_mdpi.tex
Merge branch 'main' of https://github.com/hkraemer/Recurrence_Spike_Spectra into main

@@
 \subsection{Period estimation for different dynamics in the R\"ossler system}
-First, we consider the R\"ossler system (Eq.~\eqref{eq_model_roessler} in Appendix \ref{sec_models_roessler}) 
+First, we consider the R\"ossler system (Eq.~\eqref{eq_model_roessler} \todo{why not C.2?} Appendix \ref{sec_models_roessler}) 
 in three different dynamical setups. We use the proposed inter spike spectrum to
@@
  \textbf{D, E, F} The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
- recurrence rate for D \& E and 5\% for F. 
+ recurrence rate for D \& E and 5\% for F \todo[inline]{what is the recurrence rate? does it relate to $\epsilon $ in Eq.(1).} 
   \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
@@
 
-We consider the Logistic map $x_{n+1}=r\cdot x_n \left( 1-x_n \right)$ for changing control parameter $r$. We vary $r$ from $r=3.4$ to $r=4$ in steps of $0.001$. For 
+We consider the Logistic map $x_{n+1}=r\cdot x_n \left( 1-x_n \right)$ for changing control parameter $r$. We vary $r$ from $r=3.4$ to $r=4$ in steps of $0.001$ \todo{is it correct?}. For 
 each setting of $r$ 
@@
 \end{itemize}
-In this example, the according null hypothesis is that the data stems from a process which yields the same auto-correlation, hence the same Fourier powerspectrum, and the same 
+In this example, the according null hypothesis \todo{null hypothesis refers to surrogate data?}is that the data stems from a process which yields the same auto-correlation, hence the same Fourier powerspectrum, and the same
 amplitude distribution. We consider the number of significant peaks in the inter spike spectrum with
@@
 A correlation with the positive Lyapunov exponent (Fig.~\ref{fig_tau_rr_logistic}A) is discernible 
-($\rho_{\text{Pearson}}=0.72$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum.
+($\rho_{\text{Pearson}}=0.72$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum. \todo{This part is not understandable}
 
@@
  \includegraphics[width=\textwidth]{./figures/fig_tau_rr_logistic}
- \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. 
+ \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. \todo[inline]{A shows also bifurcation diagram?}
  \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 

### 2022-07-21 Manuscript/inter_spike_manuscript_mdpi.tex
tiny changes according to MAs comments

--- 2022-07-20 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 \end{equation}
-The simple idea to 
-track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, but also for its 
+The crucial free parameter $\varepsilon$ (recurrence threshold) determines the visible structures in the RP. It can be chosen such, that the recurrence rate 
+$RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value.
+The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, but also for its 
 quantification, using certain structures in the RP, such as diagonal or vertical lines \cite{marwan2007}.
@@
  \textbf{D} Subset of the recurrence plot and the corresponding $\tau$-recurrence rate obtained from the state space trajectory in \textbf{C}. 
-\sout{The shaded interval in the time series in \textbf{A} corresponds to the shown subset.}
- \textbf{E} Fourier Power spectrum obtained from the $\tau$-recurrence (subset shown in panel \textbf{D}) \cite{Zbilut2008}.
-\todo[inline]{\textbf{D} and \textbf{E} show the results of a part of the time series in \textbf{A} which is highlighted in pink.
-}\todo[inline]{I think Fig.~\ref{fig_tau_rr_spectrum_example} should be restructured.
-We could talk about it.}
+ \textbf{E} Fourier Power spectrum obtained from the $\tau$-recurrence rate (subset shown in panel \textbf{D}) \cite{Zbilut2008}.
+\textbf{D} and \textbf{E} show the results of a part of the time series,
+ which is highlighted in pink in \textbf{A}.\todo[inline]{MA: I think Fig.~\ref{fig_tau_rr_spectrum_example} should be restructured. We could talk about it.}
  }\label{fig_tau_rr_spectrum_example}
@@
 \end{itemize}
-In this example, the according null hypothesis is that the data stems from a process which yields the same auto-correlation, hence the same Fourier powerspectrum, and the same 
+In this example, the according null hypothesis for constructing the surrogate data is that the data stems from a process which yields the same auto-correlation, 
+hence the same Fourier powerspectrum, and the same 
 amplitude distribution. We consider the number of significant peaks in the inter spike spectrum with
@@
 A correlation with the positive Lyapunov exponent (Fig.~\ref{fig_tau_rr_logistic}A) is discernible 
-($\rho_{\text{Pearson}}=0.72$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum.
+($\rho_{\text{Pearson}}=0.72$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum. \todo{MA: This part is not understandable}
 
@@
  \includegraphics[width=\textwidth]{./figures/fig_tau_rr_logistic}
- \caption{\textbf{A} Lyapunov exponent of the Logistic map as a function of the control parameter $r$. 
+ \caption{\textbf{A} Bifurcation diagram and Lyapunov exponent and of the Logistic map as a function of the control parameter $r$.
  \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 
@@
 
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+\begin{itemize}
+\item computationally expensive.
+\item STLS and LASSO yield different results.
+\item incorporates FFT-peaks (see Vostok data).
+\item bifurcation detection only possible when additional period(s) is not an integer multiple of the former period(s).
+\end{itemize}
 
@@
 
-\section{Inter spike spectra for noisy R\"ossler system}
-
-\begin{figure}[h!]
- \centering
- \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
- \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
- in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.
-\todo[inline]{MA: Where do you add the additive noise?
-for all components, i.e.
-x, y and z?
-What is the take home message of this figure?
-In your abstract you mention that " The proposed measure is robust to noise and is able to detect and analyze bifurcations." but then here there is also no noise effect on FFT.
-So please make clear the main message of this figure.
- }}
-\label{fig_tau_rr_example_roessler_noise}
-\end{figure}
-
-\section{Power grid frequency time series}\label{sec_power_grid_appendix}
-
-\begin{figure}
- \centering
- \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
- \caption{CAPTION WILL BE ADDED}
-\label{fig_power_grid_time_series}
-\end{figure}
-
 \section{Exemplary models}
@@
 obtained from which we computed the RPs and the corresponding $\tau$-RR's. For the inter spike spectra only the first $1,000$ values of the $\tau$-RR's were considered.
+
+\section{Inter spike spectra for noisy R\"ossler system}
+
+\begin{figure}[h!]
+ \centering
+ \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
+ \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
+ in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.
+\todo[inline]{MA: Where do you add the additive noise?
+for all components, i.e.
+x, y and z?
+What is the take home message of this figure?
+In your abstract you mention that " The proposed measure is robust to noise and is able to detect and analyze bifurcations." but then here there is also no noise effect on FFT.
+So please make clear the main message of this figure.
+ }}
+\label{fig_tau_rr_example_roessler_noise}
+\end{figure}
+
+\section{Power grid frequency time series}\label{sec_power_grid_appendix}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
+ \caption{CAPTION WILL BE ADDED}
+\label{fig_power_grid_time_series}
+\end{figure}
 

### 2022-07-22 Manuscript/inter_spike_manuscript_mdpi.tex
comment no. 2
Last try for CENOGRID

@@
 % Authors, for the paper (add full first names)
-\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1,4}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}
+\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Period estimation for different dynamics in the R\"ossler system}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Bifurcations in the Logistic map}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Inter spike spectra of power grid frequency data}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
+\subsection{Evolutionary inter spike spectra of astronomical data}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}\label{sec_tau_rr_discussion}
 

### 2022-07-22 Applications/CENOGRID/windowed spectrograms/compute_windowed_spectrograms_cenogrid.m

@@ -13,8 +13,8 @@ t = data(:,1);
 t = flipud(t);
 t = t.*1000000;
 
-O18 = load("../data/O18_filtered_time_reverse.txt");
-C13 = load("../data/C13_filtered_time_reverse.txt");
+O18 = flipud(data(:,3));
+C13 = flipud(data(:,2));
 
 % sampling time is dt = 5,000 yrs
 
@@ -32,13 +32,18 @@ M = length(1:ws:N-windowsize); % number of computed spectra
 window_tau = 200; % sampling time is 5.000 yrs so this corresponds to 1 Mio yrs
 length_of_spectra = ceil(window_tau/2);
 
-spectrum_O18_mcdts = zeros(length_of_spectra,M); 
+spectrum_O18_mcdts = zeros(length_of_spectra,M);
+spectrum_O18_cao = zeros(length_of_spectra,M);
 spectrum_O18_ne = zeros(length_of_spectra,M);
 spectrum_C13_mcdts = zeros(length_of_spectra,M); 
+spectrum_C13_cao = zeros(length_of_spectra,M); 
 spectrum_C13_ne = zeros(length_of_spectra,M);
 
 taus_O18_mcdts = [0  50  104  35  43  149  39  47  45]; % from script `compute_embedding_parameters.jl`
 taus_C13_mcdts = [0  136  32  123  130  126  133  128]; % from script `compute_embedding_parameters.jl`
+
+taus_O18_cao = [0, 7, 14, 21, 28, 35]; % from script `compute_embedding_parameters.jl`
+taus_C13_cao = [0, 15, 30, 45, 60, 75, 90]; % from script `compute_embedding_parameters.jl`
 
 %%
 cnt = 1;
@@ -49,30 +54,41 @@ for i = 1:ws:M
     x = O18(i:i+windowsize);
     y = C13(i:i+windowsize);
     % 1) MCDTS embedding gained from whole dataset analysis
-    Yx = genembed(x,taus_O18_mcdts, ones(1,length(taus_O18_mcdts)));
-    Yy = genembed(x,taus_C13_mcdts, ones(1,length(taus_C13_mcdts)));
+%     Yx = genembed(x,taus_O18_mcdts, ones(1,length(taus_O18_mcdts)));
+%     Yy = genembed(x,taus_C13_mcdts, ones(1,length(taus_C13_mcdts)));
+    % 2) Cao embedding
[…]

### 2022-07-22 Applications/CENOGRID/windowed spectrograms/plot_evolutionary_spectrograms.m

@@ -23,10 +23,14 @@ C13 = flipud(C13);
 
 spectrum_O18_mcdts_mse = load("./computed spectra/spectrum_O18_mcdts.mat");
 spectrum_O18_mcdts_mse = spectrum_O18_mcdts_mse.spectrum_O18_mcdts;
+spectrum_O18_cao = load("./computed spectra/spectrum_O18_cao.mat");
+spectrum_O18_cao = spectrum_O18_cao.spectrum_O18_cao;
 spectrum_O18_ne = load("./computed spectra/spectrum_O18_ne.mat");
 spectrum_O18_ne = spectrum_O18_ne.spectrum_O18_ne;
 spectrum_C13_mcdts_mse = load("./computed spectra/spectrum_C13_mcdts.mat");
 spectrum_C13_mcdts_mse = spectrum_C13_mcdts_mse.spectrum_C13_mcdts;
+spectrum_C13_cao = load("./computed spectra/spectrum_C13_cao.mat");
+spectrum_C13_cao = spectrum_C13_cao.spectrum_C13_mcdts;
 spectrum_C13_ne = load("./computed spectra/spectrum_C13_ne.mat");
 spectrum_C13_ne = spectrum_C13_ne.spectrum_C13_ne;
 
@@ -56,20 +60,24 @@ f = spec_filtered.f;
 
 %% Plot the wavelet-like spectrograms for both isotope-time series
 
-method = 1; % 1 = MCDTS, 2 = no embedding
+method = 2; % 1 = MCDTS, 2 = CAO, 3 = no embedding
 
-m_string = ["(MCDTS)", "(no embedding)"];
+m_string = ["(MCDTS)", "(CAO)", "(no embedding)"];
 
 fs = 22;
 lw2 = 1;
 
 len = 90;
 cax_max = 0.013;
+cax_max = 0.9;
 
 if method == 1
     data1 = spectrum_C13_mcdts_mse;
     data2 = spectrum_O18_mcdts_mse; 
 elseif method == 2
+    data1 = spectrum_C13_cao;
+    data2 = spectrum_O18_cao;
+elseif method == 3
     data1 = spectrum_C13_ne;
     data2 = spectrum_O18_ne;
 end
@@ -140,9 +148,9 @@ grid on
 
 %% FFT- and ISS for raw data
 
-method = 1; % 1 = MCDTS, 2 = no embedding
[…]

### 2022-07-22 Applications/Laskar/windowed spectrograms/plot_evolutionary_spectrograms.m

@@ -50,7 +50,7 @@ end
 
 %% Plot the wavelet-like spectrograms 
 
-method = 2; % 1 = MCDTS, 2 = no embedding
+method = 1; % 1 = MCDTS, 2 = no embedding
 
 m_string = ["(MCDTS)", "(no embedding)"];
 

### 2022-07-22 Applications/Power Grid/CE and GB frequencies/compute_embedding_parameters.jl

@@ -19,3 +19,5 @@ D_gb, τ_gb, E_gb = optimal_traditional_de(f_gb[1:14400], "ifnn", "mi_min"; τs,
 # out Cao
 # D_ce = 7, τ_ce = 19 
 # D_gb = 7, τ_gb = 17
+
+# changing embedding params for different signal lengths

### 2022-07-22 Applications/Power Grid/CE and GB frequencies/compute_iss_spectrogram_downsampled.jl

@@ -7,28 +7,37 @@ using RecurrenceAnalysis
 using Statistics
 
 ## Downsampled frequency data
-f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled.csv"))
-f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled.csv"))
+# f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled.csv"))
+# f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled.csv"))
 
 # f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled_30s.csv"))
 # f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled_30s.csv"))
 
-T_ce = 60 # sampling time in secs
-T_gb = 60
+f_ce = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_ce_downsampled_20s.csv"))
+f_gb = vec(readdlm("./Applications/Power Grid/CE and GB frequencies/data/frequencies_gb_downsampled_20s.csv"))
+
+# T_ce = 60 # sampling time in secs
+# T_gb = 60
 
 # T_ce = 30 # sampling time in secs
 # T_gb = 30
 
-L_block_ce = 1440 # block length covering one full day (24 hours)
-L_block_gb = 1440
+T_ce = 20 # sampling time in secs
+T_gb = 20
+
+# L_block_ce = 1440 # block length covering one full day (24 hours)
+# L_block_gb = 1440
 
 # L_block_ce = 2880 # block length covering one full day (24 hours)
 # L_block_gb = 2880
 
+L_block_ce = 4320 # block length covering one full day (24 hours)
+L_block_gb = 4320
+
 rho = 0.95
 epsilon = 0.08
 τs = 0:150
-tau_window = 200
+tau_window = 600
 
 spec_ce, d_ce, taus_ce = iss_spec(f_ce, L_block_ce, τs, epsilon, tau_window, rho; embed_method="afnn")
[…]

### 2022-07-22 Manuscript/inter_spike_manuscript_mdpi.tex
Some improvements regarding MA's comments

@@
 \textbf{D} and \textbf{E} show the results of a part of the time series,
- which is highlighted in pink in \textbf{A}.\todo[inline]{MA: I think Fig.~\ref{fig_tau_rr_spectrum_example} should be restructured. We could talk about it.}
+ which is highlighted in pink in \textbf{A}.\todo[inline]{MA: I think Fig.~\ref{fig_tau_rr_spectrum_example} should be restructured. We could talk about it.\\ HK: I will do that.}
  }\label{fig_tau_rr_spectrum_example}
@@
 
-The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal \todo{MA: what do you mean with any signal?
-do you mean to look at data set instead of $\tau$-RP or RP?}--
-is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
+The signal, which we would like to transform is decomposed into a set of appropriate basis functions.\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
+such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} Instead of using trigonometric 
+functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
 different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
@@
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure) \todo{MA: $n$ in eq.6 is not clear for me}
+(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure)
 \begin{align}
-\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
-\label{eq_basis_matrix}
+\label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
+\label{eq_T_is} T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
@@
 than $\ceil*{N/2}+1$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which can not be uniquely assigned to a certain inter spike period 
-(blue sheared). \textbf{B} The final set of unambiguous, but still linearly dependent, basis functions aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
+(blue sheared).
+$T_{\text{is}}$ for each row can be obtained by Eq.~\eqref{eq_T_is}.
+\textbf{B} The final set of unambiguous, but still linearly dependent, basis functions aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
 \end{figure}
@@
   corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
-  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
-\todo[inline]{MA: why you have not used STLS method here?} }
+  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I. }
 \label{fig_tau_rr_example_roessler}
@@
 A correlation with the positive Lyapunov exponent (Fig.~\ref{fig_tau_rr_logistic}A) is discernible 
-($\rho_{\text{Pearson}}=0.72$). Moreover, this analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum. \todo{MA: This part is not understandable}
+($\rho_{\text{Pearson}}(\text{Lyapunov})=0.72$). This analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum. 
+However, whenever the periods of the ``new'' cycles coincide with integer multiples of the periods of already existing cycles, this approach can not detect 
+period-doubling. A similar case can be observed in Fig.~\ref{fig_tau_rr_example_roessler}J,K where the number of peaks does not change, but  their mutual distance does.
 
@@
 from a binomial distribution with probability parameter $p$ set to the recurrence rate of the RP of the signal. This way $100$ surrogate $\tau$-RRs are computed in step (5). 
-The results are even slightly better compared to the ones obtained from the iAAFT surrogates (Fig.~\ref{fig_tau_rr_logistic}B, $\rho_{\text{Pearson}}=0.81$). The first period doubling at 
-$r \approx 3.458$ cannot be detected by any of the surrogates.
+The results are even slightly better compared to the ones obtained from the iAAFT surrogates (Fig.~\ref{fig_tau_rr_logistic}B, $\rho_{\text{Pearson}}(\text{Lyapunov})=0.81$). 
+The first period doubling at $r \approx 3.458$ cannot be detected by any of the surrogates.
 
@@
 according inter spike spectra is still revealing important information (Fig.~\ref{fig_tau_rr_example_roessler}) and practitioners can design appropriate quantifying statistics based 
-on these spectra, which suit the 
-research task.
+on these spectra, which suit the research task.
 
@@
 the grid operators (in Europe and many parts of the world this is $50$ \si{Hz} or $60$ \si{Hz} in America and, for example, southern Japan).
-For example, if there is more (less) demand than supply supply, the network frequency decreases (increases) compared to the nominal frequency \cite{kundur1994power}.
+For example, if there is more (less) demand than supply, the network frequency decreases (increases) compared to the nominal frequency \cite{kundur1994power}.
 \\
@@
 renewable energies (REs), demands on the grid \cite{anvari2020stochastic} and, moreover, the effect of regular dispatches due to the trading market 
-\cite{meyer2020identifying}. The latter induce periodic frequency jumps. The frequency trajectory for the Great Britain (GB) and Continental Europe (CE) 
-grid shown in Fig.~\ref{fig_power_grid_time_series} demonstrates clear jumps every hour \todo[inline]{(maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. 
-Furthermore, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{fig_power_grid_spectra}). These peaks are caused by a mismatch of power 
-supply and demand \cite{weissbach2009high} during dispatches. In most electricity grids the
-operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
-might exist. Looking at the frequency spectrum in Fig.~\ref{fig_power_grid_spectra}, however, does not display sharp peaks exactly at $30$ and $60$ \si{min}. \\
-
-\todo[inline]{Now we should start the story of Inter-spike-spectrum}.
+\cite{meyer2020identifying}. The latter induce periodic frequency jumps. Here we look at the frequency time series for the Great Britain (GB) and Continental Europe 
+(CE) (Appendix \ref{sec_power_grid_appendix} and Fig.~\ref{fig_power_grid_time_series}A,C). Clear jumps every 30 and 60 minutes are discernible and quantitatively reflected in the corresponding 
+autocorrelations (Fig.~\ref{fig_power_grid_time_series}B,D). Furthermore, the autocorrelation of the CE frequency time series shows regular peaks every $15$ \si{min} 
+(see Fig.~\ref{fig_power_grid_time_series}B). These peaks are caused by a mismatch of power supply and demand \cite{weissbach2009high} during dispatches. 
+In most electricity grids the operation of dispatchable power plants is scheduled in 1-hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
+might exist.\\
 
@@
  \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra}
- \caption{CAPTION WILL BE ADDED}
+ \caption{Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}). 
+ The corresponding averaged inter spike spectra of the according $\tau$-RR's, Eq.~\eqref{eq_tau_rr}, are shown in \textbf{C} and \textbf{D}, respectively. Vertical red dashed lines correspond to 
+ $15$, $30$ and $60$ \si{min}. For technical details on the calculation of the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}.}  
 \label{fig_power_grid_spectra}
@@
 
+The Fourier frequency spectra in Figure~\ref{fig_power_grid_spectra}A,B, however, do not display sharp peaks exactly at $15$, $30$ and $60$ \si{min} (for technical details on the calculation of 
+the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Especially the $30$ and $60$ \si{min} 
+peaks are split into two adjacent peaks and the local minimum in between these ``double''-peaks correspond to the exact times. 
+In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Fig.~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
+at $30$ and $60$ \si{min}. In front of these peaks, smaller local peaks can be seen, which correspond to the local peaks of the Fourier power spectra at $28$ and $55$ \si{min}, respectively.
+Moreover, there is an additional peak at 
+$40$ \si{min} for both datasets, which is absent in the Fourier spectrum and which is not a multiple of the missing $15$ \si{min} peak. The position and magnitude of the peaks in the shown 
+inter spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.\\
+
+We interpret the results presented as follows. The missing $15$ \si{min} in the inter spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min} 
+(see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter spike spectra are not able to detect it and the 
+sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks.\todo[inline]{at Mehrnaz: please add more to the ``story''}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Evolutionary inter spike spectra of astronomical data}
+
+\todo[inline]{Add this section and keep it very very short.}
 
@@
 \item computationally expensive.
-\item STLS and LASSO yield different results.
-\item incorporates FFT-peaks (see Vostok data).
-\item bifurcation detection only possible when additional period(s) is not an integer multiple of the former period(s).
+\item STLS and LASSO yield different results (qualitatively similar but not quantitatively). \todo[inline]{Add figure to the appendix explaining the search for the correct regularization}
+\item incorporates FFT-peaks (see Laskar data).
+\item bifurcation detection only possible when additional period(s) is not an integer multiple of the former period(s). For this: Maybe incorporate mutual distance for a better correlation 
+to the Lyapunov exponent. 
 \end{itemize}
+
+\todo[inline]{Move stuff from Conclusion section into Discussion section}
 
@@
  \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
- in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.
-\todo[inline]{MA: Where do you add the additive noise?
-for all components, i.e.
-x, y and z?
-What is the take home message of this figure?
-In your abstract you mention that " The proposed measure is robust to noise and is able to detect and analyze bifurcations." but then here there is also no noise effect on FFT.
-So please make clear the main message of this figure.
- }}
+ in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.}
 \label{fig_tau_rr_example_roessler_noise}
@@
 
+The raw frequency time series have length $\tilde{N}_{\text{CE}}=58,752,000$ and $\tilde{N}_{\text{GB}}=31,622,400$ with sampling times $\Delta t_{\text{CE}}=0.2$\si{s} and 
+$\Delta t_{\text{GB}}=1$\si{s}, respectively. \todo[inline]{to Mehrnaz: Please add the information which time these time series covered and maybe the source for the data} 
+We downsample these time series to a sampling time of $\Delta t_{\text{CE}}= \Delta t_{\text{GB}}=20$\si{s}, which lead to total time series lengths of 
+$N_{\text{CE}}=587,520$ and $N_{\text{GB}}=1,581,120$ which we use for the further analysis.
+
 \begin{figure}
@@
  \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
- \caption{CAPTION WILL BE ADDED}
+ \caption{Subset of the frequency time series of \textbf{A} Central Europe (CE) and \textbf{C} Great Britain (GB) along with their autocorrelation functions in \textbf{B} and 
+ \textbf{D}, respectively. The normalized autocorrelations in \textbf{B}, \textbf{D} have been computed on the entire time series, wheres as the subsets shown in \textbf{A}, \textbf{C} 
+ contain only $1,441$ samples.}
 \label{fig_power_grid_time_series}
 \end{figure}
+
+In this analysis we divide the time series into 
+non-overlapping blocks of length $N_{\text{block}}=4,320$, covering a time span of $24$ hours. For each time series block we compute Fourier spectra and recurrence plots (RPs), 
+Eq.~\eqref{eq_rp_definition}, along with their $\tau$-RR's, Eq.~\ref{eq_tau_rr}. The RPs are obtained from a uniform 5-dimensional time-delay embedding of each time series with 
+the delay set to the first minimum of the mutual information \cite{fraser1986,hegger1999} and a fixed recurrence threshold corresponding to 8\% recurrence rate is used in order 
+to ensure comparability \cite{kraemer2018}. The first $600$ data points of the $\tau$-RR's are used for finally obtaining inter spike spectra with a LASSO regression and a 
+regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The spectra shown in all panels of Figure~\ref{fig_power_grid_spectra} 
+are averages over all blocks, following \citet{meyer2020identifying}.
 

### 2022-07-22 Applications/Power Grid/CE and GB frequencies/acorr.m

@@ -1,0 +1,101 @@
+function Z = acorr(varargin)
+% Input:
+% Minimum input-arguments : 1
+% Maximum input-arguments : 3
+% Z = acorr(Y,tau_max,Show)
+% 
+%
+% This function computes the autocorrelationvalues of timeseries Y versus the 
+% time delayed version of itself. If not specified in the second input-argument 
+% the maximum  timelag value 'tau_max' is set to 10.
+% The optional output contains the timelag-values (first column) and
+% the corresponding autocorrelation-values (second column)
+% If input 'Show' is set to 1 (Default is 0) the autocorrelation as a
+% function of the time lag is plotted along with a horizontal line marking
+% the 1/exp-decay.
+%
+% K.H.Kraemer, 2019
+
+%% Assign input
+
+y = varargin{1};
+
+try
+    tau_max = varargin{2};
+catch 
+    tau_max = 10;
+end
+
+try
+    show = varargin{3};
+catch 
+    show = 0;
+end
+
+N = length(y);
+
+
+%% Check input
+narginchk(1,3)
+nargoutchk(0,1)
+
+% Check if tau-values are positive integers
+if rem(tau_max,1)~=0
+   error('tau-values must be positive integers.')
+end
+
+if tau_max<1
+    error('tau-values must be positive integers.')
+end
+   
+% Check if input-vector is a column- or line-vector
+if size(y,1)<size(y,2)
+    y=y';
+end
+
+if show~=0 && show~=1
+    warning('input show needs to be 1 (display figure) or 0 (no figure displayed). Now set to 0.')
+    show = 0;
+end
+
+tau_min = 0;
+
+%% Calculate Autocorrelation
+
+mu=nanmean(y);
+v=nanvar(y);
+
+auto=zeros(1,length(tau_min:tau_max));
+cnt = 1;
+for i=tau_min:tau_max
+    
+    % lag the time series 
+
+    N2 = N-i;
+    y_ = y(1:N2,:);
+    y_lag = y(1+i:N2+i,:);
+        
+    auto(cnt) = ((y_lag-mu)'*(y_-mu)/N2) / v;
+    cnt = cnt + 1; 
+end
+
+Z(:,1)= tau_min:tau_max;
+Z(:,2)= auto(:);
+
+%% Plotting Autocorrelationfunction against lag tau
+if show
+    figure
[…]

### 2022-07-22 Applications/Power Grid/CE and GB frequencies/plot_frequency_results.m

@@ -1,4 +1,4 @@
-% We plot the downsampled time series 
+% We plot the downsampled time series and its autocorrelation 
 % (computed in `compute_fft_spectrogram_downsampled`), the FFT-spectrograms 
 % (computed in `compute_fft_spectrogram_downsampled`) and the according ISS 
 % (computed in `compute_iss_spectrogram_downsampled.jl`).
@@ -46,7 +46,6 @@ fs_gb= Fs_gb*(0:(L_block_gb/2))/L_block_gb;
 font = 22; % fontsize
 lw1 = 2.5;
 lw2 = 2;
-
 
 figure('Units','normalized','Position',[.001 .001 .999 .999])
 subplot(221)
@@ -99,7 +98,7 @@ ylim([0 0.01])
 set(gca, 'LineWidth', lw2, 'FontSize', font)
 grid on
 
-%% Plot time series
+%% Plot time series and autocorrelation
 
 font = 24; % fontsize
 lw1 = 3;
@@ -109,20 +108,45 @@ init = 4459;
 factor = 3; % corresponds to 24/factor hours
 t_len = L_block_ce/factor + 1; 
 
+% compute autocorrelation
+t_len2 = 300;
+ac_ce = acorr(f_ce, t_len2, 0);
+ac_gb = acorr(f_gb, t_len2, 0);
+
+%%
+
 figure('Units','normalized','Position',[.001 .001 .999 .999])
 subplot(211)
 plot(t_ce(1:t_len), f_ce(init: init+L_block_ce/factor), '.-', 'LineWidth', lw1)
 title('F_{CE}')
+ylabel('frequency (Hz)')
+xlabel('time (min)')
+xlim([0 24/factor*60])
+set(gca, 'LineWidth', lw2, 'FontSize', font)
+grid on
+
+subplot(212)
+plot(t_ce(1:t_len2+1), ac_ce(1:end,2), '.-', 'LineWidth', lw1)
+ylabel('normal. acorr')
+xlabel('time lag \tau (min)')
+xlim([1 100])
+set(gca, 'LineWidth', lw2, 'FontSize', font)
+grid on
+
+figure('Units','normalized','Position',[.001 .001 .999 .999])
+subplot(211)
+plot(t_gb(1:t_len), f_gb(init: init+L_block_gb/factor),  '.-', 'LineWidth', lw1)
+title('F_{GB}')
+xlabel('time (min)')
[…]

### 2022-07-25 Manuscript/inter_spike_manuscript_mdpi.tex
complete Appendix C

@@
 The raw frequency time series have length $\tilde{N}_{\text{CE}}=58,752,000$ and $\tilde{N}_{\text{GB}}=31,622,400$ with sampling times $\Delta t_{\text{CE}}=0.2$\si{s} and 
-$\Delta t_{\text{GB}}=1$\si{s}, respectively. \todo[inline]{to Mehrnaz: Please add the information which time these time series covered and maybe the source for the data} 
+$\Delta t_{\text{GB}}=1$\si{s}, respectively.
+GB frequency data was measured during 2016, and has been gotten from \cite{GB}.
+CE frequency data belongs to 2017 and has been gotten from \cite{haehne2018footprint}.
+
 We downsample these time series to a sampling time of $\Delta t_{\text{CE}}= \Delta t_{\text{GB}}=20$\si{s}, which lead to total time series lengths of 
@@
  \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
- \caption{Subset of the frequency time series of \textbf{A} Central Europe (CE) and \textbf{C} Great Britain (GB) along with their autocorrelation functions in \textbf{B} and 
+ \caption{Subset of the frequency time series of \textbf{A} Central Europe (CE) \cite{haehne2018footprint} and \textbf{C} Great Britain (GB) \cite{GB} along with their autocorrelation functions in \textbf{B} and
  \textbf{D}, respectively. The normalized autocorrelations in \textbf{B}, \textbf{D} have been computed on the entire time series, wheres as the subsets shown in \textbf{A}, \textbf{C} 

### 2022-07-25 Manuscript/inter_spike_manuscript_mdpi.tex
finish frequency section

@@
  \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra}
- \caption{Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}). 
+ \caption{\todo[inline]{could you please become sure that A and B are not the same plots.
+They are super similar}.Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}).
  The corresponding averaged inter spike spectra of the according $\tau$-RR's, Eq.~\eqref{eq_tau_rr}, are shown in \textbf{C} and \textbf{D}, respectively. Vertical red dashed lines correspond to 
@@
 (see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter spike spectra are not able to detect it and the 
-sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks.\todo[inline]{at Mehrnaz: please add more to the ``story''}.
+sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks.
+Moreover, the inter spike spectra, unlike the Fourier spectra demonstrates sharp peaks exactly at $30$ and $60$ \si{min}, i.e.
+during dispatches.
+Eventually, here we have found a clear sharp peak at $40$ \si{min} which can occur because of any regular controls in a power grid, and can be a hint to develop the existing stochastic processes to model precisely the power grid frequency \cite{gorjao2020data}.
 

### 2022-07-25 Applications/Power Grid/CE and GB frequencies/compute_fft_spectrogram_downsampled.m
Fixed Fig.6 PowerGrid spectra bug; fixed bib-error

@@ -64,7 +64,7 @@ spec_gb = mean(spectrum_gb,2);
 % save("./data/frequencies_gb_downsampled_20s.csv", "f_gb_ds", "-ascii")
 
 save("./data/fft_spec_ce.csv","spec_ce","-ascii")
-save("./data/fft_spec_gb.csv","spec_ce","-ascii")
+save("./data/fft_spec_gb.csv","spec_gb","-ascii")
 
 
 %%

### 2022-07-26 Manuscript/inter_spike_manuscript_mdpi.tex
Potential restructuring of Fig.1

@@
 can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived 
-powerspectrum, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D), instead 
-of $C(\tau)$ (Fig.~\ref{fig_tau_rr_spectrum_example}C): There are no assumptions for stationarity or sampling, when constructing a RP.
+powerspectrum, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
+of $C(\tau)$: There are no assumptions for stationarity or sampling, when constructing a RP.
 Furthermore, the correlation structures of higher dimensional spaces can be resolved in the recurrence-derived Fourier-spectrum.\\
@@
 \textbf{D} and \textbf{E} show the results of a part of the time series,
- which is highlighted in pink in \textbf{A}.\todo[inline]{MA: I think Fig.~\ref{fig_tau_rr_spectrum_example} should be restructured. We could talk about it.\\ HK: I will do that.}
+ which is highlighted in pink in \textbf{A}.
  }\label{fig_tau_rr_spectrum_example}
@@
 map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g. \cite{Schild1982,Cordoba1989}, see 
-Fig.~\ref{fig_tau_rr_spectrum_example}D). Thus, it is not intuitive how to extract meaningful information about dominant frequencies of the systems' state space trajectory.
+Fig.~\ref{fig_tau_rr_spectrum_example}E). Thus, it is not intuitive how to extract meaningful information about dominant frequencies of the systems' state space trajectory.
 
@@
  \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra}
- \caption{\todo[inline]{could you please become sure that A and B are not the same plots.
-They are super similar}.Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}).
+ \caption{Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}). 
  The corresponding averaged inter spike spectra of the according $\tau$-RR's, Eq.~\eqref{eq_tau_rr}, are shown in \textbf{C} and \textbf{D}, respectively. Vertical red dashed lines correspond to 

### 2022-07-27 Manuscript/inter_spike_manuscript_mdpi.tex
Laskar section added

@@
 \begin{itemize}[noitemsep]
-\item[(1)] Compute a RP of the trajectory of the system, Eq.~\eqref{eq_rp_definition}. 
+\item[(1)] Compute a RP of the trajectory of the system, Eq.~\eqref{eq_rp_definition}. If only univariate data is available, perform a state space reconstruction for obtaining the trajectory first.
 \item[(2)] Compute the $\tau$-RR of that RP, Eq.~\eqref{eq_tau_rr}.
@@
 
-The Fourier frequency spectra in Figure~\ref{fig_power_grid_spectra}A,B, however, do not display sharp peaks exactly at $15$, $30$ and $60$ \si{min} (for technical details on the calculation of 
+The Fourier frequency spectra for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min} 
+(for technical details on the calculation of 
 the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Especially the $30$ and $60$ \si{min} 
-peaks are split into two adjacent peaks and the local minimum in between these ``double''-peaks correspond to the exact times. 
+peaks are split into two adjacent peaks and the local minimum in between these ``double''-peaks correspond to the exact times. The Great Britain counterpart in Fig.~\ref{fig_power_grid_spectra}B 
+has sharp peaks at $15$ and $30$ \si{min} and also ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
 In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Fig.~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
@@
 (see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter spike spectra are not able to detect it and the 
-sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks.
-Moreover, the inter spike spectra, unlike the Fourier spectra demonstrates sharp peaks exactly at $30$ and $60$ \si{min}, i.e.
-during dispatches.
-Eventually, here we have found a clear sharp peak at $40$ \si{min} which can occur because of any regular controls in a power grid, and can be a hint to develop the existing stochastic processes to model precisely the power grid frequency \cite{gorjao2020data}.
+sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks. Moreover, the inter spike spectra, unlike the Fourier spectra demonstrates sharp peaks exactly 
+at $30$ and $60$ \si{min}, i.e. during dispatches (not valid in case of the GB dataset). Eventually, here we have found a clear sharp peak at $40$ \si{min} which can occur 
+because of any regular controls in a power grid, and can be a hint to develop the existing stochastic processes to model precisely the power grid frequency \cite{gorjao2020data}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolutionary inter spike spectra of astronomical data}
+\subsection{Evolutionary inter spike spectra of Earth's orbit data}
 
-\todo[inline]{Add this section and keep it very very short.}
+When applying the proposed inter spike spectrum to the $\tau$-RR of a time series we expect additional frequency/period information, due to the fact that the recurrence plot (RP), 
+Eq.~\eqref{eq_rp_definition}, and its corresponding $\tau$-RR, Eq.~\eqref{eq_tau_rr}, visualize the trajectory of the embedded time series in an embedding space of higher dimension. 
+However, given a sufficient embedding of the time series, we would also expect that major frequencies/periods of the non-embedded time series are incorporated in the RP, its $\tau$-RR, 
+and eventually in the inter spike spectrum of the $\tau$-RR. In order to demonstrate this we apply the inter spike spectrum to the freely available eccentricity time series of \citet{Laskar2011}. 
+This astronomical computation of the orbital motion of the Earth (here we focus on the eccentricity only) has a clear expectation value of the incorporated frequencies/periods. The three leading 
+eccentricity cycles of 405 kyr period, 95 kyr period and 124 kyr period are well known in paleoclimate studies \cite{Laskar2004}. Our aim in this section is to show that the inter spike spectrum 
+of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier powerspectrum of the non-embedded eccentricity time series. We will further 
+show that Fourier-transforming the $\tau$-RR instead of applying the proposed inter spike spectrum will lead to non satisfying results, since the spiky $\tau$-RR excites a variety of harmonics in 
+the corresponding Fourier spectrum (cf. Section \ref{sec_tau_rr_intro}). We use a time series which covers the past \mytilde $67$ Mio. years, which a total length of $N=13,421$ samples and a 
+sampling period of $\Delta t= 5,000$.\\
+First we compute an evolutionary short time Fourier transform (FT) using a windowsize of $ws=1,000$ samplepoints ($\equiv 5 Mys$) shifted by unity and a 
+Hamming window. The spectrogram is shown in Figure \ref{fig_laskar_spectra}A, where the expected periods mentioned and highlighted are clearly visible. 
+The spectrogram is shown in Figure A, where the expected periods mentioned and highlighted are clearly visible.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_laskar_spectra}
+ \caption{\textbf{A} Evolutionary Fourier power spectra of eccentricity time series. \textbf{B} Inter spike spectrogram of the $\tau$-recurrence rate of the eccentricity time 
+ series and \textit{C} its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
+ For comparability, in all cases the spectra aligned in the columns of the shown plots are normalized to probabilities (sum of unity for 
+ each power spectrum). For further computational details, please refer to the main text.}  
+\label{fig_laskar_spectra}
+\end{figure}
+
+\noindent Then we construct the inter spike spectrogram of the $\tau$-RR by first determining an appropriate embedding. By using a recent Tree-Embedding-Ansatz \cite{Kraemer2022} we minimize the 
+\textit{false nearest neighbor} statistic \cite{hegger1999} and use the continuity statistic \cite{pecora2007} for potential delays. Eventually we obtain an $8$-dimensional embedding 
+with delays $\tau s=[0, 18, 36, 48, 62, 101, 114]$ (in sampling units) for the entire time series. Similar to the preceding approach we embed the time series with these embedding parameters 
+on windows of size $ws=1,200$ and a unity shift. \footnote{We use a slightly larger window here than in the short FT, because the embedding causes a ``loss'' of data points and we want to 
+cover similar time spans.} The RPs are computed on these embedded trajectories with a fixed recurrence threshold corresponding to $10\%$ global recurrence rate \cite{kraemer2018} 
+and the inter spike spectra of the corresponding $\tau$-RR's is obtained by using STLS regression (see Section \ref{sec_tau_rr_method}) and a regularization threshold corresponding to 
+$\rho=0.9$ accordance of $\tau$-RR's and re-composed signals. We only use the first $200$ data points of the $\tau$-RR (covering a time span of $1$ Myrs). 
+The spectrogram shown in Figure \ref{fig_laskar_spectra}B also highlights the $95$, $124$ and $405$ kyrs periods as expected. 
+Additional power is distributed in its harmonics at $190$ and $248$ kyrs periods. Finally, the standard FT with a Hamming window of the same $\tau$-RR's used to obtain the inter spike 
+spectrogram in panel B, yields a smeared spectrogram which does not reflect the expected periods, but rather suffers from the spike train behavior, i.e. many excited harmonics, of the 
+FT described in Section \ref{sec_tau_rr_intro} and Fig.~\ref{fig_tau_rr_dirac_comb}. The shown results are robust to a change of embedding parameters and windowsizes. However, a too low 
+regularization threshold smears the clear spectrogram in panel B.
 

### 2022-07-27 Manuscript/inter_spike_manuscript_mdpi.tex
Added Discussion section including regularization figure

@@
 \end{align}
+\todo[inline]{Make Eq.\eqref{eq_T_is} nicer}
 Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Inter spike spectra of power grid frequency data}
+\subsection{Inter spike spectra of power grid frequency data}\label{sec_power_grid}
 
@@
 
-\begin{itemize}
-\item computationally expensive.
-\item STLS and LASSO yield different results (qualitatively similar but not quantitatively). \todo[inline]{Add figure to the appendix explaining the search for the correct regularization}
-\item incorporates FFT-peaks (see Laskar data).
-\item bifurcation detection only possible when additional period(s) is not an integer multiple of the former period(s). For this: Maybe incorporate mutual distance for a better correlation 
-to the Lyapunov exponent. 
-\end{itemize}
+We have successfully used the idea of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter spike spectra, 
+and thus a null model, the number of significant peaks in the inter spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve 
+period-doubling bifurcations. However, we have to admit this way the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 
+This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter spike power spectra for period-2, period-3 and chaotic dynamics.
+Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter spike spectra of power grid 
+frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis. And last but not least, we showed that our approach 
+really incorporates frequencies, which are apparent in the Fourier spectrum of the signal, by applying it to analytically derived eccentricity data, where the dominant frequencies are well 
+known.
 
-\todo[inline]{Move stuff from Conclusion section into Discussion section}
+We discuss some more technical details in the following, which will also affect any application of the proposed method. 
+First of all, the number of required basis functions 
+$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ for an input signal of length $N$ is the crucial bottleneck of this approach, which is why it does not show good scaling behavior. The subsequent sparse 
+regression, therefore, gets computationally intensive for $N>1,000$. Depending on the memory of the computer used, input signals $N>2,000$ usually do not work anymore. This means that signals 
+often need to get downsampled as a preprocessing step (e.g., see Appendix \ref{sec_power_grid_appendix}). Second, the regularization parameter $\alpha$ for the regression is a crucial free parameter. 
+As described in Section \ref{sec_tau_rr_method} our idea in this paper is to select the $\alpha$ such that the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ matches a 
+given (Pearson) correlation coefficient $\rho_{\bf{s},\tilde{\bf{s}}}$ between the original signal $\bf{s}$ and itself. This ensures that $\alpha$ adjusts itself to the data as well as to the 
+used regression method. We found that this increases the comparability of different spectra, especially when performing a running window approach in order to obtain an evolutionary spectrogram 
+(Fig.~\ref{fig_laskar_spectra}). 
+However, the two different sparse regression algorithms we encountered in this article (LASSO and STLS) yield different results for the same desired $\rho_{\bf{s},\tilde{\bf{s}}}$. 
+Even if the spectra obtained in this way look qualitatively similar, they are not always quantitatively similar. The reason for this 
+is that $\rho_{\bf{s},\tilde{\bf{s}}}$ is not a smooth function of $\alpha$ in case of STLS, due to the hard-thresholding involved \cite{Brunton2016}, which is shown in Figure~\ref{fig_regularization}.
+Third, when adopting our idea of applying the inter spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters. 
+This is not a drawback of the proposed method, but rather a drawback of the particular application method that we have heavily used in this article and which was the main motivation for developing 
+the proposed method.
+As a very last remark, we draw attention to the fact that sparse regression can be transformed into sparse logistic regression when the signal we would like to transform is binary.
 
@@
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
-appearance. Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
+of the period (or frequency) the inter spike spectrum is obtained. 
+Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method be considered 
+as an additional source of information and not as a substitute for ordinary Fourier analysis. 
+Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
 appearance of the obtained inter spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
@@
 which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
-in the $\tau$-RR are not sensitive to noise, the corresponding inter spike spectrum also yields robust results in the presence of noise. We have successfully used the idea 
-of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter spike spectra, and thus a null model, 
-the number of significant peaks in the inter spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve period-doubling bifurcations. 
-\todo[inline]{Here a quick summary of the other applications.}
+in the $\tau$-RR are not sensitive to noise, the corresponding inter spike spectrum also yields robust results in the presence of noise.
 
@@
 
+\clearpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\section{Inter spike spectra for noisy R\"ossler system}
-
-\begin{figure}[h!]
- \centering
- \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
- \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
- in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.}
-\label{fig_tau_rr_example_roessler_noise}
-\end{figure}
-
 \section{Power grid frequency time series}\label{sec_power_grid_appendix}
@@
 are averages over all blocks, following \citet{meyer2020identifying}.
+
+\clearpage
+
+\section{Inter spike spectra for noisy R\"ossler system}
+
+\begin{figure}[h!]
+ \centering
+ \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
+ \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
+ in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.}
+\label{fig_tau_rr_example_roessler_noise}
+\end{figure}
+
+\clearpage
+
+\section{Regularizationparameters for different sparse regression techniques}\label{sec_regularization_appendix}
+
+\begin{figure}[h!]
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_regularization}
+ \caption{Pearson correlation coefficient $\rho_{\bf{s},\tilde{\bf{s}}}$ between the input signal signal $\bf{s}$ and the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ as a 
+ function of the regularization parameter $\alpha$ for \textbf{A} LASSO and \textbf{B} sequentially thresholded least squares (STLS) regression (see also Section \ref{sec_tau_rr_method}). 
+ The input time series is of length $N=200$ and stems from the $\tau$-RR of R\"ossler system in regular dynamics.}
+\label{fig_regularization}
+\end{figure}
 

### 2022-07-27 Applications/Regularization details/create_single_basis_function.m

@@ -1,0 +1,42 @@
+function cs = create_single_basis_function(N, period)
+% CREATE_SINGLE_BASIS_FUNCTION generates a matrix containing all (shifted)
+% basis functions of a spike train (Dirac-Comb) of length N.
+%    
+%    basis = generate_basis_functions(N, period) generates
+%    (period-by-N)-matrix containing spike-trains (Dirac-Combs) with
+%    interspike-interval `period` in all possible shifted variants.
+%
+%    Further reading:
+%    H. K. Kraemer et al., … 2021
+%
+%    See also ....
+
+% Copyright (c) 2021
+% K. Hauke Kraemer
+% Potsdam Institute for Climate Impact Research, Germany
+% http://www.pik-potsdam.de
+%
+% This program is free software and runs under MIT licence.
+%% check input
+narginchk(2,2)
+nargoutchk(1,1)
+assert(isscalar(N),"Input N must be a postive integer number")
+assert(mod(N,1) == 0,"Input N must be a postive integer number")
+assert(N > 0,"Input N must be a postive integer number")
+assert(isscalar(period),"Input period must be a postive integer number")
+assert(mod(period,1) == 0,"Input period must be a postive integer number")
+assert(period > 0,"Input period must be a postive integer number")
+assert(N>=period, "N must be larger or equal to the given priod")
+%%
+cs = zeros(period,N);
+for i = 1:period:N
+    cs(1,i) = 1;
+end
+
+css = horzcat(cs(1,:),zeros(1,period-1));
+for j = 1:period-1
+    inp_array = circshift(css,j);
+    cs(j+1,:) = inp_array(1:N);
+end
+
+end

### 2022-07-27 Applications/Regularization details/generate_basis_functions.m

@@ -1,0 +1,38 @@
+function basis = generate_basis_functions(N)
+% GENERATE_BASIS_FUNCTION generates a matrix containing all (shifted)
+% basis functions of a spike train (Dirac-Comb) of length N.
+%    
+%    basis = GENERATE_BASIS_FUNCTION(N) generates spike-trains (Dirac-Combs) 
+%    of all possible periods (=interspike interval), including all possible
+%    time shifts of those spike trains. This is a (M-by-N)-matrix, with M
+%    being `sum(1:ceil(N/2))+1`.
+%
+%    Further reading:
+%    H. K. Kraemer et al., … 2022
+%
+%    See also ....
+
+% Copyright (c) 2022
+% K. Hauke Kraemer
+% Potsdam Institute for Climate Impact Research, Germany
+% http://www.pik-potsdam.de
+%
+% This program is free software and runs under MIT licence.
+%%
+narginchk(1,1)
+nargoutchk(1,1)
+assert(isscalar(N),"Input N must be a postive integer number")
+assert(mod(N,1) == 0,"Input N must be a postive integer number")
+assert(N > 0,"Input N must be a postive integer number")
+
+%%
+num_of_basis_functions = sum(1:ceil(N/2))+1;
+basis = zeros(num_of_basis_functions, N);
+cnt = 1;
+for i = 1:ceil(N/2)
+   basis(cnt:cnt+i-1,:) = create_single_basis_function(N, i);
+   cnt = cnt + i;
+end
+temp = create_single_basis_function(N, ceil(N/2)+1);
+basis(end,:) = temp(1,:);
+end

### 2022-07-27 Applications/Regularization details/plot_and_compute_regularization_detail.m

@@ -1,0 +1,87 @@
+% Here we compute and plot the actual corrcoeff between input signal and 
+% re-composed signal as a function of the regularization parameter.
+
+clear, clc
+
+% generate some data
+dt = 0.1;  % sampling
+N = 1000; % length of considered tau-RR
+NN = 2000; % length of considered trajectory
+transients = 5000;
+e = 0.1; % recurrence threshold
+e_chaos = 0.05; % threshold for chaotic dynamics
+thres_meth = 'var';
+sigma = 0.05; % noise level
+
+% parameters and initial condition
+a = 0.36;
+b = 2;
+c = 4;
+x0=[.7, -1, 0.4];
+
+[~,x] = Rossler(a,b,c,x0,NN,dt,transients,0);
+
+Y1 = x';
+Y1 = (Y1 - mean(Y1)) ./ std(Y1);
+
+RP1 = rp(Y1,e,thres_meth);
+tau_rr1 = tau_recurrence_rate(RP1);
+
+s = tau_rr1(1:200)';
+
+%% Compute inter spike spectra
+
+lambdas = 0:0.0005:0.05; % the encountered regularization thresholds
+
+% normalize time series
+s = (s - mean(s)) ./ std(s);
+s = s - min(s);
+s = s ./ max(s);
+
+N = length(s);
+% get set of basis functions
+Theta = generate_basis_functions(N)';
+
+coeffs_stls = zeros(1,length(lambdas));
+coeffs_lasso = zeros(1,length(lambdas));
+
+
+for i = 1:length(lambdas)
+    display(i)
+    actual_lambda = lambdas(i);
+    % STLS
+    y_act = stls(s, Theta, actual_lambda);
+    rr = corrcoef(regenerate_signal(Theta, y_act), s);
+    coeffs_stls(i) = rr(2);
+
+    % LASSO
+    y_act = lasso(Theta, s, 'Lambda', actual_lambda, 'Alpha', 1);
+    rr = corrcoef(regenerate_signal(Theta, y_act), s);
+    coeffs_lasso(i) = rr(2);
+end
+
+%% Plot results
+lw = 2;
+fs = 20;
+sw = 60;
+
+ylims = [0.84 1];
+
+figure
+subplot(121)
+scatter(lambdas,coeffs_lasso,sw,'filled')
+title("LASSO")
+ylabel("\rho_{Pearson}")
+xlabel("regularization parameter \alpha")
[…]

### 2022-07-27 Applications/Regularization details/regenerate_signal.m

@@ -1,0 +1,7 @@
+function reg = regenerate_signal(Theta, coefs)
+% regenerate a decomposed signal from basis functions and its coefficients
+
+assert(size(Theta,2) == length(coefs),"Number of basis functions must match number of coefficients")
+reg =  Theta*coefs;
+
+end

### 2022-07-27 Applications/Regularization details/stls.m

@@ -1,0 +1,24 @@
+function coeffs = stls(s, Theta, lambda)
+% Sequential Thresholded Least Squares sparse regression method
+
+max_iterations = 10;
+tol = 1e-5;
+
+coeffs = pinv(Theta)*s;     % initial guess least squares
+biginds_old = coeffs;
+
+k = 1;
+while k < max_iterations
+    smallinds(:) = (abs(coeffs)<lambda);  % find small coefficients 
+    coeffs(smallinds) = 0;  % threshold these coeffs
+    biginds(:) = ~smallinds;
+    % check convergence
+    if max(abs(biginds - biginds_old')) < tol
+        break
+    end
+    % regress onto remaining terms
+    coeffs(biginds) = pinv(Theta(:,biginds))*s;
+    biginds_old(:) = biginds;
+    k = k + 1;
+end
+end

### 2022-08-02 Manuscript/inter_spike_manuscript_mdpi.tex
some minor revisions.

--- 2022-07-26 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
+\abstract{A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
 clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
@@
 idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
-along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
+along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter-spike spectrum can be interpreted as a nonlinear power 
 spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
@@
 
-Recurrence Plots (RPs) provide a vivid representation of complex dynamics stemming from potentially high dimensional systems, Eq.~\eqref{eq_rp_definition}. 
+Recurrence Plots (RPs) provide a vivid representation of complex dynamics stemming from potentially high dimensional systems \cite{marwan2007}
 \begin{equation}\label{eq_rp_definition}
@@
 \end{equation}
-The crucial free parameter $\varepsilon$ (recurrence threshold) determines the visible structures in the RP. It can be chosen such, that the recurrence rate 
-$RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value.
+The crucial free parameter $\varepsilon$ (recurrence threshold) determines the visible structures in the RP. It can be chosen such that the recurrence rate 
+$RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
 The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, but also for its 
@@
 However, there is a drawback to this approach. Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for 
-map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g. \cite{Schild1982,Cordoba1989}, see 
+map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g., \cite{Schild1982,Cordoba1989}, see 
 Fig.~\ref{fig_tau_rr_spectrum_example}E). Thus, it is not intuitive how to extract meaningful information about dominant frequencies of the systems' state space trajectory.
@@
 For clarification, consider the signal we would like to analyze 
-(e.g. the $\tau$-RR of a system) to be a Dirac comb (DC) with inter-spike period $T_\text{is}$: 
+(e.g., the $\tau$-RR of a system) to be a Dirac comb (DC) with inter-spike period $T_\text{is}$: 
 \begin{equation}
@@
 \end{equation}
-i.e., a series of Dirac delta functions for a period $T_\text{is}$. There is only one single period -- $T_\text{is}$ -- in this signal (Fig.~\ref{fig_tau_rr_dirac_comb}A, D), so 
+i.e., a series of Dirac delta functions for a period $T_\text{is}$. There is only one single period, $T_\text{is}$, in this signal (Fig.~\ref{fig_tau_rr_dirac_comb}A, D), so 
 in principle we would strive for a single peak in the frequency domain of this signal at a frequency $f=1/T_\text{is}$. Surprisingly the Fourier spectrum does not meet this expectation 
-and instead of a single frequency, there are exceptionally many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is, because the Fourier components add constructively 
+and instead of a single frequency, there are exceptionally many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
 for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.
@@
  \textbf{B} its FFT-based powerspectrum.
- \textbf{C} Proposed inter spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
+ \textbf{C} Proposed inter-spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
  \textbf{D} DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in \textbf{A}, and
  \textbf{E} its FFT-based powerspectrum. 
- \textbf{F} Proposed inter spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
- Inter spike spectra were obtained with a LASSO regression and a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and 
+ \textbf{F} Proposed inter-spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
+ Inter-spike spectra were obtained with a LASSO regression and a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and 
  its re-composed signals (c.f. Section~\ref{sec_tau_rr_method}). 
@@
 
-In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter spike spectrum} does not show resonance 
+In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter-spike spectrum} does not show resonance 
 behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
 any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
-FT. In Section \ref{sec_tau_rr_application} we exemplify the usage of inter spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter spike spectrum 
+FT. In Section \ref{sec_tau_rr_application} we exemplify the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
 can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
@@
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
-vector $\bf{s}$. 
-First, $\tilde{N}$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
+vector $\vec{s}$. 
+First, $\tilde{N}$ different DCs of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
 for possible phase shifts of 
-these basis functions occurring in $\bf{s}$, each of these $\tilde{N}$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
+these basis functions occurring in $\vec{s}$, each of these $\tilde{N}$ different DCs also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
 $M = \sum_{i=1}^{\tilde{N}}i$ 
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure)
+(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure):
 \begin{align}
-\label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-\label{eq_T_is} T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\label{eq_basis_matrix} 
+\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
+\label{eq_T_is} T_\text{is}(i)&= n, \quad \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
 Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
-Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter spike period, 
-if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
+Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter-spike period, 
+if we would include all $N$ possible inter-spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
 The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, here 
-the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
+the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
 Fig.~\ref{fig_tau_rr_basis_functions}B).\\
@@
 \begin{equation}
-\bf{X}^T \boldsymbol\beta=\bf{s}
+\bfX^T \boldsymbol{\beta}=\vec{s}
 \label{eq_linear_system}
@@
 has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
-particularly interested in those solutions, which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
+particularly interested in those solutions, which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\vec{s}$ into a minimal number of basis 
 functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
@@
 $T_\text{is}$ into $\hat{\boldsymbol\beta}_f$ and obtain the 
-\textit{inter spike spectrum} by simply plotting $\hat{\boldsymbol\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$
+\textit{inter-spike spectrum} by simply plotting $\hat{\boldsymbol\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$
 (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
@@
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_basis_functions}
-\caption{\textbf{A} Example for a full set of basis functions for an input signal of length $N=4$, aligned in the matrix $\bfX'$. Inter spike periods $T_{\text{is}}$ larger 
-than $\ceil*{N/2}+1$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which can not be uniquely assigned to a certain inter spike period 
+\caption{\textbf{A} Example for a full set of basis functions for an input signal of length $N=4$, aligned in the matrix $\bfX'$. inter-spike periods $T_{\text{is}}$ larger 
+than $\ceil*{N/2}+1$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which cannot be uniquely assigned to a certain inter-spike period 
 (blue sheared).
@@
 which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$.
-Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small,
-since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~\ref{eq_linear_system} and not sparse. On the other hand, 
-only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter spike spectrum, are obtained when $\alpha$ is sufficiently large. 
+Obviously, there will be numerous peaks in the inter-spike spectrum of a given signal, when $\alpha$ is small,
+since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
+only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
 The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
-different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ matches a 
-given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.
+different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
+given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and itself.
 
@@
 
-We exemplify the use of the inter spike spectrum in combination with the $\tau$-RR as outlined in 
+We exemplify the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
 Section \ref{sec_tau_rr_intro} on several interesting research questions. The procedure is the following:
 \begin{itemize}[noitemsep]
-\item[(1)] Compute a RP of the trajectory of the system, Eq.~\eqref{eq_rp_definition}. 
+\item[(1)] Compute a RP of the trajectory of the system, Eq.~\eqref{eq_rp_definition}. If only univariate data is available, perform a state space reconstruction for obtaining the trajectory first.
 \item[(2)] Compute the $\tau$-RR of that RP, Eq.~\eqref{eq_tau_rr}.
-\item[(3)] Transform the $\tau$-RR into the proposed inter spike spectrum, see Section \ref{sec_tau_rr_method}.
+\item[(3)] Transform the $\tau$-RR into the proposed inter-spike spectrum, see Section \ref{sec_tau_rr_method}.
 \end{itemize}
@@
 First, we consider the R\"ossler system (Eq.~\eqref{eq_model_roessler} in Appendix \ref{sec_models_roessler}) 
-in three different dynamical setups. We use the proposed inter spike spectrum to
+in three different dynamical setups. We use the proposed inter-spike spectrum to
 identify the type of dynamics.
@@
  \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler}
- \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
+ \caption{Inter-spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
  \textbf{A} Trajectory of the system in a period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
@@
  recurrence rate for D \& E and 5\% for F. 
-  \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
-  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a LASSO regression and a regularization threshold 
-  corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
-  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I. }
+  \textbf{G, H, I} $\tau$-RRs of the shown RPs. 
+  \textbf{J, K, L} The proposed inter-spike spectra of the $\tau$-RRs shown in panels G, H, I. Spectra were obtained with a LASSO regression and a regularization threshold 
+  corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
+  \textbf{M, N, P} Fourier power spectra of the $\tau$-RRs shown in panels G, H, I. }
 \label{fig_tau_rr_example_roessler}
@@
 
-The inter spike spectra unravel the specific dynamics, which are also apparent in the state space portraits (Fig.~\ref{fig_tau_rr_example_roessler}A, B, C) and in the 
+The inter-spike spectra unravel the specific dynamics, which are also apparent in the state space portraits (Fig.~\ref{fig_tau_rr_example_roessler}A, B, C) and in the 
 $\tau$-RRs (Fig.~\ref{fig_tau_rr_example_roessler}G, H, I). The proposed idea is also 
 robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. While the peak shape does 
-change in the presence of noise, its position does not, and this is what the inter spike spectrum encrypts after all.
+change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all.
 
@@
 \item[(5)] $\tau$-RR, Eq.~\eqref{eq_tau_rr}, is computed from the RP of the signal and from the RPs of the surrogates,
-\item[(6)] inter spike spectra are obtained from $\tau$-RR of the signal and from the $\tau$-RRs of the surrogates, see Section \ref{sec_tau_rr_method}, and finally,
-\item[(7)] from the distribution of the surrogate inter spike spectra the $95^\text{th}$ percentile is computed. The peaks of the inter spike spectrum of the signal which exceed 
+\item[(6)] inter-spike spectra are obtained from $\tau$-RR of the signal and from the $\tau$-RRs of the surrogates, see Section \ref{sec_tau_rr_method}, and finally,
+\item[(7)] from the distribution of the surrogate inter-spike spectra the $95^\text{th}$ percentile is computed. The peaks of the inter-spike spectrum of the signal which exceed 
 this percentile are counted. 
@@
 hence the same Fourier powerspectrum, and the same 
-amplitude distribution. We consider the number of significant peaks in the inter spike spectrum with
+amplitude distribution. We consider the number of significant peaks in the inter-spike spectrum with
 respect to the control parameter in order to distinguish the corresponding dynamics (Fig.~\ref{fig_tau_rr_logistic}C).
 A correlation with the positive Lyapunov exponent (Fig.~\ref{fig_tau_rr_logistic}A) is discernible 
-($\rho_{\text{Pearson}}(\text{Lyapunov})=0.72$). This analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter spike spectrum. 
-However, whenever the periods of the ``new'' cycles coincide with integer multiples of the periods of already existing cycles, this approach can not detect 
+($\rho_{\text{Pearson}}(\text{Lyapunov})=0.72$). This analysis can tackle period-doubling, since it ``measures'' the dominant cycles via the inter-spike spectrum. 
+However, whenever the periods of the ``new'' cycles coincide with integer multiples of the periods of already existing cycles, this approach cannot detect 
 period-doubling. A similar case can be observed in Fig.~\ref{fig_tau_rr_example_roessler}J,K where the number of peaks does not change, but  their mutual distance does.
@@
 time series. This translates into a null hypothesis 
-that the $\tau$-RR and its corresponding inter spike spectrum stems from a RP of a random signal. In this case the probability of finding a black point in the RP can be obtained 
+that the $\tau$-RR and its corresponding inter-spike spectrum stems from a RP of a random signal. In this case the probability of finding a black point in the RP can be obtained 
 from a binomial distribution with probability parameter $p$ set to the recurrence rate of the RP of the signal. This way $100$ surrogate $\tau$-RRs are computed in step (5). 
@@
 On the contrary, highly sampled (flow-) data often yield not as 
-spiky $\tau$-RR's and, thus, the number of significant peaks in the inter spike spectrum may not be sensitive enough to detect period-doubling bifurcations. Moreover the sensitivity of the 
-inter spike spectrum to detect the regime shifts also depends on the critical regularization threshold. Nevertheless the 
-according inter spike spectra is still revealing important information (Fig.~\ref{fig_tau_rr_example_roessler}) and practitioners can design appropriate quantifying statistics based 
+spiky $\tau$-RRs and, thus, the number of significant peaks in the inter-spike spectrum may not be sensitive enough to detect period-doubling bifurcations. Moreover the sensitivity of the 
+inter-spike spectrum to detect the regime shifts also depends on the critical regularization threshold. Nevertheless the 
+according inter-spike spectra is still revealing important information (Fig.~\ref{fig_tau_rr_example_roessler}) and practitioners can design appropriate quantifying statistics based 
 on these spectra, which suit the research task.
@@
  \caption{\textbf{A} Bifurcation diagram and Lyapunov exponent and of the Logistic map as a function of the control parameter $r$.
- \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 
+ \textbf{B} Number of significant peaks ($\alpha=0.05$) in the inter-spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in \textbf{A} 
  (white noise surrogates). 
- \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}. For obtaining the inter spike spectra we used 
- a LASSO regression and a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals.  
+ \textbf{C} Same as \textbf{B}, but for iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates \cite{Schreiber1996,Schreiber2000}. For obtaining the inter-spike spectra we used 
+ a LASSO regression and a regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals.  
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Inter spike spectra of power grid frequency data}
+\subsection{Inter-spike spectra of power grid frequency data}
 
@@
  \caption{Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}). 
- The corresponding averaged inter spike spectra of the according $\tau$-RR's, Eq.~\eqref{eq_tau_rr}, are shown in \textbf{C} and \textbf{D}, respectively. Vertical red dashed lines correspond to 
+ The corresponding averaged inter-spike spectra of the according $\tau$-RRs, Eq.~\eqref{eq_tau_rr}, are shown in \textbf{C} and \textbf{D}, respectively. Vertical red dashed lines correspond to 
  $15$, $30$ and $60$ \si{min}. For technical details on the calculation of the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}.}  
@@
 $40$ \si{min} for both datasets, which is absent in the Fourier spectrum and which is not a multiple of the missing $15$ \si{min} peak. The position and magnitude of the peaks in the shown 
-inter spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.\\
+inter-spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.\\
 
-We interpret the results presented as follows. The missing $15$ \si{min} in the inter spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min} 
-(see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter spike spectra are not able to detect it and the 
-sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks.
-Moreover, the inter spike spectra, unlike the Fourier spectra demonstrates sharp peaks exactly at $30$ and $60$ \si{min}, i.e.
-during dispatches.
-Eventually, here we have found a clear sharp peak at $40$ \si{min} which can occur because of any regular controls in a power grid, and can be a hint to develop the existing stochastic processes to model precisely the power grid frequency \cite{gorjao2020data}.
+We interpret the results presented as follows. The missing $15$ \si{min} in the inter-spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min} 
+(see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter-spike spectra are not able to detect it and the 
+sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks. Moreover, the inter-spike spectra, unlike the Fourier spectra demonstrates sharp peaks exactly 
+at $30$ and $60$ \si{min}, i.e. during dispatches (not valid in case of the GB dataset). Eventually, here we have found a clear sharp peak at $40$ \si{min} which can occur 
+because of any regular controls in a power grid, and can be a hint to develop the existing stochastic processes to model precisely the power grid frequency \cite{gorjao2020data}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Evolutionary inter spike spectra of astronomical data}
+\subsection{Evolutionary inter-spike spectra of Earth's orbit data}
 
-\todo[inline]{Add this section and keep it very very short.}
+When applying the proposed inter-spike spectrum to the $\tau$-RR of a time series we expect additional frequency/period information, due to the fact that the recurrence plot (RP), 
+Eq.~\eqref{eq_rp_definition}, and its corresponding $\tau$-RR, Eq.~\eqref{eq_tau_rr}, visualize the trajectory of the embedded time series in an embedding space of higher dimension. 
+However, given a sufficient embedding of the time series, we would also expect that major frequencies/periods of the non-embedded time series are incorporated in the RP, its $\tau$-RR, 
+and eventually in the inter-spike spectrum of the $\tau$-RR. In order to demonstrate this we apply the inter-spike spectrum to the freely available eccentricity time series of \citet{Laskar2011}. 
+This astronomical computation of the orbital motion of the Earth (here we focus on the eccentricity only) has a clear expectation value of the incorporated frequencies/periods. The three leading 
+eccentricity cycles of 405 kyr period, 95 kyr period and 124 kyr period are well known in palaeoclimate studies \cite{Laskar2004}\todo{das ist aber keine palaeoclimate study sondern die numerische loesung der milankovich cycles.
+vielleicht besser ein palaeo-paper zitieren?
+z.
+b.
+westerhold?}.
+Our aim in this section is to show that the inter-spike spectrum
+of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier powerspectrum of the non-embedded eccentricity time series. We will further 
+show that Fourier-transforming the $\tau$-RR instead of applying the proposed inter-spike spectrum will lead to non-satisfying results, since the spiky $\tau$-RR excites a variety of harmonics in 
+the corresponding Fourier spectrum (cf. Section \ref{sec_tau_rr_intro}). We use a time series which covers the past \mytilde $67$ Mio.~years (Myr), with a total length of $N=13,421$ samples and a 
+sampling period of $\Delta t= 5,000$.\\
+First we compute an evolutionary short time Fourier transform (FT) using a windowsize of $ws=1,000$ samplepoints ($\equiv 5$ Myr) shifted by unity and a 
+Hamming window. The spectrogram reveals the expected periods mentioned, which are highlighted and clearly visible (Fig.~\ref{fig_laskar_spectra}A).
+
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_laskar_spectra}
+ \caption{\textbf{A} Evolutionary Fourier power spectra of eccentricity time series. \textbf{B} Inter-spike spectrogram of the $\tau$-recurrence rate of the eccentricity time 
+ series and \textit{C} its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
+ For comparability, in all cases the spectra aligned in the columns of the shown plots are normalized to probabilities (sum of unity for 
+ each power spectrum). For further computational details, please refer to the main text.}  
+\label{fig_laskar_spectra}
+\end{figure}
+
+\noindent Then we construct the inter-spike spectrogram of the $\tau$-RR by first determining an appropriate embedding. By using a recent Tree-Embedding-Ansatz \cite{Kraemer2022} we minimize the 
+\textit{false nearest neighbor} statistic \cite{hegger1999} and use the continuity statistic \cite{pecora2007} for potential delays. Eventually we obtain an $8$-dimensional embedding 
+with delays $\tau s=[0, 18, 36, 48, 62, 101, 114]$ (in sampling units) for the entire time series. Similar to the preceding approach we embed the time series with these embedding parameters 
+on windows of size $ws=1,200$ and a unity shift.\footnote{We use a slightly larger window here than in the short FT, because the embedding causes a ``loss'' of data points and we want to 
+cover similar time spans.} The RPs are computed on these embedded trajectories with a fixed recurrence threshold corresponding to $10\%$ global recurrence rate \cite{kraemer2018} 
+and the inter-spike spectra of the corresponding $\tau$-RRs is obtained by using STLS regression (see Section \ref{sec_tau_rr_method}) and a regularization threshold corresponding to 
+$\rho=0.9$ accordance of $\tau$-RRs and re-composed signals. We only use the first $200$ data points of the $\tau$-RR (covering a time span of $1$ Myr). 
+The spectrogram also highlights the $95$, $124$ and $405$ kyr periods as expected (Fig.~\ref{fig_laskar_spectra}B). 
+Additional power is distributed in its harmonics at $190$ and $248$ kyr periods. Finally, the standard FT with a Hamming window of the same $\tau$-RRs used to obtain the inter-spike 
+spectrogram in panel B, yields a smeared spectrogram which does not reflect the expected periods, but rather suffers from the spike train behavior, i.e. many excited harmonics, of the 
+FT described in Section \ref{sec_tau_rr_intro} and Fig.~\ref{fig_tau_rr_dirac_comb}. The shown results are robust to a change of embedding parameters and windowsizes. However, a too low 
+regularization threshold smears the clear spectrogram in panel B.
 
@@
 
-A novel type of powerspectrum, the \textit{inter spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
+A novel type of powerspectrum, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
 combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution (we chose LASSO or a sequentially 
@@
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
+of the period (or frequency) the inter-spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
 appearance. Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
-appearance of the obtained inter spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
-the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
+appearance of the obtained inter-spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
+the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
 
-The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RR's) into their frequency domain. 
+The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RRs) into their frequency domain. 
 This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
-The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, and the inter spike spectrum can reliably reveal the system's dominant frequencies, 
+The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, and the inter-spike spectrum can reliably reveal the system's dominant frequencies, 
 which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
-in the $\tau$-RR are not sensitive to noise, the corresponding inter spike spectrum also yields robust results in the presence of noise. We have successfully used the idea 
-of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter spike spectra, and thus a null model, 
-the number of significant peaks in the inter spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve period-doubling bifurcations. 
+in the $\tau$-RR are not sensitive to noise, the corresponding inter-spike spectrum also yields robust results in the presence of noise. We have successfully used the idea 
+of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter-spike spectra, and thus a null model, 
+the number of significant peaks in the inter-spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve period-doubling bifurcations. 
 \todo[inline]{Here a quick summary of the other applications.}
 
-We could think of a broad range of applications of the proposed idea. The inter spike spectrum itself can serve as a valuable tool for the analysis of any sort of 
-spike-train-like data. On the other hand, the inter spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
+We could think of a broad range of applications of the proposed idea. The inter-spike spectrum itself can serve as a valuable tool for the analysis of any sort of 
+spike-train-like data. On the other hand, the inter-spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
 When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021,Kraemer2022} show that 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, KHK and FH; methodology, KHK, FH and NM; software, KHK and FH; validation, KHK, FH, MA and NM.; formal analysis, KHK; data curation, KHK and MA; writing---original draft preparation, KHK; writing---review and editing, KHK, FH, MA and NM; visualization, KHK; supervision, NM; project administration, JK; All authors have read and agreed to the published version of the manuscript.}
+\authorcontributions{Conceptualization, KHK and FH; methodology, KHK, FH and NM; software, KHK and FH; validation, KHK, FH, MA and NM; formal analysis, KHK; data curation, KHK and MA; writing---original draft preparation, KHK; writing---review and editing, KHK, FH, MA and NM; visualization, KHK; supervision, NM; project administration, JK; All authors have read and agreed to the published version of the manuscript.}
 
@@
 \end{align}
-For producing Figs.~\ref{fig_tau_rr_example_roessler_noise} and ~\ref{fig_tau_rr_example_roessler}, the initial condition for producing panels \textbf{A} \& \textbf{B} was set to $u_0=[.7, -1, 0.4]$ with a sampling time
+For producing Figs.~\ref{fig_tau_rr_example_roessler_noise} and ~\ref{fig_tau_rr_example_roessler}, the initial condition for producing panels \textbf{A} \& \textbf{B} was set to $u_0=[0.7, -1, 0.4]$ with a sampling time
 of $dt=0.05$ and in case of panel \textbf{C}, $u_0=[-0.1242, -2.5415, 0.2772]$ with a sampling time of $dt=0.1$.
 The first $5,000$ samples were discarded as transients and trajectories of length $N=5,000$ were
-obtained from which we computed the RPs and the corresponding $\tau$-RR's. For the inter spike spectra only the first $1,000$ values of the $\tau$-RR's were considered.
+obtained from which we computed the RPs and the corresponding $\tau$-RRs. For the inter-spike spectra only the first $1,000$ values of the $\tau$-RRs were considered.
 
-\section{Inter spike spectra for noisy R\"ossler system}
+\section{Inter-spike spectra for noisy R\"ossler system}
 
@@
  \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
- \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter spike spectra 
+ \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter-spike spectra 
  in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.}
@@
 
-We downsample these time series to a sampling time of $\Delta t_{\text{CE}}= \Delta t_{\text{GB}}=20$\si{s}, which lead to total time series lengths of 
-$N_{\text{CE}}=587,520$ and $N_{\text{GB}}=1,581,120$ which we use for the further analysis.
+We downsampled these time series to a sampling time of $\Delta t_{\text{CE}}= \Delta t_{\text{GB}}=20$\si{s}, which led to total time series lengths of 
+$N_{\text{CE}}=587,520$ and $N_{\text{GB}}=1,581,120$ which we used for the further analysis.
 
@@
 
-In this analysis we divide the time series into 
-non-overlapping blocks of length $N_{\text{block}}=4,320$, covering a time span of $24$ hours. For each time series block we compute Fourier spectra and recurrence plots (RPs), 
-Eq.~\eqref{eq_rp_definition}, along with their $\tau$-RR's, Eq.~\ref{eq_tau_rr}. The RPs are obtained from a uniform 5-dimensional time-delay embedding of each time series with 
-the delay set to the first minimum of the mutual information \cite{fraser1986,hegger1999} and a fixed recurrence threshold corresponding to 8\% recurrence rate is used in order 
-to ensure comparability \cite{kraemer2018}. The first $600$ data points of the $\tau$-RR's are used for finally obtaining inter spike spectra with a LASSO regression and a 
-regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The spectra shown in all panels of Figure~\ref{fig_power_grid_spectra} 
+In this analysis we divided the time series into 
+non-overlapping blocks of length $N_{\text{block}}=4,320$, covering a time span of $24$ hours. For each time series block we computed Fourier spectra and recurrence plots (RPs), 
+Eq.~\eqref{eq_rp_definition}, along with their $\tau$-RRs, Eq.~\ref{eq_tau_rr}. The RPs were obtained from a uniform 5-dimensional time-delay embedding of each time series with 
+the delay set to the first minimum of the mutual information \cite{fraser1986,hegger1999} and a fixed recurrence threshold corresponding to 8\% recurrence rate was used in order 
+to ensure comparability \cite{kraemer2018}. The first $600$ data points of the $\tau$-RRs were used for finally obtaining inter-spike spectra with a LASSO regression and a 
+regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals. The spectra shown in all panels of Figure~\ref{fig_power_grid_spectra} 
 are averages over all blocks, following \citet{meyer2020identifying}.

### 2022-08-03 Manuscript/inter_spike_manuscript_mdpi.tex
last comment

--- 2022-07-27 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 \label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-\label{eq_T_is} T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\label{eq_T_is} T_\text{is}(i)&= n \quad,~s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
-\todo[inline]{Make Eq.\eqref{eq_T_is} nicer}
+\todo[inline]{HK: Eq.\eqref{eq_basis_matrix} is somehow ugly. Maybe someone can get rid of that sum and make it nicer? I tried with 
+modulo, but just could not figure it out exactly. There must be an easy way I do not see.}
 Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 

### 2022-08-03 Manuscript/inter_spike_manuscript_mdpi.tex

--- 2022-08-02 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 \begin{align}
-\label{eq_basis_matrix} 
-\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-\label{eq_T_is} T_\text{is}(i)&= n, \quad \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
+\label{eq_T_is} T_\text{is}(i)&= n \quad,~s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
+\todo[inline]{HK: Eq.\eqref{eq_basis_matrix} is somehow ugly. Maybe someone can get rid of that sum and make it nicer? I tried with 
+modulo, but just could not figure it out exactly. There must be an easy way I do not see.}
 Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Inter-spike spectra of power grid frequency data}
+\subsection{Inter spike spectra of power grid frequency data}\label{sec_power_grid}
 
@@
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter-spike spectrum is obtained. This novel powerspectrum is superior to an ordinary FFT-based powerspectrum, when the signal has a spike-train-like 
-appearance. Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
-appearance of the obtained inter-spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
-the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
+of the period (or frequency) the inter spike spectrum is obtained. 
+Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method be considered 
+as an additional source of information and not as a substitute for ordinary Fourier analysis. 
+Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
+appearance of the obtained inter spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
+the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
 
@@
 which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
-in the $\tau$-RR are not sensitive to noise, the corresponding inter-spike spectrum also yields robust results in the presence of noise. We have successfully used the idea 
-of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter-spike spectra, and thus a null model, 
-the number of significant peaks in the inter-spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve period-doubling bifurcations. 
-\todo[inline]{Here a quick summary of the other applications.}
+in the $\tau$-RR are not sensitive to noise, the corresponding inter spike spectrum also yields robust results in the presence of noise.
 
@@
 
-\section{Inter-spike spectra for noisy R\"ossler system}
-
-\begin{figure}[h!]
- \centering
- \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler_noise}
- \caption{Same as in Fig.~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter-spike spectra 
- in \textbf{J, K, L}, and the Fourier spectra in \textbf{M, N, P} are unaffected by the additive noise.}
-\label{fig_tau_rr_example_roessler_noise}
-\end{figure}
-
 \section{Power grid frequency time series}\label{sec_power_grid_appendix}

### 2022-08-04 Manuscript/inter_spike_manuscript_mdpi.tex
add orcid
minor issues

@@
 \newcommand{\orcidauthorA}{0000-0002-9943-5391} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0001-6643-9508} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0003-1437-7039} % Add \orcidB{} behind the author's name
 
 % Authors, for the paper (add full first names)
-\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}
+\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1}$\orcidB{}, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,2,3,}$*\orcidC{}}
 
@@
 \begin{align}
-\label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-\label{eq_T_is} T_\text{is}(i)&= n \quad,~s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\label{eq_basis_matrix} 
+\bfX_{i,j} &= \sum_{k=0}^{N}\delta\bigl(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \bigr), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
+\label{eq_T_is} T_\text{is}(i)&= n, \quad s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Inter spike spectra of power grid frequency data}\label{sec_power_grid}
+\subsection{inter-spike spectra of power grid frequency data}\label{sec_power_grid}
 
@@
 Additional power is distributed in its harmonics at $190$ and $248$ kyr periods. Finally, the standard FT with a Hamming window of the same $\tau$-RRs used to obtain the inter-spike 
-spectrogram in panel B, yields a smeared spectrogram which does not reflect the expected periods, but rather suffers from the spike train behavior, i.e. many excited harmonics, of the 
+spectrogram in panel B, yields a smeared spectrogram which does not reflect the expected periods, but rather suffers from the spike train behavior, i.e., many excited harmonics, of the 
 FT described in Section \ref{sec_tau_rr_intro} and Fig.~\ref{fig_tau_rr_dirac_comb}. The shown results are robust to a change of embedding parameters and windowsizes. However, a too low 
@@
 
-We have successfully used the idea of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter spike spectra, 
-and thus a null model, the number of significant peaks in the inter spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve 
+We have successfully used the idea of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter-spike spectra, 
+and thus a null model, the number of significant peaks in the inter-spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve 
 period-doubling bifurcations. However, we have to admit this way the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 
-This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter spike power spectra for period-2, period-3 and chaotic dynamics.
-Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter spike spectra of power grid 
+This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike power spectra for period-2, period-3, and chaotic dynamics.
+Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter-spike spectra of power grid 
 frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis. And last but not least, we showed that our approach 
@@
 often need to get downsampled as a preprocessing step (e.g., see Appendix \ref{sec_power_grid_appendix}). Second, the regularization parameter $\alpha$ for the regression is a crucial free parameter. 
-As described in Section \ref{sec_tau_rr_method} our idea in this paper is to select the $\alpha$ such that the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ matches a 
-given (Pearson) correlation coefficient $\rho_{\bf{s},\tilde{\bf{s}}}$ between the original signal $\bf{s}$ and itself. This ensures that $\alpha$ adjusts itself to the data as well as to the 
+As described in Sect.~\ref{sec_tau_rr_method}, our idea in this paper is to select the $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
+given (Pearson) correlation coefficient $\rho_{\vec{s},\tilde{\vec{s}}}$ between the original signal $\vec{s}$ and itself. This ensures that $\alpha$ adjusts itself to the data as well as to the 
 used regression method. We found that this increases the comparability of different spectra, especially when performing a running window approach in order to obtain an evolutionary spectrogram 
 (Fig.~\ref{fig_laskar_spectra}). 
-However, the two different sparse regression algorithms we encountered in this article (LASSO and STLS) yield different results for the same desired $\rho_{\bf{s},\tilde{\bf{s}}}$. 
+However, the two different sparse regression algorithms we encountered in this article (LASSO and STLS) yield different results for the same desired $\rho_{\vec{s},\tilde{\vec{s}}}$. 
 Even if the spectra obtained in this way look qualitatively similar, they are not always quantitatively similar. The reason for this 
-is that $\rho_{\bf{s},\tilde{\bf{s}}}$ is not a smooth function of $\alpha$ in case of STLS, due to the hard-thresholding involved \cite{Brunton2016}, which is shown in Figure~\ref{fig_regularization}.
-Third, when adopting our idea of applying the inter spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters. 
+is that $\rho_{\vec{s},\tilde{\vec{s}}}$ is not a smooth function of $\alpha$ in case of STLS, due to the hard-thresholding involved \cite{Brunton2016}, which is shown in Fig.~\ref{fig_regularization}.
+Third, when adopting our idea of applying the inter-spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters. 
 This is not a drawback of the proposed method, but rather a drawback of the particular application method that we have heavily used in this article and which was the main motivation for developing 
@@
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter spike spectrum is obtained. 
+of the period (or frequency) the inter-spike spectrum is obtained. 
 Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method be considered 
@@
 Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
-appearance of the obtained inter spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
-the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
+appearance of the obtained inter-spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
+the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.
 
@@
 which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
-in the $\tau$-RR are not sensitive to noise, the corresponding inter spike spectrum also yields robust results in the presence of noise.
+in the $\tau$-RR are not sensitive to noise, the corresponding inter-spike spectrum also yields robust results in the presence of noise.
 
@@
 
-\section{Inter spike spectra for noisy R\"ossler system}
+\section{inter-spike spectra for noisy R\"ossler system}
 
@@
  \includegraphics[width=\textwidth]{./figures/fig_regularization}
- \caption{Pearson correlation coefficient $\rho_{\bf{s},\tilde{\bf{s}}}$ between the input signal signal $\bf{s}$ and the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ as a 
+ \caption{Pearson correlation coefficient $\rho_{\vec{s},\tilde{\vec{s}}}$ between the input signal signal $\vec{s}$ and the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ as a 
  function of the regularization parameter $\alpha$ for \textbf{A} LASSO and \textbf{B} sequentially thresholded least squares (STLS) regression (see also Section \ref{sec_tau_rr_method}). 

### 2022-08-31 Manuscript/inter_spike_manuscript_mdpi.tex
Final 1st submission

@@
 % Contact information of the corresponding author
-\corres{Correspondence: hkraemer@pik-potsdam.de; marwan@pik-potsdam.de}
+\corres{Correspondence: hauke\_kraemer@hotmail.com; marwan@pik-potsdam.de}
 
@@
 \end{align}
-\todo[inline]{HK: Eq.\eqref{eq_basis_matrix} is somehow ugly. Maybe someone can get rid of that sum and make it nicer? I tried with 
-modulo, but just could not figure it out exactly. There must be an easy way I do not see.}
+
 Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
@@
 This astronomical computation of the orbital motion of the Earth (here we focus on the eccentricity only) has a clear expectation value of the incorporated frequencies/periods. The three leading 
-eccentricity cycles of 405 kyr period, 95 kyr period and 124 kyr period are well known in palaeoclimate studies \cite{Laskar2004}\todo{das ist aber keine palaeoclimate study sondern die numerische loesung der milankovich cycles.
-vielleicht besser ein palaeo-paper zitieren?
-z.
-b.
-westerhold?}.
+eccentricity cycles of 405 kyr period, 95 kyr period and 124 kyr period are well known in palaeoclimate studies \cite{Laskar2004,Westerhold2020}.
 Our aim in this section is to show that the inter-spike spectrum

### 2022-08-31 Manuscript/inter_spike_manuscript_mdpi.tex
1st submission last changes

@@
 $RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
-The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, but also for its 
+The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, 
+but also for its 
 quantification, using certain structures in the RP, such as diagonal or vertical lines \cite{marwan2007}.
@@
 Some of these recurrence quantification measures, the entropy of diagonal lines and the entropy of 
-recurrence times, can be related to the Kolmogorov-Sinai entropy \cite{march2005,baptista2010}. However, these quantifiers have a free parameter, the minimal considered line length, and 
+recurrence times, can be related to basic characteristics of complex systems, such as the Kolmogorov-Sinai entropy \cite{march2005,baptista2010}.
+However, these quantifiers have a free parameter, the minimal considered line length, and
 are usually biased, due to the finite size of the RP and thickened diagonal lines, which needs to be corrected \cite{Kraemer2019}. Moreover, the mentioned statistics cannot account for 
@@
 A novel type of powerspectrum, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
-combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution (we chose LASSO or a sequentially 
-thresholded least squares regression STLS). Since there are 
+combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. Wee chose LASSO or a sequentially 
+thresholded least squares regression STLS in this letter. Since there are 
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
 of the period (or frequency) the inter-spike spectrum is obtained. 
-Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method be considered 
-as an additional source of information and not as a substitute for ordinary Fourier analysis. 
+Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
+be considered 
+as an additional source of information but not as a substitute for ordinary Fourier analysis. 
 Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 

### 2022-10-19 Manuscript/rebuttal.md
add rebuttal letter and start revision based on first comments of rev. 1

Rebuttal letter
===============

We thank the reviewers for their careful reading of our manuscript and their useful comments. We have considered all of them and improved the manuscript accordingly. Our responses to all reviewer comments (listed below in italic) in the following.

Reviewer 1
----------

_Introduction: a clear formulation of the mathematical problem, the state-of-the-art in terms of the existing literature, a summary of the solution proposed and of its pros and cons are totally lacking._

We thank for this comment, but do not agree completely with this criticism. In our opinion, the problem is well stated and the outline of the manuscript is summarised. But the literature review can be improved, which with the help of the suggestions of the reviewer 2 we finally did. "a summary of the solution proposed" as well as "pros and cons" do not belong to the introduction. These are provided in the conclusion of the manuscript. We added some further introductory sentences to the beginning of the introduction.

_Equation (1) is poorly introduced. Although the authors cite a reference ([1]), the x_i, x_j vectors, as well as the parameters d and N, are not explained. The "trajectory x_i", for example, is introduced only at the end of page 1. Moreover, R_{i,j}(\epsilon) is not explicitly stated and explained._

In deed, out intention was to have a short but clear introduction into the recurrence plot method, which reviewer 2 obviously liked very much. Nevertheless, we have now added an explanation on the recurrence plot definition. An unfamiliar reader should now better understand the method.

_(lines 20-21) "Furthermore, the correlation structures of higher dimensional spaces can be resolved in the recurrence-derived Fourier-spectrum." What do the authors mean with "correlation structures of higher dimensional spaces"? And what do they mean with the term "resolve"?_

TBD

_Figs. 2C, 2F: the "Inter Spike Spectrum of perfect DC" is equal to the "Inter Spike Spectrum of randomized DC", although the time domain signals (Figs. 2A, 2D, respectively) are not. This might prove that the new tool introduced in the manuscript is not invertible: Definitely a major issue._

TBD

_(beginning of Sec. 2) "Let s(t_i) be the normalized signal we want to transform...". It is unclear how s(t_i) is obtained (i.e. "normalized") from x(t)._

TBD

_The way in which basis functions are defined is confusing._

TBD

_The authors state that they "either use" the LASSO or the STLS methods to obtain β. It is not clear when the authors prefer one method over the other one, and why. Moreover, although a direct comparison between the methods, namely the different behavior of the regularization parameter, is shown in Fig. A3, a thorough comparison between the two methods is lacking: Figs. 2, 4 and 5 appear to be obtained by using only the LASSO method. One of the few mentions of the STLS method is in the Discussion section, where it is stated that (lines 236-237) "[...] the two different sparse regression algorithms [...] yield different results for the same desired ρ". How do the authors support this statement? There is no clear way for a reader to either compare the two methods, or to understand why the authors did not consider a single method from the very beginning._

TBD

_At line 51 the authors introduce the term "loading": The authors should explain the meaning of this term._

TBD

_With regard to the analysis of power grid frequency time series (Sec. 3.3, Fig. 6) The criterion followed by the authors to evaluate the importance of the spectral peaks is unclear._

TBD

_Overall, the details of the power spectrum estimation procedure are not fully described: in particular, no information on windowing is provided. It is thus hard to evaluate the significance of the "peak splitting" discussed by the authors in Sec. 3.3 and concerning Fig. 6(A): could this splitting be due to spurious effects such as spectral leakage? It is worth noting that the information on windowing is instead provided in the case of the "evolutionary" spectra of Earth's orbit data._

TBD

_The claimed robustness to noise is evaluated by showing the results of the method applied to the Roessler system with 5% additive Gaussian white noise (Fig. A2). While the results indeed appear to be unchanged with respect to the noiseless case (Fig. 4), a single example is hardly sufficient to claim that the method is "robust to noise". At which signal-to-noise ratio does the method fail to provide reliable results?_

TBD

_The authors unduly use the term "powerspectrum". However, this word does not exist in English. They might consider, for example, power spectral density._

We do not agree with this criticism. "Powerspectrum" (or "power spectrum") is common term in data analysis, see, e.g., <https://mathworld.wolfram.com/PowerSpectrum.html>. Nevertheless, we have modified the term to "power spectral density".

_The abbreviation "DC" for "Dirac comb" is introduced four times (lines 27, caption of Fig. 2, beginning of Sec. 2, line 248)._

TBD

_The abbreviation "s.t." in Eq.(6) is unclear. Does it stand for "such that"? Why not using "where"?_

"s.t." means "such that" or "so that" and is frequently used in equations. Nevertheless, we have now explicetely given "such that" (which is correct, and not "where", because the following part is the condition for variable $n$).

_(lines 241-244) "This is not a drawback of the proposed method, but rather a drawback of the particular application method that we have heavily used in this article and which was the main motivation for developing the proposed method." This sentence is unclear: which "application method" are the authors referring to?_

TBD

 _Some typos:
 in page 2, Wiener-Khinchim ---> Wiener-Khinchin;_

 We corrected this typo.

 _in the Conclusion, "Wee chose LASSO..." (unless Wee is a surname)._

 We corrected this typo.

Reviewer 2
----------

_Starting a detailed assessment from the beginning, it is necessary to emphasize the comprehensive and impeccable introduction to the issue of the construction of a novel kind of power spectrum, which is the inter-spike spectrum._

TBD

_Moreover, the Authors explained the algorithm in great detail (in numerous pictures). By the way, also with outer -spike. Literature examples below review._

(I don't understand this comment)

_The illustrations of tau-recurrence rate based spectrum (Fig. 1) and the transformation diagrams of the series of Dirac delta function (Fig. 2), including the two proposed inter-spikes spectrum, deserve emphasis._

TBD

_A small remark - regarding verse 35: what will be with stochastic resonance, because we are dealing with impulse disturbances.?_

TBD

_Chapter 2 presents the signal decomposition into set of appropriate basis functions using Dirac comb. Here, too, we can distinguish a graphic representation of the decomposition procedure (Fig. 3). Nevertheless, the Authors could cite a position in the literature that discusses other methods of decomposition._

TBD

_A small note on Appendix C: It would be interesting to present an inter-spike spectra also for one of the nonlinear systems from Duffing, Mackey-Glass or Chen systems._

TBD

### 2022-10-19 Manuscript/inter_spike_manuscript_mdpi.tex
add rebuttal letter and start revision based on first comments of rev. 1

@@
 For preprints.org, the editorial staff will make this change immediately prior to posting.
-
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
-
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
-
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
@@
 
-Recurrence Plots (RPs) provide a vivid representation of complex dynamics stemming from potentially high dimensional systems \cite{marwan2007}
+The dynamics of complex systems as provided by measured time series usually show complicated and chaotic patterns.
+Quantifying their recurrence features is a powerful way to describe them and to infer information about 
+the type of dynamics, stability, regime changes, or couplings and synchronisation \cite{marwan2007,marwan2008epjst,webber2015}.
+Even more challenging are signals which do have a heavy tailed-distribution or appear as a spike-train,
+e.g., neuron firings \cite{Dummer2014,Orcioni2020}, heart beat variability \cite{marwan2002herz}, 
+or extreme flood events \cite{banerjee2021}.
+Deriving useful information from spike-train signals or inter-spike time series is an important
+topic in data analysis in many scientific fields \cite{Kajikawa2005,Dummer2014,Orcioni2020,Canale2021}.
+
+Recurrence plots (RPs) provide a vivid representation of complex dynamics $\vec{x}_i$ stemming from potentially high dimensional systems \cite{marwan2007}
 \begin{equation}\label{eq_rp_definition}
 R_{i,j}(\varepsilon) = \Theta\left(\varepsilon - D_{i,j}\right) 
-= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N].
+= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N],
 \end{equation}
-The crucial free parameter $\varepsilon$ (recurrence threshold) determines the visible structures in the RP. It can be chosen such that the recurrence rate 
+with $\mathbf{R}$ the recurrence matrix, $\vec{x}_i$ the state vector at time 
+$t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ the number of
+sampling points (or length of data series), and $d$ the dimension of the system.
+The crucial free parameter $\varepsilon$ is the recurrence threshold, determining what is a recurrences
+and, thus, the visible structures in the RP. It can be chosen such that the recurrence rate 
 $RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
@@
 changing regular (non-chaotic) dynamics, such as period-doubling bifurcations.
+
 A rather simple idea is to look at the $\tau$-recurrence rate of the RP ($\tau$-RR, Eq.~\ref{eq_tau_rr}) \cite{marwan2002pla,Zbilut2008}.
@@
 $\vec{x}_i = \vec{x}(\Delta t \cdot i),\, i=1,\ldots,N$. 
-\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
-``generalized'' powerspectrum can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 
+It represents the period length of cycles in the data (Fig.~\ref{fig_tau_rr_spectrum_example}D).
+
+\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem a 
+``generalized'' power spectral density can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived 
-powerspectrum, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
+power spectral density, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
 of $C(\tau)$: There are no assumptions for stationarity or sampling, when constructing a RP.
@@
  \textbf{A} Dirac Comb (DC) with equal amplitudes and
- \textbf{B} its FFT-based powerspectrum.
+ \textbf{B} its FFT-based power spectral density.
  \textbf{C} Proposed inter-spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
  \textbf{D} DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in \textbf{A}, and
- \textbf{E} its FFT-based powerspectrum. 
+ \textbf{E} its FFT-based power spectral density. 
  \textbf{F} Proposed inter-spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
@@
 
-In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter-spike spectrum} does not show resonance 
+In this article we propose a new way of transforming a spike-train-like signal into its frequency domain as 
+an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
+spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
 behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
@@
 \bfX_{i,j} &= \sum_{k=0}^{N}\delta\bigl(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \bigr), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-\label{eq_T_is} T_\text{is}(i)&= n, \quad s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\label{eq_T_is} T_\text{is}(i)&= n, \quad \text{such that}\quad n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
@@
 In this example, the according null hypothesis for constructing the surrogate data is that the data stems from a process which yields the same auto-correlation, 
-hence the same Fourier powerspectrum, and the same 
+hence, the same Fourier power spectral density, and the same 
 amplitude distribution. We consider the number of significant peaks in the inter-spike spectrum with
@@
 Our aim in this section is to show that the inter-spike spectrum
-of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier powerspectrum of the non-embedded eccentricity time series. We will further 
+of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier power spectral density of the non-embedded eccentricity time series.
+We will further
 show that Fourier-transforming the $\tau$-RR instead of applying the proposed inter-spike spectrum will lead to non-satisfying results, since the spiky $\tau$-RR excites a variety of harmonics in 
@@
 
-A novel type of powerspectrum, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
-combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. Wee chose LASSO or a sequentially 
+A novel type of power spectral density, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
+combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
 thresholded least squares regression STLS in this letter. Since there are 

### 2022-10-20 Manuscript/inter_spike_manuscript_mdpi.tex
abstract

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
+\abstract{In reccurance analysis, the $\tau$-recurrence rate encodes crucial information on the cycles of the underlying high-dimensional timeseries.
+It plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations, however, it is not amenable to analysis by Fourier decomposition.
+Thus there is no natural analogue to the power spectrum in recurrence analysis.
+In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an overcomplete basis of Dirac combs together with a sparsity regularization.
+We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis.
+We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying timeseries in a wide variety of examples and is robust to measurement noise.
+
+A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
 clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 

### 2022-10-20 Manuscript/inter_spike_manuscript_mdpi.tex
abstract and minor edits in the introduction

@@
 We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis.
-We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying timeseries in a wide variety of examples and is robust to measurement noise.
-
-A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
-clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
-We invent this instructive approach with the 
-idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
-along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter-spike spectrum can be interpreted as a nonlinear power 
-spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
+We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying timeseries in a wide variety of examples and is robust to measurement noise.}
+%
+%A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
+%clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
+%We invent this instructive approach with the 
+%idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
+%along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter-spike spectrum can be interpreted as a nonlinear power 
+%spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
 
@@
 
-\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem a 
-``generalized'' power spectral density can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 
+\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem, provide an analogue,
+``generalized'', power spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 
-However, there is a drawback to this approach. Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for 
+However, the interpretation of this generalized power spectral density is unclear, and it is typically hard to interpret.
+$\tau$-RR directly encodes the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
+Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
 map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g., \cite{Schild1982,Cordoba1989}, see 
-Fig.~\ref{fig_tau_rr_spectrum_example}E). Thus, it is not intuitive how to extract meaningful information about dominant frequencies of the systems' state space trajectory.
+Fig.~\ref{fig_tau_rr_spectrum_example}E). Thus, it is not intuitive how to extract meaningful information about the systems' state space trajectory.
 
-For clarification, consider the signal we would like to analyze 
+For example, consider the signal we would like to analyze 
 (e.g., the $\tau$-RR of a system) to be a Dirac comb (DC) with inter-spike period $T_\text{is}$: 
@@
 i.e., a series of Dirac delta functions for a period $T_\text{is}$. There is only one single period, $T_\text{is}$, in this signal (Fig.~\ref{fig_tau_rr_dirac_comb}A, D), so 
-in principle we would strive for a single peak in the frequency domain of this signal at a frequency $f=1/T_\text{is}$. Surprisingly the Fourier spectrum does not meet this expectation 
-and instead of a single frequency, there are exceptionally many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
+in principle we would strive for a single peak in the frequency domain of this signal at a frequency $f=1/T_\text{is}$. The Fourier spectrum does not meet this expectation 
+and instead of a single frequency, there are many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
 for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.
@@
 
-In this article we propose a new way of transforming a spike-train-like signal into its frequency domain as 
+In this article we propose a new way of decomposing a spike-train-like signal into periodic components as 
 an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
 spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
-behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
-any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
-FT. In Section \ref{sec_tau_rr_application} we exemplify the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
+behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+Section \ref{sec_tau_rr_method} explains the idea.
+Note that this approach can be used to decompose arbitrary signals, and is not specifc to $\tau$-RR.
+However, the more spiky the signal is, the more useful our new approach is compared to a
+FT. In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
 can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
@@
 
-In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
-which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$.
+When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important periodicities more clearly.
+This choice is mediated by a regression regularization parameter $\alpha$.
+Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
+Our general approach to fixing $\alpha$ is to require that we preserve most of the original siginal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
+
+%
+%In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
+%which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$.
 Obviously, there will be numerous peaks in the inter-spike spectrum of a given signal, when $\alpha$ is small,
-since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
-only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
-The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
-different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
-given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and itself.
+%since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
+%only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
+%The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
+%different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
+%given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and itself.
 
@@
 
-We exemplify the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
+We demonstrate the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
 Section \ref{sec_tau_rr_intro} on several interesting research questions. The procedure is the following:

### 2022-10-20 Manuscript/inter_spike_manuscript_mdpi.tex
abstract and minor edits in the introduction

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{In reccurance analysis, the $\tau$-recurrence rate encodes crucial information on the cycles of the underlying high-dimensional timeseries.
-It plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations, however, it is not amenable to analysis by Fourier decomposition.
-Thus there is no natural analogue to the power spectrum in recurrence analysis.
+\abstract{In reccurance analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional timeseries.
+It thus plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations.
+However, its Fourier decomposition does not have a clean interpretation.
+Thus there is no satisfactory analogue to the power spectrum in recurrence analysis.
 In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an overcomplete basis of Dirac combs together with a sparsity regularization.
-We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis.
-We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying timeseries in a wide variety of examples and is robust to measurement noise.}
+We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series.
+We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying system in a wide variety of examples and is robust to measurement noise.}
 %

### 2022-10-24 Applications/Roessler Example/compute_roessler_spike_spectra_for_different_noise_levels.jl
computed spike spectra for different noise levels in Roessler example

@@ -1,0 +1,73 @@
+import Pkg
+Pkg.activate(".")
+using InterSpikeSpectra
+using DelimitedFiles
+using DSP
+
+# load the computed data (computed in `compute_roessler_trajectories_and_tau_rr_for_different_noise_levels.m`)
+τ_rrs_1 = readdlm("./Applications/Roessler Example/computed data/tau_rr_1_all.csv")
+τ_rrs_2 = readdlm("./Applications/Roessler Example/computed data/tau_rr_2_all.csv")
+τ_rrs_3 = readdlm("./Applications/Roessler Example/computed data/tau_rr_3_all.csv")
+
+N, M = size(τ_rrs_1)
+
+# the sampling times for the different setups (limit-2, limit-3, chaos)
+dt1 = 0.1
+dt2 = 0.1
+dt3 = 0.05
+
+# compute power spectra
+perio_1_freqs = zeros(N, Int(floor(M/2)+1))
+perio_2_freqs = zeros(N, Int(floor(M/2)+1))
+perio_3_freqs = zeros(N, Int(floor(M/2)+1))
+perio_1_power = zeros(N, Int(floor(M/2)+1))
+perio_2_power = zeros(N, Int(floor(M/2)+1))
+perio_3_power = zeros(N, Int(floor(M/2)+1))
+
+for i = 1:N
+    print(i)
+    perio1 = DSP.Periodograms.periodogram(vec(τ_rrs_1[i,:]); fs = 1/dt1)
+    perio2 = DSP.Periodograms.periodogram(vec(τ_rrs_2[i,:]); fs = 1/dt2)
+    perio3 = DSP.Periodograms.periodogram(vec(τ_rrs_3[i,:]); fs = 1/dt3)
+
+    perio_1_freqs[i,:] = perio1.freq
+    perio_1_power[i,:] = perio1.power
+    perio_2_freqs[i,:] = perio2.freq
+    perio_2_power[i,:] = perio2.power
+    perio_3_freqs[i,:] = perio3.freq
+    perio_3_power[i,:] = perio3.power
+end
+
+
+# compute spike spectra for different thresholds
+thresholds = [0.9 0.95 0.99]
+spectrum1 = zeros(length(thresholds), N, Int(M/2))
+spectrum2 = zeros(length(thresholds), N, Int(M/2))
+spectrum3 = zeros(length(thresholds), N, Int(M/2))
+
+for (i, ρ) in enumerate(thresholds)
[…]

### 2022-10-25 Applications/Roessler Example/compute_roessler_spike_spectra_distances.jl
computed spectra for different noise levels corrected

@@ -1,0 +1,29 @@
+using OptimalTransport
+using Distances
+using Distributions
+using DelimitedFiles
+
+
+num_levels = 51; # number of noise levels
+sigmas = range(0, 0.5, num_levels); # noise levels
+thresholds = [0.9; 0.95; 0.99]; # regularization thresholds
+N = 500; # length of the spectra 
+# the sampling times for the different setups (limit-2, limit-3, chaos)
+dt1 = 0.1
+dt2 = 0.1
+dt3 = 0.05
+support1 = dt1:dt1:(N*dt1)
+support2 = dt2:dt2:(N*dt2)
+support3 = dt3:dt3:(N*dt3)
+
+k = 1;
+rho = thresholds[1]
+a = vec(readdlm("./Applications/Roessler Example/computed data/tauRR_spectrum1_roessler_($(rho))_$k.csv"));
+k = 2;
+b = vec(readdlm("./Applications/Roessler Example/computed data/tauRR_spectrum1_roessler_($(rho))_$k.csv"));
+
+# normalization
+a = DiscreteNonParametric(sigmas, a./sum(a))
+b = DiscreteNonParametric(sigmas, b./sum(b))
+
+dist = OptimalTransport.wasserstein(a, b)

### 2022-10-25 Applications/Roessler Example/compute_roessler_spike_spectra_for_different_noise_levels.jl

@@ -64,10 +64,10 @@ writedlm("./Applications/Roessler Example/computed data/perio_2_power.csv", peri
 writedlm("./Applications/Roessler Example/computed data/perio_3_power.csv", perio_3_power)
 
 
-for (i, ρ) in enumerate(thresholds)
+for (i, rho) in enumerate(thresholds)
     for k = 1:N
-        writedlm("./Applications/Roessler Example/computed data/tauRR_spectrum1_roessler_($ρ)_$k.csv", spectrum1[i, k, :])
-        writedlm("./Applications/Roessler Example/computed data/tauRR_spectrum2_roessler_($ρ)_$k.csv", spectrum2[i, k, :])
-        writedlm("./Applications/Roessler Example/computed data/tauRR_spectrum3_roessler_($ρ)_$k.csv", spectrum3[i, k, :])
+        writedlm("./Applications/Roessler Example/computed data/tauRR_spectrum1_roessler_$(rho)_$k.csv", spectrum1[i, k, :])
+        writedlm("./Applications/Roessler Example/computed data/tauRR_spectrum2_roessler_$(rho)_$k.csv", spectrum2[i, k, :])
+        writedlm("./Applications/Roessler Example/computed data/tauRR_spectrum3_roessler_$(rho)_$k.csv", spectrum3[i, k, :])
     end
 end

### 2022-10-25 Applications/Roessler Example/compute_roessler_spike_spectra_distances.jl
Roessler example: distances for noisy spectra

@@ -5,25 +5,57 @@ using DelimitedFiles
 
 
 num_levels = 51; # number of noise levels
-sigmas = range(0, 0.5, num_levels); # noise levels
 thresholds = [0.9; 0.95; 0.99]; # regularization thresholds
 N = 500; # length of the spectra 
 # the sampling times for the different setups (limit-2, limit-3, chaos)
 dt1 = 0.1
 dt2 = 0.1
 dt3 = 0.05
-support1 = dt1:dt1:(N*dt1)
-support2 = dt2:dt2:(N*dt2)
-support3 = dt3:dt3:(N*dt3)
+supports = [dt1:dt1:(N*dt1) dt2:dt2:(N*dt2) dt3:dt3:(N*dt3)];
 
-k = 1;
-rho = thresholds[1]
-a = vec(readdlm("./Applications/Roessler Example/computed data/tauRR_spectrum1_roessler_($(rho))_$k.csv"));
-k = 2;
-b = vec(readdlm("./Applications/Roessler Example/computed data/tauRR_spectrum1_roessler_($(rho))_$k.csv"));
+# preallocate matrix storing all distances
+dist_kl_div = zeros(length(thresholds), num_levels-1, 3)
+dist_cosine = zeros(length(thresholds), num_levels-1, 3)
+dist_hellinger = zeros(length(thresholds), num_levels-1, 3)
+dist_wasserstein = zeros(length(thresholds), num_levels-1, 3)
 
-# normalization
-a = DiscreteNonParametric(sigmas, a./sum(a))
-b = DiscreteNonParametric(sigmas, b./sum(b))
+# compute distances to noise-free spectrum
+for (i, rho) in enumerate(thresholds)
+    println("rho is $rho:")
+    for system = 1:3
+        println("system is $system:")
+        # noise-free spectrum
+        # load the computed data (computed in `compute_roessler_spike_spectra_for_different_noise_levels.jl`)
+        a = vec(readdlm("./Applications/Roessler Example/computed data/tauRR_spectrum$(system)_roessler_$(rho)_1.csv"));
+        # normalization
+        a = a./sum(a);
+        # for wasserstein distance make a distribution
+        a_ = DiscreteNonParametric(supports[:, system], a)
 
-dist = OptimalTransport.wasserstein(a, b)
+        for k = 2:num_levels
+
+            # load the computed data (computed in `compute_roessler_spike_spectra_for_different_noise_levels.jl`)
[…]

### 2022-10-25 Applications/Roessler Example/compute_roessler_spike_spectra_for_different_noise_levels.jl

@@ -49,9 +49,9 @@ for (i, ρ) in enumerate(thresholds)
     println("This is for ρ: $ρ")
     for k = 1:N  
         println(k)
-        spectrum1[i, k, :], _ = inter_spike_spectrum(vec(τ_rrs_1[i,:]); ρ_thres = ρ)
-        spectrum2[i, k, :], _ = inter_spike_spectrum(vec(τ_rrs_2[i,:]); ρ_thres = ρ)
-        spectrum3[i, k, :], _ = inter_spike_spectrum(vec(τ_rrs_3[i,:]); ρ_thres = ρ)
+        spectrum1[i, k, :], _ = inter_spike_spectrum(vec(τ_rrs_1[k,:]); ρ_thres=ρ, method=lasso(), regression_type=normal())
+        spectrum2[i, k, :], _ = inter_spike_spectrum(vec(τ_rrs_2[k,:]); ρ_thres=ρ, method=lasso(), regression_type=normal())
+        spectrum3[i, k, :], _ = inter_spike_spectrum(vec(τ_rrs_3[k,:]); ρ_thres=ρ, method=lasso(), regression_type=normal())
     end
 end
 

### 2022-10-25 Applications/Roessler Example/computed data/testing.m

@@ -1,27 +1,0 @@
-clear, clc
-
-a = load("tauRR_spectrum1_roessler_0.9_1.csv");
-b = load("tauRR_spectrum1_roessler_0.9_50.csv");
-
-subplot(211)
-plot(a)
-subplot(212)
-plot(b)
-
-
-tau_1 = load("tau_rr_1_all.csv");
-
-%%
-subplot(211)
-plot(tau_1(1,:))
-subplot(212)
-plot(tau_1(51,:))
-
-s1 = inter_spike_spectrum(tau_1(1,:), 'type', "normal", 'threshold', 0.9);
-s2 = inter_spike_spectrum(tau_1(51,:), 'type', "normal", 'threshold', 0.9);
-
-%%
-subplot(211)
-plot(s1)
-subplot(212)
-plot(s2)

### 2022-10-25 Applications/Roessler Example/plot_spike_spectra_distances_for_noisy_roessler.m

@@ -1,0 +1,122 @@
+% We plot the distances of all noisy spectra with respect to the noise free
+% case for all three considered systems (limit-2, limit-3, chaos). We
+% considered 50 different noise levels ranging from 1%-50% additive noise.
+
+% The noisy time series along with their recurrence plots and their
+% tau-recurrence rate have been computed in 
+% `compute_roessler_trajectories_and_tau_rr_for_different_noise_levels.m`
+
+% The corresponding inter spike spectra, using three different
+% regularization thresholds of 0.9, 0.95 and 0.99 have been computed in 
+% `compute_roessler_spike_spectra_distances.jl`. We used a normal lasso
+% regression.
+
+% The distances of all noisy spectra compared to the noise-free spectrum
+% have been computed in `compute_roessler_spike_spectra_distances.jl`
+
+clear, clc
+
+num_levels = 50; % number of noise levels (excluding 0)
+sigmas = linspace(0.01,0.5,num_levels).*100; % noise levels
+
+fs = 25; % fontsize for plotting
+lw = 2.5; % linewidth for plotting
+sz = 40; % scatter size
+% the different considered systems
+systems = ["Rössler system (a = 0.36)", "Rössler system (a = 0.41)", "Rössler system (a = 0.428)"];
+
+%% Cosine distance
+
+for i = 1:3
+    dist1 = load(strcat("./computed data/dist_cosine_rho_0.9_system_", num2str(i), ".csv"));
+    dist2 = load(strcat("./computed data/dist_cosine_rho_0.95_system_", num2str(i), ".csv"));
+    dist3 = load(strcat("./computed data/dist_cosine_rho_0.99_system_", num2str(i), ".csv"));
+    
+    figure('Units', 'normalized', 'Position', [.2 .2 .6 .6])
+    p1 = plot(sigmas, dist1, 'LineWidth', lw, 'LineStyle', '-'); hold on
+    scatter(sigmas, dist1, sz, p1.Color, 'filled'), hold on
+    p2 = plot(sigmas, dist2, 'LineWidth', lw, 'LineStyle', '-'); hold on
+    scatter(sigmas, dist2, sz, p2.Color, 'filled'), hold on
[…]

### 2022-10-26 Applications/Roessler Example/plot_spike_spectra_distances_for_noisy_roessler.m
Roessler example: Plot distances of spectra for different noise levels

@@ -19,20 +19,20 @@ clear, clc
 num_levels = 50; % number of noise levels (excluding 0)
 sigmas = linspace(0.01,0.5,num_levels).*100; % noise levels
 
-fs = 25; % fontsize for plotting
+fs = 20; % fontsize for plotting
 lw = 2.5; % linewidth for plotting
 sz = 40; % scatter size
 % the different considered systems
 systems = ["Rössler system (a = 0.36)", "Rössler system (a = 0.41)", "Rössler system (a = 0.428)"];
 
 %% Cosine distance
-
+figure('Units', 'normalized', 'Position', [.001 .2 .999 .6])
 for i = 1:3
     dist1 = load(strcat("./computed data/dist_cosine_rho_0.9_system_", num2str(i), ".csv"));
     dist2 = load(strcat("./computed data/dist_cosine_rho_0.95_system_", num2str(i), ".csv"));
     dist3 = load(strcat("./computed data/dist_cosine_rho_0.99_system_", num2str(i), ".csv"));
     
-    figure('Units', 'normalized', 'Position', [.2 .2 .6 .6])
+    subplot(1,3,i)
     p1 = plot(sigmas, dist1, 'LineWidth', lw, 'LineStyle', '-'); hold on
     scatter(sigmas, dist1, sz, p1.Color, 'filled'), hold on
     p2 = plot(sigmas, dist2, 'LineWidth', lw, 'LineStyle', '-'); hold on
@@ -46,17 +46,19 @@ for i = 1:3
     legend('Location','northwest')
     grid on
     set(gca, 'LineWidth', 2, 'FontSize', fs)
-    ylim([0 0.6])
+    ylim([0 0.8])
+    xlim([0 50])
 end
 
 %% KL Divergence
 
+figure('Units', 'normalized', 'Position', [.001 .2 .999 .6])
 for i = 1:3
     dist1 = load(strcat("./computed data/dist_kl_div_rho_0.9_system_", num2str(i), ".csv"));
     dist2 = load(strcat("./computed data/dist_kl_div_rho_0.95_system_", num2str(i), ".csv"));
     dist3 = load(strcat("./computed data/dist_kl_div_rho_0.99_system_", num2str(i), ".csv"));
     
-    figure('Units', 'normalized', 'Position', [.2 .2 .6 .6])
+    subplot(1,3,i)
[…]

### 2022-10-26 Manuscript/1st resubmission/rebuttal.md
Rebuttal: One more comment of reviewer 2 answered

--- 2022-10-19 Manuscript/rebuttal.md
@@
 
-TBD
+We have extended the introduction and hope it is now more clear.
 
@@
 (I don't understand this comment)
+
+We have added some further references on spike-train analysis and, in particular, on spike-train power spectra. Thanks for the literature suggestions, which were really helpful!
 
@@
 
-TBD
+We thank the reviewer for this suggestion.
+In fact, we were computing numerous inter-spike spectra for different systems.
+But regarding the manuscript, we decided to present a variety of possible applications, which includes the analysis of exemplary nonlinear system (like the Roessler we showed or systems you suggest) as well as "real-world" data (power grid frequency data) and data stemming from a geophysical context (orbital data).
+Each of these applications could, of course, be expanded or other applications could be shown, but here we must concentrate on presenting the method itself as concisely as possible while keeping the size of the manuscript within tolerable limits.
+Moreover, when analyzing a nonlinear system we would potentially be interested in different dynamical setups, which would, in turn, lead to a variety of aspects we would additionally need to consider and cover with the proposed method.
+The idea of this paper is to outline the proposed method and provide the code/package for its use.
+We would certainly be pleased if researchers decided to publish a thorough study of a number of different nonlinear systems using this method.

### 2022-10-27 Manuscript/1st resubmission/rebuttal.md
More refs for answering reviewer 2 comments

@@
 
-In deed, out intention was to have a short but clear introduction into the recurrence plot method, which reviewer 2 obviously liked very much.
+Indeed, out intention was to have a short but clear introduction into the recurrence plot method, which reviewer 2 obviously liked very much.
 Nevertheless, we have now added an explanation on the recurrence plot definition.
@@
 
-(I don't understand this comment)
-
 We have added some further references on spike-train analysis and, in particular, on spike-train power spectra. Thanks for the literature suggestions, which were really helpful!
@@
 1) and the transformation diagrams of the series of Dirac delta function (Fig.
-2), including the two proposed inter-spikes spectrum, deserve emphasis._
-
-TBD
-
-_A small remark - regarding verse 35: what will be with stochastic resonance, because we are dealing with impulse disturbances.?_
+2), including the two proposed inter-spikes spectrum, deserve emphasis.
+A small remark - regarding verse 35: what will be with stochastic resonance, because we are dealing with impulse disturbances.?_
 

### 2022-10-27 Manuscript/inter_spike_manuscript_mdpi.tex
More refs for answering reviewer 2 comments

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{In reccurance analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional timeseries.
+\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional time series.
 It thus plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations.
@@
 Thus there is no satisfactory analogue to the power spectrum in recurrence analysis.
-In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an overcomplete basis of Dirac combs together with a sparsity regularization.
+In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
 We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series.
@@
 and instead of a single frequency, there are many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
-for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.
+for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.\footnote{This can also 
+be observed for neuron spike trains, e.g. \cite{Orcioni2020,Biagetti2017}.}
 

### 2022-10-31 Manuscript/inter_spike_manuscript_mdpi.tex
Reviewer2 more refs on other decomposition techniques

@@
 and instead of a single frequency, there are many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
-for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.\footnote{This can also 
+for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$ \cite{Norden1998}.\footnote{This can also 
 be observed for neuron spike trains, e.g. \cite{Orcioni2020,Biagetti2017}.}
@@
 Section \ref{sec_tau_rr_method} explains the idea.
-Note that this approach can be used to decompose arbitrary signals, and is not specifc to $\tau$-RR.
+Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
 However, the more spiky the signal is, the more useful our new approach is compared to a
@@
 
-The signal, which we would like to transform is decomposed into a set of appropriate basis functions.\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
-such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} Instead of using trigonometric 
-functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
+The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
+such time series are often spiky, which favors the proposed decomposition technique.
+But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions.
+The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree. 
+A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
+trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
+eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
+or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
+
+Here we propose to use Dirac combs (DC) with 
 different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 

### 2022-11-01 Manuscript/inter_spike_manuscript_mdpi.tex
More questions answered of Reviewer 1 and 2. Mehrnaz' comments incorporated

@@
 \citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem, provide an analogue,
-``generalized'', power spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
+``generalized'', spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 \end{equation}
-can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived 
-power spectral density, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
+can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived spectral density, 
+i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
 of $C(\tau)$: There are no assumptions for stationarity or sampling, when constructing a RP.
-Furthermore, the correlation structures of higher dimensional spaces can be resolved in the recurrence-derived Fourier-spectrum.\\
+Furthermore, since an RP can represent high-dimensional dynamics and its $\tau$-RR serves as a plug-in for $C(\tau)$, the correlation structures of higher dimensional spaces can be read from 
+the recurrence-derived Fourier-spectrum.\\
 
@@
 spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
-behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+behavior of the signal's inherent inter-spike frequencies in such a way that harmonics of these frequencies are also excited (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
 Section \ref{sec_tau_rr_method} explains the idea.
@@
 Here we propose to use Dirac combs (DC) with 
-different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
+different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the min-max-normalized signal we want to transform of length $N$ and 
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
@@
 functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
-(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$.
-Finally, we group loadings
+(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Any other 
+sparse regression technique could be used. Finally, we group loadings 
 which correspond to basis functions having the same period 
@@
 Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
-Our general approach to fixing $\alpha$ is to require that we preserve most of the original siginal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
+Our general approach to fixing $\alpha$ is to require that we preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
+The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization given by a
+selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
+We will discuss this in more detail in Section 4. Section \ref{sec_tau_rr_discussion}.
 
@@
  \caption{\textbf{A} Evolutionary Fourier power spectra of eccentricity time series. \textbf{B} Inter-spike spectrogram of the $\tau$-recurrence rate of the eccentricity time 
- series and \textit{C} its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
+ series and \textbf{C} its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
  For comparability, in all cases the spectra aligned in the columns of the shown plots are normalized to probabilities (sum of unity for 
@@
 period-doubling bifurcations. However, we have to admit this way the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 
-This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike power spectra for period-2, period-3, and chaotic dynamics.
+This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike spectra for period-2, period-3, and chaotic dynamics.
 Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter-spike spectra of power grid 
@@
 
-A novel type of power spectral density, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
+A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
 combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
@@
 of the period (or frequency) the inter-spike spectrum is obtained. 
-Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
+Although this novel spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
 be considered 

### 2022-11-02 Manuscript/inter_spike_manuscript_mdpi.tex
Roessler example: Added figures for noise analysis

@@
 $\tau$-RRs (Fig.~\ref{fig_tau_rr_example_roessler}G, H, I). The proposed idea is also 
-robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. While the peak shape does 
-change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all.
+robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. 
+Figure \ref{fig_roessler_peaks} illustrates that 
+while the peak shape does change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all 
+(see Fig.~\ref{fig_roessler_spectra_distances} in the Appendix for further analysis).
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_different_noise_levels_peaks}
+ \caption{Peak positions of the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
+ \textbf{A} period-2 limit-cycle, \textbf{B} period-3 limit-cycle and \textbf{C} chaos.
+The size of the plotted markers scale with the detected peak height.
+The noise-free spectra are shown in Fig.~\ref{fig_tau_rr_example_roessler}J, K, L and
+ an example of these spectra with 5\% additive noise is shown in Fig.~\ref{fig_tau_rr_example_roessler_noise}J, K, L. Spectra were obtained with a LASSO regression and a regularization threshold 
+  corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals.}
+\label{fig_roessler_peaks}
+\end{figure}
 
@@
 All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
-and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
+and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018}, \textit{DifferentialEquations.jl} \cite{rackauckas2017}, \textit{Distances.jl} and 
+\textit{OptimalTransport.jl} \cite{Zhang2022}.
 }
@@
 
+\begin{figure}[h!]
+ \centering
+ \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_spectra_distances}
+ \caption{Wasserstein distances for the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
+ \textbf{A} period-2 limit-cycle, \textbf{B} period-3 limit-cycle and \textbf{C} chaos. For each noise level the obtained spectrum is compared to the noise-free spectrum (these are shown 
+ in Fig.~\ref{fig_tau_rr_example_roessler}J, K, L for a regularization threshold corresponding to $\rho=0.95$) by computing its Wasserstein distance. Inter-spike spectra were obtained with a 
+ LASSO regression and three different regularization thresholds corresponding to $\rho=0.9$ (blue), $\rho=0.95$ (orange) and $\rho=0.99$ (green) accordance of $\tau$-RRs and re-composed signals. 
+ Up to a noise level of 20\% the distances are small and rather constant. The fluctuations depend on the chosen regularization threshold as well as on the underlying dynamics.}
+\label{fig_roessler_spectra_distances}
+\end{figure}
+
 \section{Regularizationparameters for different sparse regression techniques}\label{sec_regularization_appendix}

### 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
Rebuttal: More questions of reviewer 1 answered

@@
 The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
-A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
+The weights (also called modes) corresponding to the individual basis functions can also
+be called \textit{loadings} and must be determined. A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
 trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
@@
 Third, when adopting our idea of applying the inter-spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters.  
-This is not a drawback of the proposed method, but rather a drawback of the particular application method that we have heavily used in this article and which was the main motivation for developing 
-the proposed method.
+This is not a drawback of the proposed decomposition method, but rather a drawback of applying this technique to the $\tau$-recurrence rate of the system, which was the main motivation for 
+developing the proposed method.
 As a very last remark, we draw attention to the fact that sparse regression can be transformed into sparse logistic regression when the signal we would like to transform is binary.

### 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
edits by frank

--- 2022-11-01 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional time series.
-It thus plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations.
-However, its Fourier decomposition does not have a clean interpretation.
-Thus there is no satisfactory analogue to the power spectrum in recurrence analysis.
-In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
+\abstract{In reccurance analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high dimensional time series.
+It thus plays a similar role to the autocorrelation for scalar time series in encoding temporal correlations.
+Unlike the autocorrelation however, its Fourier decomposition does not have a natural interpretation.
+Thus there is no direct analogue to the power spectrum in recurrence analysis.
+In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an overcomplete basis of Dirac combs together with a sparsity regularization.
 We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series.
@@
 \end{equation}
-with $\mathbf{R}$ the recurrence matrix, $\vec{x}_i$ the state vector at time 
+with $\mathbf{R}$ the recurrence matrix, satisfactory$\vec{x}_i$ the state vector at time 
 $t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ the number of
@@
 
-\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem, provide an analogue,
-``generalized'', spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
+\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ for a scalar time series.
+However, as there is no equivalent of the Wiener-Khinchin theorem its Fourier Transform (FT) only provides a ``generalized'' kind of power spectral density.
+There are clear advantages to such a recurrence-derived
+power spectral density, the (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E): There are no assumptions for stationarity or sampling, when constructing a RP, and the approch directly applies to higher-dimensional timeseries for which the auto-correlation is a matrix.\\
+
+\textbf{Please check the above paragraph for correctness, I did not understand the following and would drop it (or explain the point better):}
+\textit{This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 \end{equation}
-can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived spectral density, 
-i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
-of $C(\tau)$: There are no assumptions for stationarity or sampling, when constructing a RP.
-Furthermore, since an RP can represent high-dimensional dynamics and its $\tau$-RR serves as a plug-in for $C(\tau)$, the correlation structures of higher dimensional spaces can be read from 
-the recurrence-derived Fourier-spectrum.\\
+can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR.}
 
@@
 
-However, the interpretation of this generalized power spectral density is unclear, and it is typically hard to interpret.
-$\tau$-RR directly encodes the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
-Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
+However, the exact meaning of this generalized power spectral density is unclear, and it is typically hard to interpret.
+$\tau$-RR spikes already directly encode the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
+\textbf{In particular it does not imply anything about the power associated to certain frequencies in the underlying timeseries.} Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
 map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g., \cite{Schild1982,Cordoba1989}, see 
@@
 and instead of a single frequency, there are many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
-for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$ \cite{Norden1998}.\footnote{This can also 
-be observed for neuron spike trains, e.g. \cite{Orcioni2020,Biagetti2017}.}
+for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.
 
@@
 an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
-spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
-behavior of the signal's inherent inter-spike frequencies in such a way that harmonics of these frequencies are also excited (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
-Section \ref{sec_tau_rr_method} explains the idea.
-Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
-However, the more spiky the signal is, the more useful our new approach is compared to a
-FT. In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
+spectra \cite{Dummer2014}.
+We instead investigate decomposing the $\tau$-RR in an overcomplete basis of spike trains using a sparsity regularization.
+Section \ref{sec_tau_rr_method} introduces the approach in detail.
+Our novel \textit{inter-spike spectrum} does not show resonance
+behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+Note that this approach can be used to decompose arbitrary signals, and is not specifc to $\tau$-RR.
+The more spiky the signal is, the more useful our new decomposition can potentially be.
+In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study.
+In this case, the inter-spike spectrum
 can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
@@
 
-The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
-such time series are often spiky, which favors the proposed decomposition technique.
-But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions.
-The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree. 
-A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
-trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
-eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
-or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
-
-Here we propose to use Dirac combs (DC) with 
-different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the min-max-normalized signal we want to transform of length $N$ and 
+The signal, which we would like to transform is decomposed into a set of appropriate basis functions. Instead of using trigonometric 
+functions as in the FT we use Dirac combs (DC) with 
+different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
@@
 functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
-(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Any other 
-sparse regression technique could be used. Finally, we group loadings 
+(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$.
+Finally, we group loadings
 which correspond to basis functions having the same period 
@@
 
-When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important periodicities more clearly.
-This choice is mediated by a regression regularization parameter $\alpha$.
+When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important spikes, and thus the most important periodicities more clearly.
+This choice is parametrized by a regression regularization parameter $\alpha$.
 Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
-Our general approach to fixing $\alpha$ is to require that we preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
-The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization given by a
-selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
-We will discuss this in more detail in Section 4. Section \ref{sec_tau_rr_discussion}.
+Our general approach to fixing $\alpha$ is to require that we preserve most of the original siginal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
 
@@
 
-We demonstrate the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
+We demonstrate the use of the inter-spike spectrum of the $\tau$-RR as outlined in 
 Section \ref{sec_tau_rr_intro} on several interesting research questions. The procedure is the following:
@@
  \caption{\textbf{A} Evolutionary Fourier power spectra of eccentricity time series. \textbf{B} Inter-spike spectrogram of the $\tau$-recurrence rate of the eccentricity time 
- series and \textbf{C} its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
+ series and \textit{C} its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
  For comparability, in all cases the spectra aligned in the columns of the shown plots are normalized to probabilities (sum of unity for 
@@
 period-doubling bifurcations. However, we have to admit this way the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 
-This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike spectra for period-2, period-3, and chaotic dynamics.
+This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike power spectra for period-2, period-3, and chaotic dynamics.
 Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter-spike spectra of power grid 
-frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis. And last but not least, we showed that our approach 
+frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis even for scalar time series.
+And last but not least, we showed that our approach
 really incorporates frequencies, which are apparent in the Fourier spectrum of the signal, by applying it to analytically derived eccentricity data, where the dominant frequencies are well 
@@
 
-A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
+A novel type of power spectral density, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
 combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
@@
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter-spike spectrum is obtained. 
-Although this novel spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
-be considered 
-as an additional source of information but not as a substitute for ordinary Fourier analysis. 
+of the period (or frequency) the inter-spike spectrum is obtained. This provides information that is complementary to the Fourier decompostion of the system.
+
 Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
@@
 
-The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RRs) into their frequency domain. 
+Applied to the $\ŧau$-RR this novel spectrum directly reveals the peridocities of the underlying system, also in cases where there is no direct analogue of the power spectrum.
 This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
-The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, and the inter-spike spectrum can reliably reveal the system's dominant frequencies, 
+The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, the spikes encode the systems periods, and the inter-spike spectrum can reliably reveal the system's dominant frequencies,
 which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
@@
 We could think of a broad range of applications of the proposed idea. The inter-spike spectrum itself can serve as a valuable tool for the analysis of any sort of 
-spike-train-like data. On the other hand, the inter-spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
+spike-train-like data. On the other hand, the inter-spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for high dimensional complex systems. 
 When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021,Kraemer2022} show that 

### 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex

@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{In reccurance analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high dimensional time series.
+
+\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high dimensional time series.
 It thus plays a similar role to the autocorrelation for scalar time series in encoding temporal correlations.
@@
 Thus there is no direct analogue to the power spectrum in recurrence analysis.
-In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an overcomplete basis of Dirac combs together with a sparsity regularization.
+In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
 We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series.
 We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying system in a wide variety of examples and is robust to measurement noise.}
+
 %
@@
 However, as there is no equivalent of the Wiener-Khinchin theorem its Fourier Transform (FT) only provides a ``generalized'' kind of power spectral density.
-There are clear advantages to such a recurrence-derived
-power spectral density, the (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E): There are no assumptions for stationarity or sampling, when constructing a RP, and the approch directly applies to higher-dimensional timeseries for which the auto-correlation is a matrix.\\
+There are clear advantages to such a recurrence-derived power spectral density, the (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E):
+There are no assumptions for stationarity or sampling, when constructing a RP, 
+and since an RP can represent high dimensional dynamics the approch directly applies to higher dimensional systems for which the auto-correlation is a matrix and no single power spectrum captures the recurrences.\\
 
@@
 and instead of a single frequency, there are many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
-for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.
+for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$ \cite{Norden1998}.\footnote{This can also 
+be observed for neuron spike trains, e.g. \cite{Orcioni2020,Biagetti2017}.}
 
@@
 behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
-Note that this approach can be used to decompose arbitrary signals, and is not specifc to $\tau$-RR.
+Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
 The more spiky the signal is, the more useful our new decomposition can potentially be.
@@
 
-The signal, which we would like to transform is decomposed into a set of appropriate basis functions. Instead of using trigonometric 
-functions as in the FT we use Dirac combs (DC) with 
-different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
+To obtain the Inter-Spike Spectrum , the signal, which we would like to analyze, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
+The general idea common to many methods is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
+The weights (in some contexts also called modes or loadings) corresponding to the individual basis functions must be determined.
+A number of decomposition techniques based on different sets of basis functions exist, e.g., 
+trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
+eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
+or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
+These methods typically share the property that the basis functions form a complete basis,
+the set of basis functions is linearly independent, and thus the weights are uniquely determined.
+
+Here we propose to use Dirac combs (DC) with 
+different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the min-max-normalized signal we want to transform of length $N$ and 
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
@@
 \end{equation}  
-has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
+has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the weights we are interested in. Along a variety of algorithms which can solve this problem, we are 
 particularly interested in those solutions, which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\vec{s}$ into a minimal number of basis 
 functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
-(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$.
-Finally, we group loadings
+(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Any other 
+sparse regression technique could be used. Finally, we group weights 
 which correspond to basis functions having the same period 
@@
 
-When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important spikes, and thus the most important periodicities more clearly.
+When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most prominent spikes, and thus the most important periodicities more clearly.
 This choice is parametrized by a regression regularization parameter $\alpha$.
 Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
-Our general approach to fixing $\alpha$ is to require that we preserve most of the original siginal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
+Our general approach to fixing $\alpha$ is to require that we preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
+The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization given by a
+selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
+We will discuss this in more detail in Section 4. Section \ref{sec_tau_rr_discussion}.
 
@@
 %since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
-%only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
+%only a sparse number of non-zero weights in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
 %The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
@@
 
-A novel type of power spectral density, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
+A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
 combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
 thresholded least squares regression STLS in this letter. Since there are 
-$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter-spike spectrum is obtained. This provides information that is complementary to the Fourier decompostion of the system.
+$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed weights as a function 
+of the period (or frequency) the inter-spike spectrum is obtained. This provides information that is complementary to the Fourier decompostion of the signal.
 

### 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
Merged and minor typos, and rebuttal

@@
 
-Applied to the $\ŧau$-RR this novel spectrum directly reveals the peridocities of the underlying system, also in cases where there is no direct analogue of the power spectrum.
+Applied to the $\tau$-RR this novel spectrum directly reveals the peridocities of the underlying system, also in cases where there is no direct analogue of the power spectrum.
 This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
typo
Last updates for the resubmission

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-
-\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high dimensional time series.
-It thus plays a similar role to the autocorrelation for scalar time series in encoding temporal correlations.
-Unlike the autocorrelation however, its Fourier decomposition does not have a natural interpretation.
-Thus there is no direct analogue to the power spectrum in recurrence analysis.
+\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional time series.
+It thus plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations.
+However, its Fourier decomposition does not have a clean interpretation.
+Thus there is no satisfactory analogue to the power spectrum in recurrence analysis.
 In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
@@
 We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying system in a wide variety of examples and is robust to measurement noise.}
-
 %
@@
 \end{equation}
-with $\mathbf{R}$ the recurrence matrix, satisfactory$\vec{x}_i$ the state vector at time 
+with $\mathbf{R}$ the recurrence matrix, $\vec{x}_i$ the state vector at time 
 $t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ the number of
@@
 
-\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ for a scalar time series.
-However, as there is no equivalent of the Wiener-Khinchin theorem its Fourier Transform (FT) only provides a ``generalized'' kind of power spectral density.
-There are clear advantages to such a recurrence-derived power spectral density, the (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E):
-There are no assumptions for stationarity or sampling, when constructing a RP, 
-and since an RP can represent high dimensional dynamics the approch directly applies to higher dimensional systems for which the auto-correlation is a matrix and no single power spectrum captures the recurrences.\\
-
-\textbf{Please check the above paragraph for correctness, I did not understand the following and would drop it (or explain the point better):}
-\textit{This is reasonable, since the average distances for a given lag $\tau$ 
+\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem, provide an analogue,
+``generalized'', spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 \end{equation}
-can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR.}
+can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived spectral density, 
+i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
+of $C(\tau)$: There are no assumptions for stationarity or sampling, when constructing a RP.
+Furthermore, since an RP can represent high-dimensional dynamics and its $\tau$-RR serves as a plug-in for $C(\tau)$, the correlation structures of higher dimensional spaces can be read from 
+the recurrence-derived Fourier-spectrum.\\
 
@@
 
-However, the exact meaning of this generalized power spectral density is unclear, and it is typically hard to interpret.
-$\tau$-RR spikes already directly encode the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
-\textbf{In particular it does not imply anything about the power associated to certain frequencies in the underlying timeseries.} Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
+However, the interpretation of this generalized power spectral density is unclear, and it is typically hard to interpret.
+$\tau$-RR directly encodes the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
+Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
 map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g., \cite{Schild1982,Cordoba1989}, see 
@@
 an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
-spectra \cite{Dummer2014}.
-We instead investigate decomposing the $\tau$-RR in an overcomplete basis of spike trains using a sparsity regularization.
-Section \ref{sec_tau_rr_method} introduces the approach in detail.
-Our novel \textit{inter-spike spectrum} does not show resonance
-behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
+behavior of the signal's inherent inter-spike frequencies in such a way that harmonics of these frequencies are also excited (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+Section \ref{sec_tau_rr_method} explains the idea.
 Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
-The more spiky the signal is, the more useful our new decomposition can potentially be.
-In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study.
-In this case, the inter-spike spectrum
+However, the more spiky the signal is, the more useful our new approach is compared to a
+FT. In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
 can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
@@
 
-To obtain the Inter-Spike Spectrum , the signal, which we would like to analyze, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
-The general idea common to many methods is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
-The weights (in some contexts also called modes or loadings) corresponding to the individual basis functions must be determined.
-A number of decomposition techniques based on different sets of basis functions exist, e.g., 
+The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
+such time series are often spiky, which favors the proposed decomposition technique.
+But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions.
+The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
+The weights (also called modes) corresponding to the individual basis functions can also
+be called \textit{loadings} and must be determined. A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
 trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
@@
 or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
-These methods typically share the property that the basis functions form a complete basis,
-the set of basis functions is linearly independent, and thus the weights are uniquely determined.
 
@@
 \end{equation}  
-has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the weights we are interested in. Along a variety of algorithms which can solve this problem, we are 
+has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
 particularly interested in those solutions, which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\vec{s}$ into a minimal number of basis 
@@
 (LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Any other 
-sparse regression technique could be used. Finally, we group weights 
+sparse regression technique could be used. Finally, we group loadings 
 which correspond to basis functions having the same period 
@@
 
-When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most prominent spikes, and thus the most important periodicities more clearly.
-This choice is parametrized by a regression regularization parameter $\alpha$.
+The proposed decomposition does not show a leakage effect by construction.
+However, when introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important periodicities more clearly.
+This choice is mediated by a regression regularization parameter $\alpha$.
 Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
@@
 %since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
-%only a sparse number of non-zero weights in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
+%only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
 %The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
@@
 
-We demonstrate the use of the inter-spike spectrum of the $\tau$-RR as outlined in 
+We demonstrate the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
 Section \ref{sec_tau_rr_intro} on several interesting research questions. The procedure is the following:
@@
 
-The Fourier frequency spectra for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min} 
-(for technical details on the calculation of 
+The Fourier frequency spectra for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min}, which may partly 
+be explained by the leakage effect (for technical details on the calculation of 
 the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Especially the $30$ and $60$ \si{min} 
@@
 In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Fig.~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
-at $30$ and $60$ \si{min}. In front of these peaks, smaller local peaks can be seen, which correspond to the local peaks of the Fourier power spectra at $28$ and $55$ \si{min}, respectively.
+at $30$ and $60$ \si{min} (there is no leakage effect due to the proposed decomposition technique). 
+In front of these peaks, smaller local peaks can be seen, which correspond to the local peaks of the Fourier power spectra at $28$ and $55$ \si{min}, respectively.
 Moreover, there is an additional peak at 
@@
 Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter-spike spectra of power grid 
-frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis even for scalar time series.
-And last but not least, we showed that our approach
+frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis. And last but not least, we showed that our approach 
 really incorporates frequencies, which are apparent in the Fourier spectrum of the signal, by applying it to analytically derived eccentricity data, where the dominant frequencies are well 
@@
 thresholded least squares regression STLS in this letter. Since there are 
-$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed weights as a function 
-of the period (or frequency) the inter-spike spectrum is obtained. This provides information that is complementary to the Fourier decompostion of the signal.
-
+$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
+of the period (or frequency) the inter-spike spectrum is obtained. A disadvantage is that the transformation is not invertible. An advantage is that there is no leakage effect.
+Although this novel spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
+be considered 
+as an additional source of information but not as a substitute for ordinary Fourier analysis. 
 Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
@@
 
-Applied to the $\tau$-RR this novel spectrum directly reveals the peridocities of the underlying system, also in cases where there is no direct analogue of the power spectrum.
+The invention of the proposed method has been motivated by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RRs) into their frequency domain. 
 This general idea \cite{Zbilut2008} allows for a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
-The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, the spikes encode the systems periods, and the inter-spike spectrum can reliably reveal the system's dominant frequencies,
+The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, and the inter-spike spectrum can reliably reveal the system's dominant frequencies, 
 which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
@@
 We could think of a broad range of applications of the proposed idea. The inter-spike spectrum itself can serve as a valuable tool for the analysis of any sort of 
-spike-train-like data. On the other hand, the inter-spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for high dimensional complex systems. 
+spike-train-like data. On the other hand, the inter-spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
 When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021,Kraemer2022} show that 
@@
 
+\begin{figure}
+ \centering
+ \includegraphics[width=\textwidth]{./figures/fig_power_grid_fft_full}
+ \caption{Fourier spectra of the frequency entire time series from \textbf{A} Central Europe (CE), $N_{\text{CE}}=587,520$ and \textbf{B} Great Britain (GB), $N_{\text{GB}}=1,581,120$.
+A subset of the underlying time series is shown in Fig.~\ref{fig_power_grid_time_series}.}
+\label{fig_power_grid_fft_full}
+\end{figure}
+
 \clearpage

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.old.tex
revision

--- 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 For preprints.org, the editorial staff will make this change immediately prior to posting.
+
+%--------------------
+% Class Options:
+%--------------------
+%----------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
+
+%---------
+% article
+%---------
+% The default type of manuscript is "article", but can be replaced by: 
+% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
+% supfile = supplementary materials
+
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional time series.
-It thus plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations.
-However, its Fourier decomposition does not have a clean interpretation.
-Thus there is no satisfactory analogue to the power spectrum in recurrence analysis.
-In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
-We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series.
-We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying system in a wide variety of examples and is robust to measurement noise.}
-%
-%A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
-%clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
-%We invent this instructive approach with the 
-%idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
-%along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter-spike spectrum can be interpreted as a nonlinear power 
-%spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
+\abstract{A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
+clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
+We invent this instructive approach with the 
+idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
+along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter-spike spectrum can be interpreted as a nonlinear power 
+spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
 
@@
 
-The dynamics of complex systems as provided by measured time series usually show complicated and chaotic patterns.
-Quantifying their recurrence features is a powerful way to describe them and to infer information about 
-the type of dynamics, stability, regime changes, or couplings and synchronisation \cite{marwan2007,marwan2008epjst,webber2015}.
-Even more challenging are signals which do have a heavy tailed-distribution or appear as a spike-train,
-e.g., neuron firings \cite{Dummer2014,Orcioni2020}, heart beat variability \cite{marwan2002herz}, 
-or extreme flood events \cite{banerjee2021}.
-Deriving useful information from spike-train signals or inter-spike time series is an important
-topic in data analysis in many scientific fields \cite{Kajikawa2005,Dummer2014,Orcioni2020,Canale2021}.
-
-Recurrence plots (RPs) provide a vivid representation of complex dynamics $\vec{x}_i$ stemming from potentially high dimensional systems \cite{marwan2007}
+Recurrence Plots (RPs) provide a vivid representation of complex dynamics stemming from potentially high dimensional systems \cite{marwan2007}
 \begin{equation}\label{eq_rp_definition}
 R_{i,j}(\varepsilon) = \Theta\left(\varepsilon - D_{i,j}\right) 
-= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N],
+= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N].
 \end{equation}
-with $\mathbf{R}$ the recurrence matrix, $\vec{x}_i$ the state vector at time 
-$t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ the number of
-sampling points (or length of data series), and $d$ the dimension of the system.
-The crucial free parameter $\varepsilon$ is the recurrence threshold, determining what is a recurrences
-and, thus, the visible structures in the RP. It can be chosen such that the recurrence rate 
+The crucial free parameter $\varepsilon$ (recurrence threshold) determines the visible structures in the RP. It can be chosen such that the recurrence rate 
 $RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
@@
 changing regular (non-chaotic) dynamics, such as period-doubling bifurcations.
-
 A rather simple idea is to look at the $\tau$-recurrence rate of the RP ($\tau$-RR, Eq.~\ref{eq_tau_rr}) \cite{marwan2002pla,Zbilut2008}.
@@
 $\vec{x}_i = \vec{x}(\Delta t \cdot i),\, i=1,\ldots,N$. 
-It represents the period length of cycles in the data (Fig.~\ref{fig_tau_rr_spectrum_example}D).
-
-\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem, provide an analogue,
-``generalized'', spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
+\citet{Zbilut2008} pointed out that $\tau$-RR could be used as a plugin value for the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchim theorem a 
+``generalized'' powerspectrum can be obtained. This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 \end{equation}
-can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived spectral density, 
-i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
+can be directly read from the distance matrix $\mathbf{D}$ and is also preserved in its thresholded version $\tau$-RR. There are clear advantages for a recurrence-derived 
+powerspectrum, i.e., Fourier transforming (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E), instead 
 of $C(\tau)$: There are no assumptions for stationarity or sampling, when constructing a RP.
-Furthermore, since an RP can represent high-dimensional dynamics and its $\tau$-RR serves as a plug-in for $C(\tau)$, the correlation structures of higher dimensional spaces can be read from 
-the recurrence-derived Fourier-spectrum.\\
+Furthermore, the correlation structures of higher dimensional spaces can be resolved in the recurrence-derived Fourier-spectrum.\\
 
@@
 
-However, the interpretation of this generalized power spectral density is unclear, and it is typically hard to interpret.
-$\tau$-RR directly encodes the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
-Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
+However, there is a drawback to this approach. Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for 
 map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g., \cite{Schild1982,Cordoba1989}, see 
-Fig.~\ref{fig_tau_rr_spectrum_example}E). Thus, it is not intuitive how to extract meaningful information about the systems' state space trajectory.
+Fig.~\ref{fig_tau_rr_spectrum_example}E). Thus, it is not intuitive how to extract meaningful information about dominant frequencies of the systems' state space trajectory.
 
-For example, consider the signal we would like to analyze 
+For clarification, consider the signal we would like to analyze 
 (e.g., the $\tau$-RR of a system) to be a Dirac comb (DC) with inter-spike period $T_\text{is}$: 
@@
 i.e., a series of Dirac delta functions for a period $T_\text{is}$. There is only one single period, $T_\text{is}$, in this signal (Fig.~\ref{fig_tau_rr_dirac_comb}A, D), so 
-in principle we would strive for a single peak in the frequency domain of this signal at a frequency $f=1/T_\text{is}$. The Fourier spectrum does not meet this expectation 
-and instead of a single frequency, there are many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
-for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$ \cite{Norden1998}.\footnote{This can also 
-be observed for neuron spike trains, e.g. \cite{Orcioni2020,Biagetti2017}.}
+in principle we would strive for a single peak in the frequency domain of this signal at a frequency $f=1/T_\text{is}$. Surprisingly the Fourier spectrum does not meet this expectation 
+and instead of a single frequency, there are exceptionally many frequencies excited (Fig.~\ref{fig_tau_rr_dirac_comb}B, E). This is because the Fourier components add constructively 
+for every frequency $1/T_\text{is}$ and therefore $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$.
 
@@
  \textbf{A} Dirac Comb (DC) with equal amplitudes and
- \textbf{B} its FFT-based power spectral density.
+ \textbf{B} its FFT-based powerspectrum.
  \textbf{C} Proposed inter-spike spectrum of the signal in \textbf{A} showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
  \textbf{D} DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in \textbf{A}, and
- \textbf{E} its FFT-based power spectral density. 
+ \textbf{E} its FFT-based powerspectrum. 
  \textbf{F} Proposed inter-spike spectrum of the signal in \textbf{D} showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
@@
 
-In this article we propose a new way of decomposing a spike-train-like signal into periodic components as 
-an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
-spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
-behavior of the signal's inherent inter-spike frequencies in such a way that harmonics of these frequencies are also excited (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
-Section \ref{sec_tau_rr_method} explains the idea.
-Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
-However, the more spiky the signal is, the more useful our new approach is compared to a
-FT. In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
+In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter-spike spectrum} does not show resonance 
+behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
+any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
+FT. In Section \ref{sec_tau_rr_application} we exemplify the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
 can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
@@
 
-The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
-such time series are often spiky, which favors the proposed decomposition technique.
-But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions.
-The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
-The weights (also called modes) corresponding to the individual basis functions can also
-be called \textit{loadings} and must be determined. A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
-trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
-eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
-or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
-
-Here we propose to use Dirac combs (DC) with 
-different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the min-max-normalized signal we want to transform of length $N$ and 
+The signal, which we would like to transform is decomposed into a set of appropriate basis functions.\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
+such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} Instead of using trigonometric 
+functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
+different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
 $t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
@@
 \bfX_{i,j} &= \sum_{k=0}^{N}\delta\bigl(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \bigr), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
-\label{eq_T_is} T_\text{is}(i)&= n, \quad \text{such that}\quad n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
+\label{eq_T_is} T_\text{is}(i)&= n, \quad s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
 \end{align}
@@
 
-The proposed decomposition does not show a leakage effect by construction.
-However, when introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important periodicities more clearly.
-This choice is mediated by a regression regularization parameter $\alpha$.
-Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
-Our general approach to fixing $\alpha$ is to require that we preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
-The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization given by a
-selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
-We will discuss this in more detail in Section 4. Section \ref{sec_tau_rr_discussion}.
-
-%
-%In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
-%which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$.
+In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
+which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$.
 Obviously, there will be numerous peaks in the inter-spike spectrum of a given signal, when $\alpha$ is small,
-%since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
-%only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
-%The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
-%different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
-%given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and itself.
+since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~(\ref{eq_linear_system}) and not sparse. On the other hand, 
+only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
+The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
+different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
+given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and itself.
 
@@
 
-We demonstrate the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
+We exemplify the use of the inter-spike spectrum in combination with the $\tau$-RR as outlined in 
 Section \ref{sec_tau_rr_intro} on several interesting research questions. The procedure is the following:
@@
 $\tau$-RRs (Fig.~\ref{fig_tau_rr_example_roessler}G, H, I). The proposed idea is also 
-robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. 
-Figure \ref{fig_roessler_peaks} illustrates that 
-while the peak shape does change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all 
-(see Fig.~\ref{fig_roessler_spectra_distances} in the Appendix for further analysis).
-
-\begin{figure}
- \centering
- \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_different_noise_levels_peaks}
- \caption{Peak positions of the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
- \textbf{A} period-2 limit-cycle, \textbf{B} period-3 limit-cycle and \textbf{C} chaos.
-The size of the plotted markers scale with the detected peak height.
-The noise-free spectra are shown in Fig.~\ref{fig_tau_rr_example_roessler}J, K, L and
- an example of these spectra with 5\% additive noise is shown in Fig.~\ref{fig_tau_rr_example_roessler_noise}J, K, L. Spectra were obtained with a LASSO regression and a regularization threshold 
-  corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals.}
-\label{fig_roessler_peaks}
-\end{figure}
+robust to noise (see Fig.~\ref{fig_tau_rr_example_roessler_noise} in the Appendix). This is because the peaks of the $\tau$-RR are insensitive to noise. While the peak shape does 
+change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts after all.
 
@@
 In this example, the according null hypothesis for constructing the surrogate data is that the data stems from a process which yields the same auto-correlation, 
-hence, the same Fourier power spectral density, and the same 
+hence the same Fourier powerspectrum, and the same 
 amplitude distribution. We consider the number of significant peaks in the inter-spike spectrum with
@@
 
-The Fourier frequency spectra for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min}, which may partly 
-be explained by the leakage effect (for technical details on the calculation of 
-the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Especially the $30$ and $60$ \si{min} 
-peaks are split into two adjacent peaks and the local minimum in between these ``double''-peaks correspond to the exact times. The Great Britain counterpart in Fig.~\ref{fig_power_grid_spectra}B 
-has sharp peaks at $15$ and $30$ \si{min} and also ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
+The Fourier frequency spectra for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min} 
+(for technical details on the calculation of 
+the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Indeed, the $15$, $30$ and $60$ \si{min} 
+peaks are split into two adjacent peaks and, FT does not demonstrate a sharp peak exactly at $15$, $30$ and $60$ minutes. The Great Britain counterpart in Fig.~\ref{fig_power_grid_spectra}B 
+has sharp peaks at $15$ \si{min} and, moreover, FT recognizes small ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
 In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Fig.~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
-at $30$ and $60$ \si{min} (there is no leakage effect due to the proposed decomposition technique). 
-In front of these peaks, smaller local peaks can be seen, which correspond to the local peaks of the Fourier power spectra at $28$ and $55$ \si{min}, respectively.
+at $30$ and $60$ \si{min}.
 Moreover, there is an additional peak at 
@@
 
-We interpret the results presented as follows. The missing $15$ \si{min} in the inter-spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min} 
+We interpret the results presented as follows.
+It should be noted firstly that ISS is not only capable to recognize the well-known periodicity in the power grid frequency because of the dispatching time, but also the ISS demonstrate more sharp peaks at this periodicity.
+The missing $15$ \si{min} in the inter-spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min}
 (see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter-spike spectra are not able to detect it and the 
@@
 Our aim in this section is to show that the inter-spike spectrum
-of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier power spectral density of the non-embedded eccentricity time series.
-We will further
+of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier powerspectrum of the non-embedded eccentricity time series. We will further 
 show that Fourier-transforming the $\tau$-RR instead of applying the proposed inter-spike spectrum will lead to non-satisfying results, since the spiky $\tau$-RR excites a variety of harmonics in 
@@
 period-doubling bifurcations. However, we have to admit this way the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 
-This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike spectra for period-2, period-3, and chaotic dynamics.
+This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike power spectra for period-2, period-3, and chaotic dynamics.
 Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter-spike spectra of power grid 
@@
 Third, when adopting our idea of applying the inter-spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters. 
-This is not a drawback of the proposed decomposition method, but rather a drawback of applying this technique to the $\tau$-recurrence rate of the system, which was the main motivation for 
-developing the proposed method.
+This is not a drawback of the proposed method, but rather a drawback of the particular application method that we have heavily used in this article and which was the main motivation for developing 
+the proposed method.
 As a very last remark, we draw attention to the fact that sparse regression can be transformed into sparse logistic regression when the signal we would like to transform is binary.
@@
 
-A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
-combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
+A novel type of powerspectrum, the \textit{inter-spike spectrum}, has been proposed. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
+combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. Wee chose LASSO or a sequentially 
 thresholded least squares regression STLS in this letter. Since there are 
 $M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
-of the period (or frequency) the inter-spike spectrum is obtained. A disadvantage is that the transformation is not invertible. An advantage is that there is no leakage effect.
-Although this novel spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
+of the period (or frequency) the inter-spike spectrum is obtained. 
+Although this novel power spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
 be considered 
@@
 All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
-and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018}, \textit{DifferentialEquations.jl} \cite{rackauckas2017}, \textit{Distances.jl} and 
-\textit{OptimalTransport.jl} \cite{Zhang2022}.
+and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
 }
@@
 
-\begin{figure}
- \centering
- \includegraphics[width=\textwidth]{./figures/fig_power_grid_fft_full}
- \caption{Fourier spectra of the frequency entire time series from \textbf{A} Central Europe (CE), $N_{\text{CE}}=587,520$ and \textbf{B} Great Britain (GB), $N_{\text{GB}}=1,581,120$.
-A subset of the underlying time series is shown in Fig.~\ref{fig_power_grid_time_series}.}
-\label{fig_power_grid_fft_full}
-\end{figure}
-
 \clearpage
@@
 \clearpage
-
-\begin{figure}[h!]
- \centering
- \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_spectra_distances}
- \caption{Wasserstein distances for the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
- \textbf{A} period-2 limit-cycle, \textbf{B} period-3 limit-cycle and \textbf{C} chaos. For each noise level the obtained spectrum is compared to the noise-free spectrum (these are shown 
- in Fig.~\ref{fig_tau_rr_example_roessler}J, K, L for a regularization threshold corresponding to $\rho=0.95$) by computing its Wasserstein distance. Inter-spike spectra were obtained with a 
- LASSO regression and three different regularization thresholds corresponding to $\rho=0.9$ (blue), $\rho=0.95$ (orange) and $\rho=0.99$ (green) accordance of $\tau$-RRs and re-composed signals. 
- Up to a noise level of 20\% the distances are small and rather constant. The fluctuations depend on the chosen regularization threshold as well as on the underlying dynamics.}
-\label{fig_roessler_spectra_distances}
-\end{figure}
 

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
revision

--- 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 these basis functions occurring in $\vec{s}$, each of these $\tilde{N}$ different DCs also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
-$M = \sum_{i=1}^{\tilde{N}}i$ 
+$M = \sum_{i=1}^{\tilde{N}}i$ {\color{red}(let's come back to your example in Fig.3, where $N=4$, regarding your explanation $M=\Sigma_i^{\tilde{N}=3} i= 1+2+3=6$.
+So finally matrix X should be 6x4 size.
+However, X does not have this size in Fig.3, which is the source of confusion.)}
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure):
+(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure) {\color{red}(Moreover, although you claim above that number of rows in X is M in eq.
+(5) you say $\tilde{N}$, and in Fig.
+3 it is four.
+You should really make it clear and cons)}:
 \begin{align}
@@
 (LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Any other 
-sparse regression technique could be used. Finally, we group weights 
+sparse regression technique could be used {\color{red} (I think this sentence can be the source of confusion.
+One could get from this sentence that weight values are independent of regression technique.
+Is it correct?)}.
+Finally, we group weights
 which correspond to basis functions having the same period 
@@
 The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization given by a
-selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
-We will discuss this in more detail in Section 4. Section \ref{sec_tau_rr_discussion}.
+selected $\rho$ (Fig.~\ref{fig_regularization} {\color{red}(It should not be Fig.
+A3?
+or you are talking about regularization parameter $\alpha$?)}).
+Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute.
+We will discuss this in more detail Section \ref{sec_tau_rr_discussion}.
 
@@
 (for technical details on the calculation of 
-the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Especially the $30$ and $60$ \si{min} 
-peaks are split into two adjacent peaks and the local minimum in between these ``double''-peaks correspond to the exact times. The Great Britain counterpart in Fig.~\ref{fig_power_grid_spectra}B 
-has sharp peaks at $15$ and $30$ \si{min} and also ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
+the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}). Indeed, the $15$, $30$ and $60$ \si{min} 
+peaks are split into two adjacent peaks and, FT does not demonstrate a sharp peak exactly at $15$, $30$ and $60$ minutes. The Great Britain counterpart in Fig.~\ref{fig_power_grid_spectra}B 
+has sharp peaks at $15$ \si{min} and, moreover, FT recognizes small ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
 In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Fig.~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
-at $30$ and $60$ \si{min}. In front of these peaks, smaller local peaks can be seen, which correspond to the local peaks of the Fourier power spectra at $28$ and $55$ \si{min}, respectively.
+at $30$ and $60$ \si{min}.
 Moreover, there is an additional peak at 
@@
 A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
-combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
+combs (DC) of different inter-spike period. The weight for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
 thresholded least squares regression STLS in this letter. Since there are 

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
rebuttal letter

--- 2022-11-03 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 \end{equation}
-with $\mathbf{R}$ the recurrence matrix, satisfactory$\vec{x}_i$ the state vector at time 
+with $\mathbf{R}$ the recurrence matrix, satisfactory $\vec{x}_i$ the state vector at time 
 $t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ the number of
@@
 There are no assumptions for stationarity or sampling, when constructing a RP, 
-and since an RP can represent high dimensional dynamics the approch directly applies to higher dimensional systems for which the auto-correlation is a matrix and no single power spectrum captures the recurrences.\\
+and since an RP can represent high dimensional dynamics the approch directly applies to higher dimensional systems for which the auto-correlation is a \todo{hm, I'm not so happy with the "matrix" here} matrix and no single power spectrum captures the recurrences.
 
+\todo[inline]{I agree that the following is not necessary and could be removed}
 \textbf{Please check the above paragraph for correctness, I did not understand the following and would drop it (or explain the point better):}
@@
 However, the exact meaning of this generalized power spectral density is unclear, and it is typically hard to interpret.
-$\tau$-RR spikes already directly encode the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
+$\tau$-RR spikes already directly encode the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the ``power'' contained in a particular frequency mode of the $\tau$-RR should have.
 \textbf{In particular it does not imply anything about the power associated to certain frequencies in the underlying timeseries.} Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
@@
 behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
-Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
+This approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
 The more spiky the signal is, the more useful our new decomposition can potentially be.
@@
 trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
-eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
-or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
+eigenvectors of the corresponding covariance matrix (principal component analysis \cite{Hotelling1933} and related techniques) 
+or intrinsic mode functions (empirical mode decomposition and Hilbert spectrum \cite{Norden1998}).
 These methods typically share the property that the basis functions form a complete basis,

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex

--- 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 \end{equation}
-with $\mathbf{R}$ the recurrence matrix, satisfactory $\vec{x}_i$ the state vector at time 
+with $\mathbf{R}$ the recurrence matrix, $\vec{x}_i$ the state vector at time 
 $t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ the number of
@@
 
-\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ for a scalar time series.
-However, as there is no equivalent of the Wiener-Khinchin theorem its Fourier Transform (FT) only provides a ``generalized'' kind of power spectral density.
-There are clear advantages to such a recurrence-derived power spectral density, the (FT) $\tau$-RR (Fig.~\ref{fig_tau_rr_spectrum_example}D,E):
-There are no assumptions for stationarity or sampling, when constructing a RP, 
-and since an RP can represent high dimensional dynamics the approch directly applies to higher dimensional systems for which the auto-correlation is a \todo{hm, I'm not so happy with the "matrix" here} matrix and no single power spectrum captures the recurrences.
-
-\todo[inline]{I agree that the following is not necessary and could be removed}
-\textbf{Please check the above paragraph for correctness, I did not understand the following and would drop it (or explain the point better):}
-\textit{This is reasonable, since the average distances for a given lag $\tau$ 
+\citet{Zbilut2008} pointed out that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener-Khinchin theorem, provide an analogue,
+``generalized'', spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
 \begin{equation}
@@
 
-However, the exact meaning of this generalized power spectral density is unclear, and it is typically hard to interpret.
-$\tau$-RR spikes already directly encode the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the ``power'' contained in a particular frequency mode of the $\tau$-RR should have.
-\textbf{In particular it does not imply anything about the power associated to certain frequencies in the underlying timeseries.} Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
+However, the interpretation of this generalized power spectral density is unclear, and it is typically hard to interpret.
+$\tau$-RR directly encodes the periodicity of the underlying signal, in contrast it is unclear what, if any, interpretation the "power" contained in a particular frequency mode of the $\tau$-RR should have.
+Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Fig.~\ref{fig_tau_rr_spectrum_example}) especially for
 map-data (low-resolution data), a FT of such a signal leads to a spike-train-like image in the frequency domain (e.g., \cite{Schild1982,Cordoba1989}, see 
@@
 an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
-spectra \cite{Dummer2014}.
-We instead investigate decomposing the $\tau$-RR in an overcomplete basis of spike trains using a sparsity regularization.
-Section \ref{sec_tau_rr_method} introduces the approach in detail.
-Our novel \textit{inter-spike spectrum} does not show resonance
-behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
-This approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
-The more spiky the signal is, the more useful our new decomposition can potentially be.
-In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study.
-In this case, the inter-spike spectrum
+spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
+behavior of the signal's inherent inter-spike frequencies in such a way that harmonics of these frequencies are also excited (Fig.~\ref{fig_tau_rr_dirac_comb}C, F).
+Section \ref{sec_tau_rr_method} explains the idea.
+Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR.
+However, the more spiky the signal is, the more useful our new approach is compared to a
+FT. In Section \ref{sec_tau_rr_application} we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
 can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.
@@
 
-To obtain the Inter-Spike Spectrum , the signal, which we would like to analyze, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
-The general idea common to many methods is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
-The weights (in some contexts also called modes or loadings) corresponding to the individual basis functions must be determined.
-A number of decomposition techniques based on different sets of basis functions exist, e.g., 
+The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
+such time series are often spiky, which favors the proposed decomposition technique.
+But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions.
+The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
+The weights (also called modes) corresponding to the individual basis functions can also
+be called \textit{loadings} and must be determined. A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
 trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
-eigenvectors of the corresponding covariance matrix (principal component analysis \cite{Hotelling1933} and related techniques) 
-or intrinsic mode functions (empirical mode decomposition and Hilbert spectrum \cite{Norden1998}).
-These methods typically share the property that the basis functions form a complete basis,
-the set of basis functions is linearly independent, and thus the weights are uniquely determined.
+eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
+or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
 
@@
 A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
-combs (DC) of different inter-spike period. The weight for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
+combs (DC) of different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
 thresholded least squares regression STLS in this letter. Since there are 
-$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed weights as a function 
-of the period (or frequency) the inter-spike spectrum is obtained. This provides information that is complementary to the Fourier decompostion of the signal.
-
+$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$ the regression can get computationally intensive for $N>1,000$. When plotting the computed loadings as a function 
+of the period (or frequency) the inter-spike spectrum is obtained. A disadvantage is that the transformation is not invertible. An advantage is that there is no leakage effect.
+Although this novel spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
+be considered 
+as an additional source of information but not as a substitute for ordinary Fourier analysis. 
 Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
some comments

--- 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 \abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high dimensional time series.
-It thus plays a similar role to the autocorrelation for scalar time series in encoding temporal correlations.
+It, thus, plays a similar role to the autocorrelation for scalar time series in encoding temporal correlations.
 Unlike the autocorrelation however, its Fourier decomposition does not have a natural interpretation.
-Thus there is no direct analogue to the power spectrum in recurrence analysis.
+Thus, there is no direct analogue to the power spectrum in recurrence analysis.
 In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
@@
 
-To obtain the Inter-Spike Spectrum , the signal, which we would like to analyze, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
+To obtain the inter-spike spectrum, the signal, which we would like to analyse, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
 The general idea common to many methods is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
@@
 These methods typically share the property that the basis functions form a complete basis,
-the set of basis functions is linearly independent, and thus the weights are uniquely determined.
+the set of basis functions is linearly independent, and, thus, the weights are uniquely determined.
 
@@
 these basis functions occurring in $\vec{s}$, each of these $\tilde{N}$ different DCs also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
-$M = \sum_{i=1}^{\tilde{N}}i$ {\color{red}(let's come back to your example in Fig.3, where $N=4$, regarding your explanation $M=\Sigma_i^{\tilde{N}=3} i= 1+2+3=6$.
+$M = \sum_{i=1}^{\tilde{N}}i$ 
+\todo[inline]{let's come back to your example in Fig.~\ref{fig_tau_rr_basis_functions}, where $N=4$, regarding your explanation $M=\Sigma_i^{\tilde{N}=3} i= 1+2+3=6$.
 So finally matrix X should be 6x4 size.
-However, X does not have this size in Fig.3, which is the source of confusion.)}
+However, X does not have this size in Fig.3, which is the source of confusion.}
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure) {\color{red}(Moreover, although you claim above that number of rows in X is M in eq.
+(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure) \todo[inline]{(Moreover, although you claim above that number of rows in X is M in eq.
 (5) you say $\tilde{N}$, and in Fig.
@@
 the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
-Fig.~\ref{fig_tau_rr_basis_functions}B).\\
+Fig.~\ref{fig_tau_rr_basis_functions}B).
 
-\noindent Eventually, an under-determined linear system
+Eventually, an under-determined linear system
 \begin{equation}
@@
 
-When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most prominent spikes, and thus the most important periodicities more clearly.
+When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most prominent spikes, and, thus, the most important periodicities more clearly.
 This choice is parametrized by a regression regularization parameter $\alpha$.
-Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and thus a full reconstruction of the signal.
+Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and, thus, a full reconstruction of the signal.
 Our general approach to fixing $\alpha$ is to require that we preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
@@
 For example, if there is more (less) demand than supply, the network frequency decreases (increases) compared to the nominal frequency \cite{kundur1994power}.
-\\
+
 The frequency variations can include other information, such as the functionality of control systems \cite{gorjao2020data}, the effect of fluctuations in
@@
 In most electricity grids the operation of dispatchable power plants is scheduled in 1-hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
-might exist.\\
+might exist.
 
@@
 $40$ \si{min} for both datasets, which is absent in the Fourier spectrum and which is not a multiple of the missing $15$ \si{min} peak. The position and magnitude of the peaks in the shown 
-inter-spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.\\
+inter-spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.
 
+\todo[inline]{ISS appears first time here and is not explained. before it was written out.}
 We interpret the results presented as follows.
@@
 the corresponding Fourier spectrum (cf. Section \ref{sec_tau_rr_intro}). We use a time series which covers the past \mytilde $67$ Mio.~years (Myr), with a total length of $N=13,421$ samples and a 
-sampling period of $\Delta t= 5,000$.\\
-First we compute an evolutionary short time Fourier transform (FT) using a windowsize of $ws=1,000$ samplepoints ($\equiv 5$ Myr) shifted by unity and a 
+sampling period of $\Delta t= 5,000$.
+
+First we compute an evolutionary short time FT using a windowsize of $ws=1,000$ samplepoints ($\equiv 5$ Myr) shifted by unity and a 
 Hamming window. The spectrogram reveals the expected periods mentioned, which are highlighted and clearly visible (Fig.~\ref{fig_laskar_spectra}A).
@@
  \centering
- \includegraphics[width=\textwidth]{./figures/fig_laskar_spectra}
+ \includegraphics[width=\textwidth]{figures/fig_laskar_spectra}
  \caption{\textbf{A} Evolutionary Fourier power spectra of eccentricity time series. \textbf{B} Inter-spike spectrogram of the $\tau$-recurrence rate of the eccentricity time 
@@
 We have successfully used the idea of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter-spike spectra, 
-and thus a null model, the number of significant peaks in the inter-spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve 
+and, thus, a null model, the number of significant peaks in the inter-spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve 
 period-doubling bifurcations. However, we have to admit this way the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 

### 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
Very last polishing before resubmission

--- 2022-11-04 Manuscript/inter_spike_manuscript_mdpi.tex
@@
 % Abstract (Do not insert blank lines, i.e. \\)
+
 \abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional time series. 
-It thus plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations.
+It, thus, plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations. 
 However, its Fourier decomposition does not have a clean interpretation. 
-Thus there is no satisfactory analogue to the power spectrum in recurrence analysis.
-In this paper we introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization.
+Thus, there is no satisfactory analogue to the power spectrum in recurrence analysis. 
+We introduce a novel way to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with a sparsity regularization. 
 We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series.
 We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying system in a wide variety of examples and is robust to measurement noise.}
-%
-%A novel kind of power spectrum is constructed, the \textit{inter-spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
-%clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
-%We invent this instructive approach with the 
-%idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
-%along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter-spike spectrum can be interpreted as a nonlinear power 
-%spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}
 
@@
 
-The signal, which we would like to transform\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
-such time series are often spiky, which favors the proposed decomposition technique.
-But the proposed method can be applied to any sort of signal.} is decomposed into a set of appropriate basis functions.
-The general idea is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
-The weights (also called modes) corresponding to the individual basis functions can also
-be called \textit{loadings} and must be determined. A number of decomposition techniques are out there based on different sets of basis functions, e.g., 
+To obtain the inter-spike spectrum, the signal, which we would like to analyse, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
+The general idea common to many methods is that the sum of these weighted functions can approximate a finite signal to a sufficient degree.
+The weights (in some contexts also called modes or loadings) corresponding to the individual basis functions must be determined.
+A number of decomposition techniques based on different sets of basis functions exist, e.g., 
 trigonometric functions (Fourier- and wavelet analysis \cite{Bracewell1986}), 
-eigenvectors of the corresponding covariance matrix (Principal Component Analysis \cite{Hotelling1933} and related techniques) 
-or Intrinsic Mode Functions (Empirical Mode Decomposition and Hilbert spectrum \cite{Norden1998}).
+eigenvectors of the corresponding covariance matrix (principal component analysis \cite{Hotelling1933} and related techniques) 
+or intrinsic mode functions (empirical mode decomposition and Hilbert spectrum \cite{Norden1998}).
+These methods typically share the property that the basis functions form a complete basis,
+the set of basis functions is linearly independent, and, thus, the weights are uniquely determined.
 
@@
 these basis functions occurring in $\vec{s}$, each of these $\tilde{N}$ different DCs also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
-$M = \sum_{i=1}^{\tilde{N}}i$ {\color{red}(let's come back to your example in Fig.3, where $N=4$, regarding your explanation $M=\Sigma_i^{\tilde{N}=3} i= 1+2+3=6$.
-So finally matrix X should be 6x4 size.
-However, X does not have this size in Fig.3, which is the source of confusion.)}
+$M = \sum_{i=1}^{\tilde{N}}i$ 
 basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
-(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure) {\color{red}(Moreover, although you claim above that number of rows in X is M in eq.
-(5) you say $\tilde{N}$, and in Fig.
-3 it is four.
-You should really make it clear and cons)}:
+(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure):
 \begin{align}
@@
 
+When introducing a sparsity regularization we give up the ability to fully reconstruct the signal from the decomposition in favor of identifying the most prominent spikes, and, thus, the most important periodicities more clearly.
+This choice is parametrized by a regression regularization parameter $\alpha$.
+Only for $\alpha = 0$ do we obtain a solution to Eq.~(\ref{eq_linear_system}) and, thus, a full reconstruction of the signal.
+Our general approach to fixing $\alpha$ is to require that we preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction.
+The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization given by a
+selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
+We will discuss this in more detail Section \ref{sec_tau_rr_discussion}.
 The proposed decomposition does not show a leakage effect by construction.
@@
 selected $\rho$ (Fig.~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster to compute. 
-We will discuss this in more detail in Section 4. Section \ref{sec_tau_rr_discussion}.
+We will discuss this in more detail in Section \ref{sec_tau_rr_discussion}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{inter-spike spectra of power grid frequency data}\label{sec_power_grid}
+\subsection{Inter-spike spectra of power grid frequency data}\label{sec_power_grid}
 
@@
  \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra}
- \caption{Averaged Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see Appendix~\ref{sec_power_grid_appendix}). 
+ \caption{Averaged evolutionary Fourier power spectra of recorded power grid frequency time series of \textbf{A} Central Europe (CE) and \textbf{B} Great Britain (GB) (see 
+ Fig.~\ref{fig_power_grid_time_series} in Appendix~\ref{sec_power_grid_appendix}). 
  The corresponding averaged inter-spike spectra of the according $\tau$-RRs, Eq.~\eqref{eq_tau_rr}, are shown in \textbf{C} and \textbf{D}, respectively. Vertical red dashed lines correspond to 
- $15$, $30$ and $60$ \si{min}. For technical details on the calculation of the spectra shown, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}.}  
+ $15$, $30$ and $60$ \si{min}.
+For technical details on the calculation of the spectra shown, i.e preprocessing and window size being used, the reader is referred to the Appendix~\ref{sec_power_grid_appendix}.}
 \label{fig_power_grid_spectra}
@@
 
-The Fourier frequency spectra for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min}, which may partly 
+The evolutionary Fourier frequency spectrum for the Central Europe data in Figure~\ref{fig_power_grid_spectra}A, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min}, which may partly
 be explained by the leakage effect (for technical details on the calculation of 
@@
 has sharp peaks at $15$ and $30$ \si{min} and also ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
+The fact that sharp peaks are seen here using the same window size and sampling frequency as in the case of the Central European data shows that the leakage effect alone is not the cause of 
+the peak splitting shown in Fig.~\ref{fig_power_grid_spectra}A.
+
 In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Fig.~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
@@
 $40$ \si{min} for both datasets, which is absent in the Fourier spectrum and which is not a multiple of the missing $15$ \si{min} peak. The position and magnitude of the peaks in the shown 
-inter-spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.\\
+inter-spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.
 
-We interpret the results presented as follows.
-It should be noted firstly that ISS is not only capable to recognize the well-known periodicity in the power grid frequency because of the dispatching time, but also the ISS demonstrate more sharp peaks at this periodicity.
-The missing $15$ \si{min} in the inter-spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min}
+We interpret the results presented as follows. The missing $15$ \si{min} in the inter-spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min} 
 (see Fig.~\ref{fig_power_grid_time_series}B,D) and because these periods are integer multiples of $15$ \si{min} the inter-spike spectra are not able to detect it and the 
@@
 
-\noindent Then we construct the inter-spike spectrogram of the $\tau$-RR by first determining an appropriate embedding. By using a recent Tree-Embedding-Ansatz \cite{Kraemer2022} we minimize the 
+\noindent Then we construct the inter-spike spectrogram of the $\tau$-RR by first determining an appropriate embedding. By using a recent tree-embedding ansatz \cite{Kraemer2022} we minimize the 
 \textit{false nearest neighbor} statistic \cite{hegger1999} and use the continuity statistic \cite{pecora2007} for potential delays. Eventually we obtain an $8$-dimensional embedding 
-with delays $\tau s=[0, 18, 36, 48, 62, 101, 114]$ (in sampling units) for the entire time series. Similar to the preceding approach we embed the time series with these embedding parameters 
+with embedding delays $\tau =[0, 18, 36, 48, 62, 101, 114]$ (in sampling units) for the entire time series. Similar to the preceding approach we embed the time series with these embedding parameters 
 on windows of size $ws=1,200$ and a unity shift.\footnote{We use a slightly larger window here than in the short FT, because the embedding causes a ``loss'' of data points and we want to 

### 2022-11-04 Applications/Power Grid/CE and GB frequencies/plot_frequency_results.m

@@ -150,3 +150,73 @@ xlabel('time lag \tau (min)')
 xlim([1 100])
 set(gca, 'LineWidth', lw2, 'FontSize', font)
 grid on
+
+
+%% Plot FFT for entire time series
+
+x = f_ce_ds;
+x2 = f_gb_ds;
+blocksize = length(x);
+blocksize2 = length(x2);
+
+Y = fft(x);
+P2 = abs(Y/blocksize);
+P1 = P2(1:blocksize/2+1);
+P1(2:end-1) = 2*P1(2:end-1);
+
+Y2 = fft(x2);
+P22 = abs(Y2/blocksize2);
+P12 = P22(1:blocksize2/2+1);
+P12(2:end-1) = 2*P12(2:end-1);
+
+%%
+
+dt_s = 20; % sampling time is sec
+dt_m = 1/ (60/dt_s);
+
+
+
+% time/period/frequency vector for FFT spectrogram
+Fs_ce = 60/dt_s; % sampling frequency min^-1
+Fs_gb = 60/dt_s;
+
+L_block_ce = blocksize; % block length covering one full day (24 hours, 60/dt_s * 60 * 24))
+L_block_gb = blocksize2;
+
+t_ce = (0:L_block_ce-1)*dt_m; % time vector for block in min
+t_gb = (0:L_block_gb-1)*dt_m;
+
+fs_ce= Fs_ce*(0:(L_block_ce/2))/L_block_ce; % frequency vector in min^1
+fs_gb= Fs_gb*(0:(L_block_gb/2))/L_block_gb;
+
+%%
+
+font = 22; % fontsize
+lw1 = 2.5;
+lw2 = 2;
+
+figure('Units','normalized','Position',[.001 .001 .999 .999])
+subplot(121)
+semilogx(1./fs_ce, P1, 'LineWidth', lw1)
+title('Single-Sided Amplitude Spectrum of F_{CE}')
+xline(15,'r--','LineWidth', lw1)
+xline(30,'r--','LineWidth', lw1)
+xline(60,'r--','LineWidth', lw1)
+xlabel('period (min)')
+ylabel('|power/period|')
+xlim([1 100])
+set(gca, 'LineWidth', lw2, 'FontSize', font)
+grid on
+
+subplot(122)
+semilogx(1./fs_gb, P12, 'LineWidth', lw1)
+title('Single-Sided Amplitude Spectrum of F_{GB}')
[…]

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
proof

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[entropy,article,accept,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{31 August 2022} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{14 November 2022} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\newcommand\hmmax{0}
\newcommand\bmmax{0}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
%\usepackage{mathptmx}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{siunitx}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Spike Spectra for Recurrences}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Spike Spectra for Recurrences}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-9943-5391} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0001-6643-9508} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0003-1437-7039} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{\hl{K. Hauke Kraemer} %MDPI: Please carefully check the accuracy of names and affiliations.
 $^{1,}$*\orcidA{}, Frank Hellmann $^{1}$, Mehrnaz Anvari $^{1}$\orcidB{}, \hl{J\"urgen Kurths} %MDPI: The name of this author is different from the submitting system. Please confirm which one is correct.
 $^{1,2,\highlighting{3} %MDPI: 
}$ and Norbert Marwan $^{1,2,\highlighting{4} %MDPI: 
,}$*\orcidC{}}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{K. Hauke Kraemer, Frank Hellmann, Mehrnaz Anvari, J\"urgen Kurths and Norbert Marwan}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Kraemer, K.H.; Hellmann, F.; Anvari, M.; Kurths, J.; Marwan, N.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system. Please confirm.
\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.
 \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
\hl{$^{4}$} \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany}

% Contact information of the corresponding author
\corres{Correspondence: hauke\_kraemer@hotmail.com (K.H.K.); marwan@pik-potsdam.de (N.M.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

% Abstract (Do not insert blank lines, i.e. \\)

\abstract{In recurrence analysis, the $\tau$-recurrence rate encodes the periods of the cycles of the underlying high-dimensional time series. 
It, thus, plays a similar role to the autocorrelation for scalar time-series in encoding temporal correlations. 
However, its Fourier decomposition does not have a clean interpretation. 
Thus, there is no satisfactory analogue to the power spectrum in recurrence analysis. 
We introduce a novel method to decompose the $\tau$-recurrence rate using an over-complete basis of Dirac combs together with sparsity regularization. 
We show that this decomposition, the \textit{inter-spike spectrum}, naturally provides an analogue to the power spectrum for recurrence analysis in the sense that it reveals the dominant periodicities of the underlying time series. 
We show that the inter-spike spectrum correctly identifies patterns and transitions in the underlying system in a wide variety of examples and is robust to measurement noise.}

% Keywords
\keyword{decomposition; frequency analysis; recurrence analysis; bifurcations}
\PACS{05.45.Tp; 05.90.+m; 89.90.+n; 02.70.Uu; 05.10.Ln; 05.45.-a; 05.45.Ac}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\section{Introduction}\label{sec_tau_rr_intro}

The dynamics of complex systems as provided by measured time series usually show complicated and chaotic patterns.
Quantifying their recurrence features is a powerful way to describe them and to infer information about 
the type of dynamics, stability, regime changes, or couplings and synchronisation \cite{marwan2007,marwan2008epjst,webber2015}.
Even more challenging are signals which do have a heavy tailed-distribution or appear as a spike-train,
e.g., neuron firings \cite{Dummer2014,Orcioni2020}, heart beat variability \cite{marwan2002herz}, 
or extreme flood events \cite{banerjee2021}.
Deriving useful information from spike-train signals or inter-spike time series is an important
topic in data analysis in many scientific fields \cite{Kajikawa2005,Dummer2014,Orcioni2020,Canale2021}.

Recurrence plots (RPs) provide a vivid representation of complex dynamics $\vec{x}_i$ stemming from potentially high dimensional systems \cite{marwan2007}
\begin{equation}\label{eq_rp_definition}
R_{i,j}(\varepsilon) = \Theta\left(\varepsilon - D_{i,j}\right) 
= \Theta\left(\varepsilon - \| \vec{x}_i - \vec{x}_j\|\right), \qquad \vec{x} \in \mathbb{R}^d, \quad i,j \in [1,\ldots, N],
\end{equation}
where $\mathbf{R}$ \hl{is} %MDPI: There is no bold in other places in the text, please confirm whether the bold here needs to be retained
 the recurrence matrix, $\vec{x}_i$ is the state vector at time 
$t = \Delta t \cdot i$ ($\Delta t$ the sampling time), $N$ is the number of
sampling points (or length of data series), and $d$ is the dimension of the system.
The crucial free parameter $\varepsilon$ is the recurrence threshold, determining what is a recurrence
and, thus, the visible structures in the RP. It can be chosen such that the recurrence rate 
$RR(\varepsilon)=N^{-2}\sum_{i,j}^N R_{i,j}(\varepsilon)$ exhibits a certain value \cite{kraemer2018}.
The simple idea to track recurring states of the $d$-dimensional trajectory $\vec{x}_i$ of the system under study not only allows for a beneficial visualization of the dynamics, 
but also for its 
quantification, using certain structures in the RP, such as diagonal or vertical lines \cite{marwan2007}.

Some of these recurrence quantification measures, the entropy of diagonal lines and the entropy of 
recurrence times, can be related to the basic characteristics of complex systems, such as Kolmogorov--Sinai entropy \cite{march2005,baptista2010}. However, these quantifiers have a free parameter, the minimal considered line length, and 
are usually biased, due to the finite size of the RP and thickened diagonal lines, which need to be corrected \cite{Kraemer2019}. Moreover, the mentioned statistics cannot account for 
changing regular (non-chaotic) dynamics, such as period-doubling bifurcations.

A rather simple idea is to look at the $\tau$-recurrence rate of the RP ($\tau$-RR, Equation~(\ref{eq_tau_rr}))~\cite{marwan2002pla,Zbilut2008}.
This is the density of recurrence points along the diagonals of the recurrence matrix, as a function of the distance $\tau$ (sampling units) to the main diagonal:
\begin{equation}\label{eq_tau_rr}
\tau\text{-RR}(\varepsilon) = RR(\tau, \varepsilon) = \frac{1}{N-\tau} \sum_{i=1}^{N-\tau	} R_{i,i+\tau}.
\end{equation}
$\tau$-RR serves as an estimator for the probability that the system recurs after time $\tau \Delta t$, with $\Delta t$ being the sampling time of the trajectory 
$\vec{x}_i = \vec{x}(\Delta t \cdot i),\, i=1,\ldots,N$. 
It represents the period length of cycles in the data (Figure~\ref{fig_tau_rr_spectrum_example}D).

\citet{Zbilut2008} found that $\tau$-RR could be interpreted as analogous to the auto-correlation function $C(\tau)$ and, hence, via the Wiener--Khinchin theorem, provide an analogue,
``generalized'', spectral density. This is reasonable, since the average distances for a given lag $\tau$ 
\begin{equation}
\overline{D}(\tau) = \frac{1}{N-\tau}\sum_{i=1}^{N-\tau} D_{i, i+\tau}
\end{equation}
can be directly read from the distance matrix $\mathbf{D}$ and are also preserved in its thresholded version $\tau$-RR. There are clear advantages to recurrence-derived spectral density, 
i.e., Fourier transforming (FT) $\tau$-RR (Figure~\ref{fig_tau_rr_spectrum_example}D,E), instead 
of $C(\tau)$. There are no assumptions for stationarity or sampling when constructing a RP.
Furthermore, since an RP can represent high-dimensional dynamics and its $\tau$-RR serves as a plug-in for $C(\tau)$, the correlation structures of higher dimensional spaces can be read from 
the recurrence-derived Fourier~spectrum.\\
\vspace{-6pt}
\begin{figure}[H]
 %\centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_spectrum_example}
 \caption{\hl{Schematic} %MDPI: Please change the hyphen (-) into minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 illustration of a $\tau$-recurrence-rate-based spectrum. (\textbf{A}) $x$-component time series of the Lorenz63-System (Equation~\eqref{eq_model_Lorenz63}) and 
 (\textbf{B}) its corresponding Fourier power spectrum. 
 (\textbf{C})~Reconstructed state space portrait from the time series shown in (\textbf{A}) using PECUZAL time-delay \hl{embedding} %MDPI: Please ensure that permission has been obtained and there is no copyright issue. If copyright is needed, please provide a citation in the following format: "Reprinted/adapted with permission from Ref. [XX]. Copyright year, copyright owner's name". More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
 \cite{Kraemer2021}. 
 (\textbf{D}) Subset of the recurrence plot and the corresponding $\tau$-recurrence rate obtained from the state space trajectory in (\textbf{C}). 
(\textbf{E}) Fourier Power spectrum obtained from the $\tau$-recurrence rate (subset shown in panel (\textbf{D}\hl{))} %MDPI: Please ensure that permission has been obtained and there is no copyright issue. If copyright is needed, please provide a citation in the following format: "Reprinted/adapted with permission from Ref. [XX]. Copyright year, copyright owner's name". More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
 \cite{Zbilut2008}. (\textbf{D},\textbf{E}) show the results of a part of the time series, 
 which is highlighted in pink in (\textbf{A}).
 }\label{fig_tau_rr_spectrum_example}
\end{figure}

However, the interpretation of this generalized power spectral density is unclear, and it is typically hard to interpret. $\tau$-RR directly encodes the periodicity of the underlying signal; in contrast, it is unclear what, if any, interpretation the ``power'' contained in a particular frequency mode of the $\tau$-RR should be. Whenever $\tau$-RR is a spike-train-like signal, which it is in most cases (see Figure~\ref{fig_tau_rr_spectrum_example}) especially for 
map-data (low-resolution data), an FT of such a signal leads to a spike-train-like image in the frequency domain (e.g.,~\cite{Schild1982,Cordoba1989}, see 
Figure~\ref{fig_tau_rr_spectrum_example}E). Thus, how to extract meaningful information about the systems' state space trajectory is not intuitive.

For example, consider the signal we would like to analyze 
(e.g., the $\tau$-RR of a system) to be a Dirac comb (DC) with inter-spike period $T_\text{is}$: 
\begin{equation}
\text{DC}_{\text{is}}(t) = \sum_{k=-\infty}^{\infty} \delta(t-kT_\text{is}),
\label{eq_dirac_comb}
\end{equation}
i.e., a series of Dirac delta functions for a period $T_\text{is}$. There is only one single period, $T_\text{is}$, in this signal (Figure~\ref{fig_tau_rr_dirac_comb}A,D); 
in principle, we would strive for a single peak in the frequency domain of this signal at frequency $f=1/T_\text{is}$. The Fourier spectrum does not meet this expectation 
and instead of a single frequency, there are many excited frequencies (Figure~\ref{fig_tau_rr_dirac_comb}B,E). This is because the Fourier components constructively contribute
to every frequency $1/T_\text{is}$; therefore, $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$ \cite{Norden1998}. ({\hl{This can also } %MDPI: footnote is not allowed in this journal, we moved here, please confirm
be observed for neuron spike trains, e.g., \cite{Orcioni2020,Biagetti2017}.})

\begin{figure}[H]
% \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_dirac_comb}
 \caption{The transformation of a Dirac comb (series of Dirac delta functions) with a single inter-spike period $T_{\text{is}}=100$ ($\widehat{=}f=0.01$) 
 into the frequency domain. 
 (\textbf{A}) Dirac Comb (DC) with equal amplitudes and
 (\textbf{B}) its FFT-based power spectral density.
 (\textbf{C}) Proposed inter-spike spectrum of the signal in (\textbf{A})~showing a single frequency, which corresponds to the inter-spike period $T_{\text{is}}$ ($f=0.01$).
 (\textbf{D}) DC with randomly chosen amplitudes and same $T_{\text{is}}$ as in (\textbf{A}), and
 (\textbf{E}) is its FFT-based power spectral density. 
 (\textbf{F}) Proposed inter-spike spectrum of the signal in (\textbf{D}) showing a single frequency, which corresponds to the expected inter-spike period $T_{\text{is}}$ ($f=0.01$). 
 Inter-spike spectra were obtained with a LASSO regression and a regularization threshold corresponding to $\rho=0.9$ accordance of the signals in (\textbf{A},\textbf{D}) and 
 its re-composed signals (c.f. Section~\ref{sec_tau_rr_method}). 
}
\label{fig_tau_rr_dirac_comb}
\end{figure}

In this article, we propose a new way of decomposing a spike-train-like signal into periodic components as 
an alternative to the RP-based method suggested in \cite{Zbilut2008} or Fourier-based spike-train power 
spectra \cite{Dummer2014}. This novel \textit{inter-spike spectrum} does not show resonance 
behavior of the signal's inherent inter-spike frequencies in such a way that the harmonics of these frequencies are also excited (Figure~\ref{fig_tau_rr_dirac_comb}C,F). Section \ref{sec_tau_rr_method} explains the idea. Note that this approach can be used to decompose arbitrary signals, and is not specific to $\tau$-RR. However, the more spiky the signal is, the more useful our new approach is compared to 
FT. In Section \ref{sec_tau_rr_application}, we demonstrate the usage of inter-spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter-spike spectrum 
can unravel characteristic time scales of high dimensional systems, which is not possible when using an FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method}\label{sec_tau_rr_method}

To obtain the inter-spike spectrum, the signal, in our case the $\tau$-RR, is decomposed into a set of appropriate basis functions. 
The general idea common to many methods is that the sum of these weighted functions can approximate a finite signal to a sufficient degree. The weights (in some contexts also called modes or loadings) corresponding to the individual basis functions must be determined.
A number of decomposition techniques based on different sets of basis functions exist, e.g., 
trigonometric functions (Fourier and wavelet analysis \cite{Bracewell1986}), 
eigenvectors of the corresponding covariance matrix (principal component analysis \cite{Hotelling1933} and related techniques) 
or intrinsic mode functions (empirical mode decomposition and Hilbert spectrum \cite{Norden1998}).
These methods typically share the property that the basis functions form a complete basis, and
the set of basis functions is linearly independent; thus, the weights are uniquely determined.

Here, we propose the use of Dirac combs (DC) with 
different inter-spike periods as basis functions, as shown in Equation~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the min-max-normalized signal we want to transform in terms of length $N$ and 
$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following sections, we label this time series as a $(1\times N)$-dimensional 
vector $\vec{s}$. 
First, $\tilde{N}$ different DCs of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
for possible phase shifts of 
these basis functions occurring in $\vec{s}$, each of these $\tilde{N}$ different DCs also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
$M = \sum_{i=1}^{\tilde{N}}i$ 
basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
(Figure~\ref{fig_tau_rr_basis_functions} illustrates the described procedure) as follows:
\begin{align}
\label{eq_basis_matrix} 
\bfX_{i,j} &= \sum_{k=0}^{N}\delta\bigl(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \bigr), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
\label{eq_T_is} T_\text{is}(i)&= n, \quad \text{such that}\quad n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
\end{align}

Note that due to the shifting of each of the basis functions of the inter-spike period $T_\text{is}$, $\bfX$ is no longer linear-independent. 
Furthermore, there will be identical basis functions, which do not allow for an unambiguous inter-spike period, 
if we would include all $N$ possible inter-spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Figure~\ref{fig_tau_rr_basis_functions}A).
The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, 
the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
Figure~\ref{fig_tau_rr_basis_functions}B).

Eventually, an under-determined linear system
\begin{equation}
\bfX^T \boldsymbol{\beta}=\vec{s}
\label{eq_linear_system}
\end{equation}  
has to be solved for $\boldsymbol\beta$, with the $(M\times 1)$-sized vector carrying the loadings we are interested in. Of the variety of algorithms which can solve this problem, we are 
particularly interested in those solutions which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\vec{s}$ into a minimal number of basis 
functions (for an excellent overview of the topic we refer readers to \citet{Brunton2019}). In this paper, we either use the \textit{least absolute shrinkage and selection operator} 
(LASSO) \cite{Tibshirani1996} or a \textit{sequentially threshold least squares} (STLS) regression~\cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Any other 
sparse regression technique can be used. Finally, we group loadings 
which correspond to basis functions with the same period 
$T_\text{is}$ into $\hat{\boldsymbol\beta}_f$ and obtain the 
\textit{inter-spike spectrum} by simply plotting $\hat{\boldsymbol\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
(Figure~\ref{fig_tau_rr_dirac_comb}C, F).

\begin{figure}[H]
%\centering
\includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_basis_functions}
\caption{(\textbf{A}) Example of a full set of basis functions for an input signal of length $N=4$, aligned in the matrix $\bfX'$. Inter-spike periods $T_{\text{is}}$ larger 
than $\ceil*{N/2}+1$ lead to redundant basis functions (i.e., repeated lines in $\bfX$, red sheared) or basis functions, which cannot be uniquely assigned to a certain inter-spike period 
(blue sheared). $T_{\text{is}}$ for each row can be obtained by Equation~\eqref{eq_T_is}. (\textbf{B}) The final set of unambiguous, but still linearly dependent, basis functions aligned in the matrix $\bfX$.} \label{fig_tau_rr_basis_functions}
\end{figure}

When introducing a sparsity regularization, we forsake the ability to fully reconstruct the signal from the decomposition in favor of identifying the most prominent spikes, and thus, the most important periodicities, more accurately. This choice is parametrized by a regression regularization parameter $\alpha$. We only obtain a solution to Equation~(\ref{eq_linear_system}) with $\alpha = 0$ as well as a full reconstruction of the signal. Our general approach to fixing $\alpha$ is to preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction. The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization of the 
selected $\rho$ (Figure~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster in terms of computation. 
We will discuss this in more detail in Section \ref{sec_tau_rr_discussion}.
The proposed decomposition does not show a leakage effect by construction. However, when introducing sparsity regularization we forsake the ability to fully reconstruct the signal from the decomposition in favor of identifying the most important periodicities more clearly. This choice is mediated by a regression regularization parameter $\alpha$. Only for $\alpha = 0$ do we obtain a solution to Equation~(\ref{eq_linear_system}) and thus a full reconstruction of the signal. Our general approach to fixing $\alpha$ is to preserve most of the original signal in the sense of matching a given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and the reconstruction. The chosen regression method (in our case, LASSO or STLS) will determine how sensitive the obtained inter-spike spectrum is with respect to the regularization achieved by a 
selected $\rho$ (Figure~\ref{fig_regularization}). Regarding this, in most of our applications LASSO yields more robust results, while STLS is usually faster in terms of computation. %Attention AE: Please check repetition in previous pragraphs%
We will discuss this in more detail in Section \ref{sec_tau_rr_discussion}.

%
%In addition to the computational complexity of solving Equation~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
%which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$. Obviously, there will be numerous peaks in the inter-spike spectrum of a given signal, when $\alpha$ is small, 
%since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Equation~(\ref{eq_linear_system}) and not sparse. On the other hand, 
%only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter-spike spectrum, are obtained when $\alpha$ is sufficiently large. 
%The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
%different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
%given (Pearson) correlation coefficient $\rho$ between the original signal $\vec{s}$ and itself.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{sec_tau_rr_application}

We demonstrate the use of the inter-spike spectrum in combination with $\tau$-RR, as outlined in 
Section \ref{sec_tau_rr_intro}, on several interesting research questions. The procedure takes place as follows:
\begin{itemize}[noitemsep]
\item[(1)] Compute an RP of the trajectory of the system, Equation~\eqref{eq_rp_definition}. If only univariate data are available, perform a state space reconstruction for obtaining the trajectory first.
\item[(2)] Compute the $\tau$-RR of the RP, as shown in Equation~\eqref{eq_tau_rr}.
\item[(3)] Transform the $\tau$-RR into the proposed inter-spike spectrum, see Section \ref{sec_tau_rr_method}.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Period Estimation for Different Dynamics in the R \"ossler System}
First, we consider the R\"ossler system (Equation~\eqref{eq_model_roessler}, shown in Appendix \ref{sec_models_roessler}), 
in three different dynamical setups. We use the proposed inter-spike spectrum to
identify the type of dynamics.
We set the parameters as $b=2$, $c=4$ and analyze period-2 limit cycle dynamics ($a=0.36$ in Figure~\ref{fig_tau_rr_example_roessler}A,D,G,J), 
period-3 limit cycle dynamics ($a=0.41$ in Figure~\ref{fig_tau_rr_example_roessler}B,E,H,K) and chaotic dynamics ($a=0.428$ in Figure~\ref{fig_tau_rr_example_roessler}C,F,I,L).

\begin{figure}[H]
% \centering
 \includegraphics[width=0.76\textwidth]{./figures/fig_tau_rr_example_roessler}
 \caption{\hl{Inter-spike spectra} %MDPI: Please use a consistent numbering style for the subfigures throughout the paper. P is after N;  Please change the hyphen (-) into minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
 of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
 (\textbf{A}) Trajectory of the system in a period-2 (parameter $a=0.36$), (\textbf{B})~in a period-3 (parameter $a=0.41$) and 
 (\textbf{C}) in a chaotic regime (parameter $a=0.428$). 
\mbox{ (\textbf{D}--\textbf{F})}~The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for (\textbf{D},\textbf{E}) and 5\% for (\textbf{F}). 
  (\textbf{G}--\textbf{I}) $\tau$-RRs of the shown RPs. 
  (\textbf{J}--\textbf{L}) The proposed inter-spike spectra of the $\tau$-RRs shown in panels (\textbf{G}--\textbf{I}). Spectra were obtained with a LASSO regression and a regularization threshold 
  corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
  (\textbf{M},\textbf{N},\textbf{P}) Fourier power spectra of the $\tau$-RRs shown in panels (\textbf{G}--\textbf{I}). }
\label{fig_tau_rr_example_roessler}
\end{figure}

The inter-spike spectra unravel the specific dynamics, which are also apparent in the state space portraits (Figure~\ref{fig_tau_rr_example_roessler}A--C) and in the 
$\tau$-RRs (Figure~\ref{fig_tau_rr_example_roessler}G--I). The proposed idea is also 
robust to noise (see Figure~\ref{fig_tau_rr_example_roessler_noise} in the Appendix~\ref{appc}). This is because the peaks of $\tau$-RR are insensitive to noise. 
Figure \ref{fig_roessler_peaks} illustrates that 
while the peak shape does change in the presence of noise, its position does not, and this is what the inter-spike spectrum encrypts 
(see Figure~\ref{fig_roessler_spectra_distances} in the Appendix~\ref{appc} for further analysis).

\begin{figure}[H]
 %\centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_different_noise_levels_peaks}
 \caption{Peak positions of the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels up to 50\% for the discussed R\"ossler dynamics, 
 (\textbf{A}) period-2 limit-cycle, (\textbf{B}) period-3 limit-cycle and (\textbf{C})~chaos. The size of the plotted markers scale with the detected peak height. The noise-free spectra are shown in Figure~\ref{fig_tau_rr_example_roessler}J--L and 
 an example of these spectra with 5\% additive noise is shown in Figure~\ref{fig_tau_rr_example_roessler_noise}J--L. Spectra were obtained with a LASSO regression and a regularization threshold 
  corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals.}
\label{fig_roessler_peaks}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bifurcations in the Logistic Map}

We consider the Logistic map $x_{n+1}=r\cdot x_n \left( 1-x_n \right)$ for changing the control parameter $r$. We vary $r$ from $r=3.4$ to $r=4$ in steps of $0.001$. For 
each setting of $r$ 
\begin{itemize}[noitemsep]
\item[(1)] A time series of length $N=201$ is computed with a random initial condition \mbox{$u_0 \in [0,\ 1]$}, neglecting the first $1,000$ samples as transients;
\item[(2)] A \textls[-15]{total of $100$ iterative Amplitude Adjusted Fourier Transform (iAAFT) surrogates}~\cite{Schreiber1996,Schreiber2000} are computed;
\item[(3)] The time series and its iAAFT surrogates are embedded in a 2-dimensional state space using a time delay of unity;
\item[(4)] The two-dimensional trajectories RPs, as shown in Equation~\eqref{eq_rp_definition}, are computed under a threshold $\varepsilon=0.05$,
\item[(5)] $\tau$-RR, as shown in Equation~\eqref{eq_tau_rr}, is computed from the RP of the signal and from the RPs of the surrogates;
\item[(6)] Inter-spike spectra are obtained from $\tau$-RR of the signal and from the $\tau$-RRs of the surrogates, as can be seen in Section \ref{sec_tau_rr_method};
\item[(7)] Finally, from the distribution of the surrogate inter-spike spectra, the 95th percentile is computed. The peaks of the inter-spike spectrum of the signal which exceed 
this percentile are counted. 
\end{itemize}

\hl{In this example} %MDPI: we add indent here, please confirm
, the null hypothesis for constructing the surrogate data is that the data stem from a process which yields the same auto-correlation, and
hence, the same Fourier power spectral density, and the same 
amplitude distribution. We consider the number of significant peaks in the inter-spike spectrum with
respect to the control parameter in order to distinguish the corresponding dynamics (Figure~\ref{fig_tau_rr_logistic}C).
A correlation with the positive Lyapunov exponent (Figure~\ref{fig_tau_rr_logistic}A) is discernible 
($\rho_{\text{Pearson}}(\text{Lyapunov})=0.72$). This analysis can handle period-doubling since it measures the dominant cycles via the inter-spike spectrum. 
However, whenever the periods of the new cycles coincide with integer multiples of the periods of already existing cycles, the approach cannot detect 
period doubling. A similar case can be observed in Figure~\ref{fig_tau_rr_example_roessler}J,K, where the number of peaks does not change, but  the mutual distance does.

A less computationally intensive approach is to compute surrogates for $\tau$-RR analytically, rather than computing an RP and its $\tau$-RR for each iAAFT surrogate of the 
time series. This translates into a null hypothesis 
that the $\tau$-RR and its corresponding inter-spike spectrum stem from an RP of a random signal. In this case, the probability of finding a black point in the RP can be obtained 
from a binomial distribution with the probability parameter $p$ set to the recurrence rate of the RP of the signal. In this way, $100$ surrogate $\tau$-RRs are computed in step (5). 
The results are even slightly better compared to the ones obtained from the iAAFT surrogates (Figure~\ref{fig_tau_rr_logistic}B, $\rho_{\text{Pearson}}(\text{Lyapunov})=0.81$). 
The first instance of period doubling at $r \approx 3.458$ cannot be detected by any of the surrogates.

The described procedure does work well for map data, because most often the $\tau$-RR for those kind of data reveals a ``spiky enough'' nature. 
On the contrary, highly sampled (flow-) data often yield not as 
spiky $\tau$-RRs; therefore, the number of significant peaks in the inter-spike spectrum may not be sensitive enough to detect period-doubling bifurcations. Moreover the sensitivity of the 
inter-spike spectrum in detecting regime shifts also depends on the critical regularization threshold. Nevertheless, the 
according inter-spike spectra still reveal important information (Figure~\ref{fig_tau_rr_example_roessler}) and practitioners can design appropriate quantifying statistics based 
on these spectra which suit the research task.

\begin{figure}[H]
 %\centering
 \includegraphics[width=\textwidth]{./figures/fig_tau_rr_logistic}
 \caption{(\textbf{A}) Bifurcation diagram and Lyapunov exponent and of the Logistic map as a function of the control parameter $r$.
 (\textbf{B}) Number of significant peaks ($\alpha=0.05$) in the inter-spike spectrum of the $\tau$-RR and its Pearson correlation coefficient to the Lyapunov exponent shown in (\textbf{A})
 (white noise surrogates). 
 (\textbf{C}) Same as (\textbf{B}), but for iterative Amplitude Adjusted Fourier Transform (iAAFT) \hl{surrogates} %MDPI: Please ensure that permission has been obtained and there is no copyright issue. If copyright is needed, please provide a citation in the following format: "Reprinted/adapted with permission from Ref. [XX]. Copyright year, copyright owner's name". More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
 \cite{Schreiber1996,Schreiber2000}. To obtain the inter-spike spectra, we used 
 a LASSO regression and a regularization threshold corresponding to the $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals.  
}
\label{fig_tau_rr_logistic}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Inter-Spike Spectra of Power Grid Frequency Data}\label{sec_power_grid}

Power grids are large, synchronized, complex networks whose stable functioning is indispensable for modern societies.
To maintain the stability of a power grid, the balance between energy consumption and energy generation must be ensured. 
In an AC-power grid, the grid frequency is an observable variable that reflects how well this balance is satisfied. 
In this process, the grid frequency and its deviations from the nominal frequency are continuously recorded and monitored by 
the grid operators (in Europe and many parts of the world this is $50$ \si{Hz} or $60$ \si{Hz} in America and, for example, southern Japan).
For example, if there is more (less) demand than supply, the network frequency decreases (increases) compared to the nominal frequency \cite{kundur1994power}.

The frequency variations can include other information, such as the functionality of control systems \cite{gorjao2020data}, the effect of fluctuations in
renewable energies (REs), demands on the grid \cite{anvari2020stochastic} and, moreover, the effect of regular dispatches due to the trading market 
\cite{meyer2020identifying}. The latter induce periodic frequency jumps. Here we look at the frequency time series for the Great Britain (GB) and Continental Europe 
(CE) (Appendix \ref{sec_power_grid_appendix} and Figure~\ref{fig_power_grid_time_series}A,C). Clear jumps every 30 and 60 min are discernible and quantitatively reflected in the corresponding 
autocorrelations (Figure~\ref{fig_power_grid_time_series}B,D). Furthermore, the autocorrelation of the CE frequency time series shows regular peaks every $15$ \si{min} 
(see Figure~\ref{fig_power_grid_time_series}B). These peaks are caused by a mismatch of power supply and demand \cite{weissbach2009high} during dispatches. 
In most electricity grids the operation of dispatchable power plants is scheduled in 1-h blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
might exist.

\begin{figure}[H]
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra}
 \caption{Averaged evolutionary Fourier power spectra of recorded power grid frequency time series of (\textbf{A}) Central Europe (CE) and (\textbf{B}) Great Britain (GB) (see 
 Figure~\ref{fig_power_grid_time_series} in Appendix~\ref{sec_power_grid_appendix}). 
 The corresponding averaged inter-spike spectra of the according $\tau$-RRs, Equation~\eqref{eq_tau_rr}, are shown in (\textbf{C},\textbf{D}), respectively. Vertical red dashed lines correspond to 
 $15$, $30$ and $60$ \si{min}. For technical details on the calculation of the spectra shown, i.e, the preprocessing and window size being used, the reader is referred to Appendix~\ref{sec_power_grid_appendix}.}  
\label{fig_power_grid_spectra}
\end{figure}

The evolutionary Fourier frequency spectrum for the Central European data in \linebreak \mbox{Figure~\ref{fig_power_grid_spectra}A}, however, does not display sharp peaks exactly at $15$, $30$ and $60$ \si{min}, which may partly 
be explained by the leakage effect (for technical details on the calculation of 
the spectra shown, the reader is referred to Appendix~\ref{sec_power_grid_appendix}). More clearly, the $30$ and $60$ \si{min} 
peaks are split into two adjacent peaks and the local minimum in between these ``double''-peaks correspond to the exact times. The Great Britain counterpart in Figure~\ref{fig_power_grid_spectra}B 
has sharp peaks at $15$ and $30$ \si{min} and also ``local predecessor peaks'' for $30$ and $60$ \si{min} at the same positions as in panel A. 
The fact that sharp peaks are seen here using the same window size and sampling frequency as in the case of the Central European data shows that the leakage effect alone is not the cause of 
the peak splitting, as shown in Figure~\ref{fig_power_grid_spectra}A.

In contrast, the $15$ \si{min} peak is completely absent from the inter-spike spectra of the $\tau$-RRs of the frequency data (Figure~\ref{fig_power_grid_spectra}C,D), but these show sharp peaks 
at $30$ and $60$ \si{min} (there is no leakage effect due to the proposed decomposition technique). 
In front of these peaks, smaller local peaks can be seen, which correspond to the local peaks of the Fourier power spectra at $28$ and $55$ \si{min}, respectively.
Moreover, there is an additional peak at 
$40$~\si{min} for both datasets, which is absent in the Fourier spectrum and which is not a multiple of the missing $15$ \si{min} peak. The position and magnitude of the peaks in the 
inter-spike spectra are robust to the chosen recurrence threshold, the regression method and its regularization as well as the sampling time of the original signal.

We interpret the results presented as follows. The missing $15$ \si{min} in the inter-spike spectra is due to the much stronger autocorrelation at $30$ and $60$ \si{min} 
(see Figure~\ref{fig_power_grid_time_series}B,D); because these periods are integer multiples of $15$ \si{min}, the inter-spike spectra are not able to detect them and the 
sparse regression ``drags'' the $15$ \si{min} periods into the mentioned $30$ and $60$ \si{min} peaks. Moreover, the inter-spike spectra, unlike the Fourier spectra, demonstrate sharp peaks exactly 
at $30$ and $60$ \si{min}, i.e., during dispatches (not valid in case of the GB dataset). Finally,  we found a clear sharp peak at $40$ \si{min} which can occur 
because of any regular controls in a power grid, and can indicate the need to develop the existing stochastic processes to model the power grid frequency more precisely \cite{gorjao2020data}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolutionary Inter-Spike Spectra of Earth'S Orbit Data}

When applying the proposed inter-spike spectrum to the $\tau$-RR of a time series we expect additional frequency/period information, due to the fact that the recurrence plot (RP), 
Equation~\eqref{eq_rp_definition}, and its corresponding $\tau$-RR, as shown in Equation~\eqref{eq_tau_rr}, visualize the trajectory of the embedded time series in an embedding space of a higher dimension. 
However, given sufficient embedding of the time series, we would also expect that major frequencies/periods of the non-embedded time series are incorporated in the RP, its $\tau$-RR, 
and eventually in the inter-spike spectrum of the $\tau$-RR. In order to demonstrate this, we apply the inter-spike spectrum to the freely available eccentricity time series of \mbox{\citet{Laskar2011}}. 
This astronomical computation of the orbital motion of the Earth (here, we focus on the eccentricity only) has a clear expectation value of the incorporated frequencies/periods. The three leading 
eccentricity cycles of 405 kyr period, 95 kyr period and 124 kyr period are well known in palaeoclimate studies \cite{Laskar2004,Westerhold2020}. Our aim in this section is to show that the inter-spike spectrum 
of the $\tau$-RR of the embedded eccentricity time series will reflect these cycles in a similar fashion as the Fourier power spectral density of the non-embedded eccentricity time series. We will further 
show that Fourier-transforming the $\tau$-RR instead of applying the proposed inter-spike spectrum will lead to non-satisfying results, since the spiky $\tau$-RR excites a variety of harmonics in 
the corresponding Fourier spectrum (cf. Section \ref{sec_tau_rr_intro}). We use a time series which covers the past \mytilde $67$ Mio.~years (Myr), with a total length of $N=13,421$ samples and a 
sampling period of $\Delta t= 5000$.

First, we compute an evolutionary short time FT using a windowsize of $ws=1000$ samplepoints ($\equiv 5$ Myr) shifted by unity and a Hamming window. The spectrogram reveals the expected periods mentioned, which are highlighted and clearly visible (Figure~\ref{fig_laskar_spectra}A).

 \hl{Then}, we construct the inter-spike spectrogram of the $\tau$-RR by first determining an appropriate embedding. By using a recent tree-embedding ansatz \cite{Kraemer2022}, we minimize the 
\textit{false nearest neighbor} statistic \cite{hegger1999} and use the continuity statistic \cite{pecora2007} for potential delays. Eventually, we obtain $8$-dimensional embedding 
with embedding delays $\tau =[0, 18, 36, 48, 62, 101, 114]$ (in sampling units) for the entire time series. Similar to the preceding approach we embed the time series with these embedding parameters 
on windows of size $ws=1,200$ and a unity shift. ({\hl{We use a slightly} larger window here than in the short FT, because the embedding causes a ``loss'' of data points and we want to 
cover similar time spans.}) The RPs are computed on these embedded trajectories with a fixed recurrence threshold corresponding to a $10\%$ global recurrence rate \cite{kraemer2018} 
and the inter-spike spectra of the corresponding $\tau$-RRs is obtained by using STLS regression (see Section \ref{sec_tau_rr_method}) and a regularization threshold corresponding to 
$\rho=0.9$ accordance of $\tau$-RRs and re-composed signals. We only use the first $200$ data points of the $\tau$-RR (covering a time span of $1$ Myr). 
The spectrogram also highlights the $95$, $124$ and $405$ kyr periods as expected (Figure~\ref{fig_laskar_spectra}B). 
Additional power is distributed in the harmonics at $190$ and $248$ kyr periods. Finally, the standard FT with a Hamming window of the same $\tau$-RRs used to obtain the inter-spike 
spectrogram in panel B yields a smeared spectrogram which does not reflect the expected periods, but rather suffers from the spike train behavior, i.e., many excited harmonics, of the 
FT described in Section \ref{sec_tau_rr_intro} and Figure~\ref{fig_tau_rr_dirac_comb}. The shown results are robust to a change of the embedding parameters and windowsizes. However, a low 
regularization threshold smears the clear spectrogram in panel B.

\begin{figure}[H]
 %\centering
 \includegraphics[width=\textwidth]{figures/fig_laskar_spectra}
 \caption{(\textbf{A}) Evolutionary Fourier power spectra of eccentricity time series. (\textbf{B}) Inter-spike spectrogram of the $\tau$-recurrence rate of the eccentricity time 
 series and (\textbf{C}) its Fourier spectrogram. Horizontal black dashed lines highlight the analytically expected orbital periods of $405$, $124$ and $95$ kyrs. 
 For comparability, in all cases the spectra aligned in the columns of the shown plots are normalized to probabilities (sum of unity for 
 each power spectrum). For further computational details, please refer to the main text.}  
\label{fig_laskar_spectra}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}\label{sec_tau_rr_discussion}

We successfully used the idea of transforming the $\tau$-RR for the detection of bifurcations in the Logistic map. By constructing appropriate surrogates of the inter-spike spectra, 
and, thus, a null model, the number of significant peaks in the inter-spike spectrum correlated well with the positive Lyapunov exponent. This measure was also able to resolve 
period-doubling bifurcations. However, we have to admit that by using this method, the detection of a bifurcation is only possible when the additional period(s) is not an integer multiple of the former period(s). 
This behavior is described in the application to the R\"ossler system, where we explicitly showed the different inter-spike spectra for period-2, period-3, and chaotic dynamics.
Further development might potentially incorporate the mutual distance of peaks in the spectrum for a better correlation to the Lyapunov exponent. The inter-spike spectra of power grid 
	frequency data illustrate that our proposed method may serve as a valuable source of information in addition to a standard Fourier analysis. Last but not least, we showed that our approach incorporates frequencies, which are apparent in the Fourier spectrum of the signal, by applying the method to analytically derived eccentricity data, where the dominant frequencies are well 
known.

We discuss some more technical details in the following sections, which will also affect any application of the proposed method. 
First of all, the number of required basis functions 
$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ for an input signal of length $N$ is the crucial bottleneck of this approach, which is why it does not show good scaling behavior. The subsequent sparse 
regression, therefore, becomes computationally intensive for $N>1000$. Depending on the memory of the computer used, input signals $N>2000$ usually do not work. This means that signals 
often need to be downsampled as a preprocessing step (e.g., see Appendix \ref{sec_power_grid_appendix}). Second, the regularization parameter $\alpha$ for the regression is a crucial free parameter. 
As described in Section~\ref{sec_tau_rr_method}, our idea in this paper is to select the $\alpha$ such that the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ matches a 
given (Pearson) correlation coefficient $\rho_{\vec{s},\tilde{\vec{s}}}$ between the original signal $\vec{s}$ and itself. This ensures that $\alpha$ adjusts itself to the data as well as to the 
used regression method. We found that this increases the comparability of different spectra, especially when performing a running window approach in order to obtain an evolutionary spectrogram 
(Figure~\ref{fig_laskar_spectra}). 
However, the two different sparse regression algorithms we encountered in this article (LASSO and STLS) yield different results for the same desired $\rho_{\vec{s},\tilde{\vec{s}}}$. 
Even if the spectra obtained in this way look qualitatively similar, they are not always quantitatively similar. The reason for this 
is that $\rho_{\vec{s},\tilde{\vec{s}}}$ is not a smooth function of $\alpha$ in case of STLS, due to the hard-thresholding involved \cite{Brunton2016}, which is shown in Figure~\ref{fig_regularization}.
Third, when adopting our idea of applying the inter-spike spectrum to the $\tau$-recurrence rate of the signals state space trajectory, the embedding process induces additional free parameters.  
This is not a drawback of the proposed decomposition method, but rather a drawback of applying this technique to the $\tau$-recurrence rate of the system, which was the main motivation for 
developing the proposed method. As a very last remark, we draw attention to the fact that sparse regression can be transformed into sparse logistic regression when the signal we would like to transform is binary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}\label{sec_tau_rr_conclusion}

A novel decomposition technique is proposed that yields the \textit{inter-spike spectrum}. The method decomposes any arbitrary signal into basis functions which consist of (lagged) Dirac 
combs (DC) of a different inter-spike period. The loading for each period is obtained by a regularized regression, which promotes sparsity in its solution. We chose LASSO or a sequentially 
thresholded least squares regression STLS in this letter. Since there are 
$M = \sum_{i=1}^{\ceil*{N/2}+1}i$ basis functions for a signal of length $N$, the regression can become computationally intensive for $N>1000$. When plotting the computed loadings as a function 
of the period (or frequency), the inter-spike spectrum is obtained. A disadvantage is that the transformation is not invertible. An advantage is that there is no leakage effect.
Although this novel spectrum is superior to an ordinary FFT-based power spectrum when the signal has a spike-train-like appearance, the authors suggest that this method should 
be considered 
as an additional source of information but not as a substitute for ordinary Fourier analysis. 
Due to the sparse regression underlying the method, there is no unique inverse of the transformation and the regularization parameter plays a crucial role and determines the 
appearance of the obtained inter-spike spectrum. Moreover, similar to the Nyquist frequency barrier in the Fourier Transform which sets a lower bound for the corresponding wave period, here 
the maximum considered inter-spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$.

The creation of the proposed method was by the idea of transforming $\tau$-recurrence rate signals ($\tau$-RRs) into their frequency domain. 
This general idea \cite{Zbilut2008} facilitates a frequency analysis of high dimensional systems, because the RP is a representation of the system's state space trajectory.   
The $\tau$-RR of a recurrence plot (RP) usually has a spiky shape, especially for map-like data, and the inter-spike spectrum can reliably reveal the system's dominant frequencies, 
which is not possible when Fourier transforming the $\tau$-RR or the underlying signal itself. Since the position of the peaks 
in the $\tau$-RR are not sensitive to noise, the corresponding inter-spike spectrum also yields robust results in the presence of~noise.

There is a broad range of applications for the proposed idea. The inter-spike spectrum itself can serve as a valuable tool for the analysis of any sort of 
spike-train-like data. On the other hand, the inter-spike spectrum of the $\tau$-RR of a signal can serve as a generalized, nonlinear frequency analysis tool for complex systems. 
When there is only a subset of state variables available, the state space has to be reconstructed as a pre-processing step. Recent findings \cite{Kraemer2021,Kraemer2022} show that 
this reconstruction process can be reliably automated and applied to multivariate data as well. This would allow for a ``running window'' approach, in order to detect transitions. 
Due to the mentioned computational constraints of our proposed method, a window size $w\leq 1000$ would possibly suffice for most data, especially when it is map-like, i.e., not 
highly sampled.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, K.H.K. and F.H.; methodology, K.H.K., F.H. and N.M.; software, K.H.K. and F.H.; validation, K.H.K., F.H., M.A. and N.M.; formal analysis, K.H.K.; data curation, K.H.K. and M.A.; writing---original draft preparation, K.H.K.; writing---review and editing, K.H.K., F.H., M.A. and N.M.; visualization, K.H.K.; supervision, N.M.; project administration, J.K. All authors have read and agreed to the published version of the manuscript.}

\funding{This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9).}

\institutionalreview {\hl{ }}%{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent {\hl{ }}%{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans. Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{The study that we present here is available as a fully reproducible code base
``repository will be published and cited here, when accepted'' and the method
will be available in the Julia language, ``package will be published and cited here, 
when accepted'' and as a MATLAB\textsuperscript{\textregistered} toolbox 
``Toolbox will be published and cited here, when accepted''.}

\acknowledgments{
All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
and we made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018}, \textit{DifferentialEquations.jl} \cite{rackauckas2017}, \textit{Distances.jl} and 
\textit{OptimalTransport.jl} \cite{Zhang2022}.
}

\conflictsofinterest{The authors declare that they have no conflict of interest.} 
\vspace{-6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{yes} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix

\section{Exemplary Models}

\subsection{Lorenz System}\label{sec_models_lorenz63}

\hl{The} classical Lorenz-63 system \cite{lorenz1963} is defined as

\begin{equation}
\begin{array}{rcl}
\dot{x}&=&\sigma(y-x) \\
\dot{y}&=&x(r-z)-y \\
\dot{z}&=&xy - \beta z.
\end{array}
\label{eq_model_Lorenz63}
\end{equation}
{For} producing Figure~\ref{fig_tau_rr_spectrum_example}, we set the initial condition to $u_0=[0.0, 10.0, 0.0]$, used a sampling time of $\Delta t=0.01$ and discarded the first 
2000 points of the integration as transients. The parameters have been set to 
$\sigma=10, \beta=8/3, \rho=28$ and we used a time series consisting of 6000 samples.

\subsection{R \"ossler System}\label{sec_models_roessler}

\hl{The} R\"ossler system \cite{roessler1976} is defined as
\begin{align}
\begin{array}{rcl}
\dot{x}&=&-y-z \\
\dot{y}&=&x+ay \\
\dot{z}&=&b+ z(x-c) .
\end{array}
\label{eq_model_roessler}
\end{align}
{For} producing Figures~\ref{fig_tau_rr_example_roessler_noise} and ~\ref{fig_tau_rr_example_roessler}, the initial condition for producing panels \textbf{A} \& \textbf{B} was set to $u_0=[0.7, -1, 0.4]$ with a sampling time 
of $dt=0.05$ and in case of panel \textbf{C}, $u_0=[-0.1242, -2.5415, 0.2772]$ with a sampling time of $dt=0.1$. The first $5000$ samples were discarded as transients and trajectories of length $N=5000$ were 
obtained from which we computed the RPs and the corresponding $\tau$-RRs. For the inter-spike spectra, only the first $1000$ values of the $\tau$-RRs were considered.

\section{Power Grid Frequency Time Series}\label{sec_power_grid_appendix}

\textls[-15]{The raw frequency time series have a length of $\tilde{N}_{\text{CE}}=58,752,000$ and} \mbox{$\tilde{N}_{\text{GB}}=31,622,400$} with sampling times $\Delta t_{\text{CE}}=0.2$ \si{s} and 
$\Delta t_{\text{GB}}=1$ \si{s}, respectively. GB frequency data were measured during 2016, and were obtained from \cite{GB}. CE frequency data were from 2017 and were obtained from \cite{haehne2018footprint}.

We downsampled these time series to a sampling time of $\Delta t_{\text{CE}}= \Delta t_{\text{GB}}=20$ \si{s}, which led to total time series lengths of 
$N_{\text{CE}}=587,520$ and $N_{\text{GB}}=1,581,120$ which we used for further analysis.

\begin{figure}[H]
% \centering
 \includegraphics[width=\textwidth]{./figures/fig_power_grid_time_series}
 \caption{Subset of the frequency time series of (\textbf{A}) Central Europe \hl{(CE)} %MDPI: Please ensure that permission has been obtained and there is no copyright issue. If copyright is needed, please provide a citation in the following format: "Reprinted/adapted with permission from Ref. [XX]. Copyright year, copyright owner's name". More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
 \cite{haehne2018footprint} and (\textbf{C}) Great Britain \hl{(GB)} %MDPI: 
 \cite{GB} along with their autocorrelation functions in (\textbf{B},\textbf{D}), respectively. The normalized autocorrelations in (\textbf{B},\textbf{D}) were computed with the entire time series, whereas the subsets shown in (\textbf{A},\textbf{C}) 
 contain only $1441$ samples.}
\label{fig_power_grid_time_series}
\end{figure}

In this analysis, we divided the time series into 
non-overlapping blocks of length $N_{\text{block}}=4320$, covering a time span of $24$ h. For each time series block we computed Fourier spectra and recurrence plots (RPs), 
Equation~\eqref{eq_rp_definition}, along with their $\tau$-RRs, Equation~(\ref{eq_tau_rr}). The RPs were obtained from a uniform 5-dimensional time-delay embedding of each time series with 
the delay set to the first minimum of the mutual information \cite{fraser1986,hegger1999} and a fixed recurrence threshold corresponding to an 8\% recurrence rate was used in order 
to ensure comparability \cite{kraemer2018}. The first $600$ data points of the $\tau$-RRs were used to obtain inter-spike spectra with a LASSO regression and a 
regularization threshold corresponding to $\rho=0.95$ accordance of $\tau$-RRs and re-composed signals. The spectra shown in all panels of Figure~\ref{fig_power_grid_spectra} 
are the averages over all blocks, following Meyer et al~\cite{meyer2020identifying}.

\begin{figure}[H]
% \centering
 \includegraphics[width=\textwidth]{./figures/fig_power_grid_fft_full}
 \caption{Fourier spectra of the frequency entire time series from (\textbf{A}) Central Europe (CE), \mbox{$N_{\text{CE}}=587,520$} and (\textbf{B}) Great Britain (GB), $N_{\text{GB}}=1,581,120$. A subset of the underlying time series is shown in Figure~\ref{fig_power_grid_time_series}.}
\label{fig_power_grid_fft_full}
\end{figure}

\section{Inter-Spike Spectra for Noisy R \"ossler System}\label{appc}

\begin{figure}[H]
 %\centering
 \includegraphics[width=0.93\textwidth]{./figures/A3A}

 \caption{\textit{Cont}.}
\label{fig:petit3leaks3D}
\end{figure}

\begin{figure}[H]\ContinuedFloat

 \includegraphics[width=0.93\textwidth]{./figures/A3B}
 \caption{\hl{Same as in} %MDPI: please add explanation for A--I
 Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter-spike spectra 
 in (\textbf{J}--\textbf{L}), and the Fourier spectra in (\textbf{M},\textbf{N},\textbf{P}) are unaffected by the additive noise.}
\label{fig_tau_rr_example_roessler_noise}
\end{figure}

\vspace{-6pt}

\begin{figure}[H]
 %\centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_roessler_spectra_distances}
 \caption{Wasserstein distances for the obtained inter-spike spectra of the $\tau$-RRs for additive noise levels of up to 50\% for the discussed R\"ossler dynamics, 
 (\textbf{A}) period-2 limit-cycle, (\textbf{B}) period-3 limit-cycle and (\textbf{C}) chaos. For each noise level the obtained spectrum is compared to the noise-free spectrum (these are shown 
 in Figure~\ref{fig_tau_rr_example_roessler}J--L for a regularization threshold corresponding to $\rho=0.95$) by computing its Wasserstein distance. Inter-spike spectra were obtained with a 
 LASSO regression and three different regularization thresholds corresponding to $\rho=0.9$ (blue), $\rho=0.95$ (orange) and $\rho=0.99$ (green) accordance of $\tau$-RRs and re-composed signals. 
 Up to a noise level of 20\% the distances are small and rather constant. The fluctuations depend on the chosen regularization threshold as well as on the underlying dynamics.}
\label{fig_roessler_spectra_distances}
\end{figure}

\section{Regularizationparameters for Different Sparse Regression Techniques}\label{sec_regularization_appendix}

\begin{figure}[H]
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_regularization}
 \caption{Pearson correlation coefficient $\rho_{\vec{s},\tilde{\vec{s}}}$ between the input signal signal $\vec{s}$ and the re-composed signal $\tilde{\vec{s}}=\bfX^T\hat{\boldsymbol\beta}$ as a 
 function of the regularization parameter $\alpha$ for (\textbf{A}) LASSO and (\textbf{B}) sequentially thresholded least squares (STLS) regression (see also Section \ref{sec_tau_rr_method}). 
 The input time series is of length $N=200$ and stems from the $\tau$-RR of R\"ossler system in regular dynamics.}
\label{fig_regularization}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

\begin{thebibliography}{999}

\bibitem[Marwan {et~al.}(2007)Marwan, Romano, Thiel, and Kurths]{marwan2007}
Marwan, N.; Romano, M.C.; Thiel, M.; Kurths, J.
\newblock {Recurrence Plots for the Analysis of Complex Systems}.
\newblock {\em Phys. Rep.} {\bf 2007}, {\em 438},~237--329.
\newblock {https://doi.org/10.1016/j.physrep.2006.11.001}.

\bibitem[Marwan(2008)]{marwan2008epjst}
Marwan, N.
\newblock {A Historical Review of Recurrence Plots}.
\newblock {\em Eur. Phys. J. Spec. Top.} {\bf 2008}, {\em
  164},~3--12.
\newblock
  {https://doi.org/10.1140/epjst/e2008-00829-1}.

\bibitem[{Webber, Jr.} and Marwan(2015)]{webber2015}
{Webber, Jr.}, C.L.; Marwan, N.
\newblock {\em {Recurrence Quantification Analysis---Theory and Best
  Practices}}; Springer: Cham, Switzerland, 2015; p.~421.
\newblock
  {https://doi.org/10.1007/978-3-319-07155-8}.

\bibitem[Dummer {et~al.}(2014)Dummer, Wieland, and Lindner]{Dummer2014}
Dummer, B.; Wieland, S.; Lindner, B.
\newblock {Self-consistent determination of the spike-train power spectrum in a
  neural network with sparse connectivity}.
\newblock {\em Front. Comput. Neurosci.} {\bf 2014}, {\em
  8},~104.
\newblock
 {https://doi.org/10.3389/fncom.2014.00104}.

\bibitem[Orcioni {et~al.}(2020)Orcioni, Paffi, Apollonio, and
  Liberti]{Orcioni2020}
Orcioni, S.; Paffi, A.; Apollonio, F.; Liberti, M.
\newblock {Revealing Spectrum Features of Stochastic Neuron Spike Trains}.
\newblock {\em Mathematics} {\bf 2020}, {\em 8},~1011.
\newblock
  {https://doi.org/10.3390/math8061011}.

\bibitem[Marwan {et~al.}(2002)Marwan, Wessel, Meyerfeldt, Schirdewan, and
  Kurths]{marwan2002herz}
Marwan, N.; Wessel, N.; Meyerfeldt, U.; Schirdewan, A.; Kurths, J.
\newblock {Recurrence Plot Based Measures of Complexity and its Application to
  Heart Rate Variability Data}.
\newblock {\em {Phys. Rev. E}} {\bf 2002}, {\em 66},~026702.
\newblock
 {https://doi.org/10.1103/PhysRevE.66.026702}.

\bibitem[Banerjee {et~al.}(2021)Banerjee, Goswami, Hirata, Eroglu, Merz,
  Kurths, and Marwan]{banerjee2021}
Banerjee, A.; Goswami, B.; Hirata, Y.; Eroglu, D.; Merz, B.; Kurths, J.;
  Marwan, N.
\newblock Recurrence analysis of extreme event-like data.
\newblock {\em Nonlinear Process. Geophys.} {\bf 2021}, {\em
  28},~213--229.
\newblock
  {https://doi.org/10.5194/npg-28-213-2021}.

\bibitem[Kajikawa and Hackett(2005)]{Kajikawa2005}
Kajikawa, Y.; Hackett, T.A.
\newblock {Entropy analysis of neuronal spike train synchrony}.
\newblock {\em J. Neurosci. Methods} {\bf 2005}, {\em 149},~90--93.
\newblock
  {https://doi.org/10.1016/j.jneumeth.2005.05.011}.

\bibitem[Canale {et~al.}(2021)Canale, Lijoi, Nipoti, and
  Pr{\"{u}}nster]{Canale2021}
Canale, A.; Lijoi, A.; Nipoti, B.; Pr{\"{u}}nster, I.
\newblock {Inner spike and slab Bayesian nonparametric models}.
\newblock {\em Econom. Stat.} {\bf 2021}.
\newblock
  {https://doi.org/10.1016/j.ecosta.2021.10.017}.

\bibitem[Kraemer {et~al.}(2018)Kraemer, Donner, Heitzig, and
  Marwan]{kraemer2018}
Kraemer, K.H.; Donner, R.V.; Heitzig, J.; Marwan, N.
\newblock Recurrence threshold selection for obtaining robust recurrence
  characteristics in different embedding dimensions.
\newblock {\em Chaos: Interdiscip. J. Nonlinear Sci.} {\bf
  2018}, {\em 28},~085720.
\newblock
  {https://doi.org/10.1063/1.5024914}.

\bibitem[March {et~al.}(2005)March, Chapman, and Dendy]{march2005}
March, T.K.; Chapman, S.C.; Dendy, R.O.
\newblock Recurrence plot statistics and the effect of embedding.
\newblock {\em Phys. D} {\bf 2005}, {\em 200},~171--184.
\newblock
  {https://doi.org/10.1016/j.physd.2004.11.002}.

\bibitem[Baptista {et~al.}(2010)Baptista, Ngamga, Pinto, Brito, and
  Kurths]{baptista2010}
Baptista, M.S.; Ngamga, E.J.; Pinto, P.R.F.; Brito, M.; Kurths, J.
\newblock {Kolmogorov-Sinai entropy from recurrence times}.
\newblock {\em Phys. Lett. A} {\bf 2010}, {\em 374},~1135--1140.
\newblock
 {https://doi.org/10.1016/j.physleta.2009.12.057}.

\bibitem[Kraemer and Marwan(2019)]{Kraemer2019}
Kraemer, K.H.; Marwan, N.
\newblock Border effect corrections for diagonal line based recurrence
  quantification analysis measures.
\newblock {\em Phys. Lett. A} {\bf 2019}, {\em 383},~125977.
\newblock
 {https://doi.org/10.1016/j.physleta.2019.125977}.

\bibitem[Marwan and Kurths(2002)]{marwan2002pla}
Marwan, N.; Kurths, J.
\newblock {Nonlinear analysis of bivariate data with cross recurrence plots}.
\newblock {\em {Phys. Lett. A}} {\bf 2002}, {\em 302},~299--307.
\newblock
  {https://doi.org/10.1016/S0375-9601(02)01170-2}.

\bibitem[Zbilut and Marwan(2008)]{Zbilut2008}
Zbilut, J.P.; Marwan, N.
\newblock The Wiener–Khinchin theorem and recurrence quantification.
\newblock {\em Phys. Lett. A} {\bf 2008}, {\em 372},~6622--6626.
\newblock
 {https://doi.org/10.1016/j.physleta.2008.09.027}.

\bibitem[Kraemer {et~al.}(2021)Kraemer, Datseris, Kurths, Kiss,
  Ocampo-Espindola, and Marwan]{Kraemer2021}
Kraemer, K.H.; Datseris, G.; Kurths, J.; Kiss, I.Z.; Ocampo-Espindola, J.L.;
  Marwan, N.
\newblock A unified and automated approach to attractor reconstruction.
\newblock {\em New J. Phys.} {\bf 2021}, {\em 23},~033017.
\newblock
  {https://doi.org/10.1088/1367-2630/abe336}.

\bibitem[Schild(1982)]{Schild1982}
Schild, D.
\newblock An Efficient Method for the Fourier Transform of a Neuronal Spike
  Train.
\newblock {\em Int. J. Neurosci.} {\bf 1982}, {\em
  17},~179--182,
\newblock
  {https://doi.org/10.3109/00207458208985921}.

\bibitem[C{\'o}rdoba(1989)]{Cordoba1989}
C{\'o}rdoba, A.
\newblock Dirac combs.
\newblock {\em Lett. Math. Phys.} {\bf 1989}, {\em 17},~191--196.
\newblock
  {https://doi.org/10.1007/BF00401584}.

\bibitem[Huang {et~al.}(1998)Huang, Shen, Long, Wu, Shih, Zheng, Yen, Tung,
  and Liu]{Norden1998}
Huang, N.E.; Shen, Z.; Long, S.R.; Wu, M.C.; Shih, H.H.; Zheng, Q.; Yen, N.C.;
  Tung, C.C.; Liu, H.H.
\newblock The empirical mode decomposition and the Hilbert spectrum for
  nonlinear and non-stationary time series analysis.
\newblock {\em Proc. R. Soc. London. Ser. Math. Phys. Eng. Sci.} {\bf 1998}, {\em
  454},~903--995.
\newblock
 {https://doi.org/10.1098/rspa.1998.0193}.

\bibitem[Biagetti {et~al.}(2017)Biagetti, Crippa, Orcioni, and
  Turchetti]{Biagetti2017}
Biagetti, G.; Crippa, P.; Orcioni, S.; Turchetti, C.
\newblock Homomorphic Deconvolution for MUAP Estimation From Surface EMG
  Signals.
\newblock {\em IEEE J. Biomed. Health Inform.} {\bf 2017},
  {\em 21},~328--338.
\newblock
  {https://doi.org/10.1109/JBHI.2016.2530943}.

\bibitem[Bracewell and Bracewell(1986)]{Bracewell1986}
Bracewell, R.N.; Bracewell, R.N.
\newblock {\em The Fourier Transform and its Applications};
  McGraw-Hill: New York, NY, USA, 1986; Volume 31999.

\bibitem[Hotelling(1933)]{Hotelling1933}
Hotelling, H.
\newblock Analysis of a complex of statistical variables into principal
  components.
\newblock {\em J. Educ. Psychol.} {\bf 1933}, {\em 24},~417.

\bibitem[Brunton and Kutz(2019)]{Brunton2019}
Brunton, S.L.; Kutz, J.N.
\newblock {\em Data-Driven Science and Engineering: Machine Learning, Dynamical
  Systems, and Control}; Cambridge University Press: Cambridge, UK, 2019.
\newblock
  {https://doi.org/10.1017/9781108380690}.

\bibitem[Tibshirani(1996)]{Tibshirani1996}
Tibshirani, R.
\newblock Regression Shrinkage and Selection Via the Lasso.
\newblock {\em J. R. Stat. Soc. Ser. B} {\bf 1996}, {\em 58},~267--288.
\newblock
 {https://doi.org/10.1111/\linebreak j.2517-6161.1996.tb02080.x}.

\bibitem[Brunton {et~al.}(2016)Brunton, Proctor, and Kutz]{Brunton2016}
Brunton, S.L.; Proctor, J.L.; Kutz, J.N.
\newblock Discovering governing equations from data by sparse identification of
  nonlinear dynamical systems.
\newblock {\em Proc. Natl. Acad. Sci. USA} {\bf 2016},
  {\em 113},~3932--3937.
\newblock
  {https://doi.org/10.1073/pnas.1517384113}.

\bibitem[Schreiber and Schmitz(1996)]{Schreiber1996}
Schreiber, T.; Schmitz, A.
\newblock Improved Surrogate Data for Nonlinearity Tests.
\newblock {\em Phys. Rev. Lett.} {\bf 1996}, {\em 77},~635--638.
\newblock
 {https://doi.org/10.1103/PhysRevLett.77.635}.

\bibitem[Schreiber and Schmitz(2000)]{Schreiber2000}
Schreiber, T.; Schmitz, A.
\newblock Surrogate time series.
\newblock {\em Phys. D: Nonlinear Phenom.} {\bf 2000}, {\em 142},~346--382.
\newblock
 {https://doi.org/10.1016/S0167-2789(00)00043-9}.

\bibitem[Kundur {et~al.}(1994)Kundur, Balu, and Lauby]{kundur1994power}
Kundur, P.; Balu, N.J.; Lauby, M.G.
\newblock {\em Power System Stability and Control}; McGraw-hill: New
  York, NY, USA, 1994; Volume~7.

\bibitem[Gorj{\~a}o {et~al.}(2020)Gorj{\~a}o, Anvari, Kantz, Beck, Witthaut,
  Timme, and Sch{\"a}fer]{gorjao2020data}
Gorj{\~a}o, L.R.; Anvari, M.; Kantz, H.; Beck, C.; Witthaut, D.; Timme, M.;
  Sch{\"a}fer, B.
\newblock Data-driven model of the power-grid frequency dynamics.
\newblock {\em IEEE Access} {\bf 2020}, {\em 8},~43082--43097.

\bibitem[Anvari {et~al.}(2020)Anvari, Gorj{\~a}o, Timme, Witthaut,
  Sch{\"a}fer, and Kantz]{anvari2020stochastic}
Anvari, M.; Gorj{\~a}o, L.R.; Timme, M.; Witthaut, D.; Sch{\"a}fer, B.; Kantz,
  H.
\newblock Stochastic properties of the frequency dynamics in real and synthetic
  power grids.
\newblock {\em Phys. Rev. Res.} {\bf 2020}, {\em 2},~013339.

\bibitem[Meyer {et~al.}(2020)Meyer, Anvari, and Kantz]{meyer2020identifying}
Meyer, P.G.; Anvari, M.; Kantz, H.
\newblock Identifying characteristic time scales in power grid frequency
  fluctuations with DFA.
\newblock {\em Chaos: Interdiscip. J. Nonlinear Sci.} {\bf
  2020}, {\em 30},~013130.

\bibitem[Wei{\ss}bach and Welfonder(2009)]{weissbach2009high}
Wei{\ss}bach, T.; Welfonder, E.
\newblock High frequency deviations within the European power system: Origins
  and proposals for improvement.
\newblock In Proceedings of the 2009 IEEE/PES Power Systems Conference and
  Exposition, Seattle, WA, USA, 15--18 March 2009; pp.~1--6.

\bibitem[{Laskar, J.} {et~al.}(2011){Laskar, J.}, {Fienga, A.}, {Gastineau,
  M.}, and {Manche, H.}]{Laskar2011}
{Laskar, J.}; {Fienga, A}.; {Gastineau, M}.; {Manche, H}.
\newblock La2010: A new orbital solution for the long-term motion of the Earth.
\newblock {\em Astron. Astrophys.} {\bf 2011}, {\em 532},~A89.
\newblock
  {https://doi.org/10.1051/0004-6361/201116836}.

\bibitem[{Laskar, J.} {et~al.}(2004){Laskar, J.}, {Robutel, P.}, {Joutel,
  F.}, {Gastineau, M.}, {Correia, A. C. M.}, and {Levrard, B.}]{Laskar2004}
{Laskar, J.}; {Robutel, P}.; {Joutel, F}.; {Gastineau, M.}; {Correia, A.C.M.}; {Levrard, B}.
\newblock A long-term numerical solution for the insolation quantities
  of~the~Earth.
\newblock {\em Astron. Astrophys.} {\bf 2004}, {\em 428},~261--285.
\newblock
  {https://doi.org/10.1051/0004-6361:20041335}.

\bibitem[Westerhold {et~al.}(2020)Westerhold, Marwan, Drury, Liebrand,
  Agnini, Anagnostou, Barnet, Bohaty, De~Vleeschouwer, Florindo, Frederichs,
  Hodell, Holbourn, Kroon, Lauretano, Littler, Lourens, Lyle, P{\"a}like,
  R{\"o}hl, Tian, Wilkens, Wilson, and Zachos]{Westerhold2020}
Westerhold, T.; Marwan, N.; Drury, A.J.; Liebrand, D.; Agnini, C.; Anagnostou,
  E.; Barnet, J.S.K.; Bohaty, S.M.; De~Vleeschouwer, D.; Florindo, F.;  et~al.
\newblock An astronomically dated record of Earth{\textquoteright}s climate and
  its predictability over the last 66 million years.
\newblock {\em Science} {\bf 2020}, {\em 369},~1383--1387.
\newblock
  {https://doi.org/10.1126/science.aba6853}.

\bibitem[Kraemer {et~al.}(2022)Kraemer, Gelbrecht, Pavithran, Sujith, and
  Marwan]{Kraemer2022}
Kraemer, K.H.; Gelbrecht, M.; Pavithran, I.; Sujith, R.I.; Marwan, N.
\newblock Optimal state space reconstruction via Monte Carlo decision tree
  search.
\newblock {\em Nonlinear Dyn.} {\bf 2022}, {\em 108},~1525--1545.
\newblock
  {https://doi.org/10.1007/s11071-022-07280-2}.

\bibitem[Hegger and Kantz(1999)]{hegger1999}
Hegger, R.; Kantz, H.
\newblock Improved false nearest neighbor method to detect determinism in time
  series data.
\newblock {\em Phys. Rev. E} {\bf 1999}, {\em 60},~4970--4973.
\newblock
  {https://doi.org/10.1103/PhysRevE.60.4970}.

\bibitem[Pecora {et~al.}(2007)Pecora, Moniz, Nichols, and
  Carroll]{pecora2007}
Pecora, L.M.; Moniz, L.; Nichols, J.; Carroll, T.L.
\newblock A unified approach to attractor reconstruction.
\newblock {\em Chaos Interdiscip. J. Nonlinear Sci.} {\bf
  2007}, {\em 17},~013110.
\newblock
  {https://doi.org/10.1063/1.2430294}.

\bibitem[Datseris(2018)]{datseris2018}
Datseris, G.
\newblock DynamicalSystems.jl: A Julia software library for chaos and nonlinear
  dynamics.
\newblock {\em J. Open Source Softw.} {\bf 2018}, {\em 3},~598.
\newblock
  {https://doi.org/10.21105/joss.00598}.

\bibitem[Rackauckas and Nie(2017)]{rackauckas2017}
Rackauckas, C.; Nie, Q.
\newblock Differentialequations.jl--a performant and feature-rich ecosystem for
  solving differential equations in julia.
\newblock {\em J. Open Res. Softw.} {\bf 2017}, {\em 5}, 15.

\bibitem[Zhang {et~al.}(2022)Zhang, Widmann, and Barreira]{Zhang2022}
\textls[-15]{Zhang, S.; Widmann, D.; Barreira, D.S}.
\newblock {JuliaOptimalTransport/OptimalTransport.jl: v0.3.19}%MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number).
. {2022}.
\newblock
   \hl{Available online:} %MDPI: we replace the correct web link, please confirm
 \url{https://zenodo.org/record/5920148\#.Y3SbbORByUk} \hl{(accessed on)} %MDPI: Please add accessed date.

\bibitem[Lorenz(1963)]{lorenz1963}
Lorenz, E.N.
\newblock Deterministic Nonperiodic Flow.
\newblock {\em J. Atmos. Sci.} {\bf 1963}, {\em
  20},~130--141.
\newblock
  {https://doi.org/10.1175/1520-0469(1963)020<0130:DNF>2.0.CO;2}.

\bibitem[Rössler(1976)]{roessler1976}
Rössler, O.
\newblock An equation for continuous chaos.
\newblock {\em Phys. Lett. A} {\bf 1976}, {\em 57},~397 -- 398.
\newblock
  {https://doi.org/10.1016/0375-9601(76)90101-8}.

\bibitem[GB()]{GB}
National Grid, Frequency Data (2014–2018).
\newblock  \hl{Available online}%MDPI: please add the website link.
:  (accessed on 25 July 2022).

\bibitem[Haehne {et~al.}(2018)Haehne, Schottler, Waechter, Peinke, and
  Kamps]{haehne2018footprint}
Haehne, H.; Schottler, J.; Waechter, M.; Peinke, J.; Kamps, O.
\newblock The footprint of atmospheric turbulence in power grid frequency
  measurements.
\newblock {\em EPL (Europhys. Lett.)} {\bf 2018}, {\em 121},~30001.

\bibitem[Fraser and Swinney(1986)]{fraser1986}
Fraser, A.M.; Swinney, H.L.
\newblock Independent coordinates for strange attractors from mutual
  information.
\newblock {\em Phys. Rev. A} {\bf 1986}, {\em 33},~1134--1140.
\newblock
  {https://doi.org/10.1103/PhysRevA.33.1134}.

\end{thebibliography}

%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
start commenting the requests

@@
 % Authors, for the paper (add full first names)
-\Author{\hl{K. Hauke Kraemer} %MDPI: Please carefully check the accuracy of names and affiliations.
+\Author{\hl{K. Hauke Kraemer} %MDPI: Please carefully check the accuracy of names and affiliations. %Authors: we agree
  $^{1,}$*\orcidA{}, Frank Hellmann $^{1}$, Mehrnaz Anvari $^{1}$\orcidB{}, \hl{J\"urgen Kurths} %MDPI: The name of this author is different from the submitting system.
 Please confirm which one is correct.
+%Authors: we agree
  $^{1,2,\highlighting{3} %MDPI: 
@@
 \address{%
-$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system.
-Please confirm.
+$^{1}$ \quad Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system.
+Please confirm.%Authors: we agree
 \\
 $^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
-\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.
+\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.%Authors: we agree
  \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
@@
 \end{equation}
-where $\mathbf{R}$ \hl{is} %MDPI: There is no bold in other places in the text, please confirm whether the bold here needs to be retained
+where $\mathbf{R}$ \hl{is} %MDPI: There is no bold in other places in the text, please confirm whether the bold here needs to be retained %Authors: we confirm that this is boldface, because it this variable represents a matrix
  the recurrence matrix, $\vec{x}_i$ is the state vector at time 

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
changed figures

@@
 $^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
-\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes.%Authors: we agree
+\hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes. %Authors: we agree
  \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
@@
  \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_spectrum_example}
- \caption{\hl{Schematic} %MDPI: Please change the hyphen (-) into minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1".
+ \caption{\hl{Schematic} %MDPI: Please change the hyphen (-) into minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1". %Authors: we changed to minus sign
  illustration of a $\tau$-recurrence-rate-based spectrum. (\textbf{A}) $x$-component time series of the Lorenz63-System (Equation~\eqref{eq_model_Lorenz63}) and 
@@
 More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
+%Authors: we confirm that we hold the copyright of this figure
  \cite{Kraemer2021}. 
@@
 More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
+%Authors: we confirm that we hold the copyright of this figure
  \cite{Zbilut2008}. (\textbf{D},\textbf{E}) show the results of a part of the time series, 
@@
 to every frequency $1/T_\text{is}$; therefore, $\text{DC}_{\text{is}}(t)$ coincides with its own Fourier transform up to a factor $1/T_\text{is}$ \cite{Norden1998}.
-({\hl{This can also } %MDPI: footnote is not allowed in this journal, we moved here, please confirm
+({\hl{This can also } %MDPI: footnote is not allowed in this journal, we moved here, please confirm  %Authors: we agree/ confirm
 be observed for neuron spike trains, e.g., \cite{Orcioni2020,Biagetti2017}.})
@@
 e.g., "-1" should be "$-$1".
+%Authors: We changed the hyphen to minus sign.
+We have modified the panel numbering to make it consistent with the other figures.
  of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
@@
 
-\hl{In this example} %MDPI: we add indent here, please confirm
+\hl{In this example} %MDPI: we add indent here, please confirm %Authors: we agree/ confirm
 , the null hypothesis for constructing the surrogate data is that the data stem from a process which yields the same auto-correlation, and
@@
 More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
+%Authors: we confirm that we hold the copyright of this figure
  \cite{Schreiber1996,Schreiber2000}. To obtain the inter-spike spectra, we used 
@@
 More details on "Copyright and Licensing" are available via the following link: https://www.mdpi.com/ethics#10.
+%Authors: we confirm that we hold the copyright of this figure
  \cite{haehne2018footprint} and (\textbf{C}) Great Britain \hl{(GB)} %MDPI: 
@@
  \caption{\hl{Same as in} %MDPI: please add explanation for A--I
- Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter-spike spectra 
+ Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. 
+ (\textbf{A}) Trajectory of the system in a period-2 (parameter $a=0.36$), (\textbf{B})~in a period-3 (parameter $a=0.41$) and 
+ (\textbf{C}) in a chaotic regime (parameter $a=0.428$). 
+\mbox{ (\textbf{D}--\textbf{F})}~The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
+ recurrence rate for (\textbf{D},\textbf{E}) and 5\% for (\textbf{F}). 
+  (\textbf{G}--\textbf{I}) $\tau$-RRs of the shown RPs, 
+  (\textbf{J}--\textbf{L}) the corresponding inter-spike spectra, and
+  (\textbf{M},\textbf{N},\textbf{P}) the Fourier power spectra. 
+ The appearance of the inter-spike spectra 
  in (\textbf{J}--\textbf{L}), and the Fourier spectra in (\textbf{M},\textbf{N},\textbf{P}) are unaffected by the additive noise.}
@@
 \newblock {JuliaOptimalTransport/OptimalTransport.jl: v0.3.19}%MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number).
+%Authors: we confirm that we hold the copyright of this figure
 . {2022}.

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
update references and textfile with all the changes

--- 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
@@
 \Author{\hl{K. Hauke Kraemer} %MDPI: Please carefully check the accuracy of names and affiliations. 
+%Authors: we agree
  $^{1,}$*\orcidA{}, Frank Hellmann $^{1}$, Mehrnaz Anvari $^{1}$\orcidB{}, \hl{J\"urgen Kurths} %MDPI: The name of this author is different from the submitting system.
 Please confirm which one is correct.
+ %Authors: we agree
  $^{1,2,\highlighting{3} %MDPI: 
@@
 \address{%
-$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system.
+$^{1}$ \quad Potsdam Institute for Climate Impact Research (PIK), Member of the Leibniz Association, 14473 Potsdam, Germany; \hl{hellmann@pik-potsdam.de (F.H.); anvari@pik-potsdam.de (M.A.); kurths@pik-potsdam.de (J.K.)} %MDPI: We added the email addresses here according to the submitting system.
 Please confirm.
+%Authors: we agree
 \\
@@
 \hl{$^{3}$} %MDPI: The affiliation numbers should appear in numerical order. Please check the suggested changes. 
+%Authors: we agree
  \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany\\
@@
 where $\mathbf{R}$ \hl{is} %MDPI: There is no bold in other places in the text, please confirm whether the bold here needs to be retained 
+%Authors: we confirm that this is boldface, because it this variable represents a matrix
  the recurrence matrix, $\vec{x}_i$ is the state vector at time 
@@
  \caption{\hl{Schematic} %MDPI: Please change the hyphen (-) into minus sign ($-$, "U+2212"). e.g., "-1" should be "$-$1". 
+ %Authors: we changed to minus sign
  illustration of a $\tau$-recurrence-rate-based spectrum. (\textbf{A}) $x$-component time series of the Lorenz63-System (Equation~\eqref{eq_model_Lorenz63}) and 
@@
 ({\hl{This can also } %MDPI: footnote is not allowed in this journal, we moved here, please confirm
+%Authors: we agree/ confirm
 be observed for neuron spike trains, e.g., \cite{Orcioni2020,Biagetti2017}.})
@@
 e.g., "-1" should be "$-$1".
+%Authors: We changed the hyphen to minus sign. We have modified the panel numbering to make it consistent with the other figures.
  of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
@@
 \hl{In this example} %MDPI: we add indent here, please confirm 
+%Authors: we agree/ confirm
 , the null hypothesis for constructing the surrogate data is that the data stem from a process which yields the same auto-correlation, and
@@
 
-\subsection{R \"ossler System}\label{sec_models_roessler}
+\subsection{R\"ossler System}\label{sec_models_roessler}
 
@@
  \caption{\hl{Same as in} %MDPI: please add explanation for A--I 
- Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. The appearance of the inter-spike spectra 
+%Authors: We have added explanations for A--I
+ Figure~\ref{fig_tau_rr_example_roessler}, but here with 5\% additive Gaussian white noise on each component $x$, $y$ and $z$. 
+ (\textbf{A}) Trajectory of the system in a period-2 (parameter $a=0.36$), (\textbf{B})~in a period-3 (parameter $a=0.41$) and 
+ (\textbf{C}) in a chaotic regime (parameter $a=0.428$). 
+\mbox{ (\textbf{D}--\textbf{F})}~The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
+ recurrence rate for (\textbf{D},\textbf{E}) and 5\% for (\textbf{F}). 
+  (\textbf{G}--\textbf{I}) $\tau$-RRs of the shown RPs, 
+  (\textbf{J}--\textbf{L}) the corresponding inter-spike spectra, and
+  (\textbf{M},\textbf{N},\textbf{P}) the Fourier power spectra. 
+ The appearance of the inter-spike spectra 
  in (\textbf{J}--\textbf{L}), and the Fourier spectra in (\textbf{M},\textbf{N},\textbf{P}) are unaffected by the additive noise.}
@@
 \textls[-15]{Zhang, S.; Widmann, D.; Barreira, D.S}.
-\newblock {JuliaOptimalTransport/OptimalTransport.jl: v0.3.19}%MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number).
+\newblock {JuliaOptimalTransport/OptimalTransport.jl: v0.3.19, Zenodo}%MDPI: Please provide more information about the type of the article, such as book (please provide the name of the publisher and location of it), online resource (please provide the URL of the website and the date it was accessed (day, month, year)), or journal article (please provide the name of the journal, the year and volume it published, and the page number).
+%Authors: we confirm that we hold the copyright of this figure %Authors: this is a Zenodo repository, no journal article, but we have added "Zenodo"
 . {2022}.
@@
    \hl{Available online:} %MDPI: we replace the correct web link, please confirm 
- \url{https://zenodo.org/record/5920148\#.Y3SbbORByUk} \hl{(accessed on)} %MDPI: Please add accessed date.
+   %Authors: we confirm
+ \url{https://zenodo.org/record/5920148\#.Y3SbbORByUk} \hl{(accessed on 16 November 2022)} %MDPI: Please add accessed date. 
+ %Authors: added
 
@@
 National Grid, Frequency Data (2014–2018).
-\newblock  \hl{Available online}%MDPI: please add the website link.
-:  (accessed on 25 July 2022).
+\newblock  \hl{Available online}%MDPI: please add the website link. %Authors: we added the link
+: 
+\url{https://www.nationalgrideso.com/industry-information/balancing-services/frequency-response-services/historic-frequency-data} (accessed on 25 July 2022).
 

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
links to Julia and Matlab published repos

@@
 \dataavailability{The study that we present here is available as a fully reproducible code base
-``repository will be published and cited here, when accepted'' and the method
-will be available in the Julia language, ``package will be published and cited here, 
-when accepted'' and as a MATLAB\textsuperscript{\textregistered} toolbox 
-``Toolbox will be published and cited here, when accepted''.}
+**Repository will be published and cited here, when accepted** and the method
+will be available in the Julia language (https://zenodo.org/record/7328513#.Y3Vb4VLMJqw) and as a MATLAB\textsuperscript{\textregistered} toolbox 
+(https://zenodo.org/record/7328499#.Y3Vb91LMJqw).}
 

### 2022-11-16 Manuscript/inter_spike_manuscript_mdpi.tex
links to Julia and Matlab published repos

@@
 **Repository will be published and cited here, when accepted** and the method
-will be available in the Julia language **Package will be published and cited here, 
-when accepted** and as a MATLAB\textsuperscript{\textregistered} toolbox 
-**Toolbox will be published and cited here, when accepted**.}
+will be available in the Julia language (https://zenodo.org/record/7328513#.Y3Vb4VLMJqw) and as a MATLAB\textsuperscript{\textregistered} toolbox 
+(https://zenodo.org/record/7328499#.Y3Vb91LMJqw).}
 

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
corrected links

@@
 **Repository will be published and cited here, when accepted** and the method
-will be available in the Julia language (https://zenodo.org/record/7328513#.Y3Vb4VLMJqw) and as a MATLAB\textsuperscript{\textregistered} toolbox 
-(https://zenodo.org/record/7328499#.Y3Vb91LMJqw).}
+will be available in the Julia language (https:doi.org/10.5281/zenodo.7328513) and as a MATLAB\textsuperscript{\textregistered} toolbox 
+(https:doi.org/10.5281/zenodo.7328499).}
 

### 2022-11-16 Manuscript/entropy-1919488  proof/entropy-1919488.tex
Final link to this repo.

@@
 \dataavailability{The study that we present here is available as a fully reproducible code base
-**Repository will be published and cited here, when accepted** and the method
+(https:doi.org/10.5281/zenodo.7328580) and the method
 will be available in the Julia language (https:doi.org/10.5281/zenodo.7328513) and as a MATLAB\textsuperscript{\textregistered} toolbox 
